### 2017-11-18 Traditional_Analysis/Analysis_exp7_2.rmd
first commit

---
title: "Analysis_exp7"
author: "hcp"
date: "2016-10-28"
output: word_document
---
<style type="text/css">

body{ /* Normal  */
   font-family: Times     
   font-size: 12px;
}
td {  /* Table  */
   font-size: 8px;
}
h1 { /* Header 1 */
 font-size: 28px;
}
h2 { /* Header 2 */
 font-size: 22px;
}
h3 { /* Header 3 */
 font-size: 18px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 10px;
}
pre { /* Code block */
  font-size: 10px
}
</style>

This script is aimed at making the analysis of the experiment 7 reproducible. We analyzezd the data using the traditional ways (d prime/Accuracy and mean of RT)

```{r Initializing, include=FALSE}
Sys.setlocale("LC_ALL", "English")  # set local encoding to English
Sys.setenv(LANG = "en") # set the feedback language to English
options(scipen = 999)   # force R to output in decimal instead of scientifc notion
options(digits=5)       # limit the number of reporting
rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions

pkgTest <- function(x)
 {
   if (!require(x,character.only = TRUE))
  {
    install.packages(x,dep = TRUE)
   if(!require(x,character.only = TRUE)) stop("Package not found")
  }
}

pkgNeeded <- (c("ez","plyr","ggplot2", "reshape2", "MBESS", "bootES","BayesFactor","psych","corrplot"))

lapply(pkgNeeded,pkgTest)
rm(pkgNeeded)
# using APA style plot
# Save some time and stor APA format-related code in an object so you can easily
# use it in multiple plots
windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
apatheme=theme_bw()+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text=element_text(family='Times'),
              legend.title=element_blank(),
              legend.position='top',
              axis.line.x = element_line(color='black'),
              axis.line.y = element_line(color='black'))

# define the d prime function
dprime <- function(hit,fa) {
        qnorm(hit) - qnorm(fa)
}

## code for calculate the summary with sE, adopted from cook book for R
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
        library(plyr)

        # New version of length which can handle NA's : if na.rm == T, don't count the
        length2 <- function(x, na.rm=FALSE){
                if(na.rm) sum(!is.na(x))
                else      length(x)
        }

        # this does the summary. For each group's data frame, return a vector with
        # N, mean, and sd
        datac <- ddply(data,groupvars, .drop=.drop,
                       .fun = function(xx,col){
                        c(N    = length2(xx[[col]],na.rm=na.rm),
                          mean = mean(xx[[col]],na.rm=na.rm),
                          sd   = sd  (xx[[col]],na.rm=na.rm)
                           )
                       },
                       measurevar
                       )
        # Rename the "mean" column

        datac <- rename(datac,c("mean" = measurevar))

        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean

        # Confidence interval mltiplier for standard error
        # calculate t-statistic for confidence interval:
        # e.g., if conf.interval is .95, use .975 (above/below), and use df.L1 = N-1
        ciMult <- qt(conf.interval/2 + .5, datac$N-1)
        datac$ci <- datac$se * ciMult

        return (datac)
}

## code for calculate the summary with sE for within subject data, adopted from cook book for R
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

        # Ensure that the betweenvars and withinvars are factors
        factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
                             FUN=is.factor, FUN.VALUE=logical(1))

        if (!all(factorvars)) {
                nonfactorvars <- names(factorvars)[!factorvars]
                message("Automatically converting the following non-factors to factors: ",
                        paste(nonfactorvars, collapse = ", "))
                data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
        }

        # Get the means from the un-normed data
        datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                           na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

        # Drop all the unused columns (these will be calculated with normed data)
        datac$sd <- NULL
        datac$se <- NULL
        datac$ci <- NULL

        # Norm each subject's data
        ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

        # This is the name of the new column
        measurevar_n <- paste(measurevar, "_norm", sep="")

        # Collapse the normed data - now we can treat between and within vars the same
        ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                            na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

        # Apply correction from Morey (2008) to the standard error and confidence interval
        #  Get the product of the number of conditions of within-S variables
        nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                                        FUN.VALUE=numeric(1)))
        correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

        # Apply the correction factor
        ndatac$sd <- ndatac$sd * correctionFactor
        ndatac$se <- ndatac$se * correctionFactor
        ndatac$ci <- ndatac$ci * correctionFactor

        # Combine the un-normed means with the normed results
        merge(datac, ndatac)
}

### code for normalizing the SE
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
        library(plyr)

        # Measure var on left, idvar + between vars on right of formula.
        data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
                               .fun = function(xx, col, na.rm) {
                                       c(subjMean = mean(xx[,col], na.rm=na.rm))
                               },
                               measurevar,
                               na.rm
        )

        # Put the subject means with original data
        data <- merge(data, data.subjMean)

        # Get the normalized data in a new column
        measureNormedVar <- paste(measurevar, "_norm", sep="")
        data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                mean(data[,measurevar], na.rm=na.rm)

        # Remove this subject mean column
        data$subjMean <- NULL

        return(data)
}

#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
        library(grid)

        # Make a list from the ... arguments and plotlist
        plots <- c(list(...), plotlist)

        numPlots = length(plots)

        # If layout is NULL, then use 'cols' to determine layout
        if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
        }

        if (numPlots==1) {
                print(plots[[1]])

        } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                        # Get the i,j matrix positions of the regions that contain this subplot
                        matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

                        print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                        layout.pos.col = matchidx$col))
                }
        }
}

```

```{r loadingData_e7_L,echo=FALSE,results='hide'}
df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
# render the numeric column
cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
# Tcols.num <- c("SubjectID","Age","Block","Bin","Trial","RT","Accuracy")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)

colnames(df.L)[colnames(df.L)=="Accuracy"] <- "ACC"
colnames(df.T)[colnames(df.T)=="Accuracy"] <- "ACC"
colnames(df.L)[colnames(df.L)=="SubjectID"] <- "Subject"
colnames(df.T)[colnames(df.T)=="SubjectID"] <- "Subject"

df.L$Subject <- factor(df.L$Subject)
df.T$Subject <- factor(df.T$Subject)

df.L$Morality[df.L$Morality == 'moral'] <- 'Good'
df.L$Morality[df.L$Morality == 'immoral'] <- 'Bad'
df.L$Identity[df.L$Identity == 'self'] <- 'Self'
df.L$Identity[df.L$Identity == 'other'] <- 'Other'

df.L$Morality <- factor(df.L$Morality, levels=c("Good","Bad")) # make the variables in a specified order
df.L$Identity <- factor(df.L$Identity, levels=c("Self","Other")) # make the variables in a specified order
df.L$Match <- factor(df.L$Match, levels=c("match","nonmatch")) # make the variables in a specified order

df.T$Morality[df.T$Morality == 'moral'] <- 'Good'
df.T$Morality[df.T$Morality == 'immoral'] <- 'Bad'
df.T$Identity[df.T$Identity == 'self'] <- 'Self'
df.T$Identity[df.T$Identity == 'other'] <- 'Other'
df.T$Task[df.T$Task == 'Self'] <- 'ID'
df.T$Task[df.T$Task == 'self'] <- 'Id_task'
df.T$Task[df.T$Task == 'moral'] <- 'Valence_task'
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad")) # make the variables in a specified order
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other")) # make the variables in a specified order
```

```{r clean the data_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT*1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

# no response equal to wrong
df.L1$ACC[df.L1$ACC == -1] <- 0

# excluded data from subjects whose trials number are not normal
procFailureSub <- c("7","8","2027","7035")
df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]
df.T1 <- df.T1[df.T1$Task != 'importance',]  # exclude the results from importance task

# delete the practicing trials (first 48 trials)
subNo <- unique(df.L1$Subject)
for (subj in subNo) {
        if (exists('df.L1.fm')){
                df.tmp <- df.L1[df.L1$Subject == subj,]
                df.tmp <- df.tmp[49:nrow(df.tmp),]
                df.L1.fm <- rbind(df.L1.fm,df.tmp)
        } else {
                df.L1.fm <- df.L1[df.L1$Subject == subj,]
                df.L1.fm <- df.L1.fm[49:nrow(df.L1.fm),]
        }
}

rm(subNo)

# calculate the overall accuracy for matching task
df.L1.acc.g <-  ddply(df.L1.fm,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

# calculate the overall accuracy for categorziation task
df.T1.acc.g <-  ddply(df.T1,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

excld.sub <- df.L1.acc.g$Subject[df.L1.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
excld.sub.T <- df.T1.acc.g$Subject[df.T1.acc.g$ACC < 0.5]    # less than 50% accuracy in categorization task
df.L1.valid <- df.L1.fm[!(df.L1.fm$Subject %in% excld.sub),] # exclude the invalid subjects
df.T1.valid <- df.T1[!(df.T1$Subject %in% excld.sub),]
df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]

length(unique(df.L1.valid$Subject)) + length(excld.sub) == length(unique(df.L1$Subject))
# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200,]
df.L1.V <- df.L1.valid[!(df.L1.valid$RT <= 200),] 
excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200,]
df.T1.V <- df.T1.valid[!(df.T1.valid$RT <= 200),] 
nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok

## Basic information of the data ####
df.L1.T.basic <- df.L1[!duplicated(df.L1$Subject), 1:4]
numT.subj <- nrow(df.L1.T.basic)
numT.female <- sum(df.L1.T.basic$Gender == 'female');
numT.male <- sum(df.L1.T.basic$Gender == 'male');
ageT.mean <- round(mean(df.L1.T.basic$Age),2);
ageT.std <- round(sd(df.L1.T.basic$Age),2);
num.excld.sub <- length(unique(excld.sub))
num.excld.sub.T <- length(unique(excld.sub.T))

# valide data for matching task
df.L1.V.basic <- df.L1.V[!duplicated(df.L1.V$Subject), 1:4]
numV.female <- sum(df.L1.V.basic$Gender == 'female');
numV.male <- sum(df.L1.V.basic$Gender == 'male');
ageV.mean <- round(mean(df.L1.V.basic$Age),2);
ageV.std <- round(sd(df.L1.V.basic$Age),2);
ratio.excld.trials.L <- nrow(excld.trials.L)/nrow(df.L1.valid)
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)

# valid data for categorization task
df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 1:4]
numV.female.T <- sum(df.T1.V.basic$Gender == 'female');
numV.male.T <- sum(df.T1.V.basic$Gender == 'male');
ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
```
## Participants
`r numT.subj+length(procFailureSub)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7. All partcipants were right handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee. Data of `r length(procFailureSub)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task. `r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.

##Results 
For the learning phase, we excluded the first 24 trials, which is suppose to be the duration participants were practicing. Also, trials that responsed less than 200 ms or no-response was excluded.For the learning phase, `r round(ratio.excld.trials.L,4)` of the total trials was excluded, for the testing phase, `r round(ratio.excld.trials.T,4)` of the total trials was excluded.

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
# calculate the d prime for each condition
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

# calculate the number of each for each condition
df.L1.V.SDT <-  ddply(df.L1.V,.(Subject,Morality, Identity,sdt), summarise, N = length(sdt))
df.L1.V.SDT <- df.L1.V.SDT[complete.cases(df.L1.V.SDT$sdt),] # exclude NA, which represents no-response trials

# long format to wide
df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0
df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)] <- 0
df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)

# standardized way to deal with the extreme values
for (i in 1:nrow(df.L1.V.SDT_w)){
        if (df.L1.V.SDT_w$hitR[i] == 1){
                df.L1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.L1.V.SDT_w$hit[i] + df.L1.V.SDT_w$miss[i]))
        }
}

for (i in 1:nrow(df.L1.V.SDT_w)){
        if (df.L1.V.SDT_w$faR[i] == 0){
                df.L1.V.SDT_w$faR[i] <- 1/(2*(df.L1.V.SDT_w$FA[i] + df.L1.V.SDT_w$CR[i]))
        }
}

# calculate the d prime for each condition
df.L1.V.SDT_w$dprime <- mapply(dprime,df.L1.V.SDT_w$hitR,df.L1.V.SDT_w$faR)

# transfor from long format to wide format
df.L1.V.SDT_ww <- dcast(df.L1.V.SDT_w, Subject ~ Identity + Morality ,value.var = "dprime")

# anova for d prime with 2*2 design
e7_L.d_anova <- ezANOVA(df.L1.V.SDT_w,dv = dprime, wid = Subject, within=.(Morality,Identity), type=3)

# summary(aov(dprime ~ Morality*Identity + Error(Subject/(Morality*Identity)), data=df.L1.V.SDT_w))
df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)
e7_L.dprime_anova_bf = anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")

# Good self vs Bad self
e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)
df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad
e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
e7_L.d.df.L1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[1]],4) 
e7_L.d.CI.L.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][2],4)

# Good other vs. Bad other
e7_L.d.t.good_bad_oth <- t.test(df.L1.V.SDT_ww$Other_Good,df.L1.V.SDT_ww$Other_Bad,paired = TRUE)
df.L1.V.SDT_ww$good_bad_oth <- df.L1.V.SDT_ww$Other_Good - df.L1.V.SDT_ww$Other_Bad
e7_L.d.t.good_bad_oth.CI <- bootES(df.L1.V.SDT_ww$good_bad_oth,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.good_bad_oth  <- round(as.numeric(e7_L.d.t.good_bad_oth[[1]]),3)
e7_L.d.df.L1.good_bad_oth  <- as.numeric(e7_L.d.t.good_bad_oth[[2]])
e7_L.d.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_oth[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[1]],4) 
e7_L.d.CI.L.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][2],4)

# Good self vs Good other
e7_L.d.t.slf_oth_good <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Other_Good,paired = TRUE)
df.L1.V.SDT_ww$slf_oth_good <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Other_Good
e7_L.d.t.slf_oth_good.CI <- bootES(df.L1.V.SDT_ww$slf_oth_good,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.slf_oth_good  <- round(as.numeric(e7_L.d.t.slf_oth_good[[1]]),3)
e7_L.d.df.L1.slf_oth_good  <- as.numeric(e7_L.d.t.slf_oth_good[[2]])
e7_L.d.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_good[[3]]),"bonferroni",4)
e7_L.d.cohens.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[1]],4) 
e7_L.d.CI.L.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][1],4)
e7_L.d.CI.H.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][2],4)

# Bad self vs. Bad other
e7_L.d.t.slf_oth_bad <- t.test(df.L1.V.SDT_ww$Self_Bad,df.L1.V.SDT_ww$Other_Bad,paired = TRUE)
df.L1.V.SDT_ww$slf_oth_bad <- df.L1.V.SDT_ww$Self_Bad - df.L1.V.SDT_ww$Other_Bad
e7_L.d.t.slf_oth_bad.CI <- bootES(df.L1.V.SDT_ww$slf_oth_bad,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.d.t.slf_oth_bad[[1]]),3)
e7_L.d.df.L1.slf_oth_bad <- as.numeric(e7_L.d.t.slf_oth_bad[[2]])
e7_L.d.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_bad[[3]]),"bonferroni",4)
e7_L.d.cohens.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[1]],4) 
e7_L.d.CI.L.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][1],4)
e7_L.d.CI.H.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][2],4)

#####save the dprime and ACC data for late used####
colnames(df.L1.V.SDT_ww) <- paste("L_d", colnames(df.L1.V.SDT_ww), sep = "_")
write.csv(df.L1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
df.L1.V.acc <-  ddply(df.L1.V,.(Subject,Match,Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))
df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
df.L1.V.acc_w$good_bad_slf <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Self_Bad
df.L1.V.acc_w$good_oth <- df.L1.V.acc_w$match_Other_Good - df.L1.V.acc_w$match_Other_Bad
df.L1.V.acc_w$slf_oth_good <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Other_Good
df.L1.V.acc_w$slf_oth_bad <- df.L1.V.acc_w$match_Self_Bad - df.L1.V.acc_w$match_Other_Bad

colnames(df.L1.V.acc_w) <- paste("L_acc", colnames(df.L1.V.acc_w), sep = "_")
colnames(df.L1.V.acc_w)[colnames(df.L1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
write.csv(df.L1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
#####

df.L1.V.SDT.sum <- summarySE(df.L1.V.SDT_w,measurevar = 'dprime',groupvars = c('Morality','Identity'))
e7_L.d.mean.GoodSelf <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.sd.GoodSelf <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.mean.BadSelf <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Self'],3)
e7_L.d.sd.BadSelf <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Self'],3)

e7_L.d.mean.GoodOther <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.sd.GoodOther <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.mean.BadOther <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Other'],3)
e7_L.d.sd.BadOther <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Other'],3)

e7_L.p_dprime1 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

e7_L.p_dprime2 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme + 
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
# tiff(filename = "e7_L.p_dprime2.tiff", width = 8, height = 8, units = 'in', res = 300)
# e7_L.p_dprime2
# dev.off()

```
ANOVA for *d'* with moral character and self-relatedness as within-subjects factors.

The main effect of `r e7_L.d_anova[[1]][1,1]`, *F*(`r e7_L.d_anova[[1]][1,2]`, `r e7_L.d_anova[[1]][1,3]`) = `r round(e7_L.d_anova[[1]][1,4],3)`, *p* = `r round(e7_L.d_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][1,7],4)`, BF10 = r e7_L.dprime_anova_bf[1].

The main effect of `r e7_L.d_anova[[1]][2,1]`: *F*(`r e7_L.d_anova[[1]][2,2]`, `r e7_L.d_anova[[1]][2,3]`) = `r round(e7_L.d_anova[[1]][2,4],3)`, *p* = `r round(e7_L.d_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][2,7],4)`,BF10 = r e7_L.dprime_anova_bf[2]

The interaction between `r e7_L.d_anova[[1]][3,1]`: *F*(`r e7_L.d_anova[[1]][3,2]`, `r e7_L.d_anova[[1]][3,3]`) = `r round(e7_L.d_anova[[1]][3,4],3)`, *p* = `r round(e7_L.d_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][3,7],4)`, BF21 = r e7_L.dprime_anova_bf[4]/e7_L.dprime_anova_bf[3]

Then we conducted post-hoc comparision:

Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.L1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* = 
`r e7_L.d.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_slf`, 95% CI [`r e7_L.d.CI.L.good_bad_slf` `r e7_L.d.CI.H.good_bad_slf`]

Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* = 
`r e7_L.d.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_oth`, 95% CI [`r e7_L.d.CI.L.good_bad_oth` `r e7_L.d.CI.H.good_bad_oth`]

Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs. Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.L1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]

Bad self (`r e7_L.d.mean.BadSelf` $\pm$ `r e7_L.d.sd.BadSelf`) vs. Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]

```{r plot1 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

The above figure shows the d prime for each condition (way 1)

```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

The above figure shows the d prime for each condition (way 2)

###Analaysis of reaction times
```{r analyzing RT_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1.V.RT <- df.L1.V[df.L1.V$ACC == 1,]

df.L1.V.RT.subj <- summarySEwithin(df.L1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
df.L1.V.RT.grand <- summarySE(df.L1.V.RT.subj,measurevar = 'RT', groupvar = c('Match','Morality','Identity'),na.rm = TRUE)

df.L1.V.RT_match <- df.L1.V.RT[df.L1.V.RT$Match == "match",]
df.L1.V.RT_nonmatch <- df.L1.V.RT[df.L1.V.RT$Match == "nonmatch",]
df.L1.V.RT_match.self <- df.L1.V.RT_match[df.L1.V.RT_match$Identity == 'Self',]
df.L1.V.RT_match.other <- df.L1.V.RT_match[df.L1.V.RT_match$Identity == 'Other',]

e7_L.rt_anova <- ezANOVA(df.L1.V.RT,dv = RT, wid = Subject, within = .(Match,Morality,Identity),within_full =  .(Match,Morality,Identity), type = 3)
e7_L.rt_anova.match <- ezANOVA(df.L1.V.RT_match,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
e7_L.rt_anova.nonmatch <- ezANOVA(df.L1.V.RT_nonmatch,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)

## t-test 
df.L1.V.RT.subj_w <- dcast(df.L1.V.RT.subj, Subject ~ Match + Identity + Morality ,value.var = "RT")

# Good self vs. Bad self
e7_L.rt.t.m.good_bad_slf <- t.test(df.L1.V.RT.subj_w$match_Self_Good,df.L1.V.RT.subj_w$match_Self_Bad,paired = TRUE)
df.L1.V.RT.subj_w$m.good_bad_slf <- df.L1.V.RT.subj_w$match_Self_Good - df.L1.V.RT.subj_w$match_Self_Bad
e7_L.rt.t.m.good_bad_slf.CI <- bootES(df.L1.V.RT.subj_w$m.good_bad_slf, R = 5000,effect.type = "cohens.d")

e7_L.rt.tvalue.good_bad_slf  <- round(as.numeric(e7_L.rt.t.m.good_bad_slf [[1]]),3)
e7_L.rt.df.L1.good_bad_slf  <- as.numeric(e7_L.rt.t.m.good_bad_slf [[2]])
e7_L.rt.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_slf [[3]]),"bonferroni",4)
e7_L.rt.cohens.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[1]],4) 
e7_L.rt.CI.L.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[12]][1],4)
e7_L.rt.CI.H.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[12]][2],4)

# Good Other vs. Bad Other
e7_L.rt.t.m.good_bad_oth <- t.test(df.L1.V.RT.subj_w$match_Other_Good,df.L1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
df.L1.V.RT.subj_w$m.good_bad_oth <- df.L1.V.RT.subj_w$match_Other_Good - df.L1.V.RT.subj_w$match_Other_Bad
e7_L.rt.t.m.good_bad_oth.CI <- bootES(df.L1.V.RT.subj_w$m.good_bad_oth, R = 5000,effect.type = "cohens.d")

e7_L.rt.tvalue.good_bad_oth  <- round(as.numeric(e7_L.rt.t.m.good_bad_oth [[1]]),3)
e7_L.rt.df.L1.good_bad_oth  <- as.numeric(e7_L.rt.t.m.good_bad_oth [[2]])
e7_L.rt.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_oth [[3]]),"bonferroni",4)
e7_L.rt.cohens.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[1]],4) 
e7_L.rt.CI.L.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[12]][1],4)
e7_L.rt.CI.H.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[12]][2],4)

# good self v. good other
e7_L.rt.t.m.slf_oth_good <- t.test(df.L1.V.RT.subj_w$match_Self_Good,df.L1.V.RT.subj_w$match_Other_Good,paired = TRUE)
df.L1.V.RT.subj_w$m.slf_oth_good <- df.L1.V.RT.subj_w$match_Self_Good - df.L1.V.RT.subj_w$match_Other_Good
e7_L.rt.t.m.slf_oth_good.CI <- bootES(df.L1.V.RT.subj_w$m.slf_oth_good, R = 5000,effect.type = "cohens.d")

e7_L.rt.tvalue.slf_oth_good  <- round(as.numeric(e7_L.rt.t.m.slf_oth_good[[1]]),3)
e7_L.rt.df.L1.slf_oth_good  <- as.numeric(e7_L.rt.t.m.slf_oth_good[[2]])
e7_L.rt.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_good[[3]]),"bonferroni",4)
e7_L.rt.cohens.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[1]],4) 
e7_L.rt.CI.L.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[12]][1],4)
e7_L.rt.CI.H.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[12]][2],4)

e7_L.rt.t.m.slf_oth_bad <- t.test(df.L1.V.RT.subj_w$match_Self_Bad,df.L1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
df.L1.V.RT.subj_w$m.slf_oth_bad <- df.L1.V.RT.subj_w$match_Self_Bad - df.L1.V.RT.subj_w$match_Other_Bad
e7_L.rt.t.m.slf_oth_bad.CI <- bootES(df.L1.V.RT.subj_w$m.slf_oth_bad, R = 5000,effect.type = "cohens.d")

e7_L.rt.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.rt.t.m.slf_oth_bad[[1]]),3)
e7_L.rt.df.L1.slf_oth_bad  <- as.numeric(e7_L.rt.t.m.slf_oth_bad[[2]])
e7_L.rt.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_bad[[3]]),"bonferroni",4)
e7_L.rt.cohens.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[1]],4) 
e7_L.rt.CI.L.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[12]][1],4)
e7_L.rt.CI.H.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[12]][2],4)

df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Match == "match",]

##### save the rt data for late used ####
colnames(df.L1.V.RT.subj_w) <- paste("L_rt", colnames(df.L1.V.RT.subj_w), sep = "_")
colnames(df.L1.V.RT.subj_w)[colnames(df.L1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
write.csv(df.L1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
#### save the rt data ###

e7_L.rt.mean.GoodSelf <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
e7_L.rt.sd.GoodSelf <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
e7_L.rt.mean.BadSelf <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
e7_L.rt.sd.BadSelf <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Self'],0)

e7_L.rt.mean.GoodOther <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
e7_L.rt.sd.GoodOther <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
e7_L.rt.mean.BadOther <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
e7_L.rt.sd.BadOther <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Other'],0)

e7_L.p_rt1 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme

e7_L.p_rt2 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +   # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) +
        scale_y_continuous("Reation Times  (ms)",breaks = seq(500,800,50),expand = c(0, 0)) +
        apatheme + 
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
#tiff(filename = "e7_L.p_rt2.tiff", width = 8, height = 8, units = 'in', res = 300)
#e7_L.p_rt2
#dev.off()

#tiff(filename = "Figure exp7. d prime and RTs of Experiment 7 (way 2).tiff", width = 8, height = 6, units = 'in', res = 300)
#multiplot(e7_L.p_dprime2,e7_L.p_rt2,cols = 2)
#dev.off()

```

We conducted a 2 * 3 * 2 rmANOVA for RT.

The effect of `r e7_L.rt_anova[[1]][1,1]`: *F*(`r e7_L.rt_anova[[1]][1,2]`, `r e7_L.rt_anova[[1]][1,3]`) = `r round(e7_L.rt_anova[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][1,7],4)`

The effect of `r e7_L.rt_anova[[1]][2,1]`: *F*(`r e7_L.rt_anova[[1]][2,2]`, `r e7_L.rt_anova[[1]][2,3]`) = `r round(e7_L.rt_anova[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][2,7],4)`

The effect of `r e7_L.rt_anova[[1]][3,1]`: *F*(`r e7_L.rt_anova[[1]][3,2]`, `r e7_L.rt_anova[[1]][3,3]`) = `r round(e7_L.rt_anova[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][3,7],4)`.

The effect of `r e7_L.rt_anova[[1]][4,1]`: *F*(`r e7_L.rt_anova[[1]][4,2]`, `r e7_L.rt_anova[[1]][4,3]`) = `r round(e7_L.rt_anova[[1]][4,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][4,7],4)`.

The effect of `r e7_L.rt_anova[[1]][5,1]`: *F*(`r e7_L.rt_anova[[1]][5,2]`, `r e7_L.rt_anova[[1]][5,3]`) = `r round(e7_L.rt_anova[[1]][5,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][5,7],4)`.

The effect of `r e7_L.rt_anova[[1]][6,1]`: *F*(`r e7_L.rt_anova[[1]][6,2]`, `r e7_L.rt_anova[[1]][6,3]`) = `r round(e7_L.rt_anova[[1]][6,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][6,7],4)`.

The effect of `r e7_L.rt_anova[[1]][7,1]`: *F*(`r e7_L.rt_anova[[1]][7,2]`, `r e7_L.rt_anova[[1]][7,3]`) = `r round(e7_L.rt_anova[[1]][7,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][7,7],4)`.

We conducted a 3 * 2 rmANOVA for RT.

**For the matched trials**, 
The effect of `r e7_L.rt_anova.match[[1]][1,1]`: *F*(`r e7_L.rt_anova.match[[1]][1,2]`, `r e7_L.rt_anova.match[[1]][1,3]`) = `r round(e7_L.rt_anova.match[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][1,7],4)`

The effect of `r e7_L.rt_anova.match[[1]][2,1]`: *F*(`r e7_L.rt_anova.match[[1]][2,2]`, `r e7_L.rt_anova.match[[1]][2,3]`) = `r round(e7_L.rt_anova.match[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][2,7],4)`

The effect of `r e7_L.rt_anova.match[[1]][3,1]`: *F*(`r e7_L.rt_anova.match[[1]][3,2]`, `r e7_L.rt_anova.match[[1]][3,3]`) = `r round(e7_L.rt_anova.match[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][3,7],4)`.

**For the nonmatched trials**, 
The effect of `r e7_L.rt_anova.nonmatch[[1]][1,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][1,2]`, `r e7_L.rt_anova.nonmatch[[1]][1,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][1,7],4)`

The effect of `r e7_L.rt_anova.nonmatch[[1]][2,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][2,2]`, `r e7_L.rt_anova.nonmatch[[1]][2,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][2,7],4)`

The effect of `r e7_L.rt_anova.nonmatch[[1]][3,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][3,2]`, `r e7_L.rt_anova.nonmatch[[1]][3,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][3,7],4)`.

We conducted post-hoc comparison

Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`): *t*(`r e7_L.rt.df.L1.good_bad_slf`) = `r e7_L.rt.tvalue.good_bad_slf`, *p* = 
`r e7_L.rt.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_slf`, 95% CI [`r e7_L.rt.CI.L.good_bad_slf` `r e7_L.rt.CI.H.good_bad_slf`]

Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`)  vs Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.L1.good_bad_oth`) = `r e7_L.rt.tvalue.good_bad_oth`, *p* = 
`r e7_L.rt.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_oth`, 95% CI [`r e7_L.rt.CI.L.good_bad_oth` `r e7_L.rt.CI.H.good_bad_oth`]

Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs. Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`) : *t*(`r e7_L.rt.df.L1.slf_oth_good`) = `r e7_L.rt.tvalue.slf_oth_good`, *p* = `r e7_L.rt.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_good`, 95% CI [`r e7_L.rt.CI.L.slf_oth_good` `r e7_L.rt.CI.H.slf_oth_good`]

Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`) vs. Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.L1.slf_oth_bad`) = `r e7_L.rt.tvalue.slf_oth_bad`, *p* = `r e7_L.rt.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_bad`, 95% CI [`r e7_L.rt.CI.L.slf_oth_bad` `r e7_L.rt.CI.H.slf_oth_bad`]

```{r plot2 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# change a way to plot
ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme
#ggsave('RT_mean_plot2.png', width=4, height=6, unit='in', dpi=300)  # save the plot

```

The above is the reaction time for each condition (way 1)

```{r plot1 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Matchness == "match",]
ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
        apatheme
#ggsave('RT_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot

```

The above is the reaction time for each condition (way 2)

### Analyzing data from testing phase
We only analyzed data for self-other categorization and Good-Bad categorization data

#### analysis of ACC
```{r clean the data_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# df.T1.V <- df.T1.V[df.T1.V$Task != "importance",]
df.T1.V$ACC[df.T1.V$ACC==-1] <-0

df.T1.V.acc.subj <-  ddply(df.T1.V,.(Subject,Task,Morality,Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

# define the level of factor# make the variables in a specified order
df.T1.V.acc.subj$Morality <- factor(df.T1.V.acc.subj$Morality, levels=c("Good","Bad")) 
df.T1.V.acc.subj$Identity <- factor(df.T1.V.acc.subj$Identity, levels=c("Self","Other"))

df.T1.V.acc.subj.Self <- df.T1.V.acc.subj[df.T1.V.acc.subj$Task == "Id_task",]
df.T1.V.acc.subj.Good <- df.T1.V.acc.subj[df.T1.V.acc.subj$Task == "Valence_task",]

e7_T.acc_anova <- ezANOVA(df.T1.V.acc.subj,dv = ACC, wid = Subject, within=.(Task,Morality,Identity), type=3)
e7_T.acc_anova.self <- ezANOVA(df.T1.V.acc.subj.Self, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
e7_T.acc_anova.Good <- ezANOVA(df.T1.V.acc.subj.Good, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)

df.T1.V.acc.sum <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Task','Morality','Identity'))

df.T1.V.acc.subj_w  <- dcast(df.T1.V.acc.subj, Subject ~ Task + Identity + Morality ,value.var = "ACC")

# calculate the mean difference for moral effect (Good-Bad)
df.T1.V.acc.subj_w$Valence_good_bad_slf <- df.T1.V.acc.subj_w$Valence_task_Self_Good - df.T1.V.acc.subj_w$Valence_task_Self_Bad
df.T1.V.acc.subj_w$Valence_good_bad_oth <- df.T1.V.acc.subj_w$Valence_task_Other_Good - df.T1.V.acc.subj_w$Valence_task_Other_Bad
df.T1.V.acc.subj_w$Id_good_bad_slf      <- df.T1.V.acc.subj_w$Id_task_Self_Good - df.T1.V.acc.subj_w$Id_task_Self_Bad
df.T1.V.acc.subj_w$ID_good_bad_oth      <- df.T1.V.acc.subj_w$Id_task_Other_Good - df.T1.V.acc.subj_w$Id_task_Other_Bad

# calculate the mean difference for self effect (self-other)
df.T1.V.acc.subj_w$Valence_slf_oth_good <- df.T1.V.acc.subj_w$Valence_task_Self_Good - df.T1.V.acc.subj_w$Valence_task_Other_Good
df.T1.V.acc.subj_w$Valence_slf_oth_bad  <- df.T1.V.acc.subj_w$Valence_task_Self_Bad - df.T1.V.acc.subj_w$Valence_task_Other_Bad
df.T1.V.acc.subj_w$Id_slf_oth_good  <- df.T1.V.acc.subj_w$Id_task_Self_Good - df.T1.V.acc.subj_w$Id_task_Other_Good
df.T1.V.acc.subj_w$Id_slf_oth_bad   <- df.T1.V.acc.subj_w$Id_task_Self_Bad - df.T1.V.acc.subj_w$Id_task_Other_Bad

colnames(df.T1.V.acc.subj_w) <- paste("T_acc", colnames(df.T1.V.acc.subj_w), sep = "_")
colnames(df.T1.V.acc.subj_w)[colnames(df.T1.V.acc.subj_w) == 'T_acc_Subject'] <- 'Subject'
write.csv(df.T1.V.acc.subj_w,"data_catigorization_v_acc.csv",row.names=FALSE)
# write.csv(df.T1.V.acc.sum,"df.T1.V.acc.sum.csv",row.names=FALSE)

# plot and save the ACC for each condition
ACC_e7_T <- ggplot(data = df.T1.V.acc.sum,aes(y = ACC, x = Morality, group = Task,shape = Task, fill = Task)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Accuracy') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Accuracy for each condition") +
        coord_cartesian(ylim=c(0.5,1)) +
        scale_y_continuous(breaks=seq(0.5,1,0.1),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        facet_grid(.~ Identity) + 
        apatheme +
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("id criteria    ","morality criteria")) +
        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("ACC_e7_T.pdf", ACC_e7_T, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")

```
ANOVA for accuracy with task type (self-other, Good-Bad) * moral character (Good vs. Bad) and self-relatedness (self v. other) as within-subjects factors.

The main effect of `r e7_T.acc_anova[[1]][1,1]`, *F*(`r e7_T.acc_anova[[1]][1,2]`, `r e7_T.acc_anova[[1]][1,3]`) = `r round(e7_T.acc_anova[[1]][1,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][1,7],4)`.

The main effect of `r e7_T.acc_anova[[1]][2,1]`: *F*(`r e7_T.acc_anova[[1]][2,2]`, `r e7_T.acc_anova[[1]][2,3]`) = `r round(e7_T.acc_anova[[1]][2,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][2,7],4)`

The main effect of `r e7_T.acc_anova[[1]][3,1]`: *F*(`r e7_T.acc_anova[[1]][3,2]`, `r e7_T.acc_anova[[1]][3,3]`) = `r round(e7_T.acc_anova[[1]][3,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][3,7],4)`.

The interaction between: `r e7_T.acc_anova[[1]][4,1]`: *F*(`r e7_T.acc_anova[[1]][4,2]`, `r e7_T.acc_anova[[1]][4,3]`) = `r round(e7_T.acc_anova[[1]][4,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][4,7],4)`.

The interaction between: `r e7_T.acc_anova[[1]][5,1]`: *F*(`r e7_T.acc_anova[[1]][5,2]`, `r e7_T.acc_anova[[1]][5,3]`) = `r round(e7_T.acc_anova[[1]][5,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][5,7],4)`.

The interaction between: `r e7_T.acc_anova[[1]][6,1]`: *F*(`r e7_T.acc_anova[[1]][6,2]`, `r e7_T.acc_anova[[1]][6,3]`) = `r round(e7_T.acc_anova[[1]][6,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][6,7],4)`.

The interaction between: `r e7_T.acc_anova[[1]][7,1]`: *F*(`r e7_T.acc_anova[[1]][7,2]`, `r e7_T.acc_anova[[1]][7,3]`) = `r round(e7_T.acc_anova[[1]][7,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][7,7],4)`.

Since there was no signficant interaction between Task type and other two variables, we combined the resuled from identity and valence based categorization. Given that the interaction between morality and identity was signficant, we further analyzed the simple effect.

```{r ACC_e7_T_simple_effect, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# combine data cross task
# tmp <- aggregate(df.T1.V.acc.subj[,7],list(df.T1.V.acc.subj$Subject,df.T1.V.acc.subj$Morality,df.T1.V.acc.subj$Identity),mean)
df.T1.V.acc.subj.noTask <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
df.T1.V.acc.subj.noTask_w <- dcast(df.T1.V.acc.subj.noTask, Subject ~ Identity + Morality ,value.var = "ACC")

df.T1.V.acc.subj.noTask_w$good_bad_slf <- df.T1.V.acc.subj.noTask_w$Self_Good - df.T1.V.acc.subj.noTask_w$Self_Bad
df.T1.V.acc.subj.noTask_w$good_bad_oth <- df.T1.V.acc.subj.noTask_w$Other_Good - df.T1.V.acc.subj.noTask_w$Other_Bad
df.T1.V.acc.subj.noTask_w$slf_oth_good <- df.T1.V.acc.subj.noTask_w$Self_Good - df.T1.V.acc.subj.noTask_w$Other_Good
df.T1.V.acc.subj.noTask_w$slf_oth_bad <- df.T1.V.acc.subj.noTask_w$Self_Bad - df.T1.V.acc.subj.noTask_w$Other_Bad

write.csv(df.T1.V.acc.subj.noTask_w, 'df.T1.V.acc.subj.noTask.csv',row.names = F)

e7_T.acc_anova_noTask1 <- ezANOVA(df.T1.V.acc.subj.noTask,dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
# e7_T.acc_anova_noTask1 is exactly the same as in three way rm ANOVA

# simple effect:

# Good self vs Bad self
e7_T.acc.t.good_bad_slf <- t.test(df.T1.V.acc.subj.noTask_w$Self_Good,df.T1.V.acc.subj.noTask_w$Self_Bad,paired = TRUE)
e7_T.acc.t.good_bad_slf.CI <- bootES(df.T1.V.acc.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")

e7_T.acc.tvalue.good_bad_slf <- round(as.numeric(e7_T.acc.t.good_bad_slf[[1]]),3)
e7_T.acc.df.good_bad_slf <- as.numeric(e7_T.acc.t.good_bad_slf[[2]])
e7_T.acc.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_T.acc.t.good_bad_slf[[3]]),"bonferroni",4)
e7_T.acc.cohens.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[1]],4) 
e7_T.acc.CI.L.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[12]][1],4)
e7_T.acc.CI.H.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[12]][2],4)

# Good other vs Bad other
e7_T.acc.t.good_bad_oth <- t.test(df.T1.V.acc.subj.noTask_w$Other_Good,df.T1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
e7_T.acc.t.good_bad_oth.CI <- bootES(df.T1.V.acc.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")

e7_T.acc.tvalue.good_bad_oth <- round(as.numeric(e7_T.acc.t.good_bad_oth[[1]]),3)
e7_T.acc.df.good_bad_oth <- as.numeric(e7_T.acc.t.good_bad_oth[[2]])
e7_T.acc.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_T.acc.t.good_bad_oth[[3]]),"bonferroni",4)
e7_T.acc.cohens.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[1]],4) 
e7_T.acc.CI.L.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[12]][1],4)
e7_T.acc.CI.H.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[12]][2],4)

# Good self vs Good other
e7_T.acc.t.slf_oth_good <- t.test(df.T1.V.acc.subj.noTask_w$Self_Good,df.T1.V.acc.subj.noTask_w$Other_Good,paired = TRUE)
e7_T.acc.t.slf_oth_good.CI <- bootES(df.T1.V.acc.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")

e7_T.acc.tvalue.slf_oth_good <- round(as.numeric(e7_T.acc.t.slf_oth_good[[1]]),3)
e7_T.acc.df.slf_oth_good <- as.numeric(e7_T.acc.t.slf_oth_good[[2]])
e7_T.acc.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_T.acc.t.slf_oth_good[[3]]),"bonferroni",4)
e7_T.acc.cohens.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[1]],4) 
e7_T.acc.CI.L.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[12]][1],4)
e7_T.acc.CI.H.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[12]][2],4)

# Bad self vs Bad other
e7_T.acc.t.slf_oth_bad <- t.test(df.T1.V.acc.subj.noTask_w$Self_Bad,df.T1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
e7_T.acc.t.slf_oth_bad.CI <- bootES(df.T1.V.acc.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")

e7_T.acc.tvalue.slf_oth_bad <- round(as.numeric(e7_T.acc.t.slf_oth_bad[[1]]),3)
e7_T.acc.df.slf_oth_bad <- as.numeric(e7_T.acc.t.slf_oth_bad[[2]])
e7_T.acc.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_T.acc.t.slf_oth_bad[[3]]),"bonferroni",4)
e7_T.acc.cohens.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[1]],4) 
e7_T.acc.CI.L.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[12]][1],4)
e7_T.acc.CI.H.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[12]][2],4)

df.T1.V.acc.sum.noTask <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Morality','Identity'))
ACC.Mean.Good.Self <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Good']
ACC.SD.Good.Self <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Good']
ACC.Mean.Bad.Self <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
ACC.SD.Bad.Self <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
ACC.Mean.Good.Other <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Good']
ACC.SD.Good.Other <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Good']
ACC.Mean.Bad.Other <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
ACC.SD.Bad.Other <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Bad']

# e7_T.acc_anova_id2 <- ezANOVA(df.T1.V.acc.subj.noTask[df.T1.V.acc.subj.noTask$Identity == 'self',],dv = ACC, wid = Subject, within=.(Morality), type=3)

# e7_T.acc_anova_id3 <- ezANOVA(df.T1.V.acc.subj[df.T1.V.acc.subj$Morality == 'Good',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
# e7_T.acc_anova_id4 <- ezANOVA(df.T1.V.acc.subj[df.T1.V.acc.subj$Morality == 'Bad',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)

# plot the data without task variable
ACC_e7_T_noTask <- ggplot(data =df.T1.V.acc.sum.noTask,aes(y = ACC, x =Morality, group = Identity,shape = Identity, fill = Identity))+
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Accuracy') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Accuracy for each condition") +
        coord_cartesian(ylim=c(0.5,1)) +
        scale_y_continuous(breaks=seq(0.5,1,0.1),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        #facet_grid(.~ Identity) + 
        apatheme +
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("ACC_e7_T_noTask.pdf", ACC_e7_T_noTask, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")

```

2 by 2 ANOVA:
The main effect of `r e7_T.acc_anova_noTask1[[1]][1,1]`, *F*(`r e7_T.acc_anova_noTask1[[1]][1,2]`, `r e7_T.acc_anova_noTask1[[1]][1,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][1,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][1,7],4)`.

The main effect of `r e7_T.acc_anova_noTask1[[1]][2,1]`: *F*(`r e7_T.acc_anova_noTask1[[1]][2,2]`, `r e7_T.acc_anova_noTask1[[1]][2,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][2,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][2,7],4)`

The interaction `r e7_T.acc_anova_noTask1[[1]][3,1]`: *F*(`r e7_T.acc_anova_noTask1[[1]][3,2]`, `r e7_T.acc_anova_noTask1[[1]][3,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][3,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][3,7],4)`.

As for the self condition, effect of moral valence was significante: t(`r e7_T.acc.df.good_bad_slf`) = `r e7_T.acc.tvalue.good_bad_slf`, p = `r e7_T.acc.pvalue.good_bad_slf.adj`, Cohen's d = `r e7_T.acc.cohens.good_bad_slf`, 95% CI[`r e7_T.acc.CI.L.good_bad_slf` `r e7_T.acc.CI.H.good_bad_slf`].
For other condition, moral valence was not significante: t(`r e7_T.acc.df.good_bad_oth`) = `r e7_T.acc.tvalue.good_bad_oth`, p = `r e7_T.acc.pvalue.good_bad_oth.adj`, Cohen's d = `r e7_T.acc.cohens.good_bad_oth`, 95% CI[`r e7_T.acc.CI.L.good_bad_oth` `r e7_T.acc.CI.H.good_bad_oth`].

The effect of identity:
for moral condition, the difference between self and other was significant:t(`r e7_T.acc.df.slf_oth_good`) = `r e7_T.acc.tvalue.slf_oth_good`, p = `r e7_T.acc.pvalue.slf_oth_good.adj`, Cohen's d = `r e7_T.acc.cohens.slf_oth_good`, 95% CI[`r e7_T.acc.CI.L.slf_oth_good` `r e7_T.acc.CI.H.slf_oth_good`].
for Bad condition, the difference between self and other was not significant:t(`r e7_T.acc.df.slf_oth_bad`) = `r e7_T.acc.tvalue.slf_oth_bad`, p = `r e7_T.acc.pvalue.slf_oth_bad.adj`, Cohen's d = `r e7_T.acc.cohens.slf_oth_bad`, 95% CI[`r e7_T.acc.CI.L.slf_oth_bad` `r e7_T.acc.CI.H.slf_oth_bad`].

Good self: `r ACC.Mean.Good.Self` + `r ACC.SD.Good.Self`
Bad self:`r ACC.Mean.Bad.Self` + `r ACC.SD.Bad.Self`
Good other: `r ACC.Mean.Good.Other` + `r ACC.SD.Good.Other`
Bad other: `r ACC.Mean.Bad.Other` + `r ACC.SD.Bad.Other`

```{r plot2 the ACC_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.T1.V.acc.sum,aes(y = ACC, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Accuracy') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Accuracy for each condition") +
        coord_cartesian(ylim=c(0.5,1))+
        scale_y_continuous(breaks = seq(0.5,1,0.1),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        facet_grid(.~Task) + 
        apatheme
# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

The above is the ACC for each condition. left panel is the results of moral-categorization task, the right panel is the self-other categorization task.

###Analaysis of reaction times
```{r analyzing RT_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.T1.V.RT <- df.T1.V[df.T1.V$ACC == 1,]
# excluded 7035 and subject8
# df.T1.V.RT <- df.T1.V.RT[!(df.T1.V.RT$Subject %in% c("8","7035")),] 
df.T1.V.RT.subj <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)

# define the level of factor
df.T1.V.RT.subj$Morality <- factor(df.T1.V.RT.subj$Morality, levels=c("Good","Bad")) # make the variables in a specified order
df.T1.V.RT.subj$Identity <- factor(df.T1.V.RT.subj$Identity, levels=c("Self","Other"))

df.T1.V.RT.subj_w  <- dcast(df.T1.V.RT.subj, Subject ~ Task + Identity + Morality ,value.var = "RT")

# calculate the mean difference for Good effect (Good-Bad)
df.T1.V.RT.subj_w$Valence_good_bad_slf  <- df.T1.V.RT.subj_w$Valence_task_Self_Good - df.T1.V.RT.subj_w$Valence_task_Self_Bad
df.T1.V.RT.subj_w$Valence_good_bad_oth <- df.T1.V.RT.subj_w$Valence_task_Other_Good - df.T1.V.RT.subj_w$Valence_task_Other_Bad
df.T1.V.RT.subj_w$Id_good_bad_slf     <- df.T1.V.RT.subj_w$Id_task_Self_Good   - df.T1.V.RT.subj_w$Id_task_Self_Bad
df.T1.V.RT.subj_w$ID_good_bad_oth    <- df.T1.V.RT.subj_w$Id_task_Other_Good - df.T1.V.RT.subj_w$Id_task_Other_Bad

# calculate the mean difference for self effect (self-other)
df.T1.V.RT.subj_w$Valence_slf_oth_good <- df.T1.V.RT.subj_w$Valence_task_Self_Good   - df.T1.V.RT.subj_w$Valence_task_Other_Good
df.T1.V.RT.subj_w$valence_slf_oth_bad <- df.T1.V.RT.subj_w$Valence_task_Self_Bad - df.T1.V.RT.subj_w$Valence_task_Other_Bad
df.T1.V.RT.subj_w$Id_slf_oth_good    <- df.T1.V.RT.subj_w$Id_task_Self_Good - df.T1.V.RT.subj_w$Id_task_Other_Good
df.T1.V.RT.subj_w$Id_slf_oth_bad    <- df.T1.V.RT.subj_w$Id_task_Self_Bad - df.T1.V.RT.subj_w$Id_task_Other_Bad

#### save the rt data for later use ####
colnames(df.T1.V.RT.subj_w) <- paste("T_rt", colnames(df.T1.V.RT.subj_w), sep = "_")
colnames(df.T1.V.RT.subj_w)[colnames(df.T1.V.RT.subj_w) == 'T_rt_Subject'] <- 'Subject'
write.csv(df.T1.V.RT.subj_w,"data_catigorization_v_rt.csv",row.names=FALSE)
###########

df.T1.V.RT.grand <- summarySE(df.T1.V.RT.subj,measurevar = 'RT', groupvar = c('Task','Morality','Identity'),na.rm = TRUE)

df.T1.V.RT_Id_task <- df.T1.V.RT[df.T1.V.RT$Task == "Id_task",]
df.T1.V.RT_Val_task <- df.T1.V.RT[df.T1.V.RT$Task == "Valence_task",]
#df.T1.V.RT_match.self <- df.T1.V.RT_match[df.T1.V.RT_match$Identity == 'self',]
#df.T1.V.RT_match.other <- df.T1.V.RT_match[df.T1.V.RT_match$Identity == 'other',]

e7_T.rt_anova <- ezANOVA(df.T1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),within_full=.(Task,Identity,Morality), type=3)

e7_T.rt_anova.Id_task <- ezANOVA(df.T1.V.RT_Id_task,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)

e7_T.rt_anova.val_task <- ezANOVA(df.T1.V.RT_Val_task,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)

RT_e7_T <- ggplot(data = df.T1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Reaction times') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Reaction times for each condition") +
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        facet_grid(.~ Identity) + 
        apatheme +
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("id criteria    ","morality criteria")) +
        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("RT_e7_T.pdf", RT_e7_T, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
# tiff(filename = "RT_e7_T.tiff", width = 8, height = 8, units = 'in', res = 300)
# RT_e7_T
# dev.off()

```

ANOVA for RT with task type (self-other, Good-Bad) * moral character (Good vs. Bad) and self-relatedness (self v. other) as within-subjects factors.

The main effect of `r e7_T.rt_anova[[1]][1,1]`, *F*(`r e7_T.rt_anova[[1]][1,2]`, `r e7_T.rt_anova[[1]][1,3]`) = `r round(e7_T.rt_anova[[1]][1,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][1,7],4)`.

The main effect of `r e7_T.rt_anova[[1]][2,1]`: *F*(`r e7_T.rt_anova[[1]][2,2]`, `r e7_T.rt_anova[[1]][2,3]`) = `r round(e7_T.rt_anova[[1]][2,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][2,7],4)`

The main effect of `r e7_T.rt_anova[[1]][3,1]`: *F*(`r e7_T.rt_anova[[1]][3,2]`, `r e7_T.rt_anova[[1]][3,3]`) = `r round(e7_T.rt_anova[[1]][3,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][3,7],4)`.

The interaction between: `r e7_T.rt_anova[[1]][4,1]`: *F*(`r e7_T.rt_anova[[1]][4,2]`, `r e7_T.rt_anova[[1]][4,3]`) = `r round(e7_T.rt_anova[[1]][4,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][4,7],4)`.

The interaction between: `r e7_T.rt_anova[[1]][5,1]`: *F*(`r e7_T.rt_anova[[1]][5,2]`, `r e7_T.rt_anova[[1]][5,3]`) = `r round(e7_T.rt_anova[[1]][5,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][5,7],4)`.

The interaction between: `r e7_T.rt_anova[[1]][6,1]`: *F*(`r e7_T.rt_anova[[1]][6,2]`, `r e7_T.rt_anova[[1]][6,3]`) = `r round(e7_T.rt_anova[[1]][6,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][6,7],4)`.

The interaction between: `r e7_T.rt_anova[[1]][7,1]`: *F*(`r e7_T.rt_anova[[1]][7,2]`, `r e7_T.rt_anova[[1]][7,3]`) = `r round(e7_T.rt_anova[[1]][7,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][7,7],4)`.

Since there was no signficant interaction between identity and other two variables for RT, we combined the results from different shape identity. Given that the interaction between Task and moral valence was signficant, we further analyzed the simple effect.

```{r RT_e7_T_simple_effect_noID, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# combine data cross identity
# tmp <- aggregate(df.T1.V.acc.subj[,7],list(df.T1.V.acc.subj$Subject,df.T1.V.acc.subj$Morality,df.T1.V.acc.subj$Identity),mean)
df.T1.V.RT.subj.noID <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Task','Morality'))
df.T1.V.RT.subj.noID_w <- dcast(df.T1.V.RT.subj.noID, Subject ~ Task + Morality ,value.var = "RT")

# valence effect under different task
df.T1.V.RT.subj.noID_w$good_bad_ID <- df.T1.V.RT.subj.noID_w$Id_task_Good - df.T1.V.RT.subj.noID_w$Id_task_Bad
df.T1.V.RT.subj.noID_w$good_bad_Val <- df.T1.V.RT.subj.noID_w$Valence_task_Good - df.T1.V.RT.subj.noID_w$Valence_task_Bad

# task effect for differnt valence
df.T1.V.RT.subj.noID_w$ID_Val_good <- df.T1.V.RT.subj.noID_w$Id_task_Good - df.T1.V.RT.subj.noID_w$Valence_task_Good
df.T1.V.RT.subj.noID_w$ID_Val_bad <- df.T1.V.RT.subj.noID_w$Id_task_Bad - df.T1.V.RT.subj.noID_w$Valence_task_Bad

write.csv(df.T1.V.RT.subj.noID_w, 'df.T1.V.RT.subj.noID_w.csv',row.names = F)

e7_T.RT_anova_noID <- ezANOVA(df.T1.V.RT.subj.noID,dv = RT, wid = Subject, within=.(Task,Morality), type=3)
# e7_T.acc_anova_noTask1 is exactly the same as in three way rm ANOVA

# simple effect:

# Id categorization task: Good v. Bad
e7_T.RT.t.good_bad_ID <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Good,df.T1.V.RT.subj.noID_w$Id_task_Bad,paired = TRUE)
e7_T.RT.t.good_bad_ID.CI <- bootES(df.T1.V.RT.subj.noID_w$good_bad_ID,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.good_bad_ID <- round(as.numeric(e7_T.RT.t.good_bad_ID[[1]]),3)
e7_T.RT.df.good_bad_ID <- as.numeric(e7_T.RT.t.good_bad_ID[[2]])
e7_T.RT.pvalue.good_bad_ID.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_ID[[3]]),"bonferroni",4)
e7_T.RT.cohens.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[1]],4) 
e7_T.RT.CI.L.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[12]][1],4)
e7_T.RT.CI.H.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[12]][2],4)

# moral task: Good v. Bad
e7_T.RT.t.good_bad_Val <- t.test(df.T1.V.RT.subj.noID_w$Valence_task_Good,df.T1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
e7_T.RT.t.good_bad_Val.CI <- bootES(df.T1.V.RT.subj.noID_w$good_bad_Val,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.good_bad_Val <- round(as.numeric(e7_T.RT.t.good_bad_Val[[1]]),3)
e7_T.RT.df.good_bad_Val <- as.numeric(e7_T.RT.t.good_bad_Val[[2]])
e7_T.RT.pvalue.good_bad_Val.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_Val[[3]]),"bonferroni",4)
e7_T.RT.cohens.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[1]],4) 
e7_T.RT.CI.L.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[12]][1],4)
e7_T.RT.CI.H.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[12]][2],4)

# Good valence: self task v. moral task
e7_T.RT.t.ID_Val_good <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Good,df.T1.V.RT.subj.noID_w$Valence_task_Good,paired = TRUE)
e7_T.RT.t.ID_Val_good.CI <- bootES(df.T1.V.RT.subj.noID_w$ID_Val_good,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.ID_Val_good <- round(as.numeric(e7_T.RT.t.ID_Val_good[[1]]),3)
e7_T.RT.df.ID_Val_good <- as.numeric(e7_T.RT.t.ID_Val_good[[2]])
e7_T.RT.pvalue.ID_Val_good.adj <- p.adjust(as.numeric(e7_T.RT.t.ID_Val_good[[3]]),"bonferroni",4)
e7_T.RT.cohens.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[1]],4) 
e7_T.RT.CI.L.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[12]][1],4)
e7_T.RT.CI.H.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[12]][2],4)

# Bad valence: self task v. moral task
e7_T.RT.t.ID_Val_bad <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Bad,df.T1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
e7_T.RT.t.ID_Val_bad.CI <- bootES(df.T1.V.RT.subj.noID_w$ID_Val_bad,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.ID_Val_bad <- round(as.numeric(e7_T.RT.t.ID_Val_bad[[1]]),3)
e7_T.RT.df.ID_Val_bad <- as.numeric(e7_T.RT.t.ID_Val_bad[[2]])
e7_T.RT.pvalue.ID_Val_bad.adj <- p.adjust(as.numeric(e7_T.RT.t.ID_Val_bad[[3]]),"bonferroni",4)
e7_T.RT.cohens.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[1]],4) 
e7_T.RT.CI.L.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[12]][1],4)
e7_T.RT.CI.H.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[12]][2],4)

RT.Mean.ID_task.Good  <- mean(df.T1.V.RT.subj.noID_w$Id_task_Good)
RT.SD.ID_task.Good  <- sd(df.T1.V.RT.subj.noID_w$Id_task_Good)
RT.Mean.ID_task.Bad <- mean(df.T1.V.RT.subj.noID_w$Id_task_Bad)
RT.SD.ID_task.Bad <- sd(df.T1.V.RT.subj.noID_w$Id_task_Bad)
RT.Mean.Val_task.Good <- mean(df.T1.V.RT.subj.noID_w$Valence_task_Good)
RT.SD.Val_task.Good <- sd(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
RT.Mean.Val_task.Bad <- mean(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
RT.SD.Val_task.Bad <- sd(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
```
2 by 2 ANOVA:
The main effect of `r e7_T.RT_anova_noID[[1]][1,1]`, *F*(`r e7_T.RT_anova_noID[[1]][1,2]`, `r e7_T.RT_anova_noID[[1]][1,3]`) = `r round(e7_T.RT_anova_noID[[1]][1,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][1,7],4)`.

The main effect of `r e7_T.RT_anova_noID[[1]][2,1]`: *F*(`r e7_T.RT_anova_noID[[1]][2,2]`, `r e7_T.RT_anova_noID[[1]][2,3]`) = `r round(e7_T.RT_anova_noID[[1]][2,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][2,7],4)`

The interaction `r e7_T.RT_anova_noID[[1]][3,1]`: *F*(`r e7_T.RT_anova_noID[[1]][3,2]`, `r e7_T.RT_anova_noID[[1]][3,3]`) = `r round(e7_T.RT_anova_noID[[1]][3,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][3,7],4)`.

As for the Identity task, effect of moral valence was significante: t(`r e7_T.RT.df.good_bad_ID`) = `r e7_T.RT.tvalue.good_bad_ID`, p = `r e7_T.RT.pvalue.good_bad_ID.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_ID`, 95% CI[`r e7_T.RT.CI.L.good_bad_ID` `r e7_T.RT.CI.H.good_bad_ID`].
For moral task : t(`r e7_T.RT.df.good_bad_Val`) = `r e7_T.RT.tvalue.good_bad_Val`, p = `r e7_T.RT.pvalue.good_bad_Val.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_Val`, 95% CI[`r e7_T.RT.CI.L.good_bad_Val` `r e7_T.RT.CI.H.good_bad_Val`].

The effect of task:
for moral condition, the difference between self and moral task:t(`r e7_T.RT.df.ID_Val_good`) = `r e7_T.RT.tvalue.ID_Val_good`, p = `r e7_T.RT.pvalue.ID_Val_good.adj`, Cohen's d = `r e7_T.RT.cohens.ID_Val_good`, 95% CI[`r e7_T.RT.CI.L.ID_Val_good` `r e7_T.RT.CI.H.ID_Val_good`].
for Bad condition, the difference between self and moral task :t(`r e7_T.RT.df.ID_Val_bad`) = `r e7_T.RT.tvalue.ID_Val_bad`, p = `r e7_T.RT.pvalue.ID_Val_bad.adj`, Cohen's d = `r e7_T.RT.cohens.ID_Val_bad`, 95% CI[`r e7_T.RT.CI.L.ID_Val_bad` `r e7_T.RT.CI.H.ID_Val_bad`].

Moral valence for self condition: `r RT.Mean.ID_task.Good ` + `r RT.SD.ID_task.Good `
Bad for self condition:`r RT.Mean.ID_task.Bad` + `r RT.SD.ID_task.Bad`
Good for moral condition: `r RT.Mean.Val_task.Good` + `r RT.SD.Val_task.Good`
Bad for moral condition: `r RT.Mean.Val_task.Bad` + `r RT.SD.Val_task.Bad`

```{r RT_e7_T_simple_effect_noTask, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.T1.V.RT.subj.noTask <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Identity','Morality'))
df.T1.V.RT.subj.noTask_w <- dcast(df.T1.V.RT.subj.noTask, Subject ~ Identity + Morality ,value.var = "RT")

df.T1.V.RT.subj.noTask_w$good_bad_slf <- df.T1.V.RT.subj.noTask_w$Self_Good - df.T1.V.RT.subj.noTask_w$Self_Bad
df.T1.V.RT.subj.noTask_w$good_bad_oth <- df.T1.V.RT.subj.noTask_w$Other_Good - df.T1.V.RT.subj.noTask_w$Other_Bad
df.T1.V.RT.subj.noTask_w$slf_oth_good <- df.T1.V.RT.subj.noTask_w$Self_Good - df.T1.V.RT.subj.noTask_w$Other_Good
df.T1.V.RT.subj.noTask_w$slf_oth_bad <- df.T1.V.RT.subj.noTask_w$Self_Bad - df.T1.V.RT.subj.noTask_w$Other_Bad

write.csv(df.T1.V.RT.subj.noTask_w, 'df.T1.V.RT.subj.noTask_w.csv',row.names = F)

e7_T.RT_anova_noTask <- ezANOVA(df.T1.V.RT.subj.noTask,dv = RT, wid = Subject, within=.(Morality,Identity), type=3)
# e7_T.RT_anova_noTask1 is exactly the same as in three way rm ANOVA

# simple effect:

# Good self vs Bad self
e7_T.RT.t.good_bad_slf <- t.test(df.T1.V.RT.subj.noTask_w$Self_Good,df.T1.V.RT.subj.noTask_w$Self_Bad,paired = TRUE)
e7_T.RT.t.good_bad_slf.CI <- bootES(df.T1.V.RT.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.good_bad_slf <- round(as.numeric(e7_T.RT.t.good_bad_slf[[1]]),3)
e7_T.RT.df.good_bad_slf <- as.numeric(e7_T.RT.t.good_bad_slf[[2]])
e7_T.RT.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_slf[[3]]),"bonferroni",4)
e7_T.RT.cohens.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[1]],4) 
e7_T.RT.CI.L.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[12]][1],4)
e7_T.RT.CI.H.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[12]][2],4)

# Good other vs Bad other
e7_T.RT.t.good_bad_oth <- t.test(df.T1.V.RT.subj.noTask_w$Other_Good,df.T1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
e7_T.RT.t.good_bad_oth.CI <- bootES(df.T1.V.RT.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.good_bad_oth <- round(as.numeric(e7_T.RT.t.good_bad_oth[[1]]),3)
e7_T.RT.df.good_bad_oth <- as.numeric(e7_T.RT.t.good_bad_oth[[2]])
e7_T.RT.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_oth[[3]]),"bonferroni",4)
e7_T.RT.cohens.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[1]],4) 
e7_T.RT.CI.L.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[12]][1],4)
e7_T.RT.CI.H.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[12]][2],4)

# Good self vs Good other
e7_T.RT.t.slf_oth_good <- t.test(df.T1.V.RT.subj.noTask_w$Self_Good,df.T1.V.RT.subj.noTask_w$Other_Good,paired = TRUE)
e7_T.RT.t.slf_oth_good.CI <- bootES(df.T1.V.RT.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.slf_oth_good <- round(as.numeric(e7_T.RT.t.slf_oth_good[[1]]),3)
e7_T.RT.df.slf_oth_good <- as.numeric(e7_T.RT.t.slf_oth_good[[2]])
e7_T.RT.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_T.RT.t.slf_oth_good[[3]]),"bonferroni",4)
e7_T.RT.cohens.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[1]],4) 
e7_T.RT.CI.L.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[12]][1],4)
e7_T.RT.CI.H.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[12]][2],4)

# Bad self vs Bad other
e7_T.RT.t.slf_oth_bad <- t.test(df.T1.V.RT.subj.noTask_w$Self_Bad,df.T1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
e7_T.RT.t.slf_oth_bad.CI <- bootES(df.T1.V.RT.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")

e7_T.RT.tvalue.slf_oth_bad <- round(as.numeric(e7_T.RT.t.slf_oth_bad[[1]]),3)
e7_T.RT.df.slf_oth_bad <- as.numeric(e7_T.RT.t.slf_oth_bad[[2]])
e7_T.RT.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_T.RT.t.slf_oth_bad[[3]]),"bonferroni",4)
e7_T.RT.cohens.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[1]],4) 
e7_T.RT.CI.L.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[12]][1],4)
e7_T.RT.CI.H.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[12]][2],4)

RT.Mean.Good.Self <- mean(df.T1.V.RT.subj.noTask_w$Self_Good)
RT.SD.Good.Self <- sd(df.T1.V.RT.subj.noTask_w$Self_Good)
RT.Mean.Bad.Self <- mean(df.T1.V.RT.subj.noTask_w$Self_Bad)
RT.SD.Bad.Self <- sd(df.T1.V.RT.subj.noTask_w$Self_Bad)
RT.Mean.Good.Other <- mean(df.T1.V.RT.subj.noTask_w$Other_Good)
RT.SD.Good.Other <- sd(df.T1.V.RT.subj.noTask_w$Other_Good)
RT.Mean.Bad.Other <- mean(df.T1.V.RT.subj.noTask_w$Other_Bad)
RT.SD.Bad.Other <- sd(df.T1.V.RT.subj.noTask_w$Other_Bad)

df.T1.V.RT.sum.noTask <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Morality','Identity'))
RT.Mean.Good.Self <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Good']
RT.SD.Good.Self <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Good']
RT.Mean.Bad.Self <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
RT.SD.Bad.Self <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
RT.Mean.Good.Other <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Good']
RT.SD.Good.Other <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Good']
RT.Mean.Bad.Other <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
RT.SD.Bad.Other <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Bad']

# plot the data without task varaible.
RT_e7_T_noTask <- ggplot(data =df.T1.V.RT.sum.noTask,aes(y = RT, x =Morality, group = Identity,shape = Identity, fill = Identity))+
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Reaction times') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Reaction times for each condition") +
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme +
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("RT_e7_T_noTask.pdf", RT_e7_T_noTask, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")

```
2 by 2 ANOVA:
The main effect of `r e7_T.RT_anova_noTask[[1]][1,1]`, *F*(`r e7_T.RT_anova_noTask[[1]][1,2]`, `r e7_T.RT_anova_noTask[[1]][1,3]`) = `r round(e7_T.RT_anova_noTask[[1]][1,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][1,7],4)`.

The main effect of `r e7_T.RT_anova_noTask[[1]][2,1]`: *F*(`r e7_T.RT_anova_noTask[[1]][2,2]`, `r e7_T.RT_anova_noTask[[1]][2,3]`) = `r round(e7_T.RT_anova_noTask[[1]][2,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][2,7],4)`

The interaction `r e7_T.RT_anova_noTask[[1]][3,1]`: *F*(`r e7_T.RT_anova_noTask[[1]][3,2]`, `r e7_T.RT_anova_noTask[[1]][3,3]`) = `r round(e7_T.RT_anova_noTask[[1]][3,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][3,7],4)`.

As for the self condition, effect of moral valence was significant: t(`r e7_T.RT.df.good_bad_slf`) = `r e7_T.RT.tvalue.good_bad_slf`, p = `r e7_T.RT.pvalue.good_bad_slf.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_slf`, 95% CI[`r e7_T.RT.CI.L.good_bad_slf` `r e7_T.RT.CI.H.good_bad_slf`].
For other condition, moral valence was not significante: t(`r e7_T.RT.df.good_bad_oth`) = `r e7_T.RT.tvalue.good_bad_oth`, p = `r e7_T.RT.pvalue.good_bad_oth.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_oth`, 95% CI[`r e7_T.RT.CI.L.good_bad_oth` `r e7_T.RT.CI.H.good_bad_oth`].

The effect of identity:
for moral condition, the difference between self and other was significant:t(`r e7_T.RT.df.slf_oth_good`) = `r e7_T.RT.tvalue.slf_oth_good`, p = `r e7_T.RT.pvalue.slf_oth_good.adj`, Cohen's d = `r e7_T.RT.cohens.slf_oth_good`, 95% CI[`r e7_T.RT.CI.L.slf_oth_good` `r e7_T.RT.CI.H.slf_oth_good`].
for Bad condition, the difference between self and other was not significant:t(`r e7_T.RT.df.slf_oth_bad`) = `r e7_T.RT.tvalue.slf_oth_bad`, p = `r e7_T.RT.pvalue.slf_oth_bad.adj`, Cohen's d = `r e7_T.RT.cohens.slf_oth_bad`, 95% CI[`r e7_T.RT.CI.L.slf_oth_bad` `r e7_T.RT.CI.H.slf_oth_bad`].

Good self: `r RT.Mean.Good.Self` + `r RT.SD.Good.Self`
Bad self:`r RT.Mean.Bad.Self` + `r RT.SD.Bad.Self`
Good other: `r RT.Mean.Good.Other` + `r RT.SD.Good.Other`
Bad other: `r RT.Mean.Bad.Other` + `r RT.SD.Bad.Other`

```{r plot2 the RT_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.T1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Reaction times') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("Reaction times for each condition") +
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        facet_grid(.~ Identity) + 
        apatheme

# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

The above is the RT for each condition. left panel is the results of moral-categorization task, the right panel is the self-other categorization task.

####Correlation analysis:

The correlation between ACC of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_ACC,echo=FALSE,warning=FALSE,message=FALSE }
# matching task -- d prime
#ncol(df.L1.V.SDT_ww)
# matching task -- ACC
#ncol(df.L1.V.acc_w)
# matching task -- rt
#ncol(df.L1.V.RT.subj_w)
# categorization task -- ACC
#ncol(df.T1.V.acc.subj_w)
# categorization task -- rt
#ncol(df.T1.V.RT.subj_w)

## correlation analysis for ACC
df.corr.acc <- merge(df.L1.V.acc_w[,1:5],df.T1.V.acc.subj_w[,1:9],by = 'Subject')
df.corr.acc <- df.corr.acc[,2:13]
acc.corr <- corr.test(df.corr.acc, use = "pairwise", method = "pearson",adjust = "holm")

postscript("corr_acc_original_p_05.eps", width = 2048, height = 2048)
# ,main = "acc_original"
corrplot.mixed(acc.corr[[1]],p.mat = acc.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(acc.corr[[1]],p.mat = acc.corr[[4]],sig.level = 0.05,insig = "blank")
```

The correlation between the self-bias and moral bias of ACC of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_ACC-bias,echo=FALSE,warning=FALSE,message=FALSE }
#df.L1.V.acc_w <- read.csv("data_matching_v_acc.csv",header = TRUE, sep = ",")
#df.T1.V.acc.subj_w <- read.csv("data_catigorization_v_acc.csv",header = TRUE,sep = ",")

df.corr.bias_acc <- merge(df.L1.V.acc_w[,c(1,10:13)],df.T1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
df.corr.bias_acc <- df.corr.bias_acc[,2:13]
acc_bias.corr <- corr.test(df.corr.bias_acc,use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE)
postscript("corr_acc_bias_p_05.eps", width = 2048, height = 1024)
#:main = "corr coefficient (matching-categorization) - ACC_bias"
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
```

The correlation between RT of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_RT,echo=FALSE,warning=FALSE,message=FALSE }
# correlaton analysis for rt
df.corr.rt <- merge(df.L1.V.RT.subj_w[,1:5],df.T1.V.RT.subj_w[,1:9],by = 'Subject')
df.corr.rt <- df.corr.rt[,2:13]
rt.corr <- corr.test(df.corr.rt)
postscript("corr_rt_original_p_05.eps", width = 2048, height = 2048)
# ,main = "acc_original"
corrplot.mixed(rt.corr[[1]],p.mat = rt.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(rt.corr[[1]],p.mat = rt.corr[[4]],sig.level = 0.05,insig = "blank")
```

The correlation between the self-bias and moral bias of RT of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_RT-bias,echo=FALSE,warning=FALSE,message=FALSE }
# merge the data by subj ID
df.corr.bias_rt <- merge(df.L1.V.RT.subj_w[,c(1,10:13)],df.T1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
df.corr.bias_rt <- df.corr.bias_rt[,2:13]
rt_bias.corr <- corr.test(df.corr.bias_rt)

postscript("corr_rt_bias_p_05.eps", width = 2048, height = 1024)
#:main = "corr coefficient (matching-categorization) - ACC_bias"
corrplot.mixed(rt_bias.corr[[1]],p.mat = rt_bias.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(rt_bias.corr[[1]],p.mat = rt_bias.corr[[4]],sig.level = 0.05,insig = "blank")
```

the effect of self on ACC
The correlation of accuracy between matching task and categrization based on morality criteria
```{r correlation of self-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_moral <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Valence_slf_oth_good)
df.acc.self_bias_moral <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Valence_slf_oth_good")]
colnames(df.acc.self_bias_moral) <- c("ACC_self_bias_match","ACC_self_bias_moral_categorization")
ggplot(df.acc.self_bias_moral, aes(x=ACC_self_bias_match, y=ACC_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self1.eps", p_corr_acc_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r correlation of self-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_id <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Id_slf_oth_good)
df.acc.self_bias_id <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Id_slf_oth_good")]
colnames(df.acc.self_bias_id) <- c("ACC_self_bias_match","ACC_self_bias_id_categorization")
ggplot(df.acc.self_bias_id, aes(x=ACC_self_bias_match, y=ACC_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self2.eps", p_corr_acc_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self2.pdf",out.type="cairo", width=8, height=6)
```

The effect of morality 
The correlation of accuracy between matching task and categrization based on morality criteria
```{r correlation of moral-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_moral <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Valence_good_bad_slf)
df.acc.moral_bias_moral <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Valence_good_bad_slf")]
colnames(df.acc.moral_bias_moral) <- c("ACC_moral_bias_match","ACC_moral_bias_moral_categorization")
ggplot(df.acc.moral_bias_moral, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and moral categorization (moral effect)") +
    apatheme
#ggsave("p_corr_acc_moral1.eps", p_corr_acc_moral1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r correlation of moral-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_id <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Id_good_bad_slf)
df.acc.moral_bias_id <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Id_good_bad_slf")]
colnames(df.acc.moral_bias_id) <- c("ACC_moral_bias_match","ACC_moral_bias_id_categorization")
ggplot(df.acc.moral_bias_id, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and id categorization (moral effect)") +
    apatheme
# ggsave("p_corr_acc_moral2.eps", p_corr_acc_moral2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral2.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of self-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_moral <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Valence_slf_oth_good)
df.rt.self_bias_moral <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Valence_slf_oth_good")]
colnames(df.rt.self_bias_moral) <- c("RT_self_bias_match","RT_self_bias_moral_categorization")
ggplot(df.rt.self_bias_moral, aes(x=RT_self_bias_match, y=RT_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self1.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of self-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Id_slf_oth_good)
df.rt.self_bias_id <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Id_slf_oth_good")]
colnames(df.rt.self_bias_id) <- c("RT_self_bias_match","RT_self_bias_id_categorization")
ggplot(df.rt.self_bias_id, aes(x=RT_self_bias_match, y=RT_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between RT of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self2.eps", p_corr_RT_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self2.pdf",out.type="cairo", width=8, height=6)

```

```{r correlation of moral-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_val <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Valence_good_bad_slf)
df.rt.moral_bias_moral <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Valence_good_bad_slf")]
colnames(df.rt.moral_bias_moral) <- c("RT_moral_bias_match","RT_moral_bias_moral_categorization")
ggplot(df.rt.moral_bias_moral, aes(x=RT_moral_bias_match, y=RT_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral1.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of moral-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Id_good_bad_slf)
df.rt.moral_bias_id <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Id_good_bad_slf")]
colnames(df.rt.moral_bias_id) <- c("RT_moral_bias_match","RT_moral_bias_id_categorization")
ggplot(df.rt.moral_bias_id, aes(x=RT_moral_bias_match, y=RT_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and id categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral2.pdf",out.type="cairo", width=8, height=6)
```

### 2017-11-18 Modelling/HDDM/HDDM_Moral_Categ_sep_170303.py

@@ -1,0 +1,164 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Mar 03 21:26:49 2017
+
+@author: hcp47
+"""
+
+import os
+
+# get the current directory and change the cd
+os.getcwd()
+os.chdir("D:\HCP_cloud\Exp.s\Project1_Moral_reputation_learning\Exp_Behav_Moral_Asso\Exp_Behav_Moral_Asso_7_behav_modeling\Results\Formal_results\HDDM\FinalVersion")
+
+# get the tool box
+import pandas as pd
+import matplotlib.pyplot as plt
+# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
+import hddm
+import time
+
+# Load match data from csv file into a NumPy structured array
+dat_M_Categ_val = hddm.load_csv('data_Categ_hddm_val_task.csv')
+dat_M_Categ_val.head(10)
+
+# Load match data from csv file into a NumPy structured array
+dat_M_Categ_id = hddm.load_csv('data_Categ_hddm_ID_task.csv')
+dat_M_Categ_id.head(10)
+
+# flip the error RTs to be negative
+dat_M_Categ_val = hddm.utils.flip_errors(dat_M_Categ_val)
+dat_M_Categ_id = hddm.utils.flip_errors(dat_M_Categ_id)
+
+# check the RT distritubtion
+fig = plt.figure()
+ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
+for i, subj_data in dat_M_Categ_val.groupby('subj_idx'):
+    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+    
+fig = plt.figure()
+ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
+for i, subj_data in dat_M_Categ_id.groupby('subj_idx'):
+    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+
+
+    
+#### model 1 for valence based categorization, free v,t,z
+M_Categ_val_vtz = hddm.HDDM(dat_M_Categ_val,depends_on = {'v':['moral','id'],'z':['moral','id'],'t':['moral','id']}, include=['v', 'z', 't'],p_outlier=.05)
+M_Categ_val_vtz.find_starting_values()
+M_Categ_val_vtz.sample(10000,burn = 1000, dbname='traces_val_vtz.db', db='pickle')
+   
[…]

### 2017-11-18 Modelling/exGaussian/Ex_Gaussian_analysis_formal.R

@@ -1,0 +1,384 @@
+## This file is aimed at fitting the data collected by Moral_asso_behavioral_exp7 Using Ex-Gaussian Model
+#  Author     Date           History of change
+# ============================================
+#  Hcp     06/07/2016        Save rawData2 as the processed data
+#  hcp     06/07/2016        begin with saved csv data
+#  hcp     19/07/2016        only the code for final analysis
+#  hcp     20/02/2017        used for the final data
+#  hcp     08/04/2017        save to pdf
+
+# run summarySE, summarySEwithin, normDatawithin, and multiplot before running this script.
+Sys.setenv(LANG = "en") # set the feedback language to English
+options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+
+
+############## load and clear data ##########################
+# read data from 6 participants
+df.T.hddm <- read.csv("data_Categ_hddm.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) 
+df.T.hddm$moral[df.T.hddm$moral=='moral'] <- 'good' 
+df.T.hddm$moral[df.T.hddm$moral=='immoral'] <- 'bad'
+df.T_sum <- summarySEwithin(df.T.hddm,measurevar = 'rt',withinvars = c('subj_idx','crit','moral','id'),idvar = 'subj_idx')
+
+
+# render the numeric column
+cols.num <- c("rt","response")
+df.T.hddm[cols.num] <- sapply(df.T.hddm[cols.num], as.numeric)
+
+# check the class for each column
+sapply(df.T.hddm,class)
+
+rm(cols.num) # remove temporary variables
+
+#########################################################################################
+
+##################### begin analysis
+library(plyr)     # using plyr package
+library(ez)       # using ez package for ANOVA
+library(ggplot2)  # using ggplot2 for plot
+library(reshape2)
+library(retimes)
+
+
+##  extract the trials with correct response
+datT.validRT <- df.T.hddm[df.T.hddm$response == 1 & df.T.hddm$rt > 0.2,]  # RT > 200ms for accurate trials
+
+colnames(datT.validRT) <- c('SubjectID','Task','Morality','Identity','RT','ACC')
+
+## analyzing the distribution parameters for correct trials
+RTsubId <- unique(datT.validRT$SubjectID)
+RTtask <- unique(datT.validRT$Task)
[…]

### 2017-12-24 Traditional_Analysis/Analysis_exp7_2.rmd
try to ignore some
pull

@@
 
-pkgNeeded <- (c("ez","plyr","ggplot2", "reshape2", "MBESS", "bootES","BayesFactor","psych","corrplot"))
+pkgNeeded <- (c("tidyverse","plyr","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))
 
@@
 
-```{r loadingData_e7_L,echo=FALSE,results='hide'}
+```{r loadingData_e7,echo=FALSE,results='hide'}
 df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
@@
 
-```{r clean the data_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
 df.L1 <- df.L
@@
 The correlation of accuracy between matching task and categrization based on morality criteria
-```{r correlation of self-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr ACC_selfBias_between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
 acc.self_bias_moral <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Valence_slf_oth_good)
@@
 The correlation of accuracy between matching task and categrization based on identity criteria
-```{r correlation of self-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr ACC_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
 acc.self_bias_id <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Id_slf_oth_good)
@@
 The correlation of accuracy between matching task and categrization based on morality criteria
-```{r correlation of moral-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr ACC_valBais between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
 acc.moral_bias_moral <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Valence_good_bad_slf)
@@
 The correlation of accuracy between matching task and categrization based on identity criteria
-```{r correlation of moral-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr ACC_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
 acc.moral_bias_id <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Id_good_bad_slf)
@@
 
-```{r correlation of self-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr RT_selfBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
 rt.self_bias_moral <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Valence_slf_oth_good)
@@
 
-```{r correlation of self-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr RT_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
 rt.self_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Id_slf_oth_good)
@@
 
-```{r correlation of moral-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr RT_valBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
 rt.moral_bias_val <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Valence_good_bad_slf)
@@
 
-```{r correlation of moral-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
+```{r corr RT_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
 rt.moral_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Id_good_bad_slf)

### 2017-12-24 Modelling/exGaussian/Ex_Gaussian_analysis_formal.R
update ex-guassioni

@@ -7,10 +7,203 @@
 #  hcp     20/02/2017        used for the final data
 #  hcp     08/04/2017        save to pdf
 
-# run summarySE, summarySEwithin, normDatawithin, and multiplot before running this script.
-Sys.setenv(LANG = "en") # set the feedback language to English
-options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+#### This part of the code is preparation ####
+# defube the the system parameters 
+Sys.setenv(LANG = "en")              # set the feedback language to English
+options(scipen = 999)                # force R to output in decimal instead of scientifc notion
+windowsFonts(Times=windowsFont("TT Times New Roman"))  # explicit mapping to "times"
+
 rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+
+# define the d prime function
+dprime <- function(hit,fa) {
+        qnorm(hit) - qnorm(fa)
+}
+# define fuctions: summarySE, summarySEwithin, normDatawithin, and multiplot.
+## code for calculate the summary with sE, adopted from cook book for R
+summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
+                      conf.interval=.95, .drop=TRUE) {
+        library(plyr)
+        
+        # New version of length which can handle NA's : if na.rm == T, don't count the
+        length2 <- function(x, na.rm=FALSE){
+                if(na.rm) sum(!is.na(x))
+                else      length(x)
+        }
+        
+        # this does the summary. For each group's data frame, return a vector with
+        # N, mean, and sd
+        datac <- ddply(data,groupvars, .drop=.drop,
+                       .fun = function(xx,col){
+                               c(N    = length2(xx[[col]],na.rm=na.rm),
+                                 mean = mean(xx[[col]],na.rm=na.rm),
+                                 sd   = sd  (xx[[col]],na.rm=na.rm)
+                               )
+                       },
+                       measurevar
+        )
+        # Rename the "mean" column
+        
+        datac <- rename(datac,c("mean" = measurevar))
+        
+        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean
+        
+        # Confidence interval mltiplier for standard error
+        # calculate t-statistic for confidence interval:
+        # e.g., if conf.interval is .95, use .975 (above/below), and use df.L1 = N-1
+        ciMult <- qt(conf.interval/2 + .5, datac$N-1)
[…]

### 2017-12-24 Traditional_Analysis/Analysis_exp7_2.rmd
revise the rmarkdown file

@@
 ---
-title: "Analysis_exp7"
+title: "Data_Analysis_exp7"
 author: "hcp"
-date: "2016-10-28"
+date: "2017-12"
 output: word_document
@@
 
-pkgNeeded <- (c("tidyverse","plyr","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))
+pkgNeeded <- (c("plyr","tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))
 
@@
 ```{r loadingData_e7,echo=FALSE,results='hide'}
-df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
-df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
-# render the numeric column
+df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
+df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task
+
+# render the data in numeric format for future analysis
 cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
-# Tcols.num <- c("SubjectID","Age","Block","Bin","Trial","RT","Accuracy")
 df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)  
@@
 
+# rename columns
 colnames(df.L)[colnames(df.L)=="Accuracy"]  <- "ACC"
@@
 
+# Change the name for different levels of independent variables
 df.L$Morality[df.L$Morality == 'moral']   <- 'Good'
@@
 
-df.L$Morality <- factor(df.L$Morality, levels=c("Good","Bad")) # make the variables in a specified order
-df.L$Identity <- factor(df.L$Identity, levels=c("Self","Other")) # make the variables in a specified order
-df.L$Match <- factor(df.L$Match, levels=c("match","nonmatch")) # make the variables in a specified order
-
+# make the variables in a specified order
+df.L$Morality <- factor(df.L$Morality, levels = c("Good","Bad"))    
+df.L$Identity <- factor(df.L$Identity, levels = c("Self","Other"))  
+df.L$Match    <- factor(df.L$Match,    levels = c("match","nonmatch"))
+
+# Change the name for different levels of independent variables
 df.T$Morality[df.T$Morality == 'moral']   <- 'Good'
@@
 df.T$Task[df.T$Task == 'moral']           <- 'Valence_task'
-df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad")) # make the variables in a specified order
-df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other")) # make the variables in a specified order
+
+# make the variables in a specified order
+df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
+df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
 ```
@@
 df.T1 <- df.T
-df.L1$RT <- df.L1$RT*1000 # transfer from seconds to min seconds
+df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
 df.T1$RT <- df.T1$RT * 1000
@@
 
+# check the number of participants are correct
 length(unique(df.L1.valid$Subject)) + length(excld.sub) == length(unique(df.L1$Subject))
@@
 excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200,]
-df.L1.V <- df.L1.valid[!(df.L1.valid$RT <= 200),] 
+df.L1.V        <- df.L1.valid[!(df.L1.valid$RT <= 200),]  # valid trial data for match task
 excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200,]
-df.T1.V <- df.T1.valid[!(df.T1.valid$RT <= 200),] 
+df.T1.V        <- df.T1.valid[!(df.T1.valid$RT <= 200),]  # valid trial data for categorization task
 nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok
@@
 ```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
-# calculate the d prime for each condition
+## calculate the d prime for each condition
+# calculate the number of hit,CR,miss or FA 
 df.L1.V$sdt <- NA
@@
 df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
-df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0
+df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0 # transfer NA to 0
 df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)]     <- 0

### 2017-12-29 Traditional_Analysis/Analysis_exp7_2.rmd
re-check the code

@@
 #### Analaysis of d prime
-```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
+```{r analyzing for d prime_e7_L, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
 ## calculate the d prime for each condition
@@
 df.corr.bias_acc <- merge(df.L1.V.acc_w[,c(1,10:13)],df.T1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
+write.csv(df.corr.bias_acc,"df.corr.bias_acc.csv",row.names = F)
 df.corr.bias_acc <- df.corr.bias_acc[,2:13]
@@
 df.corr.bias_rt <- merge(df.L1.V.RT.subj_w[,c(1,10:13)],df.T1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
+write.csv(df.corr.bias_rt,"df.corr.bias_rt.csv",row.names = F)
 df.corr.bias_rt <- df.corr.bias_rt[,2:13]

### 2017-12-29 Modelling/HDDM/data_analysis_exp7_HDDM_categ_linux_final.py

@@ -2,14 +2,26 @@
 """
 Created on Fri Mar 03 21:26:49 2017
 
-@author: hcp47
+last reivsion: 29th Dec 2017
+
+@author: hcp4715
+"""
+
+"""
+Spyder Editor
+
+This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
+This experiment included two tasks: matching judgment and categorization.
+This script used for HDDM analysis of categorization task.
 """
 
 import os
 
 # get the current directory and change the cd
 os.getcwd()
-os.chdir("D:\HCP_cloud\Exp.s\Project1_Moral_reputation_learning\Exp_Behav_Moral_Asso\Exp_Behav_Moral_Asso_7_behav_modeling\Results\Formal_results\HDDM\FinalVersion")
+
+# change the current directory to the working directory
+os.chdir("/home/brain/host/hddm_exp7/")
 
 # get the tool box
 import pandas as pd
@@ -18,11 +30,14 @@ import matplotlib.pyplot as plt
 import hddm
 import time
 
-# Load match data from csv file into a NumPy structured array
+from cycler import cycler
+plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
+
+# load data from cateogriztion based on moral valence
 dat_M_Categ_val = hddm.load_csv('data_Categ_hddm_val_task.csv')
 dat_M_Categ_val.head(10)
 
-# Load match data from csv file into a NumPy structured array
+# load data from cateogriztion based on identity
 dat_M_Categ_id = hddm.load_csv('data_Categ_hddm_ID_task.csv')
 dat_M_Categ_id.head(10)
 
@@ -35,13 +50,16 @@ fig = plt.figure()
 ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
 for i, subj_data in dat_M_Categ_val.groupby('subj_idx'):
     subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+plt.savefig('plot_exp7_Categ_val_flipped.pdf')
     
 fig = plt.figure()
[…]

### 2017-12-30 Traditional_Analysis/Analysis_exp7_2.rmd
revise code again

@@
 
-lapply(pkgNeeded,pkgTest)
-rm(pkgNeeded)
-# using APA style plot
-# Save some time and stor APA format-related code in an object so you can easily
-# use it in multiple plots
+lapply(pkgNeeded,pkgTest) # please pay attention to the overlap between differen libraries.
+rm(pkgNeeded)             # remove the pkgNeeded variable
+
+# using APA style plot for later use
 windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
@@
 
-        datac <- rename(datac,c("mean" = measurevar))
+        datac <- plyr::rename(datac,c("mean" = measurevar))
 
@@
 df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
-df.T1$RT <- df.T1$RT * 1000
+df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian
 
@@
 #### Analaysis of d prime
-```{r analyzing for d prime_e7_L, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+```{r analyzing for d prime_e7_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
 ## calculate the d prime for each condition
@@
 
-# summary(aov(dprime ~ Morality*Identity + Error(Subject/(Morality*Identity)), data=df.L1.V.SDT_w))
-df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)
-e7_L.dprime_anova_bf = anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")
+df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)  # make the subject "factor"
+
+# using Bayesfactor analysis (which is not reported in the document)
+e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")
 
 # Good self vs Bad self
-e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)
-df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad
-e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d")
-
+e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
+df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad                   # calculate the differences
+e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES
+
+# give new names for each key information, for later use in the markdown
 e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
@@
 
-#####save the dprime and ACC data for late used####
+#####save the dprime and ACC data for late used ####
 colnames(df.L1.V.SDT_ww) <- paste("L_d", colnames(df.L1.V.SDT_ww), sep = "_")
@@
 write.csv(df.L1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
-#####
+##### save data for later analysis ####
 
@@
                       #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = .3,
+                      size = 1,
                       width = .2,
@@
         #theme_classic()
-        apatheme
+        apatheme  + 
+        theme(axis.text = element_text (size = 24,color = 'black')) + 
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad"))+
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 
@@
                       #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = .3,
+                      size = 1,
+                      width = .2,
+                      position=position_dodge(.6)) +
+        labs(x = 'Moral valence',y = 'd prime') +
+        ggtitle("d prime for each condition") +
+        coord_cartesian(ylim=c(1,3.5))+
+        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
+        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
+        apatheme + 
+        theme(axis.text = element_text (size = 24,color = 'black')) + 
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
+# save the plot to pdf file
+ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
+
+```
+ANOVA for *d'* with moral character and self-relatedness as within-subjects factors.
+
+The main effect of `r e7_L.d_anova[[1]][1,1]`, *F*(`r e7_L.d_anova[[1]][1,2]`, `r e7_L.d_anova[[1]][1,3]`) = `r round(e7_L.d_anova[[1]][1,4],3)`, *p* = `r round(e7_L.d_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][1,7],4)`, BF10 = r e7_L.dprime_anova_bf[1].
+
+The main effect of `r e7_L.d_anova[[1]][2,1]`: *F*(`r e7_L.d_anova[[1]][2,2]`, `r e7_L.d_anova[[1]][2,3]`) = `r round(e7_L.d_anova[[1]][2,4],3)`, *p* = `r round(e7_L.d_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][2,7],4)`,BF10 = r e7_L.dprime_anova_bf[2]
+
+The interaction between `r e7_L.d_anova[[1]][3,1]`: *F*(`r e7_L.d_anova[[1]][3,2]`, `r e7_L.d_anova[[1]][3,3]`) = `r round(e7_L.d_anova[[1]][3,4],3)`, *p* = `r round(e7_L.d_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][3,7],4)`, BF21 = r e7_L.dprime_anova_bf[4]/e7_L.dprime_anova_bf[3]
+
+Then we conducted post-hoc comparision:
+
+Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.L1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* =
+`r e7_L.d.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_slf`, 95% CI [`r e7_L.d.CI.L.good_bad_slf` `r e7_L.d.CI.H.good_bad_slf`]
+
+Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* =
+`r e7_L.d.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_oth`, 95% CI [`r e7_L.d.CI.L.good_bad_oth` `r e7_L.d.CI.H.good_bad_oth`]
+
+Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs.
+Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.L1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]
+
+Bad self (`r e7_L.d.mean.BadSelf` $\pm$ `r e7_L.d.sd.BadSelf`) vs.
+Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]
+
+```{r plot1 the d prime_e7_match, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
+ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
+        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
+        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
+        #geom_errorbar(aes(ymin = 1, ymax = 4),
+                      size = 1,     # width of the error bar
+                      width = .2,
+                      position=position_dodge(.6)) +
+        labs(x = 'self-referential',y = 'd prime') +
+        ggtitle("d prime for each condition") +
+        coord_cartesian(ylim=c(1,3.5))+
+        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
+        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
+        apatheme + 
+        theme(axis.text = element_text (size = 24,color = 'black')) + 
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad")) +
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
+
+```
+
+The above figure shows the d prime for each condition (way 1)
+
+```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
+ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
+        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
+        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
+        #geom_errorbar(aes(ymin = 1, ymax = 4),
+                      size = 1,
                       width = .2,
@@
         apatheme + 
-        theme(axis.text = element_text (size = 24)) + 
+        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
         theme(axis.title = element_text (size = 24)) + 
@@
 
-ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-# tiff(filename = "e7_L.p_dprime2.tiff", width = 8, height = 8, units = 'in', res = 300)
-# e7_L.p_dprime2
-# dev.off()
-
-```
-ANOVA for *d'* with moral character and self-relatedness as within-subjects factors.
-
-The main effect of `r e7_L.d_anova[[1]][1,1]`, *F*(`r e7_L.d_anova[[1]][1,2]`, `r e7_L.d_anova[[1]][1,3]`) = `r round(e7_L.d_anova[[1]][1,4],3)`, *p* = `r round(e7_L.d_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][1,7],4)`, BF10 = r e7_L.dprime_anova_bf[1].
-
-The main effect of `r e7_L.d_anova[[1]][2,1]`: *F*(`r e7_L.d_anova[[1]][2,2]`, `r e7_L.d_anova[[1]][2,3]`) = `r round(e7_L.d_anova[[1]][2,4],3)`, *p* = `r round(e7_L.d_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][2,7],4)`,BF10 = r e7_L.dprime_anova_bf[2]
-
-The interaction between `r e7_L.d_anova[[1]][3,1]`: *F*(`r e7_L.d_anova[[1]][3,2]`, `r e7_L.d_anova[[1]][3,3]`) = `r round(e7_L.d_anova[[1]][3,4],3)`, *p* = `r round(e7_L.d_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][3,7],4)`, BF21 = r e7_L.dprime_anova_bf[4]/e7_L.dprime_anova_bf[3]
-
-Then we conducted post-hoc comparision:
-
-Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.L1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* =
-`r e7_L.d.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_slf`, 95% CI [`r e7_L.d.CI.L.good_bad_slf` `r e7_L.d.CI.H.good_bad_slf`]
-
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* =
-`r e7_L.d.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_oth`, 95% CI [`r e7_L.d.CI.L.good_bad_oth` `r e7_L.d.CI.H.good_bad_oth`]
-
-Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs.
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.L1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]
-
-Bad self (`r e7_L.d.mean.BadSelf` $\pm$ `r e7_L.d.sd.BadSelf`) vs.
-Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]
-
-```{r plot1 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = .3,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'self-referential',y = 'd prime') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        apatheme
-
-# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
-```
-
-The above figure shows the d prime for each condition (way 1)
-
-```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = .3,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'd prime') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        apatheme
-
-# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
 ```
@@
 write.csv(df.L1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
-#### save the rt data ###
+#### save the rt data ####
 
@@
         geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
-                      size = .3,
+                      size = 1,
                       width = .2,
@@
         #scale_y_continuous("Reation Times (ms)") + 
-        apatheme
+        apatheme + 
+        theme(axis.text    = element_text(size = 24, color = 'black')) + 
+        theme(axis.title   = element_text(size = 24)) + 
+        theme(plot.title   = element_text(size = 24)) +
+        theme(legend.text  = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad")) +
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 
@@
         ggtitle("RT for each condition") +
-        #scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) +
         scale_y_continuous("Reation Times  (ms)",breaks = seq(500,800,50),expand = c(0, 0)) +
         apatheme + 
-        theme(axis.text = element_text (size = 24)) + 
+        theme(axis.text = element_text (size = 24, color = 'black')) + 
         theme(axis.title = element_text (size = 24)) + 
@@
 ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-#tiff(filename = "e7_L.p_rt2.tiff", width = 8, height = 8, units = 'in', res = 300)
-#e7_L.p_rt2
-#dev.off()
-
-#tiff(filename = "Figure exp7. d prime and RTs of Experiment 7 (way 2).tiff", width = 8, height = 6, units = 'in', res = 300)
-#multiplot(e7_L.p_dprime2,e7_L.p_rt2,cols = 2)
-#dev.off()
 
@@
         #scale_y_continuous("Reation Times (ms)") + 
-        apatheme
-#ggsave('RT_mean_plot2.png', width=4, height=6, unit='in', dpi=300)  # save the plot
+        apatheme + 
+        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad"))+
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 
@@
         scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
-        apatheme
-#ggsave('RT_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
+        apatheme + 
+        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 
@@
         #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = .3,
+                      size = 1,
                       width = .2,
@@
         apatheme +
-        theme(axis.text = element_text (size = 24)) + 
+        theme(axis.text = element_text (size = 24, color = 'black')) + 
         theme(axis.title = element_text (size = 24)) + 
@@
         theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
         scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
@@
         facet_grid(.~Task) + 
-        apatheme
-# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
+        apatheme  +
+        theme(axis.text = element_text (size = 24, color = 'black')) + 
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
+        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 ```
@@
 
-e7_T.rt_anova <- ezANOVA(df.T1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),within_full=.(Task,Identity,Morality), type=3)
-
-e7_T.rt_anova.Id_task <- ezANOVA(df.T1.V.RT_Id_task,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-
-e7_T.rt_anova.val_task <- ezANOVA(df.T1.V.RT_Val_task,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
+e7_T.rt_anova <- ezANOVA(df.T1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),
+                         within_full=.(Task,Identity,Morality), type=3)
+
+e7_T.rt_anova.Id_task <- ezANOVA(df.T1.V.RT_Id_task,dv = RT, wid = Subject, 
+                                 within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
+
+e7_T.rt_anova.val_task <- ezANOVA(df.T1.V.RT_Val_task,dv = RT, wid = Subject,
+                                  within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
 
@@
         scale_fill_manual(values=c("grey20", "grey80"),labels=c("id criteria    ","morality criteria")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
+        theme(strip.text.x = element_text(size = 16, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
         theme(axis.line.x = element_line(color="black", size = 1),
@@
 ggsave("RT_e7_T.pdf", RT_e7_T, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-# tiff(filename = "RT_e7_T.tiff", width = 8, height = 8, units = 'in', res = 300)
-# RT_e7_T
-# dev.off()
 
@@
 # combine data cross identity
-# tmp <- aggregate(df.T1.V.acc.subj[,7],list(df.T1.V.acc.subj$Subject,df.T1.V.acc.subj$Morality,df.T1.V.acc.subj$Identity),mean)
 df.T1.V.RT.subj.noID <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Task','Morality'))
@@
 e7_T.RT_anova_noID <- ezANOVA(df.T1.V.RT.subj.noID,dv = RT, wid = Subject, within=.(Task,Morality), type=3)
-# e7_T.acc_anova_noTask1 is exactly the same as in three way rm ANOVA
 
@@
         labs(x = 'Moral valence',y = 'Reaction times') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
         ggtitle("Reaction times for each condition") +
@@
         scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
         facet_grid(.~ Identity) + 
-        apatheme
-
-# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
+        apatheme +
+        theme(axis.text = element_text (size = 24, color = 'black')) + 
+        theme(axis.title = element_text (size = 24)) + 
+        theme(plot.title = element_text(size = 24)) +
+        theme(legend.text = element_text(size =24)) +
+        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
+        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
+        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Id_task  ","Moral_task")) +
+        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
+        theme(axis.line.x = element_line(color="black", size = 1),
+        axis.line.y = element_line(color="black", size = 1))
 ```

### 2018-05-18 preproc/Analysis_exp7_prepro_QC.rmd
add quality control rmd file

---
title: "Quality_Control_&_Preprocessing_for_Moral_Categ_Replication"
author: "hcp"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---
<style type="text/css">

body{ /* Normal  */
   font-family: Times     
   font-size: 12px;
}
td {  /* Table  */
   font-size: 8px;
}
h1 { /* Header 1 */
 font-size: 28px;
}
h2 { /* Header 2 */
 font-size: 22px;
}
h3 { /* Header 3 */
 font-size: 18px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 10px;
}
pre { /* Code block */
  font-size: 10px
}
</style>

This script is used for quality control and preprocessing of the replication data.

```{r Initializing, include=FALSE,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
source('Initial.r')

```

```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# get the file names for files contain "data_exp7_rep_match_"
fNames.m <- list.files(path = "./data/", pattern = "data_exp7_rep_match_*")
# add the directory information to the filenames
fNames.m <- paste('./data/',fNames.m, sep = '')

# read these files and combine them into one file, get the raw data for matching task
df.L    <- do.call("rbind",lapply(as.list(fNames.m),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))

# do the same to data from categorization, get the raw data for categorization task
fNames.c <- list.files(path = "./data/", pattern = "data_exp7_rep_categ_*")
fNames.c <- paste('./data/',fNames.c, sep = '')
df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))

# render the data in numeric format for future analysis
cols.num <- c('Sub',"Age","Block","Bin","Trial","RT","ACC")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)  
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)  
df.L <- df.L[!is.na(df.L$ACC),]
df.T <- df.T[!is.na(df.T$ACC),]

# get the independent varialbes
# moral valence
df.L$Morality[grepl("moral", df.L$Shape, fixed=TRUE)]   <- "Good"
df.L$Morality[grepl("immoral", df.L$Shape, fixed=TRUE)] <- "Bad"

# self-referential
df.L$Identity[grepl("Self", df.L$Shape, fixed=TRUE)]    <- "Self"
df.L$Identity[grepl("Other", df.L$Shape, fixed=TRUE)]   <- "Other"

df.T$Morality[grepl("moral", df.T$Shape, fixed=TRUE)]   <- "Good"
df.T$Morality[grepl("immoral", df.T$Shape, fixed=TRUE)] <- "Bad"

df.T$Identity[grepl("Self", df.T$Shape, fixed=TRUE)]    <- "Self"
df.T$Identity[grepl("Other", df.T$Shape, fixed=TRUE)]   <- "Other"

df.T$Task[df.T$Task == 'self']            <- 'Id'
df.T$Task[df.T$Task == 'moral']           <- 'Val'

# rename columns
colnames(df.L)[colnames(df.L)=="Sub"] <- "Subject"
colnames(df.T)[colnames(df.T)=="Sub"] <- "Subject"

# order the variables
df.L$Morality <- factor(df.L$Morality, levels = c("Good","Bad"))    
df.L$Identity <- factor(df.L$Identity, levels = c("Self","Other"))  
df.L$Match    <- factor(df.L$Match,    levels = c("match","mismatch"))

# make the variables in a specified order
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
```

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L[,c("Subject", "Age", "Sex", "Match", "Morality", "Identity", "ACC","RT")]
df.T1 <- df.T[,c("Subject", "Age", "Sex", "Task", "Morality", "Identity", "ACC","RT")]
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

# no response equal to wrong
 df.L1$ACC[df.L1$ACC != 1] <- 0
 df.T1$ACC[df.T1$ACC != 1] <- 0

# check the number of trials are correct
excldSub1_L <- c() # subject ID of those who failed matching task
excldSub1_T <- c() # subject ID of those who failed categorization task

df.L1.trials <-  plyr::ddply(df.L1,.(Subject, Match, Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC))
subjlistL <- unique(df.L1.trials$Subject)
for (ii in 1:length(subjlistL)){
  tmp <- subset(df.L1.trials,Subject == subjlistL[ii])
  if(sum(tmp$N != 75)){ # if the number of trials in matching task correct 
    excldSub1_L[ii] <- subjlistL[ii]
    print(paste0("ERROR: the trials number of subject ", subjlistL[ii] , 
                 " in matching task is not correct"))
}}

df.T1.trials <-  plyr::ddply(df.T1,.(Subject, Task, Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC))

subjlistT <- unique(df.T1.trials$Subject)
for (jj in 1:length(subjlistT)){
  tmp <- subset(df.T1.trials,Subject == subjlistT[jj])
  if(sum(tmp$N != 90)){ # if the number of trials in matching task correct 
    excldSub1_T[jj] <- subjlistT[jj]
    print(paste0("ERROR: the trials number of subject ", subjlistT[jj] , 
                 " in categ task is not correct"))
  }}

# get all the participants who were excluded:
excldSub1 <- c(excldSub1_L, excldSub1_T)
excldSub1 <- excldSub1[!duplicated(excldSub1)]

# df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
# df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]

# calculate the overall accuracy for matching task
df.L1.acc.g <-  plyr::ddply(df.L1,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

# calculate the overall accuracy for categorziation task
df.T1.acc.g <-  plyr::ddply(df.T1,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

excldSub2_L <- df.L1.acc.g$Subject[df.L1.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
excldSub2_T <- df.T1.acc.g$Subject[df.T1.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
excldSub2   <- c(excldSub2_L, excldSub2_T)
excldSub2 <- excldSub2[!duplicated(excldSub2)]   # invalid because of low overall accuracy

excldSub   <- c(excldSub1, excldSub2)
excldSub <- excldSub[!duplicated(excldSub)]   # total excluded

valdSub <- setdiff(subjlistL, excldSub)

df.L1.valid <- df.L1[!(df.L1$Subject %in% excldSub),]   # exclude the invalid subjects
df.T1.valid <- df.T1[!(df.T1$Subject %in% excldSub),]
# df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]

# check the number of participants are correct
length(valdSub) + length(excldSub) == length(unique(df.L1$Subject))

# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200 & df.L1.valid$ACC == 1,]
df.L1.V        <- df.L1.valid[!(df.L1.valid$RT <= 200 & df.L1.valid$ACC == 1),]  # valid trial data for match task
excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200 & df.T1.valid$ACC == 1,]
df.T1.V        <- df.T1.valid[!(df.T1.valid$RT <= 200 & df.T1.valid$ACC == 1),]  # valid trial data for categorization task
nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok

## Basic information of the data ####
df.L1.T.basic <- df.L1[!duplicated(df.L1$Subject), 2:5]
numT.subj     <- nrow(df.L1.T.basic)
numT.female   <- sum(df.L1.T.basic$Sex == 'female');
numT.male     <- sum(df.L1.T.basic$Sex == 'male');
ageT.mean     <- round(mean(df.L1.T.basic$Age),2);
ageT.std      <- round(sd(df.L1.T.basic$Age),2);
num.excld.sub <- length(unique(excldSub))
# num.excld.sub.T <- length(unique(excld.sub.T))

# valide data for matching task
df.L1.V.basic <- df.L1.V[!duplicated(df.L1.V$Subject), 2:5]
numV.female   <- sum(df.L1.V.basic$Sex == 'female');
numV.male     <- sum(df.L1.V.basic$Sex == 'male');
ageV.mean     <- round(mean(df.L1.V.basic$Age),2);
ageV.std      <- round(sd(df.L1.V.basic$Age),2);
ratio.excld.trials.L <- nrow(excld.trials.L)/nrow(df.L1.valid)
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)

# valid data for categorization task
df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 2:5]
numV.female.T <- sum(df.T1.V.basic$Sex == 'female');
numV.male.T <- sum(df.T1.V.basic$Sex == 'male');
ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
```
## Participants
Total participants: `r numT.subj` (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`)

Excluded because of wrong trials number:

matching task: `r excldSub1_L` ;

categ. task: `r excldSub1_T`;

total: `r excldSub1`.

Excluded because the overall accuracy is lower than 50%: 
matching task: `r excldSub2_L` ;

categ. task: `r excldSub2_T`;

total: `r excldSub2`.

Remaining participant: `r length(valdSub)` (`r valdSub`)

```{r preproc_match,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.L1.V.acc  <-  ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Morality + Identity,value.var = "ACC")

# rename the column number
colnames(df.L1.V.acc_w)[2:9] <- paste("ACC", colnames(df.L1.V.acc_w[,2:9]), sep = "_")

# d prime #### 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match"){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "mismatch"){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match"){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "mismatch"){
                df.L1.V$sdt[i] <- "FA"
        }
}

# calculate the number of each for each condition
df.L1.V.SDT <-  ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
                     N = length(sdt))

# long format to wide
df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Age + Sex+ Morality + Identity  ~ sdt,value.var = "N")
df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0
df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)] <- 0
df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)

# standardized way to deal with the extreme values
for (i in 1:nrow(df.L1.V.SDT_w)){
        if (df.L1.V.SDT_w$hitR[i] == 1){
                df.L1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.L1.V.SDT_w$hit[i] + df.L1.V.SDT_w$miss[i]))
        }
}

for (i in 1:nrow(df.L1.V.SDT_w)){
        if (df.L1.V.SDT_w$faR[i] == 0){
                df.L1.V.SDT_w$faR[i] <- 1/(2*(df.L1.V.SDT_w$FA[i] + df.L1.V.SDT_w$CR[i]))
        }
}

# calculate the d prime for each condition
df.L1.V.SDT_w$dprime <- mapply(dprime,df.L1.V.SDT_w$hitR,df.L1.V.SDT_w$faR)
df.L1.V.SDT_ww   <- dcast(df.L1.V.SDT_w, Subject + Sex + Age ~ Morality + Identity ,value.var = "dprime")

df.L1.V.SDT_l <- df.L1.V.SDT_w[,c(1:5,12)]

# rename the column number
colnames(df.L1.V.SDT_ww)[4:7] <- paste("d", colnames(df.L1.V.SDT_ww[,4:7]), sep = "_")

## doing the analysis for RT ####
df.L1.V.RT <- df.L1.V[df.L1.V$ACC == 1,]  # exclued inaccurate data
df.L1.V.RT.subj <- summarySEwithin(df.L1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
df.L1.V.RT.subj_w <- dcast(df.L1.V.RT.subj, Subject ~ Match + Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.L1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.L1.V.RT.subj_w[,2:9]), sep = "_")

## saving data ####
# merge the dprime and RT data and save
df.L1.V.sum_w <- merge(df.L1.V.acc_w,  df.L1.V.SDT_ww,by = "Subject")
df.L1.V.sum_w <- merge(df.L1.V.sum_w,df.L1.V.RT.subj_w,by = 'Subject')

# merge the RT and ACC data (long-format)
df.L1.V.sum_rt_acc_l <- merge(df.L1.V.acc,df.L1.V.RT.subj,by = c("Subject","Match","Morality",'Identity'))
df.L1.V.sum_rt_acc_l <- df.L1.V.sum_rt_acc_l[order(df.L1.V.sum_rt_acc_l$Subject),]

df.L1.V.sum_rt_acc_l <- df.L1.V.sum_rt_acc_l[,c("Subject","Match","Morality",'Identity',"N.x","countN","ACC","RT")]
colnames(df.L1.V.sum_rt_acc_l) <- c("Subject","Match","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")

# order the columns
df.L1.V.sum_w <- df.L1.V.sum_w[,c(colnames(df.L1.V.sum_w)[c(1,10:11,2:9,12:23)])]

# write files
setwd('..')
write.csv(df.L1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
write.csv(df.L1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
write.csv(df.L1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
setwd('./preproc')

```

```{r preproc_categ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
### ACC ####
df.T1.V.acc  <-  ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

df.T1.V.acc_w <- dcast(df.T1.V.acc, Subject ~ Task + Morality + Identity,value.var = "ACC")

# rename the column number
colnames(df.T1.V.acc_w)[2:9] <- paste("ACC", colnames(df.T1.V.acc_w[,2:9]), sep = "_")

## doing the analysis for RT ####
df.T1.V.RT <- df.T1.V[df.T1.V$ACC == 1,]  # exclued inaccurate data
df.T1.V.RT.subj <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
df.T1.V.RT.subj_w <- dcast(df.T1.V.RT.subj, Subject ~ Task + Morality + Identity ,value.var = "RT")

# rename the columns of RT data
colnames(df.T1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.T1.V.RT.subj_w[,2:9]), sep = "_")

## saving data ####
# merge the dprime and RT data and save
df.T1.V.sum_w <- merge(df.T1.V.acc_w,  df.T1.V.RT.subj_w,by = "Subject")

# merge the RT and ACC data (long-format)
df.T1.V.sum_rt_acc_l <- merge(df.T1.V.acc,df.T1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[order(df.T1.V.sum_rt_acc_l$Subject),]

df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[,c("Subject","Task","Morality",'Identity',"N.x","countN","ACC","RT")]
colnames(df.T1.V.sum_rt_acc_l) <- c("Subject","Task","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")

# order the columns
#df.T1.V.sum_w <- df.T1.V.sum_w[,c(colnames(df.T1.V.sum_w)[c(1,10:11,2:9,12:23)])]

# write files to an upper-lelel folder
setwd('..')
write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
setwd('./preproc')
```

```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}

df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
df.L1.V.sum_rt_acc_l_p$cond <- paste(df.L1.V.sum_rt_acc_l_p$Morality,df.L1.V.sum_rt_acc_l_p$Identity,sep = '_')
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l_p,Morality == 'Good')
ggplot(data=df.L1.V.sum_rt_acc_l_p, aes(x=cond, y=RT, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

# plot the d prime for good other and good self
# concatenate the conditions
df.L1.V.SDT_l$cond <- paste(df.L1.V.SDT_l$Morality,df.L1.V.SDT_l$Identity, sep = '_')
# select only the moral positive coniditions
df.L1.V.SDT_l_p <- df.L1.V.SDT_l[df.L1.V.SDT_l$Morality == 'Good',]
# plot 
ggplot(data=df.L1.V.SDT_l_p, aes(x=cond, y=dprime, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

```

### 2018-05-18 preproc/Initial.r
modified readme

@@ -1,0 +1,215 @@
+# this script is used for initializing the analysis
+# preparing necessary functions used in current analysis
+
+Sys.setlocale("LC_ALL", "English")  # set local encoding to English
+Sys.setenv(LANG = "en") # set the feedback language to English
+options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+options(digits=5)       # limit the number of reporting
+rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+
+pkgTest <- function(x)
+{
+        if (!require(x,character.only = TRUE))
+        {
+                install.packages(x,dep = TRUE)
+                if(!require(x,character.only = TRUE)) stop("Package not found")
+        }
+}
+
+pkgNeeded <- (c("tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", 
+                "BayesFactor","psych","corrplot",'plyr'))
+
+lapply(pkgNeeded,pkgTest)
+rm('pkgNeeded') # remove the variable 'pkgNeeded';
+
+# Save some time and stor APA format-related code in an object so you can easily
+# use it in multiple plots
+windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
+apatheme=theme_bw()+
+        theme(panel.grid.major = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.background = element_blank(),
+              panel.border = element_blank(),
+              text=element_text(family='Times'),
+              legend.title=element_blank(),
+              legend.text = element_text(size =20),
+              legend.position='top',
+              plot.title = element_text(size = 20),
+              axis.text = element_text (size = 20, color = 'black'),
+              axis.title = element_text (size = 20),
+              axis.title.y = element_text(margin=margin(0,20,0,0)),  # increase the space between title and y axis
+              axis.title.x = element_text(margin=margin(20,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.line.x = element_line(color='black', size = 1),   # increase the size of font
+              axis.line.y = element_line(color='black', size = 1))   # increase the size of font
+
+# define the d prime function
+dprime <- function(hit,fa) {
+        qnorm(hit) - qnorm(fa)
+}
+
+## below is the code from blog, and adapted from A C Del Re from email
+d.sgpp <- function(m.1,m.2,sd.1,sd.2,n,r=.5)
+{
+        # m.1 = mean at time 1
+        # m.2 = mean at time 2
+        # sd.1 = standard dev. at time 1
[…]

### 2018-06-06 preproc/Analysis_exp7_prepro.rmd
add preprocessing code

--- 2018-05-18 preproc/Analysis_exp7_prepro_QC.rmd
@@
 ---
-title: "Quality_Control_&_Preprocessing_for_Moral_Categ_Replication"
+title: "Preprocessing_&_Plot_for_Moral_Categ_Replication"
 author: "hcp"
@@
 ```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+# set the directories
+curDir <- getwd()   # directory for preprocessing
+rootDir <- gsub('.{7}$', '', curDir)
+rawDir <- paste(curDir,'/data/',sep = '')
+traDir <- paste(rootDir,'tradAnal',sep = '')
+ddmDir <- paste(rootDir,'hddmMod',sep = '')
+
 # get the file names for files contain "data_exp7_rep_match_"
-fNames.m <- list.files(path = "./data/", pattern = "data_exp7_rep_match_*")
+fNames.m <- list.files(path = rawDir, pattern = "data_exp7_rep_match_*")
 # add the directory information to the filenames
-fNames.m <- paste('./data/',fNames.m, sep = '')
+fNames.m <- paste(rawDir,fNames.m, sep = '')
 
@@
 # do the same to data from categorization, get the raw data for categorization task
-fNames.c <- list.files(path = "./data/", pattern = "data_exp7_rep_categ_*")
-fNames.c <- paste('./data/',fNames.c, sep = '')
+fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
+fNames.c <- paste(rawDir,fNames.c, sep = '')
 df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
@@
 ```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+
+# get the data file for hddm analysis
+df.L.hddm <- subset(df.L, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
+df.T.hddm <- subset(df.T, ACC ==1 | ACC == 0)
+
+df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
+df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
+colnames(df.L.hddm_m) <- c("subj_idx","Morality",'id','rt','response')     # change column name
+
+df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
+df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.L.hddm_nm) <- c("subj_idx","Morality",'id','rt','response')
+
+df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
+df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.T.hddm_val) <- c("subj_idx","Morality",'id','rt','response')
+df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
+df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.T.hddm_id) <- c("subj_idx","Morality",'id','rt','response')
+
+setwd(ddmDir)
+write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
+write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
+write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
+write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
+rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
+setwd(curDir)
+
+# clean data for trad. analysis
 df.L1 <- df.L[,c("Subject", "Age", "Sex", "Match", "Morality", "Identity", "ACC","RT")]
@@
 # write files
-setwd('..')
+setwd(traDir)
 write.csv(df.L1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
@@
 write.csv(df.L1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
-setwd('./preproc')
+setwd(curDir)
 
@@
 # write files to an upper-lelel folder
-setwd('..')
+setwd(traDir)
 write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
 write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
-setwd('./preproc')
+setwd(curDir)
+
 ```
@@
 ```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}
-
 df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
@@
 
+#ggstatsplot::ggbetweenstats(
+#  data = df.L1.V.sum_rt_acc_l_p,
+#  x = c(Morality,Identity),
+#  y = RT,
+#  notch = TRUE,                                   # show notched box plot
+#  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
+#  #type = "parametric",                            # which type of test is to be run
+#  outlier.tagging = FALSE,                         # whether outliers need to be tagged
+#  #outlier.label = RT,                    # variable to be used for the outlier tag
+#  xlab = "conditions",                       # label for the x-axis variable
+#  ylab = "Reaction time (ms)",               # label for the y-axis variable
+#  title = "Dataset: Iris flower data set",        # title text for the plot
+#  caption = expression(                           # caption text for the plot 
+#    paste(italic("Note"), ": this is a demo")
+#  ),
+#  messages = FALSE
+#) +                                               # further modification outside of ggstatsplot
+#  ggplot2::coord_cartesian(ylim = c(500, 800)) + 
+#  ggplot2::scale_y_continuous(breaks = seq(500, 800, by = 50)) 
 ```

### 2018-06-07 preproc/Analysis_exp7_prepro.rmd
fixed the code for gender information

@@
 df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
+
+# change all gender from number to string
+df.L$Sex[df.L$Sex == '1'] <- 'male'
+df.L$Sex[df.L$Sex == '2'] <- 'female'
+df.T$Sex[df.T$Sex == '1'] <- 'male'
+df.T$Sex[df.T$Sex == '2'] <- 'female'
 ```

### 2018-06-24 preproc/Initial.r
update hddm code

@@ -17,7 +17,7 @@ pkgTest <- function(x)
 }
 
 pkgNeeded <- (c("tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", 
-                "BayesFactor","psych","corrplot",'plyr'))
+                "BayesFactor","psych","corrplot",'plyr','ggstatsplot'))
 
 lapply(pkgNeeded,pkgTest)
 rm('pkgNeeded') # remove the variable 'pkgNeeded';
@@ -25,20 +25,20 @@ rm('pkgNeeded') # remove the variable 'pkgNeeded';
 # Save some time and stor APA format-related code in an object so you can easily
 # use it in multiple plots
 windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
-apatheme=theme_bw()+
+apatheme = theme_bw()+
         theme(panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               panel.background = element_blank(),
               panel.border = element_blank(),
               text=element_text(family='Times'),
               legend.title=element_blank(),
-              legend.text = element_text(size =20),
+              legend.text = element_text(size =16),
               legend.position='top',
-              plot.title = element_text(size = 20),
-              axis.text = element_text (size = 20, color = 'black'),
-              axis.title = element_text (size = 20),
-              axis.title.y = element_text(margin=margin(0,20,0,0)),  # increase the space between title and y axis
-              axis.title.x = element_text(margin=margin(20,0,0,0)),  # increase the sapce betwen title and x axis
+              plot.title = element_text(size = 16),
+              axis.text = element_text (size = 16, color = 'black'),
+              axis.title = element_text (size = 16),
+              axis.title.y = element_text(margin=margin(0,16,0,0)),  # increase the space between title and y axis
+              axis.title.x = element_text(margin=margin(16,0,0,0)),  # increase the sapce betwen title and x axis
               axis.line.x = element_line(color='black', size = 1),   # increase the size of font
               axis.line.y = element_line(color='black', size = 1))   # increase the size of font
 

### 2018-06-24 tradAnal/cross-task analysis.R

@@ -1,0 +1,96 @@
+library(tidyverse)
+setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
+# read data
+M_ACC_data <- read_csv("exp7_rep_match__dprime_long.csv") %>%
+  select(Subject,Morality,Identity,dprime) %>%
+  unite(Type,Morality,Identity) %>%
+  spread(key = Type, value = dprime) %>%
+  mutate("self-referential" = Good_Self - Good_Other, "valence" = Good_Self - Bad_Self)
+M_RT_data<- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
+  filter(Match == "match") %>%
+  select(Subject,Morality,Identity,RT) %>%
+  unite(Type,Morality,Identity) %>%
+  spread(key = Type, value = RT) %>%
+  mutate("self-referential" = Good_Self - Good_Other, "valence" = Good_Self - Bad_Self)
[…]

### 2018-06-24 Modelling/HDDM/data_analysis_exp7_HDDM_categ_linux_final.py
remove needless folder 1

@@ -1,309 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Fri Mar 03 21:26:49 2017
-
-last reivsion: 29th Dec 2017
-
-@author: hcp4715
-"""
-
-"""
-Spyder Editor
-
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks: matching judgment and categorization.
-This script used for HDDM analysis of categorization task.
-"""
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-
-# change the current directory to the working directory
-os.chdir("/home/brain/host/hddm_exp7/")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
-# load data from cateogriztion based on moral valence
-dat_M_Categ_val = hddm.load_csv('data_Categ_hddm_val_task.csv')
-dat_M_Categ_val.head(10)
-
-# load data from cateogriztion based on identity
-dat_M_Categ_id = hddm.load_csv('data_Categ_hddm_ID_task.csv')
-dat_M_Categ_id.head(10)
-
-# flip the error RTs to be negative
-dat_M_Categ_val = hddm.utils.flip_errors(dat_M_Categ_val)
-dat_M_Categ_id = hddm.utils.flip_errors(dat_M_Categ_id)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_M_Categ_val.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('plot_exp7_Categ_val_flipped.pdf')
-    
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
[…]

### 2018-06-24 Modelling/HDDM/data_analysis_exp7_HDDM_match_linux_final.py
remove

@@ -1,249 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Jul 13 21:55:21 2016
-
-@author: hcp4715
-
-Last revision: 29th Dec. 2017
-
-"""
-
-# -*- coding: utf-8 -*-
-"""
-Spyder Editor
-
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making.
-"""
-# %reset #this code will delete all the varibles in the memory
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-os.chdir("/home/brain/host/hddm_exp7/")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
-# Load match data from csv file into a NumPy structured array
-dat_M_match = hddm.load_csv('data_M_match_hddm.csv')
-dat_M_match.head(10)
-
-# flip the error RTs to be negative
-dat_M_match = hddm.utils.flip_errors(dat_M_match)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_M_match.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('plot_exp7_match_flipped.pdf')
-
-#### model 1, free v,t,z
-M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'t':['moral','id']}, include=['v', 'z', 't'],p_outlier=.05)
-M_match_vtz.find_starting_values()
-M_match_vtz.sample(10000,burn = 1000, dbname='traces_vtz.db', db='pickle')
-# save the model
-M_match_vtz.save('M_match_vtz')
-# M_match_vtz = hddm.load('M_match_vtz')
-
-# check convergence of MCMC  #### out put of gelman_rubin ######
-models_vtz = list()
[…]

### 2018-06-24 Modelling/exGaussian/Ex_Gaussian_analysis_formal.R

@@ -1,629 +1,0 @@
-## This file is aimed at fitting the data collected by Moral_asso_behavioral_exp7 Using Ex-Gaussian Model
-#  Author     Date           History of change
-# ============================================
-#  Hcp     06/07/2016        Save rawData2 as the processed data
-#  hcp     06/07/2016        begin with saved csv data
-#  hcp     19/07/2016        only the code for final analysis
-#  hcp     20/02/2017        used for the final data
-#  hcp     08/04/2017        save to pdf
-
-#### This part of the code is preparation ####
-# defube the the system parameters 
-Sys.setenv(LANG = "en")              # set the feedback language to English
-options(scipen = 999)                # force R to output in decimal instead of scientifc notion
-windowsFonts(Times=windowsFont("TT Times New Roman"))  # explicit mapping to "times"
-
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
-# define the d prime function
-dprime <- function(hit,fa) {
-        qnorm(hit) - qnorm(fa)
-}
-# define fuctions: summarySE, summarySEwithin, normDatawithin, and multiplot.
-## code for calculate the summary with sE, adopted from cook book for R
-summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
-                      conf.interval=.95, .drop=TRUE) {
-        library(plyr)
-        
-        # New version of length which can handle NA's : if na.rm == T, don't count the
-        length2 <- function(x, na.rm=FALSE){
-                if(na.rm) sum(!is.na(x))
-                else      length(x)
-        }
-        
-        # this does the summary. For each group's data frame, return a vector with
-        # N, mean, and sd
-        datac <- ddply(data,groupvars, .drop=.drop,
-                       .fun = function(xx,col){
-                               c(N    = length2(xx[[col]],na.rm=na.rm),
-                                 mean = mean(xx[[col]],na.rm=na.rm),
-                                 sd   = sd  (xx[[col]],na.rm=na.rm)
-                               )
-                       },
-                       measurevar
-        )
-        # Rename the "mean" column
-        
-        datac <- rename(datac,c("mean" = measurevar))
-        
-        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean
-        
-        # Confidence interval mltiplier for standard error
[…]

### 2018-06-24 exp7_rep_results/preproc/Analysis_exp7_QC.rmd
move files to exp7_rep_results

--- 2018-05-18 preproc/Analysis_exp7_prepro_QC.rmd
@@
 ---
-title: "Quality_Control_&_Preprocessing_for_Moral_Categ_Replication"
+title: "Quality_Control_for_Moral_Categ_Replication"
 author: "hcp"

### 2018-06-24 Procedure/procedure_final/Moral_self_asso_exp7_rep_MainProc.m
adjust folders

@@ -1,0 +1,123 @@
+function Moral_self_asso_exp7_rep_MainProc
+%%
+% History: Based on my previous stuy; 
+% 
+% Date         Author          Notes for change
+% =========================================================================
+% 17/12/2017   hcp4715         Start to modifying the code
+%
+% =========================================================================
+% Aim: Replicate my Experiment 7 of moral association, which dedicated for
+% categorization task.
+%
+% This is the main m file for the experiment, which refer to the following
+% scripts:
+% 1. Moral_self_asso_exp7_rep_subinfo_vf.m
+% 2. Moral_self_asso_exp7_rep_getParams.m
+% 3. Moral_self_asso_exp7_rep_match
+% 4. Moral_self_asso_exp7_rep_categ
+
+% Experimental design for the categorization task: 
+% 2 (id: self vs. other) * 3 (moral valence: postive, neutral, vs. negative) *
+% 2 categorization task(tasks type: morality, self)
+
+% Input variables:
+% subjects' ID, age, sex, and condition;
+
+% This experiment was aimed to replicate my previous studies, so that 
+% we can confirm our resulting patter. In this exp., we also have two phases:
+% First, Learning phase, in which participant making match judgmnet;
+% Second,Categorization phase, judge the category of stimuli according to
+% criteria.
+% 
+% Differences from exp7:
+% Items          replication    original
+% =============  =============  ==========
+% Moral valence  three levels    two levels
+% Categ. task    two tasks       three tasks
+% feedback       words           schema faces
+
+%% details about trials
+% trials for matching task
+% 500ms(fixation) + 100ms(target display) + blank(800-1100ms) +
+% 500ms(feedabkc)
+% one trial: 2,200ms
+
+% trials for categorization task: 
+% Fixation: 500ms + target display: 200ms + blank: 800-1200ms, No feedback
+
+% One trial: 1500-2100ms
+
+% Stimuli: 
+% 6 shapes in this Exp: 2( identity: self vs. other)*2( moral valence: positive, neutral vs. negative);
+
+% Moral Self(MS),   Neutral Self (NS),  Immoral Self (IS); 
+% Moral Other (MO), Neutral Other (NN), Immoral Other (IO);
+
+% Six labels in this Exp.;
[…]

### 2018-06-24 Procedure/procedure_final/Moral_self_asso_exp7_rep_getParams.m

@@ -1,0 +1,175 @@
+function params = Moral_self_asso_exp7_rep_getParams(subID)
+
+% function params = getParams
+% 
+% This function makes the struct that holds th parameters for the
+% presentation of the stimuli and such.
+%
+% progammer         Date               History of reivision
+% ==========      ===================  =====================
+% Hcp             2012/12/29            original code
+% hcp             2016/05/29            adjust for categorization task, not
+%                                       finished
+% hcp             2016/06/19            adjust for new balance design
+% hcp             2017/12/17            modified to repliation of exp7
+
+%% define the useful directory in this experiment
+params.rootDir = pwd;
+params.stimDir = [params.rootDir '\stimuli\'];  % the same set of stimuli were used.
+params.dataDir = [params.rootDir '\data\'];
+
+%% Set the experimental conditions
+% make counterbalance matrix
+% balance the shape
+balanceMatrix.moralSelf = repmat({'C','S','P','Tra','C','S','P','Tra'},[1,9]);
+balanceMatrix.immoralSelf = repmat({'S','P','Tra','C','S','P','Tra','C'},[1,9]);
+balanceMatrix.moralOther = repmat({'P','Tra','C','S','P','Tra','C','S',},[1,9]);
+balanceMatrix.immoralOther = repmat({'Tra','C','S','P','Tra','C','S','P'},[1,9]);
+
+% balance responding keys
+balanceMatrix.matchResp    = repmat({'N','N','N','N','M','M','M','M'},[1,9]);  % response for "match" trials in match tasks
+balanceMatrix.mismatchResp = repmat({'M','M','M','M','N','N','N','N'},[1,9]);  % response for "mismatch" trials in match tasks
+balanceMatrix.selfResp     = repmat({'H','J','J','J','H','H','H','J'},[1,9]);  % response for "self" trials in self-other categorization tasks
+balanceMatrix.otherResp    = repmat({'J','H','H','H','J','J','J','H'},[1,9]);  % response for "other" trials in self-other categorization  in match tasks
+balanceMatrix.moralResp    = repmat({'U','U','Y','Y','Y','U','U','U'},[1,9]);  % response for "moral" trials in self-other categorization 
[…]

### 2018-06-24 exp7_proc/Procedure/Moral_self_asso_exp7_rep_MainProc.m
adjust folder

@@ -1,123 +1,0 @@
-function Moral_self_asso_exp7_rep_MainProc
-%%
-% History: Based on my previous stuy; 
-% 
-% Date         Author          Notes for change
-% =========================================================================
-% 17/12/2017   hcp4715         Start to modifying the code
-%
-% =========================================================================
-% Aim: Replicate my Experiment 7 of moral association, which dedicated for
-% categorization task.
-%
-% This is the main m file for the experiment, which refer to the following
-% scripts:
-% 1. Moral_self_asso_exp7_rep_subinfo_vf.m
-% 2. Moral_self_asso_exp7_rep_getParams.m
-% 3. Moral_self_asso_exp7_rep_match
-% 4. Moral_self_asso_exp7_rep_categ
-
-% Experimental design for the categorization task: 
-% 2 (id: self vs. other) * 3 (moral valence: postive, neutral, vs. negative) *
-% 2 categorization task(tasks type: morality, self)
-
-% Input variables:
-% subjects' ID, age, sex, and condition;
-
-% This experiment was aimed to replicate my previous studies, so that 
-% we can confirm our resulting patter. In this exp., we also have two phases:
-% First, Learning phase, in which participant making match judgmnet;
-% Second,Categorization phase, judge the category of stimuli according to
-% criteria.
-% 
-% Differences from exp7:
-% Items          replication    original
-% =============  =============  ==========
-% Moral valence  three levels    two levels
-% Categ. task    two tasks       three tasks
-% feedback       words           schema faces
-
-%% details about trials
-% trials for matching task
-% 500ms(fixation) + 100ms(target display) + blank(800-1100ms) +
-% 500ms(feedabkc)
-% one trial: 2,200ms
-
-% trials for categorization task: 
-% Fixation: 500ms + target display: 200ms + blank: 800-1200ms, No feedback
-
-% One trial: 1500-2100ms
-
-% Stimuli: 
-% 6 shapes in this Exp: 2( identity: self vs. other)*2( moral valence: positive, neutral vs. negative);
-
-% Moral Self(MS),   Neutral Self (NS),  Immoral Self (IS); 
-% Moral Other (MO), Neutral Other (NN), Immoral Other (IO);
-
-% Six labels in this Exp.;
-% "好我","常我","坏我";"好人","常人","坏人"
[…]

### 2018-06-24 exp7_proc/Procedure/Moral_self_asso_exp7_rep_categ.m

@@ -1,411 +1,0 @@
-function Moral_self_asso_exp7_test_vf(subID,gender,age,handness,task,block,binNum)
-%%
-% History: Based on :LiuMinghui 2013, SelfLabelMatching; Guo Jichengsi 2013;
-% 
-% Date         Author          Notes for change
-% =========================================================================
-% 25/05/2016   hcp4715         modified the code for categorization tasks.
-% 28/05/2016   hcp4715         change the way to control the trial practice
-% 29/05/2016   hcp4715         change the way of counterbalance   
-% 29/05/2016   hcp4715         delete subject input in this script, cite
-% these variable from the other script.
-% 30/05/2016   hcp4715         delete other unneccessary code
-% 06/06/2016   hcp4715         add an input to decide important item before
-%                               task
-% 21/06/2016   hcp4715         delete feedback;
-% 04/07/2016   hcp4715         set small circle
-% =========================================================================
-% Aim: The learning phase is to make sure the pariticipants associate
-% between shapes and labels. each assoication had to be responded
-% correctlyh for 6 times in a row.
-
-% Experimental design: 
-% 2 (id: self vs. other) * 2 (moral valence: postive vs. negative) *
-% 3(tasks type: morality, self, or importance)
-
-% Input variables:
-% subjects' ID, age, sex, and condition;
-
-% Learning phase: matching task
-% Categorization phase: categorization; 120 trials for each block, 2 blocks
-% for each categorization task
-% One trials for task: 
-% Fixation: 500ms + target display: 200ms + blank: 800-1200ms, No feedback
-
-% One trial: 1500-2100ms
-
-% Stimuli: 
-% 4 shapes in this Exp: 2( identity: self vs. other)*2( moral valence: positive vs. negative);
-
-% Moral Self(MS), Immoral Self (IS); Moral Other (MO), Immoral Other (IO);
-
-% Four labels in this Exp.;
-% "好我","坏我";"好人","坏人"
-% Task：Categorization, Whether the shape presented belongs to one categories?
-
-% counterbalance between shape and label:
-%           "好我"     "坏我"    "好人"     "坏人"        M/S/Imp      Imm/Oth/Unim
-% ============================================================================
-% expGroup1: circle,   square,   pentagon,  trapezoid,  left        right
-% expGroup2: square,   pentagon, trapezoid, circle,     left        right
-% expGroup3: pentagon, trapezoid, circle,   square,     left        right
-% expGroup4: trapezoid, circle,   square,   pentagon,   left        right
[…]

### 2018-06-24 exp7_proc/Procedure/Moral_self_asso_exp7_rep_getParams.m

@@ -1,175 +1,0 @@
-function params = Moral_self_asso_exp7_rep_getParams(subID)
-
-% function params = getParams
-% 
-% This function makes the struct that holds th parameters for the
-% presentation of the stimuli and such.
-%
-% progammer         Date               History of reivision
-% ==========      ===================  =====================
-% Hcp             2012/12/29            original code
-% hcp             2016/05/29            adjust for categorization task, not
-%                                       finished
-% hcp             2016/06/19            adjust for new balance design
-% hcp             2017/12/17            modified to repliation of exp7
-
-%% define the useful directory in this experiment
-params.rootDir = pwd;
-params.stimDir = [params.rootDir '\stimuli\'];  % the same set of stimuli were used.
-params.dataDir = [params.rootDir '\data\'];
-
-%% Set the experimental conditions
-% make counterbalance matrix
-% balance the shape
-balanceMatrix.moralSelf = repmat({'C','S','P','Tra','C','S','P','Tra'},[1,9]);
-balanceMatrix.immoralSelf = repmat({'S','P','Tra','C','S','P','Tra','C'},[1,9]);
-balanceMatrix.moralOther = repmat({'P','Tra','C','S','P','Tra','C','S',},[1,9]);
-balanceMatrix.immoralOther = repmat({'Tra','C','S','P','Tra','C','S','P'},[1,9]);
-
-% balance responding keys
-balanceMatrix.matchResp    = repmat({'N','N','N','N','M','M','M','M'},[1,9]);  % response for "match" trials in match tasks
-balanceMatrix.mismatchResp = repmat({'M','M','M','M','N','N','N','N'},[1,9]);  % response for "mismatch" trials in match tasks
-balanceMatrix.selfResp     = repmat({'H','J','J','J','H','H','H','J'},[1,9]);  % response for "self" trials in self-other categorization tasks
-balanceMatrix.otherResp    = repmat({'J','H','H','H','J','J','J','H'},[1,9]);  % response for "other" trials in self-other categorization  in match tasks
-balanceMatrix.moralResp    = repmat({'U','U','Y','Y','Y','U','U','U'},[1,9]);  % response for "moral" trials in self-other categorization 
[…]

### 2018-06-24 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
adjust folders

--- 2018-06-07 preproc/Analysis_exp7_prepro.rmd
@@
 ```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-
 # get the data file for hddm analysis
@@
 df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
-colnames(df.L.hddm_m) <- c("subj_idx","Morality",'id','rt','response')     # change column name
+colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
 
@@
 df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.L.hddm_nm) <- c("subj_idx","Morality",'id','rt','response')
+colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')
 
@@
 df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_val) <- c("subj_idx","Morality",'id','rt','response')
+colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')
+
 df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
 df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_id) <- c("subj_idx","Morality",'id','rt','response')
+colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')
 
@@
 # get all the participants who were excluded:
-excldSub1 <- c(excldSub1_L, excldSub1_T)
+extraExcld <- c(7338)  # this participant didn't understand the instruction, one condition's Accuracy is 0
+excldSub1 <- c(excldSub1_L, excldSub1_T,extraExcld)
 excldSub1 <- excldSub1[!duplicated(excldSub1)]
@@
 ### ACC ####
-df.L1.V.acc  <-  ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
+df.L1.V.acc  <-  plyr::ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
                     N = length(ACC),
@@
 # calculate the number of each for each condition
-df.L1.V.SDT <-  ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
+df.L1.V.SDT <-  plyr::ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
                      N = length(sdt))
@@
 
+# calculate the effect of self-ref and valence
+df.L1.v.sum_eff_w <- df.L1.V.sum_w[,1:3]
+df.L1.v.sum_eff_w$d_Good_Self_Other <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Good_Other
+df.L1.v.sum_eff_w$d_Self_Good_Bad   <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Bad_Self
+
+df.L1.v.sum_eff_w$RT_Good_Self_Other <- df.L1.V.sum_w$RT_match_Good_Other -  df.L1.V.sum_w$RT_match_Good_Self
+df.L1.v.sum_eff_w$RT_Self_Good_Bad   <- df.L1.V.sum_w$RT_match_Bad_Self -  df.L1.V.sum_w$RT_match_Good_Self
+
 # write files
@@
 ### ACC ####
-df.T1.V.acc  <-  ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
+df.T1.V.acc  <-  plyr::ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
                     N = length(ACC),
@@
 
+# combing data from diff task for analyzing the interaction btw val and id
+df.T1.V.acc_noTask  <-  plyr::ddply(df.T1.V,.(Subject, Morality, Identity), summarise,
+                    N = length(ACC),
+                    countN = sum(ACC),
+                    ACC = sum(ACC)/length(ACC))
+
+df.T1.V.acc_noTask_w <- dcast(df.T1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")
+
+# rename the column number
+colnames(df.T1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.T1.V.acc_noTask_w[,2:5]), sep = "_")
+
 ## doing the analysis for RT ####
@@
 
+# combining data form different task for analyszing interaction of val and id
+df.T1.V.RT.subj_noTask <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.T1.V.RT.subj_noTask_w <- dcast(df.T1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")
+
+# rename the columns of RT data
+colnames(df.T1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.T1.V.RT.subj_noTask_w[,2:5]), sep = "_")
+
 ## saving data ####
-# merge the dprime and RT data and save
+# merge the accuracy and RT data and save
 df.T1.V.sum_w <- merge(df.T1.V.acc_w,  df.T1.V.RT.subj_w,by = "Subject")
+df.T1.V.sum_noTask_w <- merge(df.T1.V.acc_noTask_w,  df.T1.V.RT.subj_noTask_w,by = "Subject")
 
-# merge the RT and ACC data (long-format)
+## calculated effects ####
+# self-reference effect
+df.T1.V.sum_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
+df.T1.V.sum_w$RT_Val_Bad_selfEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Bad_Self
+df.T1.V.sum_w$RT_Id_Good_selfEffect  <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
+df.T1.V.sum_w$RT_Id_Bad_selfEffect   <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Self
+# valence effect
+df.T1.V.sum_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
+df.T1.V.sum_w$RT_Val_Other_valEffect <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Good_Other
+df.T1.V.sum_w$RT_Id_Self_valEffect   <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self
+df.T1.V.sum_w$RT_Id_Other_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Good_Other
+# task effect
+df.T1.V.sum_w$RT_Good_Self_taskEffect  <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Self
+df.T1.V.sum_w$RT_Bad_Self_taskEffect   <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Id_Bad_Self
+df.T1.V.sum_w$RT_Good_Other_taskEffect <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Other
+df.T1.V.sum_w$RT_Bad_Other_taskEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Other
+
+# calculate the effect of self-ref and valence
+df.T1.v.sum_eff_w <- data.frame(df.T1.V.sum_w[,c('Subject')])
+colnames(df.T1.v.sum_eff_w) <- 'Subject'
+df.T1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
+df.T1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
+df.T1.v.sum_eff_w$RT_Id_Good_selfEffect <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
+df.T1.v.sum_eff_w$RT_Id_Self_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self
+
+df.T1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.T1.V.sum_w$ACC_Val_Good_Other - df.T1.V.sum_w$ACC_Val_Good_Self
+df.T1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.T1.V.sum_w$ACC_Val_Bad_Self - df.T1.V.sum_w$ACC_Val_Good_Self
+df.T1.v.sum_eff_w$ACC_Id_Good_selfEffect <- df.T1.V.sum_w$ACC_Id_Good_Other - df.T1.V.sum_w$ACC_Id_Good_Self
+df.T1.v.sum_eff_w$ACC_Id_Self_valEffect  <- df.T1.V.sum_w$ACC_Id_Bad_Self - df.T1.V.sum_w$ACC_Id_Good_Self
+
+# merge the effect file
+df.v.sum_eff_all_w <- merge(df.L1.v.sum_eff_w,df.T1.v.sum_eff_w,by="Subject")
+
+# merge the RT and ACC data (long-format) ####
 df.T1.V.sum_rt_acc_l <- merge(df.T1.V.acc,df.T1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
@@
 write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
+write.csv(df.T1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
 write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
+write.csv(df.v.sum_eff_all_w,'exp7_cross_taskeffect_wide.csv',row.names = F)
 setwd(curDir)
-
 ```
 
-```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}
-df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
-df.L1.V.sum_rt_acc_l_p$cond <- paste(df.L1.V.sum_rt_acc_l_p$Morality,df.L1.V.sum_rt_acc_l_p$Identity,sep = '_')
-df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l_p,Morality == 'Good')
-ggplot(data=df.L1.V.sum_rt_acc_l_p, aes(x=cond, y=RT, group=Subject, colour=Subject)) +
-    geom_line() +
-    geom_point() +
-    apatheme
+```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
+RTdata1 <- df.L1.V.sum_rt_acc_l %>%
+  select(Subject,Match,Morality,Identity,RT) %>% 
+  filter(Match == "match" & Morality == "Good")
+RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
+                     xlab = "Good", ylab = "Reaction times (ms)",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2))
 
-# plot the d prime for good other and good self
-# concatenate the conditions
-df.L1.V.SDT_l$cond <- paste(df.L1.V.SDT_l$Morality,df.L1.V.SDT_l$Identity, sep = '_')
-# select only the moral positive coniditions
-df.L1.V.SDT_l_p <- df.L1.V.SDT_l[df.L1.V.SDT_l$Morality == 'Good',]
-# plot 
-ggplot(data=df.L1.V.SDT_l_p, aes(x=cond, y=dprime, group=Subject, colour=Subject)) +
-    geom_line() +
-    geom_point() +
-    apatheme
+RTdata2 <- df.L1.V.sum_rt_acc_l %>%
+  select(Subject,Match,Morality,Identity,RT) %>% 
+  filter(Match == "match" & Morality == "Bad")
+RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16),
+                                                             axis.text.x=element_text(size=14,color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+setwd(traDir)
+tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_rt_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+multiplot(p1,p2,cols = 2)
+```
 
-#ggstatsplot::ggbetweenstats(
-#  data = df.L1.V.sum_rt_acc_l_p,
-#  x = c(Morality,Identity),
-#  y = RT,
-#  notch = TRUE,                                   # show notched box plot
-#  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
-#  #type = "parametric",                            # which type of test is to be run
-#  outlier.tagging = FALSE,                         # whether outliers need to be tagged
-#  #outlier.label = RT,                    # variable to be used for the outlier tag
-#  xlab = "conditions",                       # label for the x-axis variable
-#  ylab = "Reaction time (ms)",               # label for the y-axis variable
-#  title = "Dataset: Iris flower data set",        # title text for the plot
-#  caption = expression(                           # caption text for the plot 
-#    paste(italic("Note"), ": this is a demo")
-#  ),
-#  messages = FALSE
-#) +                                               # further modification outside of ggstatsplot
-#  ggplot2::coord_cartesian(ylim = c(500, 800)) + 
-#  ggplot2::scale_y_continuous(breaks = seq(500, 800, by = 50)) 
+```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
+Ddata1 <- df.L1.V.SDT_l %>%
+  select(Subject,Morality,Identity,dprime) %>% 
+  filter(Morality == "Good")
+Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = Ddata1, x = Identity, y = dprime,  
+                     xlab = "Good", ylab = "d prime",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2))
+
+Ddata2 <- df.L1.V.SDT_l %>%
+  select(Subject,Morality,Identity,dprime) %>% 
+  filter(Morality == "Bad")
+Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = Ddata2, x = Identity, y = dprime,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16),
+                                                             axis.text.x=element_text(size=14,color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+p_dprime_match <- multiplot(p1,p2,cols = 2)
+# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
+setwd(traDir)
+tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_dprime_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+#multiplot(p1,p2,cols = 2)
 ```
+
+```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
+ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,ACC) %>% 
+  filter(Task == "Val"& Morality == 'Good')
+ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
+                     xlab = "Good", ylab = "Accuracy",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2))
+
+ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,ACC) %>% 
+  filter(Task == "Val"& Morality == 'Bad')
+ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16),
+                                                             axis.text.x=element_text(size=14,color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+setwd(traDir)
+tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_rt_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+multiplot(p1,p2,cols = 2)
+```
+
+```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
+ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,ACC) %>% 
+  filter(Task == "Id"& Morality == 'Good')
+ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
+                     xlab = "Good", ylab = "Accuracy",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2))
+
+ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,ACC) %>% 
+  filter(Task == "Id"& Morality == 'Bad')
+ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16),
+                                                             axis.text.x=element_text(size=14,color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+setwd(traDir)
+tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_rt_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+multiplot(p1,p2,cols = 2)
+```
+
+```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
+RTdata1 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,RT) %>% 
+  filter(Task == "Val"& Morality == 'Good')
+RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
+                     xlab = "Good", ylab = "Reaction times (ms)",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2))
+
+RTdata2 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,RT) %>% 
+  filter(Task == "Val"& Morality == 'Bad')
+RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16),
+                                                             axis.text.x=element_text(size=14,color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+setwd(traDir)
+tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_rt_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+multiplot(p1,p2,cols = 2)
+```
+
+```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
+RTdata1 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,RT) %>% 
+  filter(Task == "Id"& Morality == 'Good')
+RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
+                     xlab = "Good", ylab = "Reaction times (ms)",
+                     type = FALSE) + scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
+                     theme_classic() + theme(legend.position = "none",
+                                                             text=element_text(family='Times'),
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=16), 
+                                                             axis.title.y=element_text(size=16),
+                                                             axis.text.x=element_text(size=14, color = "black"),
+                                                             axis.text.y=element_text(size=14, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
+                                                             axis.ticks.y=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+                    #+ coord_cartesian(ylim=c(300,900))
+
+#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
+RTdata2 <- df.T1.V.sum_rt_acc_l %>%
+  select(Subject,Task,Morality,Identity,RT) %>% 
+  filter(Task == "Id"& Morality == 'Bad')
+RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
+                     xlab = "Bad", ylab = "",
+                     type = FALSE)+
+      scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
+      theme_classic() +
+      theme(legend.position = "none",text=element_text(family='Times'),
+                               axis.line.x=element_line(size=1.2),
+                               axis.title.x =element_text(size=16),
+                               axis.text.x=element_text(size=14,color = "black"),
+                               axis.ticks.x=element_line(size=1.2))
+
+setwd(traDir)
+tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+p_rt_match <- multiplot(p1,p2,cols = 2)
+dev.off()
+setwd(curDir)
+multiplot(p1,p2,cols = 2)
+```

### 2018-06-24 Replication/Procedure/exp7_rep_proc/Moral_self_asso_exp7_rep_MainProc.m

@@ -1,0 +1,156 @@
+ function Moral_self_asso_exp7_rep_MainProc
+%%
+% History: Based on my previous stuy; 
+% 
+% Date         Author          Notes for change
+% =========================================================================
+% 17/12/2017   hcp4715         Start to modifying the code
+% 06/02/2018   hcp4715         finished revision
+% 18/03/2018   hcp4715         fixed small bug for recording data
+% 27/03/2018   hcp4715         changed back to 2 * 2 design.
+% 05/04/2018   hcp4715         delete the unneccessary blank delay ITI
+% 02/05/2018   hcp4715         add flag to matchign task script for better
+% data recording
+% =========================================================================
+% Aim: Replicate my Experiment 7 of moral association, which dedicated for
+% categorization task.
+%
+% This is the main m file for the experiment, which refer to the following
+% scripts:
+% 1. Moral_self_asso_exp7_rep_subinfo.m
+% 2. Moral_self_asso_exp7_rep_getParams.m
+% 3. Moral_self_asso_exp7_rep_match
+% 4. Moral_self_asso_exp7_rep_categ
+%
+% Experimental design for the categorization task: 
+% 2 (id: self vs. other) * 2 (moral valence: postive vs. negative) *
+% 2 categorization task(tasks type: morality, self)
+%
+%  %%%%% Input variables %%%%%%%%
+% subjects' ID, age, sex, and condition;
+%
+%  %%%%% output file %%%%%%
+%  data_exp7_rep_subBalance_(subNo.).out   % this record counterbalance info
+%  data_exp7_rep_match_(subNo.).out        % record the matching task data
+%  data_exp7_rep_categ_(subNo.).out        % record the categorization
+%                                           results
+%  data_exp7_rep_match_prac_(subNo.).out   % record the data for practicing
+%
+% This experiment was aimed to replicate my previous studies, so that 
+% we can confirm our resulting patter. In this exp., we also have two phases:
+% First, Learning phase, in which participant making match judgmnet;
+% Second,Categorization phase, judge the category of stimuli according to
+% criteria.
+% 
+% Differences from exp7:
+% Items          replication    original
+% =============  =============  ==========
[…]

### 2018-06-24 Replication/Procedure/exp7_rep_proc/Moral_self_asso_exp7_rep_subinfo.m

@@ -1,0 +1,16 @@
+function [subID, age, gender, handness] = Moral_self_asso_exp7_rep_subinfo()
+while 1
+    prompt  = {'序号/participant ID:','性别/gender[male-男,femal-女]:','年龄/age：', '利手/handness[R/L]:'};
+    dlgTitle= 'Please input personal information';
+    lineNo  = 1;
+    defaultanswer={'1','female','22','R'};
+    info     = inputdlg(prompt,dlgTitle,lineNo,defaultanswer);
+    subID    = str2double(info{1});
+    gender   = info{2};
+    age      = str2double(info{3});
+    handness = info{4};
+     if isreal(subID) && isreal(age) && isreal(gender) && isreal(handness)
+       break;
+     end
+end
+return

### 2018-06-24 Replication/Results/data_analysis/hddmMod/data_analysis_exp7_HDDM_match_linux_final.py

@@ -1,0 +1,257 @@
+# -*- coding: utf-8 -*-
+"""
+Original code created on Wed Jul 13 21:55:21 2016
+
+@author: hcp4715
+
+Last revision: 29th Dec. 2017
+
+adapted to exp7_rep @ 12 Jun. 2018
+"""
+
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
+This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making.
+"""
+# %reset -s #this code will delete all the varibles in the memory
+
+import os
+
+# get the current directory and change the cd
+os.getcwd()
+os.chdir("/home/brain/host/hddm_exp7_rep/")
+
+# get the tool box
+import pandas as pd
+import matplotlib.pyplot as plt
+# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
+import hddm
+import time
+
+from cycler import cycler
+plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
+
+# Load match data from csv file into a NumPy structured array
+dat_M_match = hddm.load_csv('exp7_rep_match_hddm.csv')
+dat_M_match.head(10)
+
+# flip the error RTs to be negative
+dat_M_match = hddm.utils.flip_errors(dat_M_match)
+
+# check the RT distritubtion
+fig = plt.figure()
+ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
+for i, subj_data in dat_M_match.groupby('subj_idx'):
+    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+plt.savefig('p_exp7_rep_m_flipped.pdf')
+
+start_time = time.time() # the start time of the processing
+
+#### model 1, free v,t,z
+M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
+M_match_vtz.find_starting_values()
+M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
[…]

### 2018-06-24 Replication/Results/data_analysis/preproc/Initial.r

@@ -1,0 +1,215 @@
+# this script is used for initializing the analysis
+# preparing necessary functions used in current analysis
+
+Sys.setlocale("LC_ALL", "English")  # set local encoding to English
+Sys.setenv(LANG = "en") # set the feedback language to English
+options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+options(digits=5)       # limit the number of reporting
+rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+
+pkgTest <- function(x)
+{
+        if (!require(x,character.only = TRUE))
+        {
+                install.packages(x,dep = TRUE)
+                if(!require(x,character.only = TRUE)) stop("Package not found")
+        }
+}
+
+pkgNeeded <- (c("tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", 
+                "BayesFactor","psych","corrplot",'plyr','ggstatsplot'))
+
+lapply(pkgNeeded,pkgTest)
+rm('pkgNeeded') # remove the variable 'pkgNeeded';
+
+# Save some time and stor APA format-related code in an object so you can easily
+# use it in multiple plots
+windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
+apatheme = theme_bw()+
+        theme(panel.grid.major = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.background = element_blank(),
+              panel.border = element_blank(),
+              text=element_text(family='Times'),
+              legend.title=element_blank(),
+              legend.text = element_text(size =16),
+              legend.position='top',
+              plot.title = element_text(size = 16),
+              axis.text = element_text (size = 16, color = 'black'),
+              axis.title = element_text (size = 16),
+              axis.title.y = element_text(margin=margin(0,16,0,0)),  # increase the space between title and y axis
+              axis.title.x = element_text(margin=margin(16,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.line.x = element_line(color='black', size = 1),   # increase the size of font
+              axis.line.y = element_line(color='black', size = 1))   # increase the size of font
+
+# define the d prime function
+dprime <- function(hit,fa) {
+        qnorm(hit) - qnorm(fa)
+}
+
+## below is the code from blog, and adapted from A C Del Re from email
+d.sgpp <- function(m.1,m.2,sd.1,sd.2,n,r=.5)
+{
+        # m.1 = mean at time 1
+        # m.2 = mean at time 2
[…]

### 2018-06-24 Replication/Results/data_analysis/tradAnal/match_accuracy_violin.R

@@ -1,0 +1,73 @@
+library(tidyverse)
+library(ggstatsplot)
+setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+ACCdata1 <- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
+  select(Subject,Match,Morality,Identity,ACC) %>% 
+  filter(Match == "match" & Morality == "Good")
+ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = ACCdata1, 
+                     x = Identity, 
+                     y = ACC,  
+                     xlab = "Good", 
+                     ylab = "Accuracy",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=14), 
+                                                             axis.title.y=element_text(size=14),
+                                                             axis.text.x=element_text(size=12, color = "black"),
+                                                             axis.text.y=element_text(size=12, color = "black"),
[…]

### 2018-06-24 Replication/Results/data_analysis/tradAnal/match_dprime_violin.R

@@ -1,0 +1,73 @@
+library(tidyverse)
+library(ggstatsplot)
+setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+dprimedata1 <- read_csv("exp7_rep_match__dprime_long.csv") %>%
+  select(Subject,Morality,Identity,dprime) %>% 
+  filter(Morality == "Good")
+dprimedata1$Identity <- factor(dprimedata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = dprimedata1, 
+                     x = Identity, 
+                     y = dprime,  
+                     xlab = "Good", 
+                     ylab = "dprime",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=14), 
+                                                             axis.title.y=element_text(size=14),
+                                                             axis.text.x=element_text(size=12, color = "black"),
+                                                             axis.text.y=element_text(size=12, color = "black"),
+                                                             axis.ticks.x=element_line(size=1.2),
[…]

### 2018-06-24 Replication/Results/data_analysis/tradAnal/match_rt_violin.R

@@ -1,0 +1,77 @@
+# to plot the RT from matched trials
+# by Yuxuan Lan
+# 2018.06.09
+
+library(tidyverse)
+library(ggstatsplot)
+setwd("D:\\HCP_cloud\\Exps\\P1_Pos_Self\\Exp_Behav_Moral_Asso\\Exp_7_model_categ\\Replication\\Results\\data_analysis\\tradAnal")
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+RTdata1 <- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
+  select(Subject,Match,Morality,Identity,RT) %>% 
+  filter(Match == "match" & Morality == "Good")
+RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
+p1 <- ggbetweenstats(data = RTdata1, 
+                     x = Identity, 
+                     y = RT,  
+                     xlab = "Good", 
+                     ylab = "Reaction times(ms)",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.line.y=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=14), 
[…]

### 2018-06-24 Replication/exp7_rep_proc/Moral_self_asso_exp7_rep_categ.m

@@ -1,337 +1,0 @@
-function Moral_self_asso_exp7_rep_categ(subID,gender,age,handness,task,block,binNum)
-%%
-% History: Based on :LiuMinghui 2013, SelfLabelMatching; Guo Jichengsi 2013;
-% 
-% Date         Author          Notes for change
-% =========================================================================
-% 04/Jan/2018   hcp4715         changed for replication study
-% 07/Jan/2018   hcp4715         changed code for response
-% 04/Apr/2018   hcp4715         change back to 2 * 2 design
-% 05/Apr/2018   hcp4715         delete the unneccessary blank delay ITI
-%
-% =========================================================================
-%
-% Experimental design: 
-% 2 (id: self vs. other) * 2 (moral valence: postive vs. negative) *
-% 2 (tasks type: morality, self)
-%
-% Input variables:
-% subjects' ID, age, handness, sex, task type, number of blocks and number of bins;
-%
-% This task will follow the matching task, and also be interweaved with small block of matching task
-%
-% Categorization phase: categorization; 120 trials for each block,3 blocks
-% for each categorization task
-% One trials for task: 
-% Fixation: 500ms + target display: 100ms + blank: 800-1200ms, No feedback
-%
-% One trial: 1500 - 2100ms
-%
-% Stimuli: 
-% 6 shapes in this Exp: 2( identity: self vs. other) * 2( moral valence: positive vs. negative);
-%
-% Moral Self (MS),   Immoral Self (IS); 
-% Moral Other (MO),  Immoral Other (IO);
-%
-% Six labels in this Exp.;
-% "好我", "坏我";
-% "好人", "坏人"
-% Task：Categorization, Whether the shape presented belongs to one categories?
-%
-% counterbalance between shape and label:
-%           "好我"     "坏我"    "好人"     "坏人"     M/S/moral  Mism/Oth/imm
-% ============================================================================
-% expGroup1: circle,   square,   pentagon,  trapezoid,  left        right
-% expGroup2: square,   pentagon, trapezoid, circle,     left        right
-% expGroup3: pentagon, trapezoid, circle,   square,     left        right
-% expGroup4: trapezoid, circle,   square,   pentagon,   left        right
-% expGroup5: circle,   square,   pentagon,  trapezoid,  right       left
-% expGroup6: square,   pentagon, trapezoid, circle,     right       left
-% expGroup7: pentagon, trapezoid, circle,   square,     right       left
-% expGroup8: trapezoid, circle,   square,   pentagon,   right       left
[…]

### 2018-06-24 Replication/exp7_rep_proc/Moral_self_asso_exp7_rep_match.m

@@ -1,346 +1,0 @@
-function Moral_self_asso_exp7_rep_match(subID,gender,age,handness,numOfBlock,binNum,flag)
-%% Information about this script
-% History: Based on :LiuMinghui 2013, SelfLabelMatching; Guo Jichengsi 2013;
-% 
-% Date         Author          Notes for change
-% =========================================================================
-% 2017/12/19   hcp4715         modified for replication of exp7
-% 2018/01/03   hcp4715         save practice data separately;
-%                              save shape and label, instead of identity
-%                              and moral valence separately, to avoid time
-%                              consumed during the proceduring running.
-% 2018/03/27   hcp4715         change to 2*2 design              
-%% Information about the task
-% =========================================================================
-% Aim: The learning phase is to make sure the pariticipants associate
-% between shapes and labels. each assoication had to be responded
-% correctly for 6 times in a row.
-%
-% Experimental design for matching task: 
-% 2 (matchness: match v. nonmatch) * 2 (id: self vs. other) * 2 (moral valence: postive vs. negative)
-% Therefore: 12 conditions
-%
-% Input variables:
-% subjects' ID, age, sex, and condition;
-%
-% Learning phase: matching task
-% Categorization phase: categorization task
-%
-% One trials for matching task: 
-% Fixation: 500ms + target display: 100ms + blank: 800-1200ms, No feedback
-%
-% One trial: 1500-2100ms
-%
-% Stimuli: 
-% 4 shapes in this Exp: 2(identity: self vs. other)* 3( moral valence: positive vs. negative);
-%
-% Moral Self (MS),   Immoral Self (IS); 
-% Moral Other (MO),  Immoral Other (IO);
-%
-% Six labels in this Exp.;
-% "好我","坏我";"好人","坏人"
-% Task：Whether the shape presented match?
-%
-%% counterbalance between shape and label (matched with "Moral_self_asso_exp7_rep_getParams.m" ):
-% counterbalance between shape and label:
-%           "好我"     "坏我"    "好人"     "坏人"     M/S/moral  Mism/Oth/imm
-% ============================================================================
-% expGroup1: circle,   square,   pentagon,  trapezoid,  left        right
-% expGroup2: square,   pentagon, trapezoid, circle,     left        right
-% expGroup3: pentagon, trapezoid, circle,   square,     left        right
-% expGroup4: trapezoid, circle,   square,   pentagon,   left        right
-% expGroup5: circle,   square,   pentagon,  trapezoid,  right       left
[…]

### 2018-06-24 Replication/exp7_rep_proc/Moral_self_asso_exp7_rep_subinfo.m

@@ -1,16 +1,0 @@
-function [subID, age, gender, handness] = Moral_self_asso_exp7_rep_subinfo()
-while 1
-    prompt  = {'序号/participant ID:','性别/gender[male-男,femal-女]:','年龄/age：', '利手/handness[R/L]:'};
-    dlgTitle= 'Please input personal information';
-    lineNo  = 1;
-    defaultanswer={'1','female','22','R'};
-    info     = inputdlg(prompt,dlgTitle,lineNo,defaultanswer);
-    subID    = str2double(info{1});
-    gender   = info{2};
-    age      = str2double(info{3});
-    handness = info{4};
-     if isreal(subID) && isreal(age) && isreal(gender) && isreal(handness)
-       break;
-     end
-end
-return

### 2018-06-24 Replication/exp7_rep_results/hddmMod/HDDM_exp7_rep_id_linux_final.py

@@ -1,167 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Jul 13 21:55:21 2016
-
-@author: hcp4715
-
-Last revision:18. Jun. 2018
-
-"""
-
-# -*- coding: utf-8 -*-
-"""
-This script is used for HDDM analysis of the id-based categorization task in replication study.
-"""
-# %reset #this code will delete all the varibles in the memory
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-os.chdir("/home/brain/host/hddm_exp7_rep/")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
-# Load match data from csv file into a NumPy structured array
-dat_C_Id = hddm.load_csv('exp7_rep_categ_id_hddm.csv')
-dat_C_Id.head(10)
-
-# flip the error RTs to be negative
-dat_C_Id = hddm.utils.flip_errors(dat_C_Id)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_C_Id.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('p_exp7_rep_Id_flipped.pdf')
-
-start_time = time.time() # the start time of the processing
-
-#### model 1, free v,t,z
-C_Id_vtz = hddm.HDDM(dat_C_Id,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
-C_Id_vtz.find_starting_values()
-C_Id_vtz.sample(10000,burn = 1000, dbname='traces_id_vtz.db', db='pickle')
-# save the model
-C_Id_vtz.save('C_Id_vtz')
-# C_Id_vtz = hddm.load('C_Id_vtz')
-
[…]

### 2018-06-24 Replication/exp7_rep_results/hddmMod/HDDM_exp7_rep_val_linux_final.py

@@ -1,177 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Fri Mar 03 21:26:49 2017
-
-last reivsion: 29th Dec 2017
-
-@author: hcp4715
-"""
-
-"""
-Spyder Editor
-
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks: matching judgment and categorization.
-This script used for HDDM analysis of categorization task.
-"""
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-
-# change the current directory to the working directory
-os.chdir("/home/brain/host/hddm_exp7_rep/")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
-# load data from cateogriztion based on moral valence
-dat_C_val = hddm.load_csv('exp7_rep_categ_val_hddm.csv')
-dat_C_val.head(10)
-
-# flip the error RTs to be negative
-dat_C_val = hddm.utils.flip_errors(dat_C_val)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_C_val.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('p_exp7_exp_val_flipped.pdf')
-    
-start_time = time.time() # the start time of the processing
-    
-#### model 1 for valence based categorization, free v,t,z
-C_val_vtz = hddm.HDDM(dat_C_val,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
-C_val_vtz.find_starting_values()
[…]

### 2018-06-24 Replication/exp7_rep_results/hddmMod/data_analysis_exp7_HDDM_match_linux_final.py

@@ -1,257 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Original code created on Wed Jul 13 21:55:21 2016
-
-@author: hcp4715
-
-Last revision: 29th Dec. 2017
-
-adapted to exp7_rep @ 12 Jun. 2018
-"""
-
-# -*- coding: utf-8 -*-
-"""
-Spyder Editor
-
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making.
-"""
-# %reset -s #this code will delete all the varibles in the memory
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-os.chdir("/home/brain/host/hddm_exp7_rep/")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
-# Load match data from csv file into a NumPy structured array
-dat_M_match = hddm.load_csv('exp7_rep_match_hddm.csv')
-dat_M_match.head(10)
-
-# flip the error RTs to be negative
-dat_M_match = hddm.utils.flip_errors(dat_M_match)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_M_match.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('p_exp7_rep_m_flipped.pdf')
-
-start_time = time.time() # the start time of the processing
-
-#### model 1, free v,t,z
-M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
-M_match_vtz.find_starting_values()
-M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
[…]

### 2018-06-24 Replication/exp7_rep_results/preproc/Initial.r

@@ -1,215 +1,0 @@
-# this script is used for initializing the analysis
-# preparing necessary functions used in current analysis
-
-Sys.setlocale("LC_ALL", "English")  # set local encoding to English
-Sys.setenv(LANG = "en") # set the feedback language to English
-options(scipen = 999)   # force R to output in decimal instead of scientifc notion
-options(digits=5)       # limit the number of reporting
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
-pkgTest <- function(x)
-{
-        if (!require(x,character.only = TRUE))
-        {
-                install.packages(x,dep = TRUE)
-                if(!require(x,character.only = TRUE)) stop("Package not found")
-        }
-}
-
-pkgNeeded <- (c("tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", 
-                "BayesFactor","psych","corrplot",'plyr','ggstatsplot'))
-
-lapply(pkgNeeded,pkgTest)
-rm('pkgNeeded') # remove the variable 'pkgNeeded';
-
-# Save some time and stor APA format-related code in an object so you can easily
-# use it in multiple plots
-windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
-apatheme = theme_bw()+
-        theme(panel.grid.major = element_blank(),
-              panel.grid.minor = element_blank(),
-              panel.background = element_blank(),
-              panel.border = element_blank(),
-              text=element_text(family='Times'),
-              legend.title=element_blank(),
-              legend.text = element_text(size =16),
-              legend.position='top',
-              plot.title = element_text(size = 16),
-              axis.text = element_text (size = 16, color = 'black'),
-              axis.title = element_text (size = 16),
-              axis.title.y = element_text(margin=margin(0,16,0,0)),  # increase the space between title and y axis
-              axis.title.x = element_text(margin=margin(16,0,0,0)),  # increase the sapce betwen title and x axis
-              axis.line.x = element_line(color='black', size = 1),   # increase the size of font
-              axis.line.y = element_line(color='black', size = 1))   # increase the size of font
-
-# define the d prime function
-dprime <- function(hit,fa) {
-        qnorm(hit) - qnorm(fa)
-}
-
-## below is the code from blog, and adapted from A C Del Re from email
-d.sgpp <- function(m.1,m.2,sd.1,sd.2,n,r=.5)
-{
-        # m.1 = mean at time 1
-        # m.2 = mean at time 2
[…]

### 2018-06-24 Replication/exp7_rep_results/tradAnal/match_accuracy_violin.R

@@ -1,73 +1,0 @@
-library(tidyverse)
-library(ggstatsplot)
-setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-  
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-  
-  numPlots = length(plots)
-  
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                     ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-  
-  if (numPlots==1) {
-    print(plots[[1]])
-    
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-    
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-      
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-ACCdata1 <- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
-  select(Subject,Match,Morality,Identity,ACC) %>% 
-  filter(Match == "match" & Morality == "Good")
-ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = ACCdata1, 
-                     x = Identity, 
-                     y = ACC,  
-                     xlab = "Good", 
-                     ylab = "Accuracy",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=14), 
-                                                             axis.title.y=element_text(size=14),
-                                                             axis.text.x=element_text(size=12, color = "black"),
-                                                             axis.text.y=element_text(size=12, color = "black"),
[…]

### 2018-06-24 Replication/exp7_rep_results/tradAnal/match_dprime_violin.R

@@ -1,73 +1,0 @@
-library(tidyverse)
-library(ggstatsplot)
-setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-  
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-  
-  numPlots = length(plots)
-  
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                     ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-  
-  if (numPlots==1) {
-    print(plots[[1]])
-    
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-    
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-      
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-dprimedata1 <- read_csv("exp7_rep_match__dprime_long.csv") %>%
-  select(Subject,Morality,Identity,dprime) %>% 
-  filter(Morality == "Good")
-dprimedata1$Identity <- factor(dprimedata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = dprimedata1, 
-                     x = Identity, 
-                     y = dprime,  
-                     xlab = "Good", 
-                     ylab = "dprime",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=14), 
-                                                             axis.title.y=element_text(size=14),
-                                                             axis.text.x=element_text(size=12, color = "black"),
-                                                             axis.text.y=element_text(size=12, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
[…]

### 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
raincloud plot

@@
 RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
-                     xlab = "Good", ylab = "Reaction times (ms)",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2))
-
+p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
 RTdata2 <- df.L1.V.sum_rt_acc_l %>%
@@
 RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
-                     xlab = "Bad", ylab = "",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16),
-                                                             axis.text.x=element_text(size=14,color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
+
 setwd(traDir)
@@
 Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = Ddata1, x = Identity, y = dprime,  
-                     xlab = "Good", ylab = "d prime",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2))
-
+p1 <- ggplot(data = Ddata1, aes(y = dprime, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(0,4))+labs(x = "Good",y = "dprime")
 Ddata2 <- df.L1.V.SDT_l %>%
@@
 Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggbetweenstats(data = Ddata2, x = Identity, y = dprime,  
-                     xlab = "Bad", ylab = "",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16),
-                                                             axis.text.x=element_text(size=14,color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+p2 <- ggplot(data = Ddata2, aes(y = dprime, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(0,4),breaks = NULL)+labs(x = "Bad",y = "")
 p_dprime_match <- multiplot(p1,p2,cols = 2)
@@
 ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
-                     xlab = "Good", ylab = "Accuracy",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2))
+p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
 
@@
 ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
-p2 <- ggbetweenstats(data = ACCdata2, x = Identity, y = ACC,  
-                     xlab = "Bad", ylab = "",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16),
-                                                             axis.text.x=element_text(size=14,color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
 setwd(traDir)
@@
 ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = ACCdata1, x = Identity, y = ACC,  
-                     xlab = "Good", ylab = "Accuracy",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2))
-
+p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
 ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
@@
 RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
-                     xlab = "Good", ylab = "Reaction times (ms)",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2))
-
+p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
 RTdata2 <- df.T1.V.sum_rt_acc_l %>%
@@
 RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = RTdata1, x = Identity, y = RT,  
-                     xlab = "Good", ylab = "Reaction times (ms)",
-                     type = FALSE) + scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
-                     theme_classic() + theme(legend.position = "none",
-                                                             text=element_text(family='Times'),
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=16), 
-                                                             axis.title.y=element_text(size=16),
-                                                             axis.text.x=element_text(size=14, color = "black"),
-                                                             axis.text.y=element_text(size=14, color = "black"),
-                                                             axis.ticks.x=element_line(size=1.2),
-                                                             axis.ticks.y=element_line(size=1.2)) +scale_y_continuous(breaks = NULL)
+p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
                     #+ coord_cartesian(ylim=c(300,900))
@@
 RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggbetweenstats(data = RTdata2, x = Identity, y = RT,  
-                     xlab = "Bad", ylab = "",
-                     type = FALSE)+
-      scale_y_continuous(limits = c(300,900),breaks = seq(300,900,100)) +
-      theme_classic() +
-      theme(legend.position = "none",text=element_text(family='Times'),
-                               axis.line.x=element_line(size=1.2),
-                               axis.title.x =element_text(size=16),
-                               axis.text.x=element_text(size=14,color = "black"),
-                               axis.ticks.x=element_line(size=1.2))
+p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
+  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+  guides(fill = FALSE) +guides(color = FALSE)+
+  theme_bw() +
+  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
 

### 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd

@@
 fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
+# remove invalid data data_exp7_rep_categ_7338.out
+fNames.c <- fNames.c[fNames.c != "data_exp7_rep_categ_7338.out"]
 fNames.c <- paste(rawDir,fNames.c, sep = '')

### 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
add separate script to save raw data

--- 2018-06-26 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
@@
 
-```
-
-```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
 # set the directories
@@
 ddmDir <- paste(rootDir,'hddmMod',sep = '')
+```
 
-# get the file names for files contain "data_exp7_rep_match_"
-fNames.m <- list.files(path = rawDir, pattern = "data_exp7_rep_match_*")
-# add the directory information to the filenames
-fNames.m <- paste(rawDir,fNames.m, sep = '')
-
+```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
 # read these files and combine them into one file, get the raw data for matching task
-df.L    <- do.call("rbind",lapply(as.list(fNames.m),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
-
-# do the same to data from categorization, get the raw data for categorization task
-fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
-fNames.c <- paste(rawDir,fNames.c, sep = '')
-df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
-
-# render the data in numeric format for future analysis
-cols.num <- c('Sub',"Age","Block","Bin","Trial","RT","ACC")
-df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)  
-df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)  
-df.L <- df.L[!is.na(df.L$ACC),]
-df.T <- df.T[!is.na(df.T$ACC),]
-
-# get the independent varialbes
-# moral valence
-df.L$Morality[grepl("moral", df.L$Shape, fixed=TRUE)]   <- "Good"
-df.L$Morality[grepl("immoral", df.L$Shape, fixed=TRUE)] <- "Bad"
-
-# self-referential
-df.L$Identity[grepl("Self", df.L$Shape, fixed=TRUE)]    <- "Self"
-df.L$Identity[grepl("Other", df.L$Shape, fixed=TRUE)]   <- "Other"
-
-df.T$Morality[grepl("moral", df.T$Shape, fixed=TRUE)]   <- "Good"
-df.T$Morality[grepl("immoral", df.T$Shape, fixed=TRUE)] <- "Bad"
-
-df.T$Identity[grepl("Self", df.T$Shape, fixed=TRUE)]    <- "Self"
-df.T$Identity[grepl("Other", df.T$Shape, fixed=TRUE)]   <- "Other"
-
-df.T$Task[df.T$Task == 'self']            <- 'Id'
-df.T$Task[df.T$Task == 'moral']           <- 'Val'
-
-# rename columns
-colnames(df.L)[colnames(df.L)=="Sub"] <- "Subject"
-colnames(df.T)[colnames(df.T)=="Sub"] <- "Subject"
-
-# order the variables
-df.L$Morality <- factor(df.L$Morality, levels = c("Good","Bad"))    
-df.L$Identity <- factor(df.L$Identity, levels = c("Self","Other"))  
-df.L$Match    <- factor(df.L$Match,    levels = c("match","mismatch"))
-
-# make the variables in a specified order
-df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
-df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
-
-# change all gender from number to string
-df.L$Sex[df.L$Sex == '1'] <- 'male'
-df.L$Sex[df.L$Sex == '2'] <- 'female'
-df.T$Sex[df.T$Sex == '1'] <- 'male'
-df.T$Sex[df.T$Sex == '2'] <- 'female'
+df.M <- read.csv('MS_rep_matchingTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
+df.C <- read.csv('MS_rep_categTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
 ```
@@
 ```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-# get the data file for hddm analysis
-df.L.hddm <- subset(df.L, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
-df.T.hddm <- subset(df.T, ACC ==1 | ACC == 0)
-
-df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
-df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
-colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
-
-df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
-df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')
-
-df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
-df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')
-
-df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
-df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')
-
-setwd(ddmDir)
-write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
-write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
-write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
-write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
-rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
-setwd(curDir)
 
 # clean data for trad. analysis
-df.L1 <- df.L[,c("Subject", "Age", "Sex", "Match", "Morality", "Identity", "ACC","RT")]
-df.T1 <- df.T[,c("Subject", "Age", "Sex", "Task", "Morality", "Identity", "ACC","RT")]
-df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
-df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian
+df.M1 <- df.M
+df.C1 <- df.C
+df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
+df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian
 
 # no response equal to wrong
-df.L1$ACC[df.L1$ACC != 1] <- 0
-df.T1$ACC[df.T1$ACC != 1] <- 0
+df.M1$ACC[df.M1$ACC != 1] <- 0
+df.C1$ACC[df.C1$ACC != 1] <- 0
 
 # check the number of trials are correct
-excldSub1_L <- c() # subject ID of those who failed matching task
-excldSub1_T <- c() # subject ID of those who failed categorization task
+excldSub1_M  <- c()     # subject ID of those who failed matching task
+excldSub1_C  <- c(7338) # subject 7338 excluded because Accuracy of one condition is zero
 
-df.L1.trials <-  plyr::ddply(df.L1,.(Subject, Match, Identity,Morality), summarise,
+df.M1.trials <-  plyr::ddply(df.M1,.(Subject, Match, Identity,Morality), summarise,
                     N = length(ACC),
                     countN = sum(ACC))
-subjlistL <- unique(df.L1.trials$Subject)
-for (ii in 1:length(subjlistL)){
-  tmp <- subset(df.L1.trials,Subject == subjlistL[ii])
+subjlistM <- unique(df.M1.trials$Subject)
+excldSub2_M <- c()
+for (ii in 1:length(subjlistM)){
+  tmp <- subset(df.M1.trials,Subject == subjlistM[ii])
   if(sum(tmp$N != 75)){ # if the number of trials in matching task correct 
-    excldSub1_L[ii] <- subjlistL[ii]
-    print(paste0("ERROR: the trials number of subject ", subjlistL[ii] , 
+    excldSub2_M[ii] <- subjlistM[ii]
+    print(paste0("ERROR: the trials number of subject ", subjlistM[ii] , 
                  " in matching task is not correct"))
@@
 
-df.T1.trials <-  plyr::ddply(df.T1,.(Subject, Task, Identity,Morality), summarise,
+df.C1.trials <-  plyr::ddply(df.C1,.(Subject, Task, Identity,Morality), summarise,
                     N = length(ACC),
@@
 
-subjlistT <- unique(df.T1.trials$Subject)
-for (jj in 1:length(subjlistT)){
-  tmp <- subset(df.T1.trials,Subject == subjlistT[jj])
+subjlistC <- unique(df.C1.trials$Subject)
+excldSub2_C <- c()
+for (jj in 1:length(subjlistC)){
+  tmp <- subset(df.C1.trials,Subject == subjlistC[jj])
   if(sum(tmp$N != 90)){ # if the number of trials in matching task correct 
-    excldSub1_T[jj] <- subjlistT[jj]
-    print(paste0("ERROR: the trials number of subject ", subjlistT[jj] , 
+    excldSub2_C[jj] <- subjlistC[jj]
+    print(paste0("ERROR: the trials number of subject ", subjlistC[jj] , 
                  " in categ task is not correct"))
@@
 
-# get all the participants who were excluded:
-extraExcld <- c(7338)  # this participant didn't understand the instruction, one condition's Accuracy is 0
-excldSub1 <- c(excldSub1_L, excldSub1_T,extraExcld)
-excldSub1 <- excldSub1[!duplicated(excldSub1)]
-
-# df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
-# df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]
+# df.M1 <- df.M1[!(df.M1$Subject %in% procFailureSub),]
+# df.C1 <- df.C1[!(df.C1$Subject %in% procFailureSub),]
 
 # calculate the overall accuracy for matching task
-df.L1.acc.g <-  plyr::ddply(df.L1,.(Subject), summarise,
+df.M1.acc.g <-  plyr::ddply(df.M1,.(Subject), summarise,
                     N = length(ACC),
@@
 # calculate the overall accuracy for categorziation task
-df.T1.acc.g <-  plyr::ddply(df.T1,.(Subject), summarise,
+df.C1.acc.g <-  plyr::ddply(df.C1,.(Subject), summarise,
                     N = length(ACC),
@@
 
-excldSub2_L <- df.L1.acc.g$Subject[df.L1.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
-excldSub2_T <- df.T1.acc.g$Subject[df.T1.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
-excldSub2   <- c(excldSub2_L, excldSub2_T)
-excldSub2 <- excldSub2[!duplicated(excldSub2)]   # invalid because of low overall accuracy
+excldSub3_M <- df.M1.acc.g$Subject[df.M1.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
+excldSub3_C <- df.C1.acc.g$Subject[df.C1.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
 
-excldSub   <- c(excldSub1, excldSub2)
-excldSub <- excldSub[!duplicated(excldSub)]   # total excluded
+excldSub_M   <- c(excldSub1_M, excldSub2_M,excldSub3_M)
+excldSub_M <- excldSub_M[!duplicated(excldSub_M)]   # total excluded for matching task
 
-valdSub <- setdiff(subjlistL, excldSub)
+excldSub_C   <- c(excldSub1_C, excldSub2_C,excldSub3_C)
+excldSub_C <- excldSub_C[!duplicated(excldSub_C)]   # total excluded for matching task
 
-df.L1.valid <- df.L1[!(df.L1$Subject %in% excldSub),]   # exclude the invalid subjects
-df.T1.valid <- df.T1[!(df.T1$Subject %in% excldSub),]
-# df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]
+valdSub_M <- setdiff(subjlistM, excldSub_M)
+valdSub_C <- setdiff(subjlistC, excldSub_C)
+
+# select valid data for further analysis
+
+df.M1.valid <- df.M1[!(df.M1$Subject %in% excldSub_M),]   # exclude the invalid subjects
+df.C1.valid <- df.C1[!(df.C1$Subject %in% excldSub_C),]
+# df.C1.valid <- df.C1.valid[!(df.C1.valid$Subject %in% excld.sub.T),]
 
 # check the number of participants are correct
-length(valdSub) + length(excldSub) == length(unique(df.L1$Subject))
+length(valdSub_M) + length(excldSub_M) == length(unique(df.M1$Subject))
+length(valdSub_C) + length(excldSub_C) == length(unique(df.C1$Subject))
 
-# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
-excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200 & df.L1.valid$ACC == 1,]
-df.L1.V        <- df.L1.valid[!(df.L1.valid$RT <= 200 & df.L1.valid$ACC == 1),]  # valid trial data for match task
-excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200 & df.T1.valid$ACC == 1,]
-df.T1.V        <- df.T1.valid[!(df.T1.valid$RT <= 200 & df.T1.valid$ACC == 1),]  # valid trial data for categorization task
-nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok
+# excluded correct trials with < 200ms RT
+excld.trials.M <- df.M1.valid[df.M1.valid$RT <= 200 & df.M1.valid$ACC == 1,]
+df.M1.V        <- df.M1.valid[!(df.M1.valid$RT <= 200 & df.M1.valid$ACC == 1),]  # valid trial data for match task
+excld.trials.C <- df.C1.valid[df.C1.valid$RT <= 200 & df.C1.valid$ACC == 1,]
+df.C1.V        <- df.C1.valid[!(df.C1.valid$RT <= 200 & df.C1.valid$ACC == 1),]  # valid trial data for categorization task
+nrow(excld.trials.C) + nrow(df.C1.V) == nrow(df.C1.valid) # if true, everything is ok
 
 ## Basic information of the data ####
-df.L1.T.basic <- df.L1[!duplicated(df.L1$Subject), 2:5]
-numT.subj     <- nrow(df.L1.T.basic)
-numT.female   <- sum(df.L1.T.basic$Sex == 'female');
-numT.male     <- sum(df.L1.T.basic$Sex == 'male');
-ageT.mean     <- round(mean(df.L1.T.basic$Age),2);
-ageT.std      <- round(sd(df.L1.T.basic$Age),2);
-num.excld.sub <- length(unique(excldSub))
+df.M1.T.basic <- df.M1[!duplicated(df.M1$Subject), 2:5]
+numT.subj     <- nrow(df.M1.T.basic)
+numT.female   <- sum(df.M1.T.basic$Sex == 'female');
+numT.male     <- sum(df.M1.T.basic$Sex == 'male');
+ageT.mean     <- round(mean(df.M1.T.basic$Age),2);
+ageT.std      <- round(sd(df.M1.T.basic$Age),2);
+# num.excld.sub <- length(unique(excldSub))
 # num.excld.sub.T <- length(unique(excld.sub.T))
@@
 # valide data for matching task
-df.L1.V.basic <- df.L1.V[!duplicated(df.L1.V$Subject), 2:5]
-numV.female   <- sum(df.L1.V.basic$Sex == 'female');
-numV.male     <- sum(df.L1.V.basic$Sex == 'male');
-ageV.mean     <- round(mean(df.L1.V.basic$Age),2);
-ageV.std      <- round(sd(df.L1.V.basic$Age),2);
-ratio.excld.trials.L <- nrow(excld.trials.L)/nrow(df.L1.valid)
-ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
+df.M1.V.basic <- df.M1.V[!duplicated(df.M1.V$Subject), 2:5]
+numV.female   <- sum(df.M1.V.basic$Sex == 'female');
+numV.male     <- sum(df.M1.V.basic$Sex == 'male');
+ageV.mean     <- round(mean(df.M1.V.basic$Age),2);
+ageV.std      <- round(sd(df.M1.V.basic$Age),2);
+ratio.excld.trials.M <- nrow(excld.trials.M)/nrow(df.M1.valid)
+num.excld.sub_M <- length(unique(valdSub_M))
 
 # valid data for categorization task
-df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 2:5]
-numV.female.T <- sum(df.T1.V.basic$Sex == 'female');
-numV.male.T <- sum(df.T1.V.basic$Sex == 'male');
-ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
-ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
-ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
+df.C1.V.basic <- df.C1.V[!duplicated(df.C1.V$Subject), 2:5]
+numV.female.C <- sum(df.C1.V.basic$Sex == 'female');
+numV.male.C <- sum(df.C1.V.basic$Sex == 'male');
+ageV.mean.C <- round(mean(df.C1.V.basic$Age),2);
+ageV.std.C <- round(sd(df.C1.V.basic$Age),2);
+ratio.excld.trials.C <- nrow(excld.trials.C)/nrow(df.C1.valid)
+num.excld.sub_C <- length(unique(valdSub_C))
+
+# get the data file for hddm analysis
+
+df.M.ddm.v <- df.M[!(df.M$Subject %in% excldSub_M),]   # exclude the invalid subjects
+df.C.ddm.v <- df.C[!(df.C$Subject %in% excldSub_C),]
+
+df.M.hddm <- subset(df.M.ddm.v, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
+df.C.hddm <- subset(df.C.ddm.v, ACC ==1 | ACC == 0)
+
+df.M.hddm_m <- subset(df.M.hddm, Match == 'match') # select data
+df.M.hddm_m <- df.M.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
+colnames(df.M.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
+
+df.M.hddm_nm <- subset(df.M.hddm, Match == 'mismatch')
+df.M.hddm_nm <- df.M.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.M.hddm_nm) <- c("subj_idx","val",'id','rt','response')
+
+df.C.hddm_val <- subset(df.C.hddm, Task == 'Val')
+df.C.hddm_val <- df.C.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.C.hddm_val) <- c("subj_idx","val",'id','rt','response')
+
+df.C.hddm_id <- subset(df.C.hddm, Task == 'Id')
+df.C.hddm_id <- df.C.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.C.hddm_id) <- c("subj_idx","val",'id','rt','response')
+
+setwd(ddmDir)
+write.csv(df.M.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
+write.csv(df.M.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
+write.csv(df.C.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
+write.csv(df.C.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
+rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
+setwd(curDir)
+
 ```
@@
 
-matching task: `r excldSub1_L` ;
+matching task: `r excldSub1_M` ;
 
-categ. task: `r excldSub1_T`;
-
-total: `r excldSub1`.
+categ. task: `r excldSub1_C`.
 
 Excluded because the overall accuracy is lower than 50%: 
-matching task: `r excldSub2_L` ;
+matching task: `r excldSub2_M` ;
 
-categ. task: `r excldSub2_T`;
+categ. task: `r excldSub2_C`.
 
-total: `r excldSub2`.
+Remaining participant:
 
-Remaining participant: `r length(valdSub)` (`r valdSub`)
+matching task`r length(valdSub_M)`; categorization task: (`r length(valdSub_C)`)
 
@@
 ### ACC ####
-df.L1.V.acc  <-  plyr::ddply(df.L1.V,.(Subject, Match, Morality, Identity), summarise,
+df.M1.V.acc  <-  plyr::ddply(df.M1.V,.(Subject, Match, Morality, Identity), summarise,
                     N = length(ACC),
@@
 
-df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Morality + Identity,value.var = "ACC")
+df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Morality + Identity,value.var = "ACC")
 
 # rename the column number
-colnames(df.L1.V.acc_w)[2:9] <- paste("ACC", colnames(df.L1.V.acc_w[,2:9]), sep = "_")
+colnames(df.M1.V.acc_w)[2:9] <- paste("ACC", colnames(df.M1.V.acc_w[,2:9]), sep = "_")
 
 # d prime #### 
-df.L1.V$sdt <- NA
-for (i in 1:nrow(df.L1.V)){
-        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match"){
-                df.L1.V$sdt[i] <- "hit"
-        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "mismatch"){
-                df.L1.V$sdt[i] <- "CR"
-        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match"){
-                df.L1.V$sdt[i] <- "miss"
-        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "mismatch"){
-                df.L1.V$sdt[i] <- "FA"
+df.M1.V$sdt <- NA
+for (i in 1:nrow(df.M1.V)){
+        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match"){
+                df.M1.V$sdt[i] <- "hit"
+        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "mismatch"){
+                df.M1.V$sdt[i] <- "CR"
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match"){
+                df.M1.V$sdt[i] <- "miss"
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "mismatch"){
+                df.M1.V$sdt[i] <- "FA"
         }
@@
 # calculate the number of each for each condition
-df.L1.V.SDT <-  plyr::ddply(df.L1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
+df.M1.V.SDT <-  plyr::ddply(df.M1.V,.(Subject,Age, Sex, Morality,Identity,sdt), summarise,
                      N = length(sdt))
@@
 # long format to wide
-df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Age + Sex+ Morality + Identity  ~ sdt,value.var = "N")
-df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0
-df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)] <- 0
-df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
-df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)
+df.M1.V.SDT_w <- dcast(df.M1.V.SDT, Subject + Age + Sex+ Morality + Identity  ~ sdt,value.var = "N")
+df.M1.V.SDT_w$miss[is.na(df.M1.V.SDT_w$miss)] <- 0
+df.M1.V.SDT_w$FA[is.na(df.M1.V.SDT_w$FA)] <- 0
+df.M1.V.SDT_w$hitR <- df.M1.V.SDT_w$hit/(df.M1.V.SDT_w$hit + df.M1.V.SDT_w$miss)
+df.M1.V.SDT_w$faR <- df.M1.V.SDT_w$FA/(df.M1.V.SDT_w$FA + df.M1.V.SDT_w$CR)
 
 # standardized way to deal with the extreme values
-for (i in 1:nrow(df.L1.V.SDT_w)){
-        if (df.L1.V.SDT_w$hitR[i] == 1){
-                df.L1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.L1.V.SDT_w$hit[i] + df.L1.V.SDT_w$miss[i]))
+for (i in 1:nrow(df.M1.V.SDT_w)){
+        if (df.M1.V.SDT_w$hitR[i] == 1){
+                df.M1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.M1.V.SDT_w$hit[i] + df.M1.V.SDT_w$miss[i]))
         }
@@
 
-for (i in 1:nrow(df.L1.V.SDT_w)){
-        if (df.L1.V.SDT_w$faR[i] == 0){
-                df.L1.V.SDT_w$faR[i] <- 1/(2*(df.L1.V.SDT_w$FA[i] + df.L1.V.SDT_w$CR[i]))
+for (i in 1:nrow(df.M1.V.SDT_w)){
+        if (df.M1.V.SDT_w$faR[i] == 0){
+                df.M1.V.SDT_w$faR[i] <- 1/(2*(df.M1.V.SDT_w$FA[i] + df.M1.V.SDT_w$CR[i]))
         }
@@
 # calculate the d prime for each condition
-df.L1.V.SDT_w$dprime <- mapply(dprime,df.L1.V.SDT_w$hitR,df.L1.V.SDT_w$faR)
-df.L1.V.SDT_ww   <- dcast(df.L1.V.SDT_w, Subject + Sex + Age ~ Morality + Identity ,value.var = "dprime")
+df.M1.V.SDT_w$dprime <- mapply(dprime,df.M1.V.SDT_w$hitR,df.M1.V.SDT_w$faR)
+df.M1.V.SDT_ww   <- dcast(df.M1.V.SDT_w, Subject + Sex + Age ~ Morality + Identity ,value.var = "dprime")
 
-df.L1.V.SDT_l <- df.L1.V.SDT_w[,c(1:5,12)]
+df.M1.V.SDT_l <- df.M1.V.SDT_w[,c(1:5,12)]
 
 # rename the column number
-colnames(df.L1.V.SDT_ww)[4:7] <- paste("d", colnames(df.L1.V.SDT_ww[,4:7]), sep = "_")
+colnames(df.M1.V.SDT_ww)[4:7] <- paste("d", colnames(df.M1.V.SDT_ww[,4:7]), sep = "_")
 
 ## doing the analysis for RT ####
-df.L1.V.RT <- df.L1.V[df.L1.V$ACC == 1,]  # exclued inaccurate data
-df.L1.V.RT.subj <- summarySEwithin(df.L1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
-df.L1.V.RT.subj_w <- dcast(df.L1.V.RT.subj, Subject ~ Match + Morality + Identity ,value.var = "RT")
+df.M1.V.RT <- df.M1.V[df.M1.V$ACC == 1,]  # exclued inaccurate data
+df.M1.V.RT.subj <- summarySEwithin(df.M1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.M1.V.RT.subj_w <- dcast(df.M1.V.RT.subj, Subject ~ Match + Morality + Identity ,value.var = "RT")
 
 # rename the columns of RT data
-colnames(df.L1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.L1.V.RT.subj_w[,2:9]), sep = "_")
+colnames(df.M1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.M1.V.RT.subj_w[,2:9]), sep = "_")
 
@@
 # merge the dprime and RT data and save
-df.L1.V.sum_w <- merge(df.L1.V.acc_w,  df.L1.V.SDT_ww,by = "Subject")
-df.L1.V.sum_w <- merge(df.L1.V.sum_w,df.L1.V.RT.subj_w,by = 'Subject')
+df.M1.V.sum_w <- merge(df.M1.V.acc_w,  df.M1.V.SDT_ww,by = "Subject")
+df.M1.V.sum_w <- merge(df.M1.V.sum_w,df.M1.V.RT.subj_w,by = 'Subject')
 
 # merge the RT and ACC data (long-format)
-df.L1.V.sum_rt_acc_l <- merge(df.L1.V.acc,df.L1.V.RT.subj,by = c("Subject","Match","Morality",'Identity'))
-df.L1.V.sum_rt_acc_l <- df.L1.V.sum_rt_acc_l[order(df.L1.V.sum_rt_acc_l$Subject),]
+df.M1.V.sum_rt_acc_l <- merge(df.M1.V.acc,df.M1.V.RT.subj,by = c("Subject","Match","Morality",'Identity'))
+df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[order(df.M1.V.sum_rt_acc_l$Subject),]
 
-df.L1.V.sum_rt_acc_l <- df.L1.V.sum_rt_acc_l[,c("Subject","Match","Morality",'Identity',"N.x","countN","ACC","RT")]
-colnames(df.L1.V.sum_rt_acc_l) <- c("Subject","Match","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
+df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[,c("Subject","Match","Morality",'Identity',"N.x","countN","ACC","RT")]
+colnames(df.M1.V.sum_rt_acc_l) <- c("Subject","Match","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
 
 # order the columns
-df.L1.V.sum_w <- df.L1.V.sum_w[,c(colnames(df.L1.V.sum_w)[c(1,10:11,2:9,12:23)])]
+df.M1.V.sum_w <- df.M1.V.sum_w[,c(colnames(df.M1.V.sum_w)[c(1,10:11,2:9,12:23)])]
 
 # calculate the effect of self-ref and valence
-df.L1.v.sum_eff_w <- df.L1.V.sum_w[,1:3]
-df.L1.v.sum_eff_w$d_Good_Self_Other <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Good_Other
-df.L1.v.sum_eff_w$d_Self_Good_Bad   <- df.L1.V.sum_w$d_Good_Self - df.L1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
+df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
+df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
 
-df.L1.v.sum_eff_w$RT_Good_Self_Other <- df.L1.V.sum_w$RT_match_Good_Other -  df.L1.V.sum_w$RT_match_Good_Self
-df.L1.v.sum_eff_w$RT_Self_Good_Bad   <- df.L1.V.sum_w$RT_match_Bad_Self -  df.L1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
 
@@
 setwd(traDir)
-write.csv(df.L1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
-write.csv(df.L1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
-write.csv(df.L1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
+write.csv(df.M1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
+write.csv(df.M1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
+write.csv(df.M1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
 setwd(curDir)
@@
 ### ACC ####
-df.T1.V.acc  <-  plyr::ddply(df.T1.V,.(Subject, Task, Morality, Identity), summarise,
+df.C1.V.acc  <-  plyr::ddply(df.C1.V,.(Subject, Task, Morality, Identity), summarise,
                     N = length(ACC),
@@
 
-df.T1.V.acc_w <- dcast(df.T1.V.acc, Subject ~ Task + Morality + Identity,value.var = "ACC")
+df.C1.V.acc_w <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity,value.var = "ACC")
 
 # rename the column number
-colnames(df.T1.V.acc_w)[2:9] <- paste("ACC", colnames(df.T1.V.acc_w[,2:9]), sep = "_")
+colnames(df.C1.V.acc_w)[2:9] <- paste("ACC", colnames(df.C1.V.acc_w[,2:9]), sep = "_")
 
 # combing data from diff task for analyzing the interaction btw val and id
-df.T1.V.acc_noTask  <-  plyr::ddply(df.T1.V,.(Subject, Morality, Identity), summarise,
+df.C1.V.acc_noTask  <-  plyr::ddply(df.C1.V,.(Subject, Morality, Identity), summarise,
                     N = length(ACC),
@@
 
-df.T1.V.acc_noTask_w <- dcast(df.T1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")
+df.C1.V.acc_noTask_w <- dcast(df.C1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")
 
 # rename the column number
-colnames(df.T1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.T1.V.acc_noTask_w[,2:5]), sep = "_")
+colnames(df.C1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.C1.V.acc_noTask_w[,2:5]), sep = "_")
 
 ## doing the analysis for RT ####
-df.T1.V.RT <- df.T1.V[df.T1.V$ACC == 1,]  # exclued inaccurate data
-df.T1.V.RT.subj <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
-df.T1.V.RT.subj_w <- dcast(df.T1.V.RT.subj, Subject ~ Task + Morality + Identity ,value.var = "RT")
+df.C1.V.RT <- df.C1.V[df.C1.V$ACC == 1,]  # exclued inaccurate data
+df.C1.V.RT.subj <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.C1.V.RT.subj_w <- dcast(df.C1.V.RT.subj, Subject ~ Task + Morality + Identity ,value.var = "RT")
 
 # rename the columns of RT data
-colnames(df.T1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.T1.V.RT.subj_w[,2:9]), sep = "_")
+colnames(df.C1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.C1.V.RT.subj_w[,2:9]), sep = "_")
 
 # combining data form different task for analyszing interaction of val and id
-df.T1.V.RT.subj_noTask <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
-df.T1.V.RT.subj_noTask_w <- dcast(df.T1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")
+df.C1.V.RT.subj_noTask <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.C1.V.RT.subj_noTask_w <- dcast(df.C1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")
 
 # rename the columns of RT data
-colnames(df.T1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.T1.V.RT.subj_noTask_w[,2:5]), sep = "_")
+colnames(df.C1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.C1.V.RT.subj_noTask_w[,2:5]), sep = "_")
 
@@
 # merge the accuracy and RT data and save
-df.T1.V.sum_w <- merge(df.T1.V.acc_w,  df.T1.V.RT.subj_w,by = "Subject")
-df.T1.V.sum_noTask_w <- merge(df.T1.V.acc_noTask_w,  df.T1.V.RT.subj_noTask_w,by = "Subject")
+df.C1.V.sum_w <- merge(df.C1.V.acc_w,  df.C1.V.RT.subj_w,by = "Subject")
+df.C1.V.sum_noTask_w <- merge(df.C1.V.acc_noTask_w,  df.C1.V.RT.subj_noTask_w,by = "Subject")
 
@@
 # self-reference effect
-df.T1.V.sum_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
-df.T1.V.sum_w$RT_Val_Bad_selfEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Bad_Self
-df.T1.V.sum_w$RT_Id_Good_selfEffect  <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
-df.T1.V.sum_w$RT_Id_Bad_selfEffect   <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Self
+df.C1.V.sum_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.V.sum_w$RT_Val_Bad_selfEffect  <- df.C1.V.sum_w$RT_Val_Bad_Other - df.C1.V.sum_w$RT_Val_Bad_Self
+df.C1.V.sum_w$RT_Id_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.V.sum_w$RT_Id_Bad_selfEffect   <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Bad_Self
 # valence effect
-df.T1.V.sum_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
-df.T1.V.sum_w$RT_Val_Other_valEffect <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Val_Good_Other
-df.T1.V.sum_w$RT_Id_Self_valEffect   <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self
-df.T1.V.sum_w$RT_Id_Other_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Other - df.T1.V.sum_w$RT_Id_Good_Other
+df.C1.V.sum_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.V.sum_w$RT_Val_Other_valEffect <- df.C1.V.sum_w$RT_Val_Bad_Other - df.C1.V.sum_w$RT_Val_Good_Other
+df.C1.V.sum_w$RT_Id_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.V.sum_w$RT_Id_Other_valEffect  <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other
 # task effect
-df.T1.V.sum_w$RT_Good_Self_taskEffect  <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Self
-df.T1.V.sum_w$RT_Bad_Self_taskEffect   <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Id_Bad_Self
-df.T1.V.sum_w$RT_Good_Other_taskEffect <- df.T1.V.sum_w$RT_Val_Good_Self - df.T1.V.sum_w$RT_Id_Good_Other
-df.T1.V.sum_w$RT_Bad_Other_taskEffect  <- df.T1.V.sum_w$RT_Val_Bad_Other - df.T1.V.sum_w$RT_Id_Bad_Other
+df.C1.V.sum_w$RT_Good_Self_taskEffect  <- df.C1.V.sum_w$RT_Val_Good_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.V.sum_w$RT_Bad_Self_taskEffect   <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Id_Bad_Self
+df.C1.V.sum_w$RT_Good_Other_taskEffect <- df.C1.V.sum_w$RT_Val_Good_Self - df.C1.V.sum_w$RT_Id_Good_Other
+df.C1.V.sum_w$RT_Bad_Other_taskEffect  <- df.C1.V.sum_w$RT_Val_Bad_Other - df.C1.V.sum_w$RT_Id_Bad_Other
 
 # calculate the effect of self-ref and valence
-df.T1.v.sum_eff_w <- data.frame(df.T1.V.sum_w[,c('Subject')])
-colnames(df.T1.v.sum_eff_w) <- 'Subject'
-df.T1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.T1.V.sum_w$RT_Val_Good_Other - df.T1.V.sum_w$RT_Val_Good_Self
-df.T1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.T1.V.sum_w$RT_Val_Bad_Self - df.T1.V.sum_w$RT_Val_Good_Self
-df.T1.v.sum_eff_w$RT_Id_Good_selfEffect <- df.T1.V.sum_w$RT_Id_Good_Other - df.T1.V.sum_w$RT_Id_Good_Self
-df.T1.v.sum_eff_w$RT_Id_Self_valEffect  <- df.T1.V.sum_w$RT_Id_Bad_Self - df.T1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w <- data.frame(df.C1.V.sum_w[,c('Subject')])
+colnames(df.C1.v.sum_eff_w) <- 'Subject'
+df.C1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$RT_Id_Good_selfEffect <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$RT_Id_Self_valEffect  <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
 
-df.T1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.T1.V.sum_w$ACC_Val_Good_Other - df.T1.V.sum_w$ACC_Val_Good_Self
-df.T1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.T1.V.sum_w$ACC_Val_Bad_Self - df.T1.V.sum_w$ACC_Val_Good_Self
-df.T1.v.sum_eff_w$ACC_Id_Good_selfEffect <- df.T1.V.sum_w$ACC_Id_Good_Other - df.T1.V.sum_w$ACC_Id_Good_Self
-df.T1.v.sum_eff_w$ACC_Id_Self_valEffect  <- df.T1.V.sum_w$ACC_Id_Bad_Self - df.T1.V.sum_w$ACC_Id_Good_Self
+df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
+df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
+df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
+df.C1.v.sum_eff_w$ACC_Id_Self_valEffect  <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self
 
 # merge the effect file
-df.v.sum_eff_all_w <- merge(df.L1.v.sum_eff_w,df.T1.v.sum_eff_w,by="Subject")
+df.v.sum_eff_all_w <- merge(df.M1.v.sum_eff_w,df.C1.v.sum_eff_w,by="Subject")
 
 # merge the RT and ACC data (long-format) ####
-df.T1.V.sum_rt_acc_l <- merge(df.T1.V.acc,df.T1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
-df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[order(df.T1.V.sum_rt_acc_l$Subject),]
+df.C1.V.sum_rt_acc_l <- merge(df.C1.V.acc,df.C1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
+df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[order(df.C1.V.sum_rt_acc_l$Subject),]
 
-df.T1.V.sum_rt_acc_l <- df.T1.V.sum_rt_acc_l[,c("Subject","Task","Morality",'Identity',"N.x","countN","ACC","RT")]
-colnames(df.T1.V.sum_rt_acc_l) <- c("Subject","Task","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
+df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[,c("Subject","Task","Morality",'Identity',"N.x","countN","ACC","RT")]
+colnames(df.C1.V.sum_rt_acc_l) <- c("Subject","Task","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
 
 # order the columns
-#df.T1.V.sum_w <- df.T1.V.sum_w[,c(colnames(df.T1.V.sum_w)[c(1,10:11,2:9,12:23)])]
+#df.C1.V.sum_w <- df.C1.V.sum_w[,c(colnames(df.C1.V.sum_w)[c(1,10:11,2:9,12:23)])]
 
@@
 setwd(traDir)
-write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
-write.csv(df.T1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
-write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
+write.csv(df.C1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
 write.csv(df.v.sum_eff_all_w,'exp7_cross_taskeffect_wide.csv',row.names = F)
@@
 ```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.L1.V.sum_rt_acc_l %>%
+RTdata1 <- df.M1.V.sum_rt_acc_l %>%
   select(Subject,Match,Morality,Identity,RT) %>% 
@@
   raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-RTdata2 <- df.L1.V.sum_rt_acc_l %>%
+RTdata2 <- df.M1.V.sum_rt_acc_l %>%
   select(Subject,Match,Morality,Identity,RT) %>% 
@@
 ```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
-Ddata1 <- df.L1.V.SDT_l %>%
+Ddata1 <- df.M1.V.SDT_l %>%
   select(Subject,Morality,Identity,dprime) %>% 
@@
   raincloud_theme+scale_y_continuous(limits = c(0,4))+labs(x = "Good",y = "dprime")
-Ddata2 <- df.L1.V.SDT_l %>%
+Ddata2 <- df.M1.V.SDT_l %>%
   select(Subject,Morality,Identity,dprime) %>% 
@@
 ```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
+ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,ACC) %>% 
@@
 
-ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
+ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,ACC) %>% 
@@
 ```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
-ACCdata1 <- df.T1.V.sum_rt_acc_l %>%
+ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,ACC) %>% 
@@
   raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
-ACCdata2 <- df.T1.V.sum_rt_acc_l %>%
+ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,ACC) %>% 
@@
 ```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.T1.V.sum_rt_acc_l %>%
+RTdata1 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,RT) %>% 
@@
   raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-RTdata2 <- df.T1.V.sum_rt_acc_l %>%
+RTdata2 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,RT) %>% 
@@
 ```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.T1.V.sum_rt_acc_l %>%
+RTdata1 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,RT) %>% 
@@
 #y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
-RTdata2 <- df.T1.V.sum_rt_acc_l %>%
+RTdata2 <- df.C1.V.sum_rt_acc_l %>%
   select(Subject,Task,Morality,Identity,RT) %>% 

### 2018-06-26 Replication/Results/data_analysis/preproc/Save_raw_to_CSV.r

@@ -1,0 +1,87 @@
+##
+# This script transfer the raw data and save them to de-identified raw data
+# create at 26 June. 2018
+# by @Chuan-Peng Hu
+# 
+
+# clear the working memory
+Sys.setlocale("LC_ALL", "English")  # set local encoding to English
+Sys.setenv(LANG = "en") # set the feedback language to English
+options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+options(digits=5)       # limit the number of reporting
+rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+
+
+# set the directories
+curDir <- getwd()   # directory for preprocessing
+rootDir <- gsub('.{7}$', '', curDir)
+rawDir <- paste(curDir,'/data/',sep = '')
+traDir <- paste(rootDir,'tradAnal',sep = '')
+ddmDir <- paste(rootDir,'hddmMod',sep = '')
+
+# get the file names for files contain "data_exp7_rep_match_"
+fNames.m <- list.files(path = rawDir, pattern = "data_exp7_rep_match_*")
+# add the directory information to the filenames
+fNames.m <- paste(rawDir,fNames.m, sep = '')
+
+# read these files and combine them into one file, get the raw data for matching task
+df.L <- do.call("rbind",lapply(as.list(fNames.m),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
+
+# do the same to data from categorization, get the raw data for categorization task
+fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
+# remove invalid data data_exp7_rep_categ_7338.out
+# fNames.c <- fNames.c[fNames.c != "data_exp7_rep_categ_7338.out"]
+fNames.c <- paste(rawDir,fNames.c, sep = '')
+df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))
+
+
+# render the data in numeric format for future analysis
+cols.num <- c('Sub',"Age","Block","Bin","Trial","RT","ACC")
[…]

### 2018-07-01 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
raincloud plot

@@
 
-# check the number of trials are correct
+# exclude participant (1st round)
 excldSub1_M  <- c()     # subject ID of those who failed matching task
@@
 subjlistM <- unique(df.M1.trials$Subject)
+
+# exclude particiapnts (2nd round: incorrect trial number)
 excldSub2_M <- c()
@@
 
-# df.M1 <- df.M1[!(df.M1$Subject %in% procFailureSub),]
-# df.C1 <- df.C1[!(df.C1$Subject %in% procFailureSub),]
-
-# calculate the overall accuracy for matching task
+# exclude participants (3rd round: < 0.5 overall accuracy)
 df.M1.acc.g <-  plyr::ddply(df.M1,.(Subject), summarise,
@@
 
+# all participants excluded
 excldSub_M   <- c(excldSub1_M, excldSub2_M,excldSub3_M)
@@
 
+# particiapnts with valid data
 valdSub_M <- setdiff(subjlistM, excldSub_M)
@@
 # select valid data for further analysis
-
 df.M1.valid <- df.M1[!(df.M1$Subject %in% excldSub_M),]   # exclude the invalid subjects
@@
 # get the data file for hddm analysis
-
 df.M.ddm.v <- df.M[!(df.M$Subject %in% excldSub_M),]   # exclude the invalid subjects
@@
 ```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.M1.V.sum_rt_acc_l %>%
-  select(Subject,Match,Morality,Identity,RT) %>% 
-  filter(Match == "match" & Morality == "Good")
-RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-RTdata2 <- df.M1.V.sum_rt_acc_l %>%
-  select(Subject,Match,Morality,Identity,RT) %>% 
-  filter(Match == "match" & Morality == "Bad")
-RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
+MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
+#RTdata1 <- df.M1.V.sum_rt_acc_l %>%
+#  select(Subject,Match,Morality,Identity,RT) %>% 
+#  filter(Match == "match" & Morality == "Good")
+#RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
+#p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
+#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+#  guides(fill = FALSE) +guides(color = FALSE)+
+#  theme_bw() +
+#  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
+#RTdata2 <- df.M1.V.sum_rt_acc_l %>%
+#  select(Subject,Match,Morality,Identity,RT) %>% 
+#  filter(Match == "match" & Morality == "Bad")
+#RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
+#p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
+#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
+#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
+#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
+#  guides(fill = FALSE) +guides(color = FALSE)+
+#  theme_bw() +
+#  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
 
-setwd(traDir)
-tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_rt_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-multiplot(p1,p2,cols = 2)
+#setwd(traDir)
+#tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
+#p_rt_match <- multiplot(p1,p2,cols = 2)
+#dev.off()
+#setwd(curDir)
+#multiplot(p1,p2,cols = 2)
 ```
@@
 ```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
-Ddata1 <- df.M1.V.SDT_l %>%
-  select(Subject,Morality,Identity,dprime) %>% 
-  filter(Morality == "Good")
-Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = Ddata1, aes(y = dprime, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,4))+labs(x = "Good",y = "dprime")
-Ddata2 <- df.M1.V.SDT_l %>%
-  select(Subject,Morality,Identity,dprime) %>% 
-  filter(Morality == "Bad")
-Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = Ddata2, aes(y = dprime, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,4),breaks = NULL)+labs(x = "Bad",y = "")
-p_dprime_match <- multiplot(p1,p2,cols = 2)
-# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-setwd(traDir)
-tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_dprime_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-#multiplot(p1,p2,cols = 2)
+MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
 ```
@@
 ```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,ACC) %>% 
-  filter(Task == "Val"& Morality == 'Good')
-ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
+MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
 
-ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,ACC) %>% 
-  filter(Task == "Val"& Morality == 'Bad')
-ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
-setwd(traDir)
-tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_rt_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-multiplot(p1,p2,cols = 2)
 ```
@@
 ```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
-ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,ACC) %>% 
-  filter(Task == "Id"& Morality == 'Good')
-ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
-ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,ACC) %>% 
-  filter(Task == "Id"& Morality == 'Bad')
-ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
-setwd(traDir)
-tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_rt_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-multiplot(p1,p2,cols = 2)
+MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
 ```
@@
 ```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,RT) %>% 
-  filter(Task == "Val"& Morality == 'Good')
-RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-RTdata2 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,RT) %>% 
-  filter(Task == "Val"& Morality == 'Bad')
-RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
+MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
 
-setwd(traDir)
-tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_rt_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-multiplot(p1,p2,cols = 2)
 ```
@@
 ```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
-RTdata1 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,RT) %>% 
-  filter(Task == "Id"& Morality == 'Good')
-RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-                    #+ coord_cartesian(ylim=c(300,900))
-
-#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
-RTdata2 <- df.C1.V.sum_rt_acc_l %>%
-  select(Subject,Task,Morality,Identity,RT) %>% 
-  filter(Task == "Id"& Morality == 'Bad')
-RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
-  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-  guides(fill = FALSE) +guides(color = FALSE)+
-  theme_bw() +
-  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
-
-setwd(traDir)
-tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-p_rt_match <- multiplot(p1,p2,cols = 2)
-dev.off()
-setwd(curDir)
-multiplot(p1,p2,cols = 2)
+MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
 ```

### 2018-07-01 Replication/Results/data_analysis/preproc/Initial.r

@@ -21,8 +21,11 @@ pkgNeeded <- (c("tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS",
                 "tidyr","Hmisc","RColorBrewer"))
 
 lapply(pkgNeeded,pkgTest)
-source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
 rm('pkgNeeded') # remove the variable 'pkgNeeded';
+
+# run the geo_flat_violin.r, which is from:https://gist.githubusercontent.com/
+# benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R
+source("geom_flat_violin.R")
 
 # Save some time and stor APA format-related code in an object so you can easily
 # use it in multiple plots
@@ -222,12 +225,125 @@ raincloud_theme <-  theme(
   axis.title.y = element_text(size = 16),
   axis.text = element_text(size = 14),
   axis.text.x = element_text(angle = 45, vjust = 0.5),
-  legend.title=element_text(size=16),
-  legend.text=element_text(size=16),
+  legend.title=element_text(size=16,colour = 'black'),
+  legend.text=element_text(size=16,colour = 'black'),
   legend.position = "right",
-  plot.title = element_text(lineheight=.8, face="bold", size = 16),
+  plot.title = element_text(lineheight=.8, face="bold", size = 16,colour = 'black'),
   panel.border = element_blank(),
   panel.grid.minor = element_blank(),
   panel.grid.major = element_blank(),
   axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
   axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
+
+# define a function for the plots
+MSplots <- function(saveDir = traDir, curDir = curDir, task = 'match',type = 'ACC', inData){
+  if(type == 'ACC'){
+    if(task == 'val'){
+      ACCdata1 <- inData %>%
+        select(Subject,Task,Morality,Identity,ACC) %>% 
+        filter(Task == "Val"& Morality == 'Good')
+      ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
[…]

### 2018-07-01 Results/HDDM/HDDM_Moral_match_170307.py

@@ -1,0 +1,596 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jul 13 21:55:21 2016
+
+@author: hcp47
+"""
+
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
+This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making
+"""
+# %reset #this code will delete all the varibles in the memory
+
+import os
+
+# get the current directory and change the cd
+os.getcwd()
+os.chdir("D:\HCP_cloud\Exp.s\Project1_Moral_reputation_learning\Exp_Behav_Moral_Asso\Exp_Behav_Moral_Asso_7_behav_modeling\Results\Formal_results\HDDM\FinalVersion")
+
+# get the tool box
+import pandas as pd
+import matplotlib.pyplot as plt
+# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
+import hddm
+
+# Load match data from csv file into a NumPy structured array
+dat_M_match = hddm.load_csv('data_M_match_hddm.csv')
+dat_M_match.head(10)
+
+# flip the error RTs to be negative
+dat_M_match = hddm.utils.flip_errors(dat_M_match)
+
+# check the RT distritubtion
+fig = plt.figure()
+ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
+for i, subj_data in dat_M_match.groupby('subj_idx'):
+    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+plt.savefig('hddm_exp7_L_match2_fig_1.pdf')
+
+#### model 1, free v,a,t,z
+M_match_vatz = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'a':['moral','id'],'t':['moral','id']}, include=['v', 'z', 'a','t'],p_outlier=.05)
+M_match_vatz.find_starting_values()
+M_match_vatz.sample(10000,burn = 1000, dbname='traces_vatz.db', db='pickle')
+   
+# save the model
+M_match_vatz.save('M_match_vatz')
+# M_match_vatz = hddm.load('M_match_vatz')
+
+# Gelman-Rubbin test
+models_vatz = list()
[…]

### 2018-07-02 Results/HDDM/Exp_MS_HDDM_categ_linux.py
revise code for exp 1

@@ -2,14 +2,26 @@
 """
 Created on Fri Mar 03 21:26:49 2017
 
-@author: hcp47
+last reivsion: 29th Dec 2017
+
+@author: hcp4715
+"""
+
+"""
+Spyder Editor
+
+This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
+This experiment included two tasks: matching judgment and categorization.
+This script used for HDDM analysis of categorization task.
 """
 
 import os
 
 # get the current directory and change the cd
 os.getcwd()
-os.chdir("D:\HCP_cloud\Exp.s\Project1_Moral_reputation_learning\Exp_Behav_Moral_Asso\Exp_Behav_Moral_Asso_7_behav_modeling\Results\Formal_results\HDDM\FinalVersion")
+
+# change the current directory to the working directory
+os.chdir("/home/brain/host/hddm_exp7/")
 
 # get the tool box
 import pandas as pd
@@ -18,11 +30,14 @@ import matplotlib.pyplot as plt
 import hddm
 import time
 
-# Load match data from csv file into a NumPy structured array
+from cycler import cycler
+plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
+
+# load data from cateogriztion based on moral valence
 dat_M_Categ_val = hddm.load_csv('data_Categ_hddm_val_task.csv')
 dat_M_Categ_val.head(10)
 
-# Load match data from csv file into a NumPy structured array
+# load data from cateogriztion based on identity
 dat_M_Categ_id = hddm.load_csv('data_Categ_hddm_ID_task.csv')
 dat_M_Categ_id.head(10)
 
@@ -35,13 +50,16 @@ fig = plt.figure()
 ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
 for i, subj_data in dat_M_Categ_val.groupby('subj_idx'):
     subj_data.rt.hist(bins=20, histtype='step', ax=ax)
+plt.savefig('plot_exp7_Categ_val_flipped.pdf')
     
 fig = plt.figure()
[…]

### 2018-07-02 Results/HDDM/Exp_MS_HDDM_match_linux.py

@@ -2,18 +2,16 @@
 """
 Created on Wed Jul 13 21:55:21 2016
 
-@author: hcp4715
-
-Last revision: 29th Dec. 2017
-
+@author: hcp47
 """
 
 # -*- coding: utf-8 -*-
 """
 Spyder Editor
 
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making.
+This is the script for analyzing the data from matching task in DDM in Hu, etal, in prep.
+This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making
+history: 2018.07.02, updated to py 3 version, deleted redundent codes.
 """
 # %reset #this code will delete all the varibles in the memory
 
@@ -45,15 +43,15 @@ fig = plt.figure()
 ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
 for i, subj_data in dat_M_match.groupby('subj_idx'):
     subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('plot_exp7_match_flipped.pdf')
+plt.savefig('hddm_exp7_L_match2_fig_1.pdf')
 
-#### model 1, free v,t,z
+#### model 1, free v, t,z
 M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'t':['moral','id']}, include=['v', 'z', 't'],p_outlier=.05)
 M_match_vtz.find_starting_values()
-M_match_vtz.sample(10000,burn = 1000, dbname='traces_vtz.db', db='pickle')
+M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
 # save the model
 M_match_vtz.save('M_match_vtz')
-# M_match_vtz = hddm.load('M_match_vtz')
+#M_match_vtz = hddm.load('M_match_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()
@@ -81,13 +79,10 @@ M_match_vtz.plot_posterior_predictive()
 ## DIC
 print("M_match_vtz DIC: %f" % M_match_vtz.dic) # -120.9797
 
[…]

### 2018-07-02 Results/HDDM/HDDM_Moral_Categ_20170125.py

@@ -1,596 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Jul 13 21:55:21 2016
-
-@author: hcp47
-"""
-
-# -*- coding: utf-8 -*-
-"""
-Spyder Editor
-
-This is the script for the drift diffusion model analysis used in Hu, etal, in prep.
-This experiment included two tasks, aimed at exmining the influence of positive in perceptual decision making
-"""
-# %reset #this code will delete all the varibles in the memory
-
-import os
-
-# get the current directory and change the cd
-os.getcwd()
-os.chdir("D:\HCP_cloud\Exp.s\Project1_Moral_reputation_learning\Exp_Behav_Moral_Asso\Exp_Behav_Moral_Asso_7_behav_modeling\Results\Formal_results\HDDM\FinalVersion")
-
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-
-# Load match data from csv file into a NumPy structured array
-dat_M_match = hddm.load_csv('data_M_match_hddm.csv')
-dat_M_match.head(10)
-
-# flip the error RTs to be negative
-dat_M_match = hddm.utils.flip_errors(dat_M_match)
-
-# check the RT distritubtion
-fig = plt.figure()
-ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
-for i, subj_data in dat_M_match.groupby('subj_idx'):
-    subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('hddm_exp7_L_match2_fig_1.pdf')
-
-#### model 1, free v,a,t,z
-M_match_vatz = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'a':['moral','id'],'t':['moral','id']}, include=['v', 'z', 'a','t'],p_outlier=.05)
-M_match_vatz.find_starting_values()
-M_match_vatz.sample(10000,burn = 1000, dbname='traces_vatz.db', db='pickle')
-   
-# save the model
-M_match_vatz.save('M_match_vatz')
-# M_match_vatz = hddm.load('M_match_vatz')
-
-# Gelman-Rubbin test
-models_vatz = list()
[…]

### 2018-07-03 Replication/Results/data_analysis/preproc/Analysis_exp7_rep_prepro.rmd
revise exp1's code

--- 2018-07-01 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
@@
 
-```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+```{r loadingData_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
 # read these files and combine them into one file, get the raw data for matching task

### 2018-07-03 Results/Traditional_Analysis/Analysis_exp7_2.rmd
revise exp1's code

--- 2017-12-30 Traditional_Analysis/Analysis_exp7_2.rmd
@@
 ```{r Initializing, include=FALSE}
-Sys.setlocale("LC_ALL", "English")  # set local encoding to English
-Sys.setenv(LANG = "en") # set the feedback language to English
-options(scipen = 999)   # force R to output in decimal instead of scientifc notion
-options(digits=5)       # limit the number of reporting
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
-pkgTest <- function(x)
- {
-   if (!require(x,character.only = TRUE))
-  {
-    install.packages(x,dep = TRUE)
-   if(!require(x,character.only = TRUE)) stop("Package not found")
-  }
-}
-
-pkgNeeded <- (c("plyr","tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))
-
-lapply(pkgNeeded,pkgTest) # please pay attention to the overlap between differen libraries.
-rm(pkgNeeded)             # remove the pkgNeeded variable
-
-# using APA style plot for later use
-windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
-apatheme=theme_bw()+
-        theme(panel.grid.major = element_blank(),
-              panel.grid.minor = element_blank(),
-              panel.background = element_blank(),
-              panel.border = element_blank(),
-              text=element_text(family='Times'),
-              legend.title=element_blank(),
-              legend.position='top',
-              axis.line.x = element_line(color='black'),
-              axis.line.y = element_line(color='black'))
-
-# define the d prime function
-dprime <- function(hit,fa) {
-        qnorm(hit) - qnorm(fa)
-}
-
-## code for calculate the summary with sE, adopted from cook book for R
-summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
-                      conf.interval=.95, .drop=TRUE) {
-        library(plyr)
-
-        # New version of length which can handle NA's : if na.rm == T, don't count the
-        length2 <- function(x, na.rm=FALSE){
-                if(na.rm) sum(!is.na(x))
-                else      length(x)
-        }
-
-        # this does the summary. For each group's data frame, return a vector with
-        # N, mean, and sd
-        datac <- ddply(data,groupvars, .drop=.drop,
-                       .fun = function(xx,col){
-                        c(N    = length2(xx[[col]],na.rm=na.rm),
-                          mean = mean(xx[[col]],na.rm=na.rm),
-                          sd   = sd  (xx[[col]],na.rm=na.rm)
-                           )
-                       },
-                       measurevar
-                       )
-        # Rename the "mean" column
-
-        datac <- plyr::rename(datac,c("mean" = measurevar))
-
-        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean
-
-        # Confidence interval mltiplier for standard error
-        # calculate t-statistic for confidence interval:
-        # e.g., if conf.interval is .95, use .975 (above/below), and use df.L1 = N-1
-        ciMult <- qt(conf.interval/2 + .5, datac$N-1)
-        datac$ci <- datac$se * ciMult
-
-        return (datac)
-}
-
-## code for calculate the summary with sE for within subject data, adopted from cook book for R
-summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {
-
-        # Ensure that the betweenvars and withinvars are factors
-        factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
-                             FUN=is.factor, FUN.VALUE=logical(1))
-
-        if (!all(factorvars)) {
-                nonfactorvars <- names(factorvars)[!factorvars]
-                message("Automatically converting the following non-factors to factors: ",
-                        paste(nonfactorvars, collapse = ", "))
-                data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
-        }
-
-        # Get the means from the un-normed data
-        datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
-                           na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
-
-        # Drop all the unused columns (these will be calculated with normed data)
-        datac$sd <- NULL
-        datac$se <- NULL
-        datac$ci <- NULL
-
-        # Norm each subject's data
-        ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)
-
-        # This is the name of the new column
-        measurevar_n <- paste(measurevar, "_norm", sep="")
-
-        # Collapse the normed data - now we can treat between and within vars the same
-        ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
-                            na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
-
-        # Apply correction from Morey (2008) to the standard error and confidence interval
-        #  Get the product of the number of conditions of within-S variables
-        nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
-                                        FUN.VALUE=numeric(1)))
-        correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )
-
-        # Apply the correction factor
-        ndatac$sd <- ndatac$sd * correctionFactor
-        ndatac$se <- ndatac$se * correctionFactor
-        ndatac$ci <- ndatac$ci * correctionFactor
-
-        # Combine the un-normed means with the normed results
-        merge(datac, ndatac)
-}
-
-### code for normalizing the SE
-normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
-                           na.rm=FALSE, .drop=TRUE) {
-        library(plyr)
-
-        # Measure var on left, idvar + between vars on right of formula.
-        data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
-                               .fun = function(xx, col, na.rm) {
-                                       c(subjMean = mean(xx[,col], na.rm=na.rm))
-                               },
-                               measurevar,
-                               na.rm
-        )
-
-        # Put the subject means with original data
-        data <- merge(data, data.subjMean)
-
-        # Get the normalized data in a new column
-        measureNormedVar <- paste(measurevar, "_norm", sep="")
-        data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
-                mean(data[,measurevar], na.rm=na.rm)
-
-        # Remove this subject mean column
-        data$subjMean <- NULL
-
-        return(data)
-}
-
-#
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-        library(grid)
-
-        # Make a list from the ... arguments and plotlist
-        plots <- c(list(...), plotlist)
-
-        numPlots = length(plots)
-
-        # If layout is NULL, then use 'cols' to determine layout
-        if (is.null(layout)) {
-                # Make the panel
-                # ncol: Number of columns of plots
-                # nrow: Number of rows needed, calculated from # of cols
-                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                                 ncol = cols, nrow = ceiling(numPlots/cols))
-        }
-
-        if (numPlots==1) {
-                print(plots[[1]])
-
-        } else {
-                # Set up the page
-                grid.newpage()
-                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-
-                # Make each plot, in the correct location
-                for (i in 1:numPlots) {
-                        # Get the i,j matrix positions of the regions that contain this subplot
-                        matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-
-                        print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                                        layout.pos.col = matchidx$col))
-                }
-        }
-}
-
+source('Initial.r')
+curDir <- getwd()   # directory for preprocessing
+rootDir <- gsub('.{7}$', '', curDir)
+#rawDir <- paste(curDir,'/data/',sep = '')
+traDir <- paste(rootDir,'Traditional_Analysis',sep = '')
+ddmDir <- paste(rootDir,'HDDM',sep = '')
 ```
@@
 ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
+
+# get the data file for hddm analysis
+
+df.L.ddm.v <- df.L[!(df.L$Subject %in% c(procFailureSub,excld.sub)),]   # exclude the invalid subjects
+
+df.T.ddm.v <- df.T[!(df.T$Subject %in% c(procFailureSub,excld.sub)),]
+df.T.ddm.v <- df.T.ddm.v[!(df.T.ddm.v$Subject %in% excld.sub.T),]
+df.T.ddm.v <- df.T[df.T$Task != 'importance',]  # exclude the results from importance task
+
+#df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
+#df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]
+
+#df.L1.valid <- df.L1.fm[!(df.L1.fm$Subject %in% excld.sub),]
+#df.T1.valid <- df.T1[!(df.T1$Subject %in% excld.sub),]
+#df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]
+
+df.L.hddm <- subset(df.L.ddm.v, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
+df.T.hddm <- subset(df.T.ddm.v, ACC ==1 | ACC == 0)
+
+df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
+df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
+colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
+
+df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
+df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')
+
+df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
+df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')
+
+df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
+df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')
+
+setwd(ddmDir)
+write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
+write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
+write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
+write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
+rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
+setwd(curDir)
 ```
@@
 ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
+
+MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
 

### 2018-07-03 Results/Traditional_Analysis/geom_flat_violin.R

@@ -1,0 +1,83 @@
+# This script is from: https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R
+#
+# somewhat hackish solution to:
+# https://twitter.com/EamonCaddigan/status/646759751242620928
+# based mostly on copy/pasting from ggplot2 geom_violin source:
+# https://github.com/hadley/ggplot2/blob/master/R/geom-violin.r
+
+library(ggplot2)
+library(dplyr)
+
+
+"%||%" <- function(a, b) {
+  if (!is.null(a)) a else b
+}
+
+geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
+                        position = "dodge", trim = TRUE, scale = "area",
+                        show.legend = NA, inherit.aes = TRUE, ...) {
+  layer(
+    data = data,
+    mapping = mapping,
+    stat = stat,
+    geom = GeomFlatViolin,
+    position = position,
+    show.legend = show.legend,
+    inherit.aes = inherit.aes,
+    params = list(
+      trim = trim,
+      scale = scale,
+      ...
+    )
+  )
+}
+
+#' @rdname ggplot2-ggproto
+#' @format NULL
+#' @usage NULL
+#' @export
+GeomFlatViolin <-
+  ggproto("GeomFlatViolin", Geom,
+          setup_data = function(data, params) {
+            data$width <- data$width %||%
+              params$width %||% (resolution(data$x, FALSE) * 0.9)
+            
+            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
+            data %>%
+              group_by(group) %>%
+              mutate(ymin = min(y),
+                     ymax = max(y),
+                     xmin = x,
+                     xmax = x + width / 2)
+            
+          },
+          
+          draw_group = function(data, panel_scales, coord) {
+            # Find the points for the line to go all the way around
+            data <- transform(data, xminv = x,
+                              xmaxv = x + violinwidth * (xmax - x))
+            
+            # Make sure it's sorted properly to draw the outline
+            newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
+                             plyr::arrange(transform(data, x = xmaxv), -y))
+            
+            # Close the polygon: set first and last point the same
+            # Needed for coord_polar and such
[…]

### 2018-07-03 Results/preproc/trans_Data.r

@@ -1,0 +1,93 @@
+# this script is used for transfer raw data to usable and sharable data
+
+# initializing
+source('Initial.r')
+
+# set directory
+curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
+rootDir <- gsub('.{7}$', '', curDir)
+rawDir  <- paste(curDir,'/rawData/',sep = '')
+traDir  <- paste(rootDir,'Traditional_Analysis',sep = '')
+ddmDir  <- paste(rootDir,'HDDM',sep = '')
+
+setwd(rawDir)
+file_list.match <- list.files(path = ".", pattern = "*_learn*")
+file_list.categ <- list.files(path = ".", pattern = "*_test*")
+
+# merge the data from each participant
+for (fileL in file_list.match){
+  # if the merged dataset doesn't exist, creat it
+  if (!exists("df.M")){
+    df.M <- read.csv(fileL,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+  }
+  
+  # if the merged dataset does exist, append to it
+  if (exists("df.M")){
+    temp_df.L <- read.csv(fileL,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+    df.M <- rbind(df.M,temp_df.L)
+    rm(temp_df.L)
+  }
+}
+df.M <- subset(df.M,SubjectID != "SubjectID")  # there should be 18672 obs. of 19 variables.
+# write.csv(df.M,"df.Learn.csv", row.names=FALSE)
+
+for (fileT in file_list.categ){
+  # if the merged dataset doesn't exist, creat it
+  if (!exists("df.C")){
+    df.C <- read.csv(fileT,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+  }
+  
+  # if the merged dataset does exist, append to it
+  if (exists("df.C")){
+    temp_df.T <- read.csv(fileT,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+    df.C <- rbind(df.C,temp_df.T)
+    rm(temp_df.T)
+  }
+}
+df.C <- subset(df.C,SubjectID != "SubjectID")   # there should be 29808 obs. of 19 variables
+# write.csv(df.C,"df.Test.csv", row.names=FALSE)  # save the data
+
+setwd(curDir)
+# render the data in numeric format for future analysis
[…]

### 2018-07-04 Results/preproc/MS_ddm_preproc.rmd
revising exp1's code

--- 2018-07-03 Results/Traditional_Analysis/Analysis_exp7_2.rmd
@@
 
-This script is aimed at making the analysis of the experiment 7 reproducible. We analyzezd the data using the traditional ways (d prime/Accuracy and mean of RT)
+This script is aimed at making the analysis of the moral self experiment (DDM) reproducible. We analyzezd the data using the traditional ways (d prime/Accuracy and mean of RT)
 
@@
 source('Initial.r')
-curDir <- getwd()   # directory for preprocessing
+curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
 rootDir <- gsub('.{7}$', '', curDir)
@@
 ```{r loadingData_e7,echo=FALSE,results='hide'}
-df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
-df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task
-
-# render the data in numeric format for future analysis
-cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
-df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)  
-df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)
-
-# rename columns
-colnames(df.L)[colnames(df.L)=="Accuracy"]  <- "ACC"
-colnames(df.T)[colnames(df.T)=="Accuracy"]  <- "ACC"
-colnames(df.L)[colnames(df.L)=="SubjectID"] <- "Subject"
-colnames(df.T)[colnames(df.T)=="SubjectID"] <- "Subject"
-
-df.L$Subject <- factor(df.L$Subject)
-df.T$Subject <- factor(df.T$Subject)
-
-# Change the name for different levels of independent variables
-df.L$Morality[df.L$Morality == 'moral']   <- 'Good'
-df.L$Morality[df.L$Morality == 'immoral'] <- 'Bad'
-df.L$Identity[df.L$Identity == 'self']    <- 'Self'
-df.L$Identity[df.L$Identity == 'other']   <- 'Other'
+df.M <- read.csv("MS_matchTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
+df.C <- read.csv("MS_categTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task
 
 # make the variables in a specified order
-df.L$Morality <- factor(df.L$Morality, levels = c("Good","Bad"))    
-df.L$Identity <- factor(df.L$Identity, levels = c("Self","Other"))  
-df.L$Match    <- factor(df.L$Match,    levels = c("match","nonmatch"))
-
-# Change the name for different levels of independent variables
-df.T$Morality[df.T$Morality == 'moral']   <- 'Good'
-df.T$Morality[df.T$Morality == 'immoral'] <- 'Bad'
-df.T$Identity[df.T$Identity == 'self']    <- 'Self'
-df.T$Identity[df.T$Identity == 'other']   <- 'Other'
-df.T$Task[df.T$Task == 'Self']            <- 'ID'
-df.T$Task[df.T$Task == 'self']            <- 'Id_task'
-df.T$Task[df.T$Task == 'moral']           <- 'Valence_task'
+df.M$Morality <- factor(df.M$Morality, levels = c("Good","Bad"))    
+df.M$Identity <- factor(df.M$Identity, levels = c("Self","Other"))  
+df.M$Match    <- factor(df.M$Match,    levels = c("match","nonmatch"))
 
 # make the variables in a specified order
-df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
-df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
-```
-
-```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.L1 <- df.L
-df.T1 <- df.T
-df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
-df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian
-
-# no response equal to wrong
-df.L1$ACC[df.L1$ACC == -1] <- 0
-
-# excluded data from subjects whose trials number are not normal
-procFailureSub <- c("7","8","2027","7035")
-df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
-df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]
-df.T1 <- df.T1[df.T1$Task != 'importance',]  # exclude the results from importance task
-
-# delete the practicing trials (first 48 trials)
-subNo <- unique(df.L1$Subject)
+df.C$Morality <- factor(df.C$Morality, levels=c("Good","Bad"))    
+df.C$Identity <- factor(df.C$Identity, levels=c("Self","Other"))
+
+# Clear data for all following analysis
+
+# Exclude Subject, criterion 1: procedure failure
+excldSub1 <- c("7","8","2027","7035")
+df.M <- df.M[!(df.M$Subject %in% excldSub1),]
+df.C <- df.C[!(df.C$Subject %in% excldSub1),]
+
+# exclude trials, criterio 1: no importance-based trials
+df.C <- df.C[df.C$Task != 'importance',]  # exclude the results from importance task, should be 17856 rows
+
+# exclude trials, criterio 2: practicing trials in matching task (first 48 trials)
+subNo <- unique(df.M$Subject)
 for (subj in subNo) {
-        if (exists('df.L1.fm')){
-                df.tmp <- df.L1[df.L1$Subject == subj,]
+        if (exists('df.M.fm')){
+                df.tmp <- df.M[df.M$Subject == subj,]
                 df.tmp <- df.tmp[49:nrow(df.tmp),]
-                df.L1.fm <- rbind(df.L1.fm,df.tmp)
+                df.M.fm <- rbind(df.M.fm,df.tmp)
         } else {
-                df.L1.fm <- df.L1[df.L1$Subject == subj,]
-                df.L1.fm <- df.L1.fm[49:nrow(df.L1.fm),]
+                df.M.fm <- df.M[df.M$Subject == subj,]
+                df.M.fm <- df.M.fm[49:nrow(df.M.fm),]
         }
-}
-
-rm(subNo)
+}   # df.M.fm should be 14880 rows
+df.M <- df.M.fm  # all the experimental trials
+rm(subNo,df.M.fm,df.tmp)
+
+# exlude subject criterion 2: less than 50% overall accuracy
+# change no response to error
+df.M.tmp <- df.M
+df.M.tmp$ACC[df.M.tmp$ACC == -1] <- 0
+df.C.tmp <- df.C
+df.C.tmp$ACC[df.C.tmp$ACC == -1] <- 0
 
 # calculate the overall accuracy for matching task
-df.L1.acc.g <-  ddply(df.L1.fm,.(Subject), summarise,
+df.M.acc.g <-  ddply(df.M.tmp,.(Subject), summarise,
                     N = length(ACC),
@@
 # calculate the overall accuracy for categorziation task
-df.T1.acc.g <-  ddply(df.T1,.(Subject), summarise,
+df.C.acc.g <-  ddply(df.C.tmp,.(Subject), summarise,
                     N = length(ACC),
@@
 
-excld.sub   <- df.L1.acc.g$Subject[df.L1.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
-excld.sub.T <- df.T1.acc.g$Subject[df.T1.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
-df.L1.valid <- df.L1.fm[!(df.L1.fm$Subject %in% excld.sub),]   # exclude the invalid subjects
-df.T1.valid <- df.T1[!(df.T1$Subject %in% excld.sub),]
-df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]
-
-# check the number of participants are correct
-length(unique(df.L1.valid$Subject)) + length(excld.sub) == length(unique(df.L1$Subject))
-# excld.trials3 <- excld.trials[!(excld.trials$Subject %in% excld.sub),]
-excld.trials.L <- df.L1.valid[df.L1.valid$RT <= 200,]
-df.L1.V        <- df.L1.valid[!(df.L1.valid$RT <= 200),]  # valid trial data for match task
-excld.trials.T <- df.T1.valid[df.T1.valid$RT <= 200,]
-df.T1.V        <- df.T1.valid[!(df.T1.valid$RT <= 200),]  # valid trial data for categorization task
-nrow(excld.trials.T) + nrow(df.T1.V) == nrow(df.T1.valid) # if true, everything is ok
+excldSub2.M <- df.M.acc.g$Subject[df.M.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
+excldSub2.C <- df.C.acc.g$Subject[df.C.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
+df.M.valid <- df.M[!(df.M$Subject %in% excldSub2.M),]        # exclude the invalid subjects
+df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.C),]
+df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),]
+rm(df.M,df.C,df.M.tmp,df.C.tmp)
+```
+
+```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+# clean data for traditional analysis
+df.M1 <- df.M.valid
+df.C1 <- df.C.valid
+df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
+df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian
+
+# no response equal to wrong
+df.M1$ACC[df.M1$ACC == -1] <- 0
+df.C1$ACC[df.C1$ACC == -1] <- 0
+
+# excld.trials, criterion 2: correct response within 200 ms
+excld.trials.M <- df.M1[df.M1$RT <= 200,]
+df.M1.V        <- df.M1[!(df.M1$RT <= 200),]  # valid trial data for match task
+excld.trials.C <- df.C1[df.C1$RT <= 200,]
+df.C1.V        <- df.C1[!(df.C1$RT <= 200),]  # valid trial data for categorization task
+nrow(excld.trials.C) + nrow(df.C1.V) == nrow(df.C1) # if true, everything is ok
 
 ## Basic information of the data ####
-df.L1.T.basic <- df.L1[!duplicated(df.L1$Subject), 1:4]
-numT.subj <- nrow(df.L1.T.basic)
-numT.female <- sum(df.L1.T.basic$Gender == 'female');
-numT.male <- sum(df.L1.T.basic$Gender == 'male');
-ageT.mean <- round(mean(df.L1.T.basic$Age),2);
-ageT.std <- round(sd(df.L1.T.basic$Age),2);
-num.excld.sub <- length(unique(excld.sub))
-num.excld.sub.T <- length(unique(excld.sub.T))
+df.M1.T.basic <- df.M1[!duplicated(df.M1$Subject), 1:4]
+numT.subj <- nrow(df.M1.T.basic)
+numT.female <- sum(df.M1.T.basic$Gender == 'female');
+numT.male <- sum(df.M1.T.basic$Gender == 'male');
+ageT.mean <- round(mean(df.M1.T.basic$Age),2);
+ageT.std <- round(sd(df.M1.T.basic$Age),2);
+num.excldSub2.M <- length(unique(excldSub2.M))
+num.excldSub2.C <- length(unique(excldSub2.C))
 
 # valide data for matching task
-df.L1.V.basic <- df.L1.V[!duplicated(df.L1.V$Subject), 1:4]
-numV.female <- sum(df.L1.V.basic$Gender == 'female');
-numV.male <- sum(df.L1.V.basic$Gender == 'male');
-ageV.mean <- round(mean(df.L1.V.basic$Age),2);
-ageV.std <- round(sd(df.L1.V.basic$Age),2);
-ratio.excld.trials.L <- nrow(excld.trials.L)/nrow(df.L1.valid)
-ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
+df.M1.V.basic <- df.M1.V[!duplicated(df.M1.V$Subject), 1:4]
+numV.female <- sum(df.M1.V.basic$Gender == 'female');
+numV.male <- sum(df.M1.V.basic$Gender == 'male');
+ageV.mean <- round(mean(df.M1.V.basic$Age),2);
+ageV.std <- round(sd(df.M1.V.basic$Age),2);
+ratio.excld.trials.M <- nrow(excld.trials.M)/nrow(df.M1)
 
 # valid data for categorization task
-df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 1:4]
-numV.female.T <- sum(df.T1.V.basic$Gender == 'female');
-numV.male.T <- sum(df.T1.V.basic$Gender == 'male');
-ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
-ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
-ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
+df.C1.V.basic <- df.C1.V[!duplicated(df.C1.V$Subject), 1:4]
+numV.female.C <- sum(df.C1.V.basic$Gender == 'female');
+numV.male.C <- sum(df.C1.V.basic$Gender == 'male');
+ageV.mean.C <- round(mean(df.C1.V.basic$Age),2);
+ageV.std.C <- round(sd(df.C1.V.basic$Age),2);
+ratio.excld.trials.C <- nrow(excld.trials.C)/nrow(df.C1)
+
+rm(df.M1,df.C1) # remove the no longer used varibles.
 
 # get the data file for hddm analysis
-
-df.L.ddm.v <- df.L[!(df.L$Subject %in% c(procFailureSub,excld.sub)),]   # exclude the invalid subjects
-
-df.T.ddm.v <- df.T[!(df.T$Subject %in% c(procFailureSub,excld.sub)),]
-df.T.ddm.v <- df.T.ddm.v[!(df.T.ddm.v$Subject %in% excld.sub.T),]
-df.T.ddm.v <- df.T[df.T$Task != 'importance',]  # exclude the results from importance task
-
-#df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
-#df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]
-
-#df.L1.valid <- df.L1.fm[!(df.L1.fm$Subject %in% excld.sub),]
-#df.T1.valid <- df.T1[!(df.T1$Subject %in% excld.sub),]
-#df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]
-
-df.L.hddm <- subset(df.L.ddm.v, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
-df.T.hddm <- subset(df.T.ddm.v, ACC ==1 | ACC == 0)
-
-df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
-df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
-colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
-
-df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
-df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')
-
-df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
-df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')
-
-df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
-df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')
+df.M.ddm.v <- df.M.valid   # exclude the invalid subjects
+df.C.ddm.v <- df.C.valid
+
+# exclusion trials, criterion: trials without response or wrong key
+# Note: we didn't remove the correct response less than 200 ms
+df.M.hddm <- subset(df.M.ddm.v, ACC ==1 | ACC == 0)  
+df.C.hddm <- subset(df.C.ddm.v, ACC ==1 | ACC == 0)
+
+df.M.hddm_m <- subset(df.M.hddm, Match == 'match') # select data
+df.M.hddm_m <- df.M.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
+colnames(df.M.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
+
+df.M.hddm_nm <- subset(df.M.hddm, Match == 'nonmatch')
+df.M.hddm_nm <- df.M.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.M.hddm_nm) <- c("subj_idx","val",'id','rt','response')
+
+df.C.hddm_val <- subset(df.C.hddm, Task == 'Val')
+df.C.hddm_val <- df.C.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.C.hddm_val) <- c("subj_idx","val",'id','rt','response')
+
+df.C.hddm_id <- subset(df.C.hddm, Task == 'Id')
+df.C.hddm_id <- df.C.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
+colnames(df.C.hddm_id) <- c("subj_idx","val",'id','rt','response')
 
 setwd(ddmDir)
-write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
-write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
-write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
-write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
-rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
+write.csv(df.M.hddm_m,'MS_match_hddm.csv',row.names = F)
+write.csv(df.M.hddm_nm,'MS_mismatch_hddm.csv',row.names = F)
+write.csv(df.C.hddm_val,'MS_categ_val_hddm.csv',row.names = F)
+write.csv(df.C.hddm_id,'MS_categ_id_hddm.csv',row.names = F)
 setwd(curDir)
+rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
 ```
 ## Participants
-`r numT.subj+length(procFailureSub)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7.
+`r numT.subj+length(excldSub1)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7.
 All partcipants were right handed, and all had normal or corrected-to-normal vision.
 Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee.
-Data of `r length(procFailureSub)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task.
+Data of `r length(excldSub1)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task.
 `r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.
@@
 # calculate the number of hit,CR,miss or FA 
-df.L1.V$sdt <- NA
-for (i in 1:nrow(df.L1.V)){
-        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
-                df.L1.V$sdt[i] <- "hit"
-        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
-                df.L1.V$sdt[i] <- "CR"
-        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
-                df.L1.V$sdt[i] <- "miss"
-        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
-                df.L1.V$sdt[i] <- "FA"
+df.M1.V$sdt <- NA
+for (i in 1:nrow(df.M1.V)){
+        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
+                df.M1.V$sdt[i] <- "hit"
+        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
+                df.M1.V$sdt[i] <- "CR"
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
+                df.M1.V$sdt[i] <- "miss"
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
+                df.M1.V$sdt[i] <- "FA"
         }
@@
 # calculate the number of each for each condition
-df.L1.V.SDT <-  ddply(df.L1.V,.(Subject,Morality, Identity,sdt), summarise, N = length(sdt))
-df.L1.V.SDT <- df.L1.V.SDT[complete.cases(df.L1.V.SDT$sdt),] # exclude NA, which represents no-response trials
+df.M1.V.SDT <-  ddply(df.M1.V,.(Subject,Morality, Identity,sdt), summarise, N = length(sdt))
+df.M1.V.SDT <- df.M1.V.SDT[complete.cases(df.M1.V.SDT$sdt),] # exclude NA, which represents no-response trials
 
 # long format to wide
-df.L1.V.SDT_w <- dcast(df.L1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
-df.L1.V.SDT_w$miss[is.na(df.L1.V.SDT_w$miss)] <- 0 # transfer NA to 0
-df.L1.V.SDT_w$FA[is.na(df.L1.V.SDT_w$FA)]     <- 0
-df.L1.V.SDT_w$hitR <- df.L1.V.SDT_w$hit/(df.L1.V.SDT_w$hit + df.L1.V.SDT_w$miss)
-df.L1.V.SDT_w$faR <- df.L1.V.SDT_w$FA/(df.L1.V.SDT_w$FA + df.L1.V.SDT_w$CR)
+df.M1.V.SDT_w <- dcast(df.M1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
+df.M1.V.SDT_w$miss[is.na(df.M1.V.SDT_w$miss)] <- 0 # transfer NA to 0
+df.M1.V.SDT_w$FA[is.na(df.M1.V.SDT_w$FA)]     <- 0
+df.M1.V.SDT_w$hitR <- df.M1.V.SDT_w$hit/(df.M1.V.SDT_w$hit + df.M1.V.SDT_w$miss)
+df.M1.V.SDT_w$faR <- df.M1.V.SDT_w$FA/(df.M1.V.SDT_w$FA + df.M1.V.SDT_w$CR)
 
 # standardized way to deal with the extreme values
-for (i in 1:nrow(df.L1.V.SDT_w)){
-        if (df.L1.V.SDT_w$hitR[i] == 1){
-                df.L1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.L1.V.SDT_w$hit[i] + df.L1.V.SDT_w$miss[i]))
+for (i in 1:nrow(df.M1.V.SDT_w)){
+        if (df.M1.V.SDT_w$hitR[i] == 1){
+                df.M1.V.SDT_w$hitR[i] <- 1 - 1/(2*(df.M1.V.SDT_w$hit[i] + df.M1.V.SDT_w$miss[i]))
         }
@@
 # calculate the d prime for each condition
-df.L1.V.SDT_w$dprime <- mapply(dprime,df.L1.V.SDT_w$hitR,df.L1.V.SDT_w$faR)
+df.M1.V.SDT_w$dprime <- mapply(dprime,df.M1.V.SDT_w$hitR,df.M1.V.SDT_w$faR)
 
 # transfor from long format to wide format
-df.L1.V.SDT_ww <- dcast(df.L1.V.SDT_w, Subject ~ Identity + Morality ,value.var = "dprime")
+df.M1.V.SDT_ww <- dcast(df.M1.V.SDT_w, Subject ~ Identity + Morality ,value.var = "dprime")
 
 # anova for d prime with 2*2 design
-e7_L.d_anova <- ezANOVA(df.L1.V.SDT_w,dv = dprime, wid = Subject, within=.(Morality,Identity), type=3)
-
-df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)  # make the subject "factor"
+e7_L.d_anova <- ezANOVA(df.M1.V.SDT_w,dv = dprime, wid = Subject, within=.(Morality,Identity), type=3)
+
+df.M1.V.SDT_w$Subject <- factor(df.M1.V.SDT_w$Subject)  # make the subject "factor"
 
 # using Bayesfactor analysis (which is not reported in the document)
-e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")
+e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.M1.V.SDT_w, whichRandom = "Subject")
 
 # Good self vs Bad self
-e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
-df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad                   # calculate the differences
-e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES
+e7_L.d.t.good_bad_slf <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
+df.M1.V.SDT_ww$good_bad_slf <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Self_Bad                   # calculate the differences
+e7_L.d.t.good_bad_slf.CI <- bootES(df.M1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES
 
@@
 e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
-e7_L.d.df.L1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
+e7_L.d.df.M1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
 e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
@@
 # Good other vs. Bad other
-e7_L.d.t.good_bad_oth <- t.test(df.L1.V.SDT_ww$Other_Good,df.L1.V.SDT_ww$Other_Bad,paired = TRUE)
-df.L1.V.SDT_ww$good_bad_oth <- df.L1.V.SDT_ww$Other_Good - df.L1.V.SDT_ww$Other_Bad
-e7_L.d.t.good_bad_oth.CI <- bootES(df.L1.V.SDT_ww$good_bad_oth,R = 20000, effect.type = "cohens.d")
+e7_L.d.t.good_bad_oth <- t.test(df.M1.V.SDT_ww$Other_Good,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
+df.M1.V.SDT_ww$good_bad_oth <- df.M1.V.SDT_ww$Other_Good - df.M1.V.SDT_ww$Other_Bad
+e7_L.d.t.good_bad_oth.CI <- bootES(df.M1.V.SDT_ww$good_bad_oth,R = 20000, effect.type = "cohens.d")
 
 e7_L.d.tvalue.good_bad_oth  <- round(as.numeric(e7_L.d.t.good_bad_oth[[1]]),3)
-e7_L.d.df.L1.good_bad_oth  <- as.numeric(e7_L.d.t.good_bad_oth[[2]])
+e7_L.d.df.M1.good_bad_oth  <- as.numeric(e7_L.d.t.good_bad_oth[[2]])
 e7_L.d.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_oth[[3]]),"bonferroni",4)
@@
 # Good self vs Good other
-e7_L.d.t.slf_oth_good <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Other_Good,paired = TRUE)
-df.L1.V.SDT_ww$slf_oth_good <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Other_Good
-e7_L.d.t.slf_oth_good.CI <- bootES(df.L1.V.SDT_ww$slf_oth_good,R = 20000, effect.type = "cohens.d")
+e7_L.d.t.slf_oth_good <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Other_Good,paired = TRUE)
+df.M1.V.SDT_ww$slf_oth_good <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Other_Good
+e7_L.d.t.slf_oth_good.CI <- bootES(df.M1.V.SDT_ww$slf_oth_good,R = 20000, effect.type = "cohens.d")
 
 e7_L.d.tvalue.slf_oth_good  <- round(as.numeric(e7_L.d.t.slf_oth_good[[1]]),3)
-e7_L.d.df.L1.slf_oth_good  <- as.numeric(e7_L.d.t.slf_oth_good[[2]])
+e7_L.d.df.M1.slf_oth_good  <- as.numeric(e7_L.d.t.slf_oth_good[[2]])
 e7_L.d.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_good[[3]]),"bonferroni",4)
@@
 # Bad self vs. Bad other
-e7_L.d.t.slf_oth_bad <- t.test(df.L1.V.SDT_ww$Self_Bad,df.L1.V.SDT_ww$Other_Bad,paired = TRUE)
-df.L1.V.SDT_ww$slf_oth_bad <- df.L1.V.SDT_ww$Self_Bad - df.L1.V.SDT_ww$Other_Bad
-e7_L.d.t.slf_oth_bad.CI <- bootES(df.L1.V.SDT_ww$slf_oth_bad,R = 20000, effect.type = "cohens.d")
+e7_L.d.t.slf_oth_bad <- t.test(df.M1.V.SDT_ww$Self_Bad,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
+df.M1.V.SDT_ww$slf_oth_bad <- df.M1.V.SDT_ww$Self_Bad - df.M1.V.SDT_ww$Other_Bad
+e7_L.d.t.slf_oth_bad.CI <- bootES(df.M1.V.SDT_ww$slf_oth_bad,R = 20000, effect.type = "cohens.d")
 
 e7_L.d.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.d.t.slf_oth_bad[[1]]),3)
-e7_L.d.df.L1.slf_oth_bad <- as.numeric(e7_L.d.t.slf_oth_bad[[2]])
+e7_L.d.df.M1.slf_oth_bad <- as.numeric(e7_L.d.t.slf_oth_bad[[2]])
 e7_L.d.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_bad[[3]]),"bonferroni",4)
@@
 #####save the dprime and ACC data for late used ####
-colnames(df.L1.V.SDT_ww) <- paste("L_d", colnames(df.L1.V.SDT_ww), sep = "_")
-write.csv(df.L1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
-df.L1.V.acc <-  ddply(df.L1.V,.(Subject,Match,Identity,Morality), summarise,
+colnames(df.M1.V.SDT_ww) <- paste("L_d", colnames(df.M1.V.SDT_ww), sep = "_")
+write.csv(df.M1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
+df.M1.V.acc <-  ddply(df.M1.V,.(Subject,Match,Identity,Morality), summarise,
                     N = length(ACC),
@@
                     ACC = sum(ACC)/length(ACC))
-df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
-df.L1.V.acc_w$good_bad_slf <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Self_Bad
-df.L1.V.acc_w$good_oth <- df.L1.V.acc_w$match_Other_Good - df.L1.V.acc_w$match_Other_Bad
-df.L1.V.acc_w$slf_oth_good <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Other_Good
-df.L1.V.acc_w$slf_oth_bad <- df.L1.V.acc_w$match_Self_Bad - df.L1.V.acc_w$match_Other_Bad
-
-colnames(df.L1.V.acc_w) <- paste("L_acc", colnames(df.L1.V.acc_w), sep = "_")
-colnames(df.L1.V.acc_w)[colnames(df.L1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
-write.csv(df.L1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
+df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
+df.M1.V.acc_w$good_bad_slf <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Self_Bad
+df.M1.V.acc_w$good_oth <- df.M1.V.acc_w$match_Other_Good - df.M1.V.acc_w$match_Other_Bad
+df.M1.V.acc_w$slf_oth_good <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Other_Good
+df.M1.V.acc_w$slf_oth_bad <- df.M1.V.acc_w$match_Self_Bad - df.M1.V.acc_w$match_Other_Bad
+
+colnames(df.M1.V.acc_w) <- paste("L_acc", colnames(df.M1.V.acc_w), sep = "_")
+colnames(df.M1.V.acc_w)[colnames(df.M1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
+write.csv(df.M1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
 ##### save data for later analysis ####
 
-df.L1.V.SDT.sum      <- summarySE(df.L1.V.SDT_w,measurevar = 'dprime',groupvars = c('Morality','Identity'))
-e7_L.d.mean.GoodSelf <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.sd.GoodSelf   <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.mean.BadSelf  <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.sd.BadSelf    <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Self'],3)
-
-e7_L.d.mean.GoodOther <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.sd.GoodOther   <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Good' & df.L1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.mean.BadOther  <- round(df.L1.V.SDT.sum$dprime[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.sd.BadOther    <- round(df.L1.V.SDT.sum$sd[df.L1.V.SDT.sum$Morality == 'Bad' & df.L1.V.SDT.sum$Identity == 'Other'],3)
-
-e7_L.p_dprime1 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
+df.M1.V.SDT.sum      <- summarySE(df.M1.V.SDT_w,measurevar = 'dprime',groupvars = c('Morality','Identity'))
+e7_L.d.mean.GoodSelf <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
+e7_L.d.sd.GoodSelf   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
+e7_L.d.mean.BadSelf  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)
+e7_L.d.sd.BadSelf    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)
+
+e7_L.d.mean.GoodOther <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
+e7_L.d.sd.GoodOther   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
+e7_L.d.mean.BadOther  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)
+e7_L.d.sd.BadOther    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)
+
+e7_L.p_dprime1 <- ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
@@
 
-e7_L.p_dprime2 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
+e7_L.p_dprime2 <- ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 
-Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.L1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* =
+Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.M1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* =
 `r e7_L.d.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_slf`, 95% CI [`r e7_L.d.CI.L.good_bad_slf` `r e7_L.d.CI.H.good_bad_slf`]
 
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* =
+Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.M1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* =
 `r e7_L.d.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_oth`, 95% CI [`r e7_L.d.CI.L.good_bad_oth` `r e7_L.d.CI.H.good_bad_oth`]
@@
 Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs.
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.L1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]
+Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.M1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]
 
 Bad self (`r e7_L.d.mean.BadSelf` $\pm$ `r e7_L.d.sd.BadSelf`) vs.
-Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.L1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]
+Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.M1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]
 
 ```{r plot1 the d prime_e7_match, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
+ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
@@
 ```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
+ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 ```{r analyzing RT_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.L1.V.RT <- df.L1.V[df.L1.V$ACC == 1,]
-
-df.L1.V.RT.subj <- summarySEwithin(df.L1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
-df.L1.V.RT.grand <- summarySE(df.L1.V.RT.subj,measurevar = 'RT', groupvar = c('Match','Morality','Identity'),na.rm = TRUE)
-
-df.L1.V.RT_match <- df.L1.V.RT[df.L1.V.RT$Match == "match",]
-df.L1.V.RT_nonmatch <- df.L1.V.RT[df.L1.V.RT$Match == "nonmatch",]
-df.L1.V.RT_match.self <- df.L1.V.RT_match[df.L1.V.RT_match$Identity == 'Self',]
-df.L1.V.RT_match.other <- df.L1.V.RT_match[df.L1.V.RT_match$Identity == 'Other',]
-
-e7_L.rt_anova <- ezANOVA(df.L1.V.RT,dv = RT, wid = Subject, within = .(Match,Morality,Identity),within_full =  .(Match,Morality,Identity), type = 3)
-e7_L.rt_anova.match <- ezANOVA(df.L1.V.RT_match,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-e7_L.rt_anova.nonmatch <- ezANOVA(df.L1.V.RT_nonmatch,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
+df.M1.V.RT <- df.M1.V[df.M1.V$ACC == 1,]
+
+df.M1.V.RT.subj <- summarySEwithin(df.M1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
+df.M1.V.RT.grand <- summarySE(df.M1.V.RT.subj,measurevar = 'RT', groupvar = c('Match','Morality','Identity'),na.rm = TRUE)
+
+df.M1.V.RT_match <- df.M1.V.RT[df.M1.V.RT$Match == "match",]
+df.M1.V.RT_nonmatch <- df.M1.V.RT[df.M1.V.RT$Match == "nonmatch",]
+df.M1.V.RT_match.self <- df.M1.V.RT_match[df.M1.V.RT_match$Identity == 'Self',]
+df.M1.V.RT_match.other <- df.M1.V.RT_match[df.M1.V.RT_match$Identity == 'Other',]
+
+e7_L.rt_anova <- ezANOVA(df.M1.V.RT,dv = RT, wid = Subject, within = .(Match,Morality,Identity),within_full =  .(Match,Morality,Identity), type = 3)
+e7_L.rt_anova.match <- ezANOVA(df.M1.V.RT_match,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
+e7_L.rt_anova.nonmatch <- ezANOVA(df.M1.V.RT_nonmatch,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
 
 ## t-test 
-df.L1.V.RT.subj_w <- dcast(df.L1.V.RT.subj, Subject ~ Match + Identity + Morality ,value.var = "RT")
+df.M1.V.RT.subj_w <- dcast(df.M1.V.RT.subj, Subject ~ Match + Identity + Morality ,value.var = "RT")
 
 # Good self vs. Bad self
-e7_L.rt.t.m.good_bad_slf <- t.test(df.L1.V.RT.subj_w$match_Self_Good,df.L1.V.RT.subj_w$match_Self_Bad,paired = TRUE)
-df.L1.V.RT.subj_w$m.good_bad_slf <- df.L1.V.RT.subj_w$match_Self_Good - df.L1.V.RT.subj_w$match_Self_Bad
-e7_L.rt.t.m.good_bad_slf.CI <- bootES(df.L1.V.RT.subj_w$m.good_bad_slf, R = 5000,effect.type = "cohens.d")
+e7_L.rt.t.m.good_bad_slf <- t.test(df.M1.V.RT.subj_w$match_Self_Good,df.M1.V.RT.subj_w$match_Self_Bad,paired = TRUE)
+df.M1.V.RT.subj_w$m.good_bad_slf <- df.M1.V.RT.subj_w$match_Self_Good - df.M1.V.RT.subj_w$match_Self_Bad
+e7_L.rt.t.m.good_bad_slf.CI <- bootES(df.M1.V.RT.subj_w$m.good_bad_slf, R = 5000,effect.type = "cohens.d")
 
 e7_L.rt.tvalue.good_bad_slf  <- round(as.numeric(e7_L.rt.t.m.good_bad_slf [[1]]),3)
-e7_L.rt.df.L1.good_bad_slf  <- as.numeric(e7_L.rt.t.m.good_bad_slf [[2]])
+e7_L.rt.df.M1.good_bad_slf  <- as.numeric(e7_L.rt.t.m.good_bad_slf [[2]])
 e7_L.rt.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_slf [[3]]),"bonferroni",4)
@@
 # Good Other vs. Bad Other
-e7_L.rt.t.m.good_bad_oth <- t.test(df.L1.V.RT.subj_w$match_Other_Good,df.L1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
-df.L1.V.RT.subj_w$m.good_bad_oth <- df.L1.V.RT.subj_w$match_Other_Good - df.L1.V.RT.subj_w$match_Other_Bad
-e7_L.rt.t.m.good_bad_oth.CI <- bootES(df.L1.V.RT.subj_w$m.good_bad_oth, R = 5000,effect.type = "cohens.d")
+e7_L.rt.t.m.good_bad_oth <- t.test(df.M1.V.RT.subj_w$match_Other_Good,df.M1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
+df.M1.V.RT.subj_w$m.good_bad_oth <- df.M1.V.RT.subj_w$match_Other_Good - df.M1.V.RT.subj_w$match_Other_Bad
+e7_L.rt.t.m.good_bad_oth.CI <- bootES(df.M1.V.RT.subj_w$m.good_bad_oth, R = 5000,effect.type = "cohens.d")
 
 e7_L.rt.tvalue.good_bad_oth  <- round(as.numeric(e7_L.rt.t.m.good_bad_oth [[1]]),3)
-e7_L.rt.df.L1.good_bad_oth  <- as.numeric(e7_L.rt.t.m.good_bad_oth [[2]])
+e7_L.rt.df.M1.good_bad_oth  <- as.numeric(e7_L.rt.t.m.good_bad_oth [[2]])
 e7_L.rt.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_oth [[3]]),"bonferroni",4)
@@
 # good self v. good other
-e7_L.rt.t.m.slf_oth_good <- t.test(df.L1.V.RT.subj_w$match_Self_Good,df.L1.V.RT.subj_w$match_Other_Good,paired = TRUE)
-df.L1.V.RT.subj_w$m.slf_oth_good <- df.L1.V.RT.subj_w$match_Self_Good - df.L1.V.RT.subj_w$match_Other_Good
-e7_L.rt.t.m.slf_oth_good.CI <- bootES(df.L1.V.RT.subj_w$m.slf_oth_good, R = 5000,effect.type = "cohens.d")
+e7_L.rt.t.m.slf_oth_good <- t.test(df.M1.V.RT.subj_w$match_Self_Good,df.M1.V.RT.subj_w$match_Other_Good,paired = TRUE)
+df.M1.V.RT.subj_w$m.slf_oth_good <- df.M1.V.RT.subj_w$match_Self_Good - df.M1.V.RT.subj_w$match_Other_Good
+e7_L.rt.t.m.slf_oth_good.CI <- bootES(df.M1.V.RT.subj_w$m.slf_oth_good, R = 5000,effect.type = "cohens.d")
 
 e7_L.rt.tvalue.slf_oth_good  <- round(as.numeric(e7_L.rt.t.m.slf_oth_good[[1]]),3)
-e7_L.rt.df.L1.slf_oth_good  <- as.numeric(e7_L.rt.t.m.slf_oth_good[[2]])
+e7_L.rt.df.M1.slf_oth_good  <- as.numeric(e7_L.rt.t.m.slf_oth_good[[2]])
 e7_L.rt.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_good[[3]]),"bonferroni",4)
@@
 
-e7_L.rt.t.m.slf_oth_bad <- t.test(df.L1.V.RT.subj_w$match_Self_Bad,df.L1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
-df.L1.V.RT.subj_w$m.slf_oth_bad <- df.L1.V.RT.subj_w$match_Self_Bad - df.L1.V.RT.subj_w$match_Other_Bad
-e7_L.rt.t.m.slf_oth_bad.CI <- bootES(df.L1.V.RT.subj_w$m.slf_oth_bad, R = 5000,effect.type = "cohens.d")
+e7_L.rt.t.m.slf_oth_bad <- t.test(df.M1.V.RT.subj_w$match_Self_Bad,df.M1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
+df.M1.V.RT.subj_w$m.slf_oth_bad <- df.M1.V.RT.subj_w$match_Self_Bad - df.M1.V.RT.subj_w$match_Other_Bad
+e7_L.rt.t.m.slf_oth_bad.CI <- bootES(df.M1.V.RT.subj_w$m.slf_oth_bad, R = 5000,effect.type = "cohens.d")
 
 e7_L.rt.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.rt.t.m.slf_oth_bad[[1]]),3)
-e7_L.rt.df.L1.slf_oth_bad  <- as.numeric(e7_L.rt.t.m.slf_oth_bad[[2]])
+e7_L.rt.df.M1.slf_oth_bad  <- as.numeric(e7_L.rt.t.m.slf_oth_bad[[2]])
 e7_L.rt.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_bad[[3]]),"bonferroni",4)
@@
 
-df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Match == "match",]
+df.M1.V.RT.grand.match <- df.M1.V.RT.grand[df.M1.V.RT.grand$Match == "match",]
 
 ##### save the rt data for late used ####
-colnames(df.L1.V.RT.subj_w) <- paste("L_rt", colnames(df.L1.V.RT.subj_w), sep = "_")
-colnames(df.L1.V.RT.subj_w)[colnames(df.L1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
-write.csv(df.L1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
+colnames(df.M1.V.RT.subj_w) <- paste("L_rt", colnames(df.M1.V.RT.subj_w), sep = "_")
+colnames(df.M1.V.RT.subj_w)[colnames(df.M1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
+write.csv(df.M1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
 #### save the rt data ####
 
-e7_L.rt.mean.GoodSelf <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.sd.GoodSelf <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.mean.BadSelf <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.sd.BadSelf <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Self'],0)
-
-e7_L.rt.mean.GoodOther <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.sd.GoodOther <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Good' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.mean.BadOther <- round(df.L1.V.RT.grand.match$RT[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.sd.BadOther <- round(df.L1.V.RT.grand.match$sd[df.L1.V.RT.grand.match$Morality == 'Bad' & df.L1.V.RT.grand.match$Identity == 'Other'],0)
-
-e7_L.p_rt1 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
+e7_L.rt.mean.GoodSelf <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
+e7_L.rt.sd.GoodSelf <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
+e7_L.rt.mean.BadSelf <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
+e7_L.rt.sd.BadSelf <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
+
+e7_L.rt.mean.GoodOther <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
+e7_L.rt.sd.GoodOther <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
+e7_L.rt.mean.BadOther <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
+e7_L.rt.sd.BadOther <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
+
+e7_L.p_rt1 <- ggplot(data = df.M1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 
-e7_L.p_rt2 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
+e7_L.p_rt2 <- ggplot(data = df.M1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +   # Thinner lines
@@
 
-Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`): *t*(`r e7_L.rt.df.L1.good_bad_slf`) = `r e7_L.rt.tvalue.good_bad_slf`, *p* =
+Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`): *t*(`r e7_L.rt.df.M1.good_bad_slf`) = `r e7_L.rt.tvalue.good_bad_slf`, *p* =
 `r e7_L.rt.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_slf`, 95% CI [`r e7_L.rt.CI.L.good_bad_slf` `r e7_L.rt.CI.H.good_bad_slf`]
 
-Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`)  vs Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.L1.good_bad_oth`) = `r e7_L.rt.tvalue.good_bad_oth`, *p* =
+Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`)  vs Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.M1.good_bad_oth`) = `r e7_L.rt.tvalue.good_bad_oth`, *p* =
 `r e7_L.rt.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_oth`, 95% CI [`r e7_L.rt.CI.L.good_bad_oth` `r e7_L.rt.CI.H.good_bad_oth`]
@@
 Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs.
-Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`) : *t*(`r e7_L.rt.df.L1.slf_oth_good`) = `r e7_L.rt.tvalue.slf_oth_good`, *p* = `r e7_L.rt.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_good`, 95% CI [`r e7_L.rt.CI.L.slf_oth_good` `r e7_L.rt.CI.H.slf_oth_good`]
+Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`) : *t*(`r e7_L.rt.df.M1.slf_oth_good`) = `r e7_L.rt.tvalue.slf_oth_good`, *p* = `r e7_L.rt.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_good`, 95% CI [`r e7_L.rt.CI.L.slf_oth_good` `r e7_L.rt.CI.H.slf_oth_good`]
 
 Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`) vs.
-Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.L1.slf_oth_bad`) = `r e7_L.rt.tvalue.slf_oth_bad`, *p* = `r e7_L.rt.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_bad`, 95% CI [`r e7_L.rt.CI.L.slf_oth_bad` `r e7_L.rt.CI.H.slf_oth_bad`]
+Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.M1.slf_oth_bad`) = `r e7_L.rt.tvalue.slf_oth_bad`, *p* = `r e7_L.rt.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_bad`, 95% CI [`r e7_L.rt.CI.L.slf_oth_bad` `r e7_L.rt.CI.H.slf_oth_bad`]
 
@@
 # change a way to plot
-ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
+ggplot(data = df.M1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 ```{r plot1 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-# df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Matchness == "match",]
-ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
+# df.M1.V.RT.grand.match <- df.M1.V.RT.grand[df.M1.V.RT.grand$Matchness == "match",]
+ggplot(data = df.M1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
@@
 ```{r clean the data_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-# df.T1.V <- df.T1.V[df.T1.V$Task != "importance",]
-df.T1.V$ACC[df.T1.V$ACC==-1] <-0
-
-df.T1.V.acc.subj <-  ddply(df.T1.V,.(Subject,Task,Morality,Identity), summarise,
+# df.C1.V <- df.C1.V[df.C1.V$Task != "importance",]
+df.C1.V$ACC[df.C1.V$ACC==-1] <-0
+
+df.C1.V.acc.subj <-  ddply(df.C1.V,.(Subject,Task,Morality,Identity), summarise,
                     N = length(ACC),
@@
 # define the level of factor# make the variables in a specified order
-df.T1.V.acc.subj$Morality <- factor(df.T1.V.acc.subj$Morality, levels=c("Good","Bad")) 
-df.T1.V.acc.subj$Identity <- factor(df.T1.V.acc.subj$Identity, levels=c("Self","Other"))
-
-df.T1.V.acc.subj.Self <- df.T1.V.acc.subj[df.T1.V.acc.subj$Task == "Id_task",]
-df.T1.V.acc.subj.Good <- df.T1.V.acc.subj[df.T1.V.acc.subj$Task == "Valence_task",]
-
-e7_T.acc_anova <- ezANOVA(df.T1.V.acc.subj,dv = ACC, wid = Subject, within=.(Task,Morality,Identity), type=3)
-e7_T.acc_anova.self <- ezANOVA(df.T1.V.acc.subj.Self, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
-e7_T.acc_anova.Good <- ezANOVA(df.T1.V.acc.subj.Good, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
-
-df.T1.V.acc.sum <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Task','Morality','Identity'))
-
-df.T1.V.acc.subj_w  <- dcast(df.T1.V.acc.subj, Subject ~ Task + Identity + Morality ,value.var = "ACC")
+df.C1.V.acc.subj$Morality <- factor(df.C1.V.acc.subj$Morality, levels=c("Good","Bad")) 
+df.C1.V.acc.subj$Identity <- factor(df.C1.V.acc.subj$Identity, levels=c("Self","Other"))
+
+df.C1.V.acc.subj.Self <- df.C1.V.acc.subj[df.C1.V.acc.subj$Task == "Id_task",]
+df.C1.V.acc.subj.Good <- df.C1.V.acc.subj[df.C1.V.acc.subj$Task == "Valence_task",]
+
+e7_T.acc_anova <- ezANOVA(df.C1.V.acc.subj,dv = ACC, wid = Subject, within=.(Task,Morality,Identity), type=3)
+e7_T.acc_anova.self <- ezANOVA(df.C1.V.acc.subj.Self, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
+e7_T.acc_anova.Good <- ezANOVA(df.C1.V.acc.subj.Good, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
+
+df.C1.V.acc.sum <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Task','Morality','Identity'))
+
+df.C1.V.acc.subj_w  <- dcast(df.C1.V.acc.subj, Subject ~ Task + Identity + Morality ,value.var = "ACC")
 
 # calculate the mean difference for moral effect (Good-Bad)
-df.T1.V.acc.subj_w$Valence_good_bad_slf <- df.T1.V.acc.subj_w$Valence_task_Self_Good - df.T1.V.acc.subj_w$Valence_task_Self_Bad
-df.T1.V.acc.subj_w$Valence_good_bad_oth <- df.T1.V.acc.subj_w$Valence_task_Other_Good - df.T1.V.acc.subj_w$Valence_task_Other_Bad
-df.T1.V.acc.subj_w$Id_good_bad_slf      <- df.T1.V.acc.subj_w$Id_task_Self_Good - df.T1.V.acc.subj_w$Id_task_Self_Bad
-df.T1.V.acc.subj_w$ID_good_bad_oth      <- df.T1.V.acc.subj_w$Id_task_Other_Good - df.T1.V.acc.subj_w$Id_task_Other_Bad
+df.C1.V.acc.subj_w$Valence_good_bad_slf <- df.C1.V.acc.subj_w$Valence_task_Self_Good - df.C1.V.acc.subj_w$Valence_task_Self_Bad
+df.C1.V.acc.subj_w$Valence_good_bad_oth <- df.C1.V.acc.subj_w$Valence_task_Other_Good - df.C1.V.acc.subj_w$Valence_task_Other_Bad
+df.C1.V.acc.subj_w$Id_good_bad_slf      <- df.C1.V.acc.subj_w$Id_task_Self_Good - df.C1.V.acc.subj_w$Id_task_Self_Bad
+df.C1.V.acc.subj_w$ID_good_bad_oth      <- df.C1.V.acc.subj_w$Id_task_Other_Good - df.C1.V.acc.subj_w$Id_task_Other_Bad
 
 # calculate the mean difference for self effect (self-other)
-df.T1.V.acc.subj_w$Valence_slf_oth_good <- df.T1.V.acc.subj_w$Valence_task_Self_Good - df.T1.V.acc.subj_w$Valence_task_Other_Good
-df.T1.V.acc.subj_w$Valence_slf_oth_bad  <- df.T1.V.acc.subj_w$Valence_task_Self_Bad - df.T1.V.acc.subj_w$Valence_task_Other_Bad
-df.T1.V.acc.subj_w$Id_slf_oth_good  <- df.T1.V.acc.subj_w$Id_task_Self_Good - df.T1.V.acc.subj_w$Id_task_Other_Good
-df.T1.V.acc.subj_w$Id_slf_oth_bad   <- df.T1.V.acc.subj_w$Id_task_Self_Bad - df.T1.V.acc.subj_w$Id_task_Other_Bad
-
-colnames(df.T1.V.acc.subj_w) <- paste("T_acc", colnames(df.T1.V.acc.subj_w), sep = "_")
-colnames(df.T1.V.acc.subj_w)[colnames(df.T1.V.acc.subj_w) == 'T_acc_Subject'] <- 'Subject'
-write.csv(df.T1.V.acc.subj_w,"data_catigorization_v_acc.csv",row.names=FALSE)
-# write.csv(df.T1.V.acc.sum,"df.T1.V.acc.sum.csv",row.names=FALSE)
+df.C1.V.acc.subj_w$Valence_slf_oth_good <- df.C1.V.acc.subj_w$Valence_task_Self_Good - df.C1.V.acc.subj_w$Valence_task_Other_Good
+df.C1.V.acc.subj_w$Valence_slf_oth_bad  <- df.C1.V.acc.subj_w$Valence_task_Self_Bad - df.C1.V.acc.subj_w$Valence_task_Other_Bad
+df.C1.V.acc.subj_w$Id_slf_oth_good  <- df.C1.V.acc.subj_w$Id_task_Self_Good - df.C1.V.acc.subj_w$Id_task_Other_Good
+df.C1.V.acc.subj_w$Id_slf_oth_bad   <- df.C1.V.acc.subj_w$Id_task_Self_Bad - df.C1.V.acc.subj_w$Id_task_Other_Bad
+
+colnames(df.C1.V.acc.subj_w) <- paste("T_acc", colnames(df.C1.V.acc.subj_w), sep = "_")
+colnames(df.C1.V.acc.subj_w)[colnames(df.C1.V.acc.subj_w) == 'T_acc_Subject'] <- 'Subject'
+write.csv(df.C1.V.acc.subj_w,"data_catigorization_v_acc.csv",row.names=FALSE)
+# write.csv(df.C1.V.acc.sum,"df.C1.V.acc.sum.csv",row.names=FALSE)
 
 # plot and save the ACC for each condition
-ACC_e7_T <- ggplot(data = df.T1.V.acc.sum,aes(y = ACC, x = Morality, group = Task,shape = Task, fill = Task)) +
+ACC_e7_T <- ggplot(data = df.C1.V.acc.sum,aes(y = ACC, x = Morality, group = Task,shape = Task, fill = Task)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 # combine data cross task
-# tmp <- aggregate(df.T1.V.acc.subj[,7],list(df.T1.V.acc.subj$Subject,df.T1.V.acc.subj$Morality,df.T1.V.acc.subj$Identity),mean)
-df.T1.V.acc.subj.noTask <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
-df.T1.V.acc.subj.noTask_w <- dcast(df.T1.V.acc.subj.noTask, Subject ~ Identity + Morality ,value.var = "ACC")
-
-df.T1.V.acc.subj.noTask_w$good_bad_slf <- df.T1.V.acc.subj.noTask_w$Self_Good - df.T1.V.acc.subj.noTask_w$Self_Bad
-df.T1.V.acc.subj.noTask_w$good_bad_oth <- df.T1.V.acc.subj.noTask_w$Other_Good - df.T1.V.acc.subj.noTask_w$Other_Bad
-df.T1.V.acc.subj.noTask_w$slf_oth_good <- df.T1.V.acc.subj.noTask_w$Self_Good - df.T1.V.acc.subj.noTask_w$Other_Good
-df.T1.V.acc.subj.noTask_w$slf_oth_bad <- df.T1.V.acc.subj.noTask_w$Self_Bad - df.T1.V.acc.subj.noTask_w$Other_Bad
-
-write.csv(df.T1.V.acc.subj.noTask_w, 'df.T1.V.acc.subj.noTask.csv',row.names = F)
-
-e7_T.acc_anova_noTask1 <- ezANOVA(df.T1.V.acc.subj.noTask,dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
+# tmp <- aggregate(df.C1.V.acc.subj[,7],list(df.C1.V.acc.subj$Subject,df.C1.V.acc.subj$Morality,df.C1.V.acc.subj$Identity),mean)
+df.C1.V.acc.subj.noTask <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
+df.C1.V.acc.subj.noTask_w <- dcast(df.C1.V.acc.subj.noTask, Subject ~ Identity + Morality ,value.var = "ACC")
+
+df.C1.V.acc.subj.noTask_w$good_bad_slf <- df.C1.V.acc.subj.noTask_w$Self_Good - df.C1.V.acc.subj.noTask_w$Self_Bad
+df.C1.V.acc.subj.noTask_w$good_bad_oth <- df.C1.V.acc.subj.noTask_w$Other_Good - df.C1.V.acc.subj.noTask_w$Other_Bad
+df.C1.V.acc.subj.noTask_w$slf_oth_good <- df.C1.V.acc.subj.noTask_w$Self_Good - df.C1.V.acc.subj.noTask_w$Other_Good
+df.C1.V.acc.subj.noTask_w$slf_oth_bad <- df.C1.V.acc.subj.noTask_w$Self_Bad - df.C1.V.acc.subj.noTask_w$Other_Bad
+
+write.csv(df.C1.V.acc.subj.noTask_w, 'df.C1.V.acc.subj.noTask.csv',row.names = F)
+
+e7_T.acc_anova_noTask1 <- ezANOVA(df.C1.V.acc.subj.noTask,dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
 # e7_T.acc_anova_noTask1 is exactly the same as in three way rm ANOVA
@@
 # Good self vs Bad self
-e7_T.acc.t.good_bad_slf <- t.test(df.T1.V.acc.subj.noTask_w$Self_Good,df.T1.V.acc.subj.noTask_w$Self_Bad,paired = TRUE)
-e7_T.acc.t.good_bad_slf.CI <- bootES(df.T1.V.acc.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
+e7_T.acc.t.good_bad_slf <- t.test(df.C1.V.acc.subj.noTask_w$Self_Good,df.C1.V.acc.subj.noTask_w$Self_Bad,paired = TRUE)
+e7_T.acc.t.good_bad_slf.CI <- bootES(df.C1.V.acc.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
 
@@
 # Good other vs Bad other
-e7_T.acc.t.good_bad_oth <- t.test(df.T1.V.acc.subj.noTask_w$Other_Good,df.T1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.acc.t.good_bad_oth.CI <- bootES(df.T1.V.acc.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
+e7_T.acc.t.good_bad_oth <- t.test(df.C1.V.acc.subj.noTask_w$Other_Good,df.C1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
+e7_T.acc.t.good_bad_oth.CI <- bootES(df.C1.V.acc.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
 
@@
 # Good self vs Good other
-e7_T.acc.t.slf_oth_good <- t.test(df.T1.V.acc.subj.noTask_w$Self_Good,df.T1.V.acc.subj.noTask_w$Other_Good,paired = TRUE)
-e7_T.acc.t.slf_oth_good.CI <- bootES(df.T1.V.acc.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
+e7_T.acc.t.slf_oth_good <- t.test(df.C1.V.acc.subj.noTask_w$Self_Good,df.C1.V.acc.subj.noTask_w$Other_Good,paired = TRUE)
+e7_T.acc.t.slf_oth_good.CI <- bootES(df.C1.V.acc.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
 
@@
 # Bad self vs Bad other
-e7_T.acc.t.slf_oth_bad <- t.test(df.T1.V.acc.subj.noTask_w$Self_Bad,df.T1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.acc.t.slf_oth_bad.CI <- bootES(df.T1.V.acc.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
+e7_T.acc.t.slf_oth_bad <- t.test(df.C1.V.acc.subj.noTask_w$Self_Bad,df.C1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
+e7_T.acc.t.slf_oth_bad.CI <- bootES(df.C1.V.acc.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
 
@@
 
-df.T1.V.acc.sum.noTask <- summarySE(df.T1.V.acc.subj,measurevar = 'ACC',groupvars = c('Morality','Identity'))
-ACC.Mean.Good.Self <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Good']
-ACC.SD.Good.Self <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Good']
-ACC.Mean.Bad.Self <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.SD.Bad.Self <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Self' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.Mean.Good.Other <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Good']
-ACC.SD.Good.Other <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Good']
-ACC.Mean.Bad.Other <- df.T1.V.acc.sum.noTask$ACC[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.SD.Bad.Other <- df.T1.V.acc.sum.noTask$sd[df.T1.V.acc.sum.noTask$Identity == 'Other' & df.T1.V.acc.sum.noTask$Morality == 'Bad']
-
-# e7_T.acc_anova_id2 <- ezANOVA(df.T1.V.acc.subj.noTask[df.T1.V.acc.subj.noTask$Identity == 'self',],dv = ACC, wid = Subject, within=.(Morality), type=3)
-
-# e7_T.acc_anova_id3 <- ezANOVA(df.T1.V.acc.subj[df.T1.V.acc.subj$Morality == 'Good',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
-# e7_T.acc_anova_id4 <- ezANOVA(df.T1.V.acc.subj[df.T1.V.acc.subj$Morality == 'Bad',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
+df.C1.V.acc.sum.noTask <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Morality','Identity'))
+ACC.Mean.Good.Self <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Good']
+ACC.SD.Good.Self <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Good']
+ACC.Mean.Bad.Self <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
+ACC.SD.Bad.Self <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
+ACC.Mean.Good.Other <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Good']
+ACC.SD.Good.Other <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Good']
+ACC.Mean.Bad.Other <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
+ACC.SD.Bad.Other <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
+
+# e7_T.acc_anova_id2 <- ezANOVA(df.C1.V.acc.subj.noTask[df.C1.V.acc.subj.noTask$Identity == 'self',],dv = ACC, wid = Subject, within=.(Morality), type=3)
+
+# e7_T.acc_anova_id3 <- ezANOVA(df.C1.V.acc.subj[df.C1.V.acc.subj$Morality == 'Good',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
+# e7_T.acc_anova_id4 <- ezANOVA(df.C1.V.acc.subj[df.C1.V.acc.subj$Morality == 'Bad',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
 
 # plot the data without task variable
-ACC_e7_T_noTask <- ggplot(data =df.T1.V.acc.sum.noTask,aes(y = ACC, x =Morality, group = Identity,shape = Identity, fill = Identity))+
+ACC_e7_T_noTask <- ggplot(data =df.C1.V.acc.sum.noTask,aes(y = ACC, x =Morality, group = Identity,shape = Identity, fill = Identity))+
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 ```{r plot2 the ACC_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.T1.V.acc.sum,aes(y = ACC, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
+ggplot(data = df.C1.V.acc.sum,aes(y = ACC, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 ```{r analyzing RT_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.T1.V.RT <- df.T1.V[df.T1.V$ACC == 1,]
+df.C1.V.RT <- df.C1.V[df.C1.V$ACC == 1,]
 # excluded 7035 and subject8
-# df.T1.V.RT <- df.T1.V.RT[!(df.T1.V.RT$Subject %in% c("8","7035")),] 
-df.T1.V.RT.subj <- summarySEwithin(df.T1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
+# df.C1.V.RT <- df.C1.V.RT[!(df.C1.V.RT$Subject %in% c("8","7035")),] 
+df.C1.V.RT.subj <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
 
 # define the level of factor
-df.T1.V.RT.subj$Morality <- factor(df.T1.V.RT.subj$Morality, levels=c("Good","Bad")) # make the variables in a specified order
-df.T1.V.RT.subj$Identity <- factor(df.T1.V.RT.subj$Identity, levels=c("Self","Other"))
-
-df.T1.V.RT.subj_w  <- dcast(df.T1.V.RT.subj, Subject ~ Task + Identity + Morality ,value.var = "RT")
+df.C1.V.RT.subj$Morality <- factor(df.C1.V.RT.subj$Morality, levels=c("Good","Bad")) # make the variables in a specified order
+df.C1.V.RT.subj$Identity <- factor(df.C1.V.RT.subj$Identity, levels=c("Self","Other"))
+
+df.C1.V.RT.subj_w  <- dcast(df.C1.V.RT.subj, Subject ~ Task + Identity + Morality ,value.var = "RT")
 
 # calculate the mean difference for Good effect (Good-Bad)
-df.T1.V.RT.subj_w$Valence_good_bad_slf  <- df.T1.V.RT.subj_w$Valence_task_Self_Good - df.T1.V.RT.subj_w$Valence_task_Self_Bad
-df.T1.V.RT.subj_w$Valence_good_bad_oth  <- df.T1.V.RT.subj_w$Valence_task_Other_Good - df.T1.V.RT.subj_w$Valence_task_Other_Bad
-df.T1.V.RT.subj_w$Id_good_bad_slf       <- df.T1.V.RT.subj_w$Id_task_Self_Good   - df.T1.V.RT.subj_w$Id_task_Self_Bad
-df.T1.V.RT.subj_w$ID_good_bad_oth       <- df.T1.V.RT.subj_w$Id_task_Other_Good - df.T1.V.RT.subj_w$Id_task_Other_Bad
+df.C1.V.RT.subj_w$Valence_good_bad_slf  <- df.C1.V.RT.subj_w$Valence_task_Self_Good - df.C1.V.RT.subj_w$Valence_task_Self_Bad
+df.C1.V.RT.subj_w$Valence_good_bad_oth  <- df.C1.V.RT.subj_w$Valence_task_Other_Good - df.C1.V.RT.subj_w$Valence_task_Other_Bad
+df.C1.V.RT.subj_w$Id_good_bad_slf       <- df.C1.V.RT.subj_w$Id_task_Self_Good   - df.C1.V.RT.subj_w$Id_task_Self_Bad
+df.C1.V.RT.subj_w$ID_good_bad_oth       <- df.C1.V.RT.subj_w$Id_task_Other_Good - df.C1.V.RT.subj_w$Id_task_Other_Bad
 
 # calculate the mean difference for self effect (self-other)
-df.T1.V.RT.subj_w$Valence_slf_oth_good <- df.T1.V.RT.subj_w$Valence_task_Self_Good   - df.T1.V.RT.subj_w$Valence_task_Other_Good
-df.T1.V.RT.subj_w$valence_slf_oth_bad  <- df.T1.V.RT.subj_w$Valence_task_Self_Bad - df.T1.V.RT.subj_w$Valence_task_Other_Bad
-df.T1.V.RT.subj_w$Id_slf_oth_good      <- df.T1.V.RT.subj_w$Id_task_Self_Good - df.T1.V.RT.subj_w$Id_task_Other_Good
-df.T1.V.RT.subj_w$Id_slf_oth_bad       <- df.T1.V.RT.subj_w$Id_task_Self_Bad - df.T1.V.RT.subj_w$Id_task_Other_Bad
+df.C1.V.RT.subj_w$Valence_slf_oth_good <- df.C1.V.RT.subj_w$Valence_task_Self_Good   - df.C1.V.RT.subj_w$Valence_task_Other_Good
+df.C1.V.RT.subj_w$valence_slf_oth_bad  <- df.C1.V.RT.subj_w$Valence_task_Self_Bad - df.C1.V.RT.subj_w$Valence_task_Other_Bad
+df.C1.V.RT.subj_w$Id_slf_oth_good      <- df.C1.V.RT.subj_w$Id_task_Self_Good - df.C1.V.RT.subj_w$Id_task_Other_Good
+df.C1.V.RT.subj_w$Id_slf_oth_bad       <- df.C1.V.RT.subj_w$Id_task_Self_Bad - df.C1.V.RT.subj_w$Id_task_Other_Bad
 
 #### save the rt data for later use ####
-colnames(df.T1.V.RT.subj_w) <- paste("T_rt", colnames(df.T1.V.RT.subj_w), sep = "_")
-colnames(df.T1.V.RT.subj_w)[colnames(df.T1.V.RT.subj_w) == 'T_rt_Subject'] <- 'Subject'
-write.csv(df.T1.V.RT.subj_w,"data_catigorization_v_rt.csv",row.names=FALSE)
+colnames(df.C1.V.RT.subj_w) <- paste("T_rt", colnames(df.C1.V.RT.subj_w), sep = "_")
+colnames(df.C1.V.RT.subj_w)[colnames(df.C1.V.RT.subj_w) == 'T_rt_Subject'] <- 'Subject'
+write.csv(df.C1.V.RT.subj_w,"data_catigorization_v_rt.csv",row.names=FALSE)
 ###########
 
-df.T1.V.RT.grand <- summarySE(df.T1.V.RT.subj,measurevar = 'RT', groupvar = c('Task','Morality','Identity'),na.rm = TRUE)
-
-df.T1.V.RT_Id_task <- df.T1.V.RT[df.T1.V.RT$Task == "Id_task",]
-df.T1.V.RT_Val_task <- df.T1.V.RT[df.T1.V.RT$Task == "Valence_task",]
-#df.T1.V.RT_match.self <- df.T1.V.RT_match[df.T1.V.RT_match$Identity == 'self',]
-#df.T1.V.RT_match.other <- df.T1.V.RT_match[df.T1.V.RT_match$Identity == 'other',]
-
-e7_T.rt_anova <- ezANOVA(df.T1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),
+df.C1.V.RT.grand <- summarySE(df.C1.V.RT.subj,measurevar = 'RT', groupvar = c('Task','Morality','Identity'),na.rm = TRUE)
+
+df.C1.V.RT_Id_task <- df.C1.V.RT[df.C1.V.RT$Task == "Id_task",]
+df.C1.V.RT_Val_task <- df.C1.V.RT[df.C1.V.RT$Task == "Valence_task",]
+#df.C1.V.RT_match.self <- df.C1.V.RT_match[df.C1.V.RT_match$Identity == 'self',]
+#df.C1.V.RT_match.other <- df.C1.V.RT_match[df.C1.V.RT_match$Identity == 'other',]
+
+e7_T.rt_anova <- ezANOVA(df.C1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),
                          within_full=.(Task,Identity,Morality), type=3)
 
-e7_T.rt_anova.Id_task <- ezANOVA(df.T1.V.RT_Id_task,dv = RT, wid = Subject, 
+e7_T.rt_anova.Id_task <- ezANOVA(df.C1.V.RT_Id_task,dv = RT, wid = Subject, 
                                  within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
 
-e7_T.rt_anova.val_task <- ezANOVA(df.T1.V.RT_Val_task,dv = RT, wid = Subject,
+e7_T.rt_anova.val_task <- ezANOVA(df.C1.V.RT_Val_task,dv = RT, wid = Subject,
                                   within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
 
-RT_e7_T <- ggplot(data = df.T1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
+RT_e7_T <- ggplot(data = df.C1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 # combine data cross identity
-df.T1.V.RT.subj.noID <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Task','Morality'))
-df.T1.V.RT.subj.noID_w <- dcast(df.T1.V.RT.subj.noID, Subject ~ Task + Morality ,value.var = "RT")
+df.C1.V.RT.subj.noID <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Task','Morality'))
+df.C1.V.RT.subj.noID_w <- dcast(df.C1.V.RT.subj.noID, Subject ~ Task + Morality ,value.var = "RT")
 
 # valence effect under different task
-df.T1.V.RT.subj.noID_w$good_bad_ID <- df.T1.V.RT.subj.noID_w$Id_task_Good - df.T1.V.RT.subj.noID_w$Id_task_Bad
-df.T1.V.RT.subj.noID_w$good_bad_Val <- df.T1.V.RT.subj.noID_w$Valence_task_Good - df.T1.V.RT.subj.noID_w$Valence_task_Bad
+df.C1.V.RT.subj.noID_w$good_bad_ID <- df.C1.V.RT.subj.noID_w$Id_task_Good - df.C1.V.RT.subj.noID_w$Id_task_Bad
+df.C1.V.RT.subj.noID_w$good_bad_Val <- df.C1.V.RT.subj.noID_w$Valence_task_Good - df.C1.V.RT.subj.noID_w$Valence_task_Bad
 
 # task effect for differnt valence
-df.T1.V.RT.subj.noID_w$ID_Val_good <- df.T1.V.RT.subj.noID_w$Id_task_Good - df.T1.V.RT.subj.noID_w$Valence_task_Good
-df.T1.V.RT.subj.noID_w$ID_Val_bad <- df.T1.V.RT.subj.noID_w$Id_task_Bad - df.T1.V.RT.subj.noID_w$Valence_task_Bad
-
-write.csv(df.T1.V.RT.subj.noID_w, 'df.T1.V.RT.subj.noID_w.csv',row.names = F)
-
-e7_T.RT_anova_noID <- ezANOVA(df.T1.V.RT.subj.noID,dv = RT, wid = Subject, within=.(Task,Morality), type=3)
+df.C1.V.RT.subj.noID_w$ID_Val_good <- df.C1.V.RT.subj.noID_w$Id_task_Good - df.C1.V.RT.subj.noID_w$Valence_task_Good
+df.C1.V.RT.subj.noID_w$ID_Val_bad <- df.C1.V.RT.subj.noID_w$Id_task_Bad - df.C1.V.RT.subj.noID_w$Valence_task_Bad
+
+write.csv(df.C1.V.RT.subj.noID_w, 'df.C1.V.RT.subj.noID_w.csv',row.names = F)
+
+e7_T.RT_anova_noID <- ezANOVA(df.C1.V.RT.subj.noID,dv = RT, wid = Subject, within=.(Task,Morality), type=3)
 
@@
 # Id categorization task: Good v. Bad
-e7_T.RT.t.good_bad_ID <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Good,df.T1.V.RT.subj.noID_w$Id_task_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_ID.CI <- bootES(df.T1.V.RT.subj.noID_w$good_bad_ID,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.good_bad_ID <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Good,df.C1.V.RT.subj.noID_w$Id_task_Bad,paired = TRUE)
+e7_T.RT.t.good_bad_ID.CI <- bootES(df.C1.V.RT.subj.noID_w$good_bad_ID,R = 20000, effect.type = "cohens.d")
 
@@
 # moral task: Good v. Bad
-e7_T.RT.t.good_bad_Val <- t.test(df.T1.V.RT.subj.noID_w$Valence_task_Good,df.T1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_Val.CI <- bootES(df.T1.V.RT.subj.noID_w$good_bad_Val,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.good_bad_Val <- t.test(df.C1.V.RT.subj.noID_w$Valence_task_Good,df.C1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
+e7_T.RT.t.good_bad_Val.CI <- bootES(df.C1.V.RT.subj.noID_w$good_bad_Val,R = 20000, effect.type = "cohens.d")
 
@@
 # Good valence: self task v. moral task
-e7_T.RT.t.ID_Val_good <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Good,df.T1.V.RT.subj.noID_w$Valence_task_Good,paired = TRUE)
-e7_T.RT.t.ID_Val_good.CI <- bootES(df.T1.V.RT.subj.noID_w$ID_Val_good,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.ID_Val_good <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Good,df.C1.V.RT.subj.noID_w$Valence_task_Good,paired = TRUE)
+e7_T.RT.t.ID_Val_good.CI <- bootES(df.C1.V.RT.subj.noID_w$ID_Val_good,R = 20000, effect.type = "cohens.d")
 
@@
 # Bad valence: self task v. moral task
-e7_T.RT.t.ID_Val_bad <- t.test(df.T1.V.RT.subj.noID_w$Id_task_Bad,df.T1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
-e7_T.RT.t.ID_Val_bad.CI <- bootES(df.T1.V.RT.subj.noID_w$ID_Val_bad,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.ID_Val_bad <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Bad,df.C1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
+e7_T.RT.t.ID_Val_bad.CI <- bootES(df.C1.V.RT.subj.noID_w$ID_Val_bad,R = 20000, effect.type = "cohens.d")
 
@@
 
-RT.Mean.ID_task.Good  <- mean(df.T1.V.RT.subj.noID_w$Id_task_Good)
-RT.SD.ID_task.Good  <- sd(df.T1.V.RT.subj.noID_w$Id_task_Good)
-RT.Mean.ID_task.Bad <- mean(df.T1.V.RT.subj.noID_w$Id_task_Bad)
-RT.SD.ID_task.Bad <- sd(df.T1.V.RT.subj.noID_w$Id_task_Bad)
-RT.Mean.Val_task.Good <- mean(df.T1.V.RT.subj.noID_w$Valence_task_Good)
-RT.SD.Val_task.Good <- sd(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
-RT.Mean.Val_task.Bad <- mean(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
-RT.SD.Val_task.Bad <- sd(df.T1.V.RT.subj.noID_w$Valence_task_Bad)
+RT.Mean.ID_task.Good  <- mean(df.C1.V.RT.subj.noID_w$Id_task_Good)
+RT.SD.ID_task.Good  <- sd(df.C1.V.RT.subj.noID_w$Id_task_Good)
+RT.Mean.ID_task.Bad <- mean(df.C1.V.RT.subj.noID_w$Id_task_Bad)
+RT.SD.ID_task.Bad <- sd(df.C1.V.RT.subj.noID_w$Id_task_Bad)
+RT.Mean.Val_task.Good <- mean(df.C1.V.RT.subj.noID_w$Valence_task_Good)
+RT.SD.Val_task.Good <- sd(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
+RT.Mean.Val_task.Bad <- mean(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
+RT.SD.Val_task.Bad <- sd(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
 ```
@@
 ```{r RT_e7_T_simple_effect_noTask, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.T1.V.RT.subj.noTask <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Identity','Morality'))
-df.T1.V.RT.subj.noTask_w <- dcast(df.T1.V.RT.subj.noTask, Subject ~ Identity + Morality ,value.var = "RT")
-
-df.T1.V.RT.subj.noTask_w$good_bad_slf <- df.T1.V.RT.subj.noTask_w$Self_Good - df.T1.V.RT.subj.noTask_w$Self_Bad
-df.T1.V.RT.subj.noTask_w$good_bad_oth <- df.T1.V.RT.subj.noTask_w$Other_Good - df.T1.V.RT.subj.noTask_w$Other_Bad
-df.T1.V.RT.subj.noTask_w$slf_oth_good <- df.T1.V.RT.subj.noTask_w$Self_Good - df.T1.V.RT.subj.noTask_w$Other_Good
-df.T1.V.RT.subj.noTask_w$slf_oth_bad <- df.T1.V.RT.subj.noTask_w$Self_Bad - df.T1.V.RT.subj.noTask_w$Other_Bad
-
-write.csv(df.T1.V.RT.subj.noTask_w, 'df.T1.V.RT.subj.noTask_w.csv',row.names = F)
-
-e7_T.RT_anova_noTask <- ezANOVA(df.T1.V.RT.subj.noTask,dv = RT, wid = Subject, within=.(Morality,Identity), type=3)
+df.C1.V.RT.subj.noTask <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Identity','Morality'))
+df.C1.V.RT.subj.noTask_w <- dcast(df.C1.V.RT.subj.noTask, Subject ~ Identity + Morality ,value.var = "RT")
+
+df.C1.V.RT.subj.noTask_w$good_bad_slf <- df.C1.V.RT.subj.noTask_w$Self_Good - df.C1.V.RT.subj.noTask_w$Self_Bad
+df.C1.V.RT.subj.noTask_w$good_bad_oth <- df.C1.V.RT.subj.noTask_w$Other_Good - df.C1.V.RT.subj.noTask_w$Other_Bad
+df.C1.V.RT.subj.noTask_w$slf_oth_good <- df.C1.V.RT.subj.noTask_w$Self_Good - df.C1.V.RT.subj.noTask_w$Other_Good
+df.C1.V.RT.subj.noTask_w$slf_oth_bad <- df.C1.V.RT.subj.noTask_w$Self_Bad - df.C1.V.RT.subj.noTask_w$Other_Bad
+
+write.csv(df.C1.V.RT.subj.noTask_w, 'df.C1.V.RT.subj.noTask_w.csv',row.names = F)
+
+e7_T.RT_anova_noTask <- ezANOVA(df.C1.V.RT.subj.noTask,dv = RT, wid = Subject, within=.(Morality,Identity), type=3)
 # e7_T.RT_anova_noTask1 is exactly the same as in three way rm ANOVA
@@
 # Good self vs Bad self
-e7_T.RT.t.good_bad_slf <- t.test(df.T1.V.RT.subj.noTask_w$Self_Good,df.T1.V.RT.subj.noTask_w$Self_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_slf.CI <- bootES(df.T1.V.RT.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.good_bad_slf <- t.test(df.C1.V.RT.subj.noTask_w$Self_Good,df.C1.V.RT.subj.noTask_w$Self_Bad,paired = TRUE)
+e7_T.RT.t.good_bad_slf.CI <- bootES(df.C1.V.RT.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
 
@@
 # Good other vs Bad other
-e7_T.RT.t.good_bad_oth <- t.test(df.T1.V.RT.subj.noTask_w$Other_Good,df.T1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_oth.CI <- bootES(df.T1.V.RT.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.good_bad_oth <- t.test(df.C1.V.RT.subj.noTask_w$Other_Good,df.C1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
+e7_T.RT.t.good_bad_oth.CI <- bootES(df.C1.V.RT.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
 
@@
 # Good self vs Good other
-e7_T.RT.t.slf_oth_good <- t.test(df.T1.V.RT.subj.noTask_w$Self_Good,df.T1.V.RT.subj.noTask_w$Other_Good,paired = TRUE)
-e7_T.RT.t.slf_oth_good.CI <- bootES(df.T1.V.RT.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.slf_oth_good <- t.test(df.C1.V.RT.subj.noTask_w$Self_Good,df.C1.V.RT.subj.noTask_w$Other_Good,paired = TRUE)
+e7_T.RT.t.slf_oth_good.CI <- bootES(df.C1.V.RT.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
 
@@
 # Bad self vs Bad other
-e7_T.RT.t.slf_oth_bad <- t.test(df.T1.V.RT.subj.noTask_w$Self_Bad,df.T1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.RT.t.slf_oth_bad.CI <- bootES(df.T1.V.RT.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
+e7_T.RT.t.slf_oth_bad <- t.test(df.C1.V.RT.subj.noTask_w$Self_Bad,df.C1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
+e7_T.RT.t.slf_oth_bad.CI <- bootES(df.C1.V.RT.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
 
@@
 
-RT.Mean.Good.Self <- mean(df.T1.V.RT.subj.noTask_w$Self_Good)
-RT.SD.Good.Self <- sd(df.T1.V.RT.subj.noTask_w$Self_Good)
-RT.Mean.Bad.Self <- mean(df.T1.V.RT.subj.noTask_w$Self_Bad)
-RT.SD.Bad.Self <- sd(df.T1.V.RT.subj.noTask_w$Self_Bad)
-RT.Mean.Good.Other <- mean(df.T1.V.RT.subj.noTask_w$Other_Good)
-RT.SD.Good.Other <- sd(df.T1.V.RT.subj.noTask_w$Other_Good)
-RT.Mean.Bad.Other <- mean(df.T1.V.RT.subj.noTask_w$Other_Bad)
-RT.SD.Bad.Other <- sd(df.T1.V.RT.subj.noTask_w$Other_Bad)
-
-df.T1.V.RT.sum.noTask <- summarySE(df.T1.V.RT.subj,measurevar = 'RT',groupvars = c('Morality','Identity'))
-RT.Mean.Good.Self <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Good']
-RT.SD.Good.Self <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Good']
-RT.Mean.Bad.Self <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
-RT.SD.Bad.Self <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'self' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
-RT.Mean.Good.Other <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Good']
-RT.SD.Good.Other <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Good']
-RT.Mean.Bad.Other <- df.T1.V.RT.sum.noTask$RT[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
-RT.SD.Bad.Other <- df.T1.V.RT.sum.noTask$sd[df.T1.V.RT.sum.noTask$Identity == 'other' & df.T1.V.RT.sum.noTask$Morality == 'Bad']
+RT.Mean.Good.Self <- mean(df.C1.V.RT.subj.noTask_w$Self_Good)
+RT.SD.Good.Self <- sd(df.C1.V.RT.subj.noTask_w$Self_Good)
+RT.Mean.Bad.Self <- mean(df.C1.V.RT.subj.noTask_w$Self_Bad)
+RT.SD.Bad.Self <- sd(df.C1.V.RT.subj.noTask_w$Self_Bad)
+RT.Mean.Good.Other <- mean(df.C1.V.RT.subj.noTask_w$Other_Good)
+RT.SD.Good.Other <- sd(df.C1.V.RT.subj.noTask_w$Other_Good)
+RT.Mean.Bad.Other <- mean(df.C1.V.RT.subj.noTask_w$Other_Bad)
+RT.SD.Bad.Other <- sd(df.C1.V.RT.subj.noTask_w$Other_Bad)
+
+df.C1.V.RT.sum.noTask <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Morality','Identity'))
+RT.Mean.Good.Self <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Good']
+RT.SD.Good.Self <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Good']
+RT.Mean.Bad.Self <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
+RT.SD.Bad.Self <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
+RT.Mean.Good.Other <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Good']
+RT.SD.Good.Other <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Good']
+RT.Mean.Bad.Other <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
+RT.SD.Bad.Other <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
 
 # plot the data without task varaible.
-RT_e7_T_noTask <- ggplot(data =df.T1.V.RT.sum.noTask,aes(y = RT, x =Morality, group = Identity,shape = Identity, fill = Identity))+
+RT_e7_T_noTask <- ggplot(data =df.C1.V.RT.sum.noTask,aes(y = RT, x =Morality, group = Identity,shape = Identity, fill = Identity))+
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 ```{r plot2 the RT_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.T1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
+ggplot(data = df.C1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
         geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
@@
 # matching task -- d prime
-#ncol(df.L1.V.SDT_ww)
+#ncol(df.M1.V.SDT_ww)
 # matching task -- ACC
-#ncol(df.L1.V.acc_w)
+#ncol(df.M1.V.acc_w)
 # matching task -- rt
-#ncol(df.L1.V.RT.subj_w)
+#ncol(df.M1.V.RT.subj_w)
 # categorization task -- ACC
-#ncol(df.T1.V.acc.subj_w)
+#ncol(df.C1.V.acc.subj_w)
 # categorization task -- rt
-#ncol(df.T1.V.RT.subj_w)
+#ncol(df.C1.V.RT.subj_w)
 
 ## correlation analysis for ACC
-df.corr.acc <- merge(df.L1.V.acc_w[,1:5],df.T1.V.acc.subj_w[,1:9],by = 'Subject')
+df.corr.acc <- merge(df.M1.V.acc_w[,1:5],df.C1.V.acc.subj_w[,1:9],by = 'Subject')
 df.corr.acc <- df.corr.acc[,2:13]
@@
 ```{r correlattion between learning and testing_ACC-bias,echo=FALSE,warning=FALSE,message=FALSE }
-#df.L1.V.acc_w <- read.csv("data_matching_v_acc.csv",header = TRUE, sep = ",")
-#df.T1.V.acc.subj_w <- read.csv("data_catigorization_v_acc.csv",header = TRUE,sep = ",")
-
-df.corr.bias_acc <- merge(df.L1.V.acc_w[,c(1,10:13)],df.T1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
+#df.M1.V.acc_w <- read.csv("data_matching_v_acc.csv",header = TRUE, sep = ",")
+#df.C1.V.acc.subj_w <- read.csv("data_catigorization_v_acc.csv",header = TRUE,sep = ",")
+
+df.corr.bias_acc <- merge(df.M1.V.acc_w[,c(1,10:13)],df.C1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
 write.csv(df.corr.bias_acc,"df.corr.bias_acc.csv",row.names = F)
@@
 # correlaton analysis for rt
-df.corr.rt <- merge(df.L1.V.RT.subj_w[,1:5],df.T1.V.RT.subj_w[,1:9],by = 'Subject')
+df.corr.rt <- merge(df.M1.V.RT.subj_w[,1:5],df.C1.V.RT.subj_w[,1:9],by = 'Subject')
 df.corr.rt <- df.corr.rt[,2:13]
@@
 # merge the data by subj ID
-df.corr.bias_rt <- merge(df.L1.V.RT.subj_w[,c(1,10:13)],df.T1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
+df.corr.bias_rt <- merge(df.M1.V.RT.subj_w[,c(1,10:13)],df.C1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
 write.csv(df.corr.bias_rt,"df.corr.bias_rt.csv",row.names = F)

### 2018-07-04 Results/preproc/trans_Data.r

@@ -89,5 +89,5 @@ df.C$Identity <- factor(df.C$Identity, levels=c("Self","Other"))
 df.M1 <- df.M[,c("Subject", "Age", "Gender", "Match", "Morality", "Identity", "ACC","RT")]
 df.C1 <- df.C[,c("Subject", "Age", "Gender", "Task", "Morality", "Identity", "ACC","RT")]
 
-write.csv(df.M1,'MS_matchingTask_raw.csv',row.names = F)
+write.csv(df.M1,'MS_matchTask_raw.csv',row.names = F)
 write.csv(df.C1,'MS_categTask_raw.csv',row.names = F)

### 2018-07-05 Results/preproc/MS_ddm_preproc.rmd
finished exp1 preproc

@@
 ---
-title: "Data_Analysis_exp7"
+title: "Data_Analysis_MS_ddm_exp1"
 author: "hcp"
@@
 source('Initial.r')
-curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
+curDir  <- getwd()
+#curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
 rootDir <- gsub('.{7}$', '', curDir)
@@
 
-```{r loadingData_e7,echo=FALSE,results='hide'}
+```{r loadingData_MS_ddm_exp1,echo=FALSE,results='hide'}
 df.M <- read.csv("MS_matchTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) # data for matching task
 df.C <- read.csv("MS_categTask_raw.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)  # data for categorization task
+
+subTotl <- unique(df.M$Subject)
 
@@
 df.C.tmp <- df.C
-df.C.tmp$ACC[df.C.tmp$ACC == -1] <- 0
+df.C.tmp$ACC[df.C.tmp$ACC == -1] <- 0 # this was not done in previous analysis, resulting the wronly excluded participants in registration
 
@@
 
-excldSub2.M <- df.M.acc.g$Subject[df.M.acc.g$ACC < 0.5]      # less 50% accuracy in matching task
-excldSub2.C <- df.C.acc.g$Subject[df.C.acc.g$ACC < 0.5]      # less than 50% accuracy in categorization task
+excldSub2.M <- df.M.acc.g$Subject[df.M.acc.g$ACC < 0.5]      # < 50% accuracy in matching task
+excldSub2.C <- df.C.acc.g$Subject[df.C.acc.g$ACC < 0.5]      # < 50% accuracy in categorization task
 df.M.valid <- df.M[!(df.M$Subject %in% excldSub2.M),]        # exclude the invalid subjects
-df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.C),]
+df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.M),]
 df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),]
@@
 
-```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+```{r clean the data,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
 # clean data for traditional analysis
@@
 
-# get the data file for hddm analysis
+# get the data file for hddm analysis ####
 df.M.ddm.v <- df.M.valid   # exclude the invalid subjects
@@
 ## Participants
-`r numT.subj+length(excldSub1)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7.
+`r length(subTotl)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in this experiment.
 All partcipants were right handed, and all had normal or corrected-to-normal vision.
 Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee.
-Data of `r length(excldSub1)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task.
-`r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.
+Data of `r length(excldSub1)` participants were excluded from matching task because of the procedura failure, and `r length(excldSub2.M)` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r nrow(df.M1.V.basic)` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task.
+`r length(excldSub2.C)` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r nrow(df.C1.V.basic)` participants (`r numV.female.C` female, age: `r ageV.mean.C` $\pm$ `r ageV.std.C` years) for categorization task.
 
@@
 For the learning phase, we excluded the first 24 trials, which is suppose to be the duration participants were practicing.
-Also, trials that responsed less than 200 ms or no-response was excluded.For the learning phase, `r round(ratio.excld.trials.L,4)` of the total trials was excluded, for the testing phase, `r round(ratio.excld.trials.T,4)` of the total trials was excluded.
+Also, trials that responsed less than 200 ms or no-response was excluded.For the learning phase, `r round(ratio.excld.trials.M,4)` of the total trials was excluded, for the testing phase, `r round(ratio.excld.trials.C,4)` of the total trials was excluded.
 
-### Results of Learning phase
 #### Analaysis of d prime
-```{r analyzing for d prime_e7_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+```{r analyzing for match task, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+### ACC ####
+df.M1.V.acc  <-  plyr::ddply(df.M1.V,.(Subject, Match, Morality, Identity), summarise,
+                    N = length(ACC),
+                    countN = sum(ACC),
+                    ACC = sum(ACC)/length(ACC))
+
+df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Morality + Identity,value.var = "ACC")
+
+# rename the column number
+colnames(df.M1.V.acc_w)[2:9] <- paste("ACC", colnames(df.M1.V.acc_w[,2:9]), sep = "_")
+
 ## calculate the d prime for each condition
@@
 for (i in 1:nrow(df.M1.V)){
-        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
+        if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "match"){
                 df.M1.V$sdt[i] <- "hit"
-        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
+        } else if (df.M1.V$ACC[i] == 1 & df.M1.V$Match[i] == "nonmatch" ){
                 df.M1.V$sdt[i] <- "CR"
-        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match" & !is.na(df.M1.V$ResponseKey[i])){
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "match"){
                 df.M1.V$sdt[i] <- "miss"
-        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "nonmatch" & !is.na(df.M1.V$ResponseKey[i])){
+        } else if (df.M1.V$ACC[i] == 0 & df.M1.V$Match[i] == "nonmatch" ){
                 df.M1.V$sdt[i] <- "FA"
@@
 # calculate the number of each for each condition
-df.M1.V.SDT <-  ddply(df.M1.V,.(Subject,Morality, Identity,sdt), summarise, N = length(sdt))
+df.M1.V.SDT <- plyr::ddply(df.M1.V,.(Subject,Age, Gender, Morality, Identity,sdt), summarise, N = length(sdt))
 df.M1.V.SDT <- df.M1.V.SDT[complete.cases(df.M1.V.SDT$sdt),] # exclude NA, which represents no-response trials
@@
 # long format to wide
-df.M1.V.SDT_w <- dcast(df.M1.V.SDT, Subject + Morality + Identity ~ sdt,value.var = "N")
+df.M1.V.SDT_w <- reshape2::dcast(df.M1.V.SDT, Subject + Age + Gender + Morality + Identity ~ sdt,value.var = "N")
 df.M1.V.SDT_w$miss[is.na(df.M1.V.SDT_w$miss)] <- 0 # transfer NA to 0
@@
 # transfor from long format to wide format
-df.M1.V.SDT_ww <- dcast(df.M1.V.SDT_w, Subject ~ Identity + Morality ,value.var = "dprime")
+df.M1.V.SDT_ww <- dcast(df.M1.V.SDT_w, Subject + Age + Gender ~ Morality + Identity ,value.var = "dprime")
+# rename the column number
+colnames(df.M1.V.SDT_ww)[4:7] <- paste("d", colnames(df.M1.V.SDT_ww[,4:7]), sep = "_")
 
-# anova for d prime with 2*2 design
-e7_L.d_anova <- ezANOVA(df.M1.V.SDT_w,dv = dprime, wid = Subject, within=.(Morality,Identity), type=3)
+df.M1.V.SDT_l <- df.M1.V.SDT_w[,c(1:5,12)]
 
-df.M1.V.SDT_w$Subject <- factor(df.M1.V.SDT_w$Subject)  # make the subject "factor"
+# preproc RT data ####
+df.M1.V.RT <- df.M1.V[df.M1.V$ACC == 1,]
 
-# using Bayesfactor analysis (which is not reported in the document)
-e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.M1.V.SDT_w, whichRandom = "Subject")
+# get the summary results
+df.M1.V.RT.subj <- summarySEwithin(df.M1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
+df.M1.V.RT.subj_w <- dcast(df.M1.V.RT.subj, Subject ~ Match + Morality + Identity ,value.var = "RT")
 
-# Good self vs Bad self
-e7_L.d.t.good_bad_slf <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
-df.M1.V.SDT_ww$good_bad_slf <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Self_Bad                   # calculate the differences
-e7_L.d.t.good_bad_slf.CI <- bootES(df.M1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES
+# rename the columns of RT data
+colnames(df.M1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.M1.V.RT.subj_w[,2:9]), sep = "_")
 
-# give new names for each key information, for later use in the markdown
-e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
-e7_L.d.df.M1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
-e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
-e7_L.d.cohens.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[1]],4) 
-e7_L.d.CI.L.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][1],4)
-e7_L.d.CI.H.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][2],4)
+## saving data ####
+# merge the dprime and RT data and save
+df.M1.V.sum_w <- merge(df.M1.V.acc_w,  df.M1.V.SDT_ww,by = "Subject")
+df.M1.V.sum_w <- merge(df.M1.V.sum_w,df.M1.V.RT.subj_w,by = 'Subject')
 
-# Good other vs. Bad other
-e7_L.d.t.good_bad_oth <- t.test(df.M1.V.SDT_ww$Other_Good,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
-df.M1.V.SDT_ww$good_bad_oth <- df.M1.V.SDT_ww$Other_Good - df.M1.V.SDT_ww$Other_Bad
-e7_L.d.t.good_bad_oth.CI <- bootES(df.M1.V.SDT_ww$good_bad_oth,R = 20000, effect.type = "cohens.d")
+# merge the RT and ACC data (long-format)
+df.M1.V.sum_rt_acc_l <- merge(df.M1.V.acc,df.M1.V.RT.subj,by = c("Subject","Match","Morality",'Identity'))
+df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[order(df.M1.V.sum_rt_acc_l$Subject),]
 
-e7_L.d.tvalue.good_bad_oth  <- round(as.numeric(e7_L.d.t.good_bad_oth[[1]]),3)
-e7_L.d.df.M1.good_bad_oth  <- as.numeric(e7_L.d.t.good_bad_oth[[2]])
-e7_L.d.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_oth[[3]]),"bonferroni",4)
-e7_L.d.cohens.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[1]],4) 
-e7_L.d.CI.L.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][1],4)
-e7_L.d.CI.H.good_bad_oth <- round(e7_L.d.t.good_bad_oth.CI[[12]][2],4)
+df.M1.V.sum_rt_acc_l <- df.M1.V.sum_rt_acc_l[,c("Subject","Match","Morality",'Identity',"N.x","countN","ACC","RT")]
+colnames(df.M1.V.sum_rt_acc_l) <- c("Subject","Match","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
 
-# Good self vs Good other
-e7_L.d.t.slf_oth_good <- t.test(df.M1.V.SDT_ww$Self_Good,df.M1.V.SDT_ww$Other_Good,paired = TRUE)
-df.M1.V.SDT_ww$slf_oth_good <- df.M1.V.SDT_ww$Self_Good - df.M1.V.SDT_ww$Other_Good
-e7_L.d.t.slf_oth_good.CI <- bootES(df.M1.V.SDT_ww$slf_oth_good,R = 20000, effect.type = "cohens.d")
+# order the columns
+df.M1.V.sum_w <- df.M1.V.sum_w[,c(colnames(df.M1.V.sum_w)[c(1,10:11,2:9,12:23)])]
 
-e7_L.d.tvalue.slf_oth_good  <- round(as.numeric(e7_L.d.t.slf_oth_good[[1]]),3)
-e7_L.d.df.M1.slf_oth_good  <- as.numeric(e7_L.d.t.slf_oth_good[[2]])
-e7_L.d.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_good[[3]]),"bonferroni",4)
-e7_L.d.cohens.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[1]],4) 
-e7_L.d.CI.L.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][1],4)
-e7_L.d.CI.H.slf_oth_good <- round(e7_L.d.t.slf_oth_good.CI[[12]][2],4)
+# calculate the effect of self-ref and valence
+df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
+df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
+df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
 
-# Bad self vs. Bad other
-e7_L.d.t.slf_oth_bad <- t.test(df.M1.V.SDT_ww$Self_Bad,df.M1.V.SDT_ww$Other_Bad,paired = TRUE)
-df.M1.V.SDT_ww$slf_oth_bad <- df.M1.V.SDT_ww$Self_Bad - df.M1.V.SDT_ww$Other_Bad
-e7_L.d.t.slf_oth_bad.CI <- bootES(df.M1.V.SDT_ww$slf_oth_bad,R = 20000, effect.type = "cohens.d")
+df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
 
-e7_L.d.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.d.t.slf_oth_bad[[1]]),3)
-e7_L.d.df.M1.slf_oth_bad <- as.numeric(e7_L.d.t.slf_oth_bad[[2]])
-e7_L.d.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.d.t.slf_oth_bad[[3]]),"bonferroni",4)
-e7_L.d.cohens.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[1]],4) 
-e7_L.d.CI.L.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][1],4)
-e7_L.d.CI.H.slf_oth_bad <- round(e7_L.d.t.slf_oth_bad.CI[[12]][2],4)
-
-#####save the dprime and ACC data for late used ####
-colnames(df.M1.V.SDT_ww) <- paste("L_d", colnames(df.M1.V.SDT_ww), sep = "_")
-write.csv(df.M1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
-df.M1.V.acc <-  ddply(df.M1.V,.(Subject,Match,Identity,Morality), summarise,
-                    N = length(ACC),
-                    countN = sum(ACC),
-                    ACC = sum(ACC)/length(ACC))
-df.M1.V.acc_w <- dcast(df.M1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
-df.M1.V.acc_w$good_bad_slf <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Self_Bad
-df.M1.V.acc_w$good_oth <- df.M1.V.acc_w$match_Other_Good - df.M1.V.acc_w$match_Other_Bad
-df.M1.V.acc_w$slf_oth_good <- df.M1.V.acc_w$match_Self_Good - df.M1.V.acc_w$match_Other_Good
-df.M1.V.acc_w$slf_oth_bad <- df.M1.V.acc_w$match_Self_Bad - df.M1.V.acc_w$match_Other_Bad
-
-colnames(df.M1.V.acc_w) <- paste("L_acc", colnames(df.M1.V.acc_w), sep = "_")
-colnames(df.M1.V.acc_w)[colnames(df.M1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
-write.csv(df.M1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
-##### save data for later analysis ####
-
-df.M1.V.SDT.sum      <- summarySE(df.M1.V.SDT_w,measurevar = 'dprime',groupvars = c('Morality','Identity'))
-e7_L.d.mean.GoodSelf <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.sd.GoodSelf   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.mean.BadSelf  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)
-e7_L.d.sd.BadSelf    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Self'],3)
-
-e7_L.d.mean.GoodOther <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.sd.GoodOther   <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Good' & df.M1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.mean.BadOther  <- round(df.M1.V.SDT.sum$dprime[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)
-e7_L.d.sd.BadOther    <- round(df.M1.V.SDT.sum$sd[df.M1.V.SDT.sum$Morality == 'Bad' & df.M1.V.SDT.sum$Identity == 'Other'],3)
-
-e7_L.p_dprime1 <- ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-                      #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'self-referential',y = 'd prime') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        apatheme  + 
-        theme(axis.text = element_text (size = 24,color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad"))+
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-e7_L.p_dprime2 <- ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-                      #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'd prime') +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        apatheme + 
-        theme(axis.text = element_text (size = 24,color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-# save the plot to pdf file
-ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-
-MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
-
-```
-ANOVA for *d'* with moral character and self-relatedness as within-subjects factors.
-
-The main effect of `r e7_L.d_anova[[1]][1,1]`, *F*(`r e7_L.d_anova[[1]][1,2]`, `r e7_L.d_anova[[1]][1,3]`) = `r round(e7_L.d_anova[[1]][1,4],3)`, *p* = `r round(e7_L.d_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][1,7],4)`, BF10 = r e7_L.dprime_anova_bf[1].
-
-The main effect of `r e7_L.d_anova[[1]][2,1]`: *F*(`r e7_L.d_anova[[1]][2,2]`, `r e7_L.d_anova[[1]][2,3]`) = `r round(e7_L.d_anova[[1]][2,4],3)`, *p* = `r round(e7_L.d_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][2,7],4)`,BF10 = r e7_L.dprime_anova_bf[2]
-
-The interaction between `r e7_L.d_anova[[1]][3,1]`: *F*(`r e7_L.d_anova[[1]][3,2]`, `r e7_L.d_anova[[1]][3,3]`) = `r round(e7_L.d_anova[[1]][3,4],3)`, *p* = `r round(e7_L.d_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.d_anova[[1]][3,7],4)`, BF21 = r e7_L.dprime_anova_bf[4]/e7_L.dprime_anova_bf[3]
-
-Then we conducted post-hoc comparision:
-
-Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs Bad self (`r e7_L.d.mean.BadSelf`  $\pm$ `r e7_L.d.sd.BadSelf`): *t*(`r e7_L.d.df.M1.good_bad_slf`) = `r e7_L.d.tvalue.good_bad_slf`, *p* =
-`r e7_L.d.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_slf`, 95% CI [`r e7_L.d.CI.L.good_bad_slf` `r e7_L.d.CI.H.good_bad_slf`]
-
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`) vs Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.M1.good_bad_oth`) = `r e7_L.d.tvalue.good_bad_oth`, *p* =
-`r e7_L.d.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.good_bad_oth`, 95% CI [`r e7_L.d.CI.L.good_bad_oth` `r e7_L.d.CI.H.good_bad_oth`]
-
-Good self (`r e7_L.d.mean.GoodSelf`  $\pm$ `r e7_L.d.sd.GoodSelf`) vs.
-Good other (`r e7_L.d.mean.GoodOther`  $\pm$ `r e7_L.d.sd.GoodOther`): *t*(`r e7_L.d.df.M1.slf_oth_good`) = `r e7_L.d.tvalue.slf_oth_good`, *p* = `r e7_L.d.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_good`, 95% CI [`r e7_L.d.CI.L.slf_oth_good` `r e7_L.d.CI.H.slf_oth_good`]
-
-Bad self (`r e7_L.d.mean.BadSelf` $\pm$ `r e7_L.d.sd.BadSelf`) vs.
-Bad other (`r e7_L.d.mean.BadOther`  $\pm$ `r e7_L.d.sd.BadOther`): *t*(`r e7_L.d.df.M1.slf_oth_bad`) = `r e7_L.d.tvalue.slf_oth_bad`, *p* = `r e7_L.d.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.d.cohens.slf_oth_bad`, 95% CI [`r e7_L.d.CI.L.slf_oth_bad` `r e7_L.d.CI.H.slf_oth_bad`]
-
-```{r plot1 the d prime_e7_match, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,     # width of the error bar
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'self-referential',y = 'd prime') +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        apatheme + 
-        theme(axis.text = element_text (size = 24,color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
+# write files
+setwd(traDir)
+write.csv(df.M1.V.sum_w,'MS_match_behav_wide.csv',row.names = F)
+write.csv(df.M1.V.SDT_l,'MS_match__dprime_long.csv',row.names = F)
+write.csv(df.M1.V.sum_rt_acc_l,'MS_match__rt_acc_long.csv',row.names = F)
+setwd(curDir)
+#ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
 ```
 
-The above figure shows the d prime for each condition (way 1)
-
-```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.M1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'd prime') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("d prime for each condition") +
-        coord_cartesian(ylim=c(1,3.5))+
-        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        apatheme + 
-        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-```
-
-The above figure shows the d prime for each condition (way 2)
-
-###Analaysis of reaction times
-```{r analyzing RT_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.M1.V.RT <- df.M1.V[df.M1.V$ACC == 1,]
-
-df.M1.V.RT.subj <- summarySEwithin(df.M1.V.RT,measurevar = 'RT', withinvar = c('Subject','Match','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
-df.M1.V.RT.grand <- summarySE(df.M1.V.RT.subj,measurevar = 'RT', groupvar = c('Match','Morality','Identity'),na.rm = TRUE)
-
-df.M1.V.RT_match <- df.M1.V.RT[df.M1.V.RT$Match == "match",]
-df.M1.V.RT_nonmatch <- df.M1.V.RT[df.M1.V.RT$Match == "nonmatch",]
-df.M1.V.RT_match.self <- df.M1.V.RT_match[df.M1.V.RT_match$Identity == 'Self',]
-df.M1.V.RT_match.other <- df.M1.V.RT_match[df.M1.V.RT_match$Identity == 'Other',]
-
-e7_L.rt_anova <- ezANOVA(df.M1.V.RT,dv = RT, wid = Subject, within = .(Match,Morality,Identity),within_full =  .(Match,Morality,Identity), type = 3)
-e7_L.rt_anova.match <- ezANOVA(df.M1.V.RT_match,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-e7_L.rt_anova.nonmatch <- ezANOVA(df.M1.V.RT_nonmatch,dv = RT, wid = Subject, within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-
-## t-test 
-df.M1.V.RT.subj_w <- dcast(df.M1.V.RT.subj, Subject ~ Match + Identity + Morality ,value.var = "RT")
-
-# Good self vs. Bad self
-e7_L.rt.t.m.good_bad_slf <- t.test(df.M1.V.RT.subj_w$match_Self_Good,df.M1.V.RT.subj_w$match_Self_Bad,paired = TRUE)
-df.M1.V.RT.subj_w$m.good_bad_slf <- df.M1.V.RT.subj_w$match_Self_Good - df.M1.V.RT.subj_w$match_Self_Bad
-e7_L.rt.t.m.good_bad_slf.CI <- bootES(df.M1.V.RT.subj_w$m.good_bad_slf, R = 5000,effect.type = "cohens.d")
-
-e7_L.rt.tvalue.good_bad_slf  <- round(as.numeric(e7_L.rt.t.m.good_bad_slf [[1]]),3)
-e7_L.rt.df.M1.good_bad_slf  <- as.numeric(e7_L.rt.t.m.good_bad_slf [[2]])
-e7_L.rt.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_slf [[3]]),"bonferroni",4)
-e7_L.rt.cohens.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[1]],4) 
-e7_L.rt.CI.L.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[12]][1],4)
-e7_L.rt.CI.H.good_bad_slf <- round(e7_L.rt.t.m.good_bad_slf.CI[[12]][2],4)
-
-# Good Other vs. Bad Other
-e7_L.rt.t.m.good_bad_oth <- t.test(df.M1.V.RT.subj_w$match_Other_Good,df.M1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
-df.M1.V.RT.subj_w$m.good_bad_oth <- df.M1.V.RT.subj_w$match_Other_Good - df.M1.V.RT.subj_w$match_Other_Bad
-e7_L.rt.t.m.good_bad_oth.CI <- bootES(df.M1.V.RT.subj_w$m.good_bad_oth, R = 5000,effect.type = "cohens.d")
-
-e7_L.rt.tvalue.good_bad_oth  <- round(as.numeric(e7_L.rt.t.m.good_bad_oth [[1]]),3)
-e7_L.rt.df.M1.good_bad_oth  <- as.numeric(e7_L.rt.t.m.good_bad_oth [[2]])
-e7_L.rt.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_L.rt.t.m.good_bad_oth [[3]]),"bonferroni",4)
-e7_L.rt.cohens.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[1]],4) 
-e7_L.rt.CI.L.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[12]][1],4)
-e7_L.rt.CI.H.good_bad_oth <- round(e7_L.rt.t.m.good_bad_oth.CI [[12]][2],4)
-
-# good self v. good other
-e7_L.rt.t.m.slf_oth_good <- t.test(df.M1.V.RT.subj_w$match_Self_Good,df.M1.V.RT.subj_w$match_Other_Good,paired = TRUE)
-df.M1.V.RT.subj_w$m.slf_oth_good <- df.M1.V.RT.subj_w$match_Self_Good - df.M1.V.RT.subj_w$match_Other_Good
-e7_L.rt.t.m.slf_oth_good.CI <- bootES(df.M1.V.RT.subj_w$m.slf_oth_good, R = 5000,effect.type = "cohens.d")
-
-e7_L.rt.tvalue.slf_oth_good  <- round(as.numeric(e7_L.rt.t.m.slf_oth_good[[1]]),3)
-e7_L.rt.df.M1.slf_oth_good  <- as.numeric(e7_L.rt.t.m.slf_oth_good[[2]])
-e7_L.rt.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_good[[3]]),"bonferroni",4)
-e7_L.rt.cohens.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[1]],4) 
-e7_L.rt.CI.L.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[12]][1],4)
-e7_L.rt.CI.H.slf_oth_good <- round(e7_L.rt.t.m.slf_oth_good.CI[[12]][2],4)
-
-e7_L.rt.t.m.slf_oth_bad <- t.test(df.M1.V.RT.subj_w$match_Self_Bad,df.M1.V.RT.subj_w$match_Other_Bad,paired = TRUE)
-df.M1.V.RT.subj_w$m.slf_oth_bad <- df.M1.V.RT.subj_w$match_Self_Bad - df.M1.V.RT.subj_w$match_Other_Bad
-e7_L.rt.t.m.slf_oth_bad.CI <- bootES(df.M1.V.RT.subj_w$m.slf_oth_bad, R = 5000,effect.type = "cohens.d")
-
-e7_L.rt.tvalue.slf_oth_bad  <- round(as.numeric(e7_L.rt.t.m.slf_oth_bad[[1]]),3)
-e7_L.rt.df.M1.slf_oth_bad  <- as.numeric(e7_L.rt.t.m.slf_oth_bad[[2]])
-e7_L.rt.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_L.rt.t.m.slf_oth_bad[[3]]),"bonferroni",4)
-e7_L.rt.cohens.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[1]],4) 
-e7_L.rt.CI.L.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[12]][1],4)
-e7_L.rt.CI.H.slf_oth_bad <- round(e7_L.rt.t.m.slf_oth_bad.CI[[12]][2],4)
-
-df.M1.V.RT.grand.match <- df.M1.V.RT.grand[df.M1.V.RT.grand$Match == "match",]
-
-##### save the rt data for late used ####
-colnames(df.M1.V.RT.subj_w) <- paste("L_rt", colnames(df.M1.V.RT.subj_w), sep = "_")
-colnames(df.M1.V.RT.subj_w)[colnames(df.M1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
-write.csv(df.M1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
-#### save the rt data ####
-
-e7_L.rt.mean.GoodSelf <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.sd.GoodSelf <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.mean.BadSelf <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
-e7_L.rt.sd.BadSelf <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Self'],0)
-
-e7_L.rt.mean.GoodOther <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.sd.GoodOther <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Good' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.mean.BadOther <- round(df.M1.V.RT.grand.match$RT[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
-e7_L.rt.sd.BadOther <- round(df.M1.V.RT.grand.match$sd[df.M1.V.RT.grand.match$Morality == 'Bad' & df.M1.V.RT.grand.match$Identity == 'Other'],0)
-
-e7_L.p_rt1 <- ggplot(data = df.M1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        xlab("Self-referential") +
-        ylab(" Reaction times (ms)") + 
-        coord_cartesian(ylim=c(500,800)) +
-        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
-        #ylim(0.3, 0.8) +
-        ggtitle("RT for each condition") +
-        #scale_y_continuous("Reation Times (ms)") + 
-        apatheme + 
-        theme(axis.text    = element_text(size = 24, color = 'black')) + 
-        theme(axis.title   = element_text(size = 24)) + 
-        theme(plot.title   = element_text(size = 24)) +
-        theme(legend.text  = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-e7_L.p_rt2 <- ggplot(data = df.M1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +   # Thinner lines
-        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        xlab("Moral valence") +
-        ylab(" Reaction times (ms)") + 
-        coord_cartesian(ylim=c(500,800))+
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
-        #ylim(0.3, 0.8) +
-        ggtitle("RT for each condition") +
-        scale_y_continuous("Reation Times  (ms)",breaks = seq(500,800,50),expand = c(0, 0)) +
-        apatheme + 
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-
-```
-
-We conducted a 2 * 3 * 2 rmANOVA for RT.
-
-The effect of `r e7_L.rt_anova[[1]][1,1]`: *F*(`r e7_L.rt_anova[[1]][1,2]`, `r e7_L.rt_anova[[1]][1,3]`) = `r round(e7_L.rt_anova[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][1,7],4)`
-
-The effect of `r e7_L.rt_anova[[1]][2,1]`: *F*(`r e7_L.rt_anova[[1]][2,2]`, `r e7_L.rt_anova[[1]][2,3]`) = `r round(e7_L.rt_anova[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][2,7],4)`
-
-The effect of `r e7_L.rt_anova[[1]][3,1]`: *F*(`r e7_L.rt_anova[[1]][3,2]`, `r e7_L.rt_anova[[1]][3,3]`) = `r round(e7_L.rt_anova[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][3,7],4)`.
-
-The effect of `r e7_L.rt_anova[[1]][4,1]`: *F*(`r e7_L.rt_anova[[1]][4,2]`, `r e7_L.rt_anova[[1]][4,3]`) = `r round(e7_L.rt_anova[[1]][4,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][4,7],4)`.
-
-The effect of `r e7_L.rt_anova[[1]][5,1]`: *F*(`r e7_L.rt_anova[[1]][5,2]`, `r e7_L.rt_anova[[1]][5,3]`) = `r round(e7_L.rt_anova[[1]][5,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][5,7],4)`.
-
-The effect of `r e7_L.rt_anova[[1]][6,1]`: *F*(`r e7_L.rt_anova[[1]][6,2]`, `r e7_L.rt_anova[[1]][6,3]`) = `r round(e7_L.rt_anova[[1]][6,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][6,7],4)`.
-
-The effect of `r e7_L.rt_anova[[1]][7,1]`: *F*(`r e7_L.rt_anova[[1]][7,2]`, `r e7_L.rt_anova[[1]][7,3]`) = `r round(e7_L.rt_anova[[1]][7,4],3)`, *p* = `r round(e7_L.rt_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova[[1]][7,7],4)`.
-
-We conducted a 3 * 2 rmANOVA for RT.
-
-**For the matched trials**, 
-The effect of `r e7_L.rt_anova.match[[1]][1,1]`: *F*(`r e7_L.rt_anova.match[[1]][1,2]`, `r e7_L.rt_anova.match[[1]][1,3]`) = `r round(e7_L.rt_anova.match[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][1,7],4)`
-
-The effect of `r e7_L.rt_anova.match[[1]][2,1]`: *F*(`r e7_L.rt_anova.match[[1]][2,2]`, `r e7_L.rt_anova.match[[1]][2,3]`) = `r round(e7_L.rt_anova.match[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][2,7],4)`
-
-The effect of `r e7_L.rt_anova.match[[1]][3,1]`: *F*(`r e7_L.rt_anova.match[[1]][3,2]`, `r e7_L.rt_anova.match[[1]][3,3]`) = `r round(e7_L.rt_anova.match[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova.match[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.match[[1]][3,7],4)`.
-
-**For the nonmatched trials**, 
-The effect of `r e7_L.rt_anova.nonmatch[[1]][1,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][1,2]`, `r e7_L.rt_anova.nonmatch[[1]][1,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][1,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][1,7],4)`
-
-The effect of `r e7_L.rt_anova.nonmatch[[1]][2,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][2,2]`, `r e7_L.rt_anova.nonmatch[[1]][2,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][2,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][2,7],4)`
-
-The effect of `r e7_L.rt_anova.nonmatch[[1]][3,1]`: *F*(`r e7_L.rt_anova.nonmatch[[1]][3,2]`, `r e7_L.rt_anova.nonmatch[[1]][3,3]`) = `r round(e7_L.rt_anova.nonmatch[[1]][3,4],3)`, *p* = `r round(e7_L.rt_anova.nonmatch[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_L.rt_anova.nonmatch[[1]][3,7],4)`.
-
-We conducted post-hoc comparison
-
-Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`): *t*(`r e7_L.rt.df.M1.good_bad_slf`) = `r e7_L.rt.tvalue.good_bad_slf`, *p* =
-`r e7_L.rt.pvalue.good_bad_slf.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_slf`, 95% CI [`r e7_L.rt.CI.L.good_bad_slf` `r e7_L.rt.CI.H.good_bad_slf`]
-
-Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`)  vs Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.M1.good_bad_oth`) = `r e7_L.rt.tvalue.good_bad_oth`, *p* =
-`r e7_L.rt.pvalue.good_bad_oth.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.good_bad_oth`, 95% CI [`r e7_L.rt.CI.L.good_bad_oth` `r e7_L.rt.CI.H.good_bad_oth`]
-
-Good self (`r e7_L.rt.mean.GoodSelf` $\pm$ `r e7_L.rt.sd.GoodSelf`) vs.
-Good other (`r e7_L.rt.mean.GoodOther` $\pm$ `r e7_L.rt.sd.GoodOther`) : *t*(`r e7_L.rt.df.M1.slf_oth_good`) = `r e7_L.rt.tvalue.slf_oth_good`, *p* = `r e7_L.rt.pvalue.slf_oth_good.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_good`, 95% CI [`r e7_L.rt.CI.L.slf_oth_good` `r e7_L.rt.CI.H.slf_oth_good`]
-
-Bad self (`r e7_L.rt.mean.BadSelf` $\pm$ `r e7_L.rt.sd.BadSelf`) vs.
-Bad other (`r e7_L.rt.mean.BadOther` $\pm$ `r e7_L.rt.sd.BadOther`): *t*(`r e7_L.rt.df.M1.slf_oth_bad`) = `r e7_L.rt.tvalue.slf_oth_bad`, *p* = `r e7_L.rt.pvalue.slf_oth_bad.adj`, *Cohen's* $d_z$ = `r e7_L.rt.cohens.slf_oth_bad`, 95% CI [`r e7_L.rt.CI.L.slf_oth_bad` `r e7_L.rt.CI.H.slf_oth_bad`]
-
-```{r plot2 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-# change a way to plot
-ggplot(data = df.M1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        xlab("Self-referential") +
-        ylab(" Reaction times (ms)") + 
-        coord_cartesian(ylim=c(500,800)) +
-        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
-        #ylim(0.3, 0.8) +
-        ggtitle("RT for each condition") +
-        #scale_y_continuous("Reation Times (ms)") + 
-        apatheme + 
-        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad"))+
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-```
-
-The above is the reaction time for each condition (way 1)
-
-```{r plot1 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-# df.M1.V.RT.grand.match <- df.M1.V.RT.grand[df.M1.V.RT.grand$Matchness == "match",]
-ggplot(data = df.M1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
-        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        xlab("Moral valence") +
-        ylab(" Reaction times (ms)") + 
-        coord_cartesian(ylim=c(500,800))+
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
-        #ylim(0.3, 0.8) +
-        ggtitle("RT for each condition") +
-        scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
-        apatheme + 
-        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-```
-
-The above is the reaction time for each condition (way 2)
-
-### Analyzing data from testing phase
-We only analyzed data for self-other categorization and Good-Bad categorization data
-
-#### analysis of ACC
-```{r clean the data_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-# df.C1.V <- df.C1.V[df.C1.V$Task != "importance",]
-df.C1.V$ACC[df.C1.V$ACC==-1] <-0
-
-df.C1.V.acc.subj <-  ddply(df.C1.V,.(Subject,Task,Morality,Identity), summarise,
+```{r preproc MS_categ_task,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+df.C1.V.acc <- plyr::ddply(df.C1.V,.(Subject,Age, Gender, Task,Morality,Identity), summarise,
                     N = length(ACC),
@@
 
-# define the level of factor# make the variables in a specified order
-df.C1.V.acc.subj$Morality <- factor(df.C1.V.acc.subj$Morality, levels=c("Good","Bad")) 
-df.C1.V.acc.subj$Identity <- factor(df.C1.V.acc.subj$Identity, levels=c("Self","Other"))
+# wide-format
+df.C1.V.acc_w  <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity ,value.var = "ACC")
 
-df.C1.V.acc.subj.Self <- df.C1.V.acc.subj[df.C1.V.acc.subj$Task == "Id_task",]
-df.C1.V.acc.subj.Good <- df.C1.V.acc.subj[df.C1.V.acc.subj$Task == "Valence_task",]
+# rename the column number
+colnames(df.C1.V.acc_w)[2:9] <- paste("ACC", colnames(df.C1.V.acc_w[,2:9]), sep = "_")
 
-e7_T.acc_anova <- ezANOVA(df.C1.V.acc.subj,dv = ACC, wid = Subject, within=.(Task,Morality,Identity), type=3)
-e7_T.acc_anova.self <- ezANOVA(df.C1.V.acc.subj.Self, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
-e7_T.acc_anova.Good <- ezANOVA(df.C1.V.acc.subj.Good, dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
+# combing data from diff task for analyzing the interaction btw val and id
+df.C1.V.acc_noTask  <-  plyr::ddply(df.C1.V,.(Subject, Morality, Identity), summarise,
+                    N = length(ACC),
+                    countN = sum(ACC),
+                    ACC = sum(ACC)/length(ACC))
 
-df.C1.V.acc.sum <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Task','Morality','Identity'))
+df.C1.V.acc_noTask_w <- dcast(df.C1.V.acc_noTask, Subject ~ Morality + Identity,value.var = "ACC")
+# rename the column number
+colnames(df.C1.V.acc_noTask_w)[2:5] <- paste("ACC", colnames(df.C1.V.acc_noTask_w[,2:5]), sep = "_")
 
-df.C1.V.acc.subj_w  <- dcast(df.C1.V.acc.subj, Subject ~ Task + Identity + Morality ,value.var = "ACC")
+# combine data cross task
+# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
+df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
+df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")
 
-# calculate the mean difference for moral effect (Good-Bad)
-df.C1.V.acc.subj_w$Valence_good_bad_slf <- df.C1.V.acc.subj_w$Valence_task_Self_Good - df.C1.V.acc.subj_w$Valence_task_Self_Bad
-df.C1.V.acc.subj_w$Valence_good_bad_oth <- df.C1.V.acc.subj_w$Valence_task_Other_Good - df.C1.V.acc.subj_w$Valence_task_Other_Bad
-df.C1.V.acc.subj_w$Id_good_bad_slf      <- df.C1.V.acc.subj_w$Id_task_Self_Good - df.C1.V.acc.subj_w$Id_task_Self_Bad
-df.C1.V.acc.subj_w$ID_good_bad_oth      <- df.C1.V.acc.subj_w$Id_task_Other_Good - df.C1.V.acc.subj_w$Id_task_Other_Bad
+df.C1.V.acc.noTask_w$good_bad_slf <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Self
+df.C1.V.acc.noTask_w$good_bad_oth <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Other
+df.C1.V.acc.noTask_w$slf_oth_good <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Good_Other
+df.C1.V.acc.noTask_w$slf_oth_bad <- df.C1.V.acc.noTask_w$Bad_Self - df.C1.V.acc.noTask_w$Bad_Other
 
-# calculate the mean difference for self effect (self-other)
-df.C1.V.acc.subj_w$Valence_slf_oth_good <- df.C1.V.acc.subj_w$Valence_task_Self_Good - df.C1.V.acc.subj_w$Valence_task_Other_Good
-df.C1.V.acc.subj_w$Valence_slf_oth_bad  <- df.C1.V.acc.subj_w$Valence_task_Self_Bad - df.C1.V.acc.subj_w$Valence_task_Other_Bad
-df.C1.V.acc.subj_w$Id_slf_oth_good  <- df.C1.V.acc.subj_w$Id_task_Self_Good - df.C1.V.acc.subj_w$Id_task_Other_Good
-df.C1.V.acc.subj_w$Id_slf_oth_bad   <- df.C1.V.acc.subj_w$Id_task_Self_Bad - df.C1.V.acc.subj_w$Id_task_Other_Bad
+## preprocessing RT data
+df.C1.V.RT <- df.C1.V[df.C1.V$ACC == 1,]  # exclued inaccurate data
+df.C1.V.RT.subj <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.C1.V.RT.subj_w <- dcast(df.C1.V.RT.subj, Subject ~ Task + Morality + Identity ,value.var = "RT")
 
-colnames(df.C1.V.acc.subj_w) <- paste("T_acc", colnames(df.C1.V.acc.subj_w), sep = "_")
-colnames(df.C1.V.acc.subj_w)[colnames(df.C1.V.acc.subj_w) == 'T_acc_Subject'] <- 'Subject'
-write.csv(df.C1.V.acc.subj_w,"data_catigorization_v_acc.csv",row.names=FALSE)
-# write.csv(df.C1.V.acc.sum,"df.C1.V.acc.sum.csv",row.names=FALSE)
+# rename the columns of RT data
+colnames(df.C1.V.RT.subj_w)[2:9] <- paste("RT", colnames(df.C1.V.RT.subj_w[,2:9]), sep = "_")
 
-# plot and save the ACC for each condition
-ACC_e7_T <- ggplot(data = df.C1.V.acc.sum,aes(y = ACC, x = Morality, group = Task,shape = Task, fill = Task)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Accuracy') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("Accuracy for each condition") +
-        coord_cartesian(ylim=c(0.5,1)) +
-        scale_y_continuous(breaks=seq(0.5,1,0.1),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        facet_grid(.~ Identity) + 
-        apatheme +
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("id criteria    ","morality criteria")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
+# combining data form different task for analyszing interaction of val and id
+df.C1.V.RT.subj_noTask <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Morality','Identity'), idvar = 'Subject',na.rm = TRUE)
+df.C1.V.RT.subj_noTask_w <- dcast(df.C1.V.RT.subj_noTask, Subject ~ Morality + Identity ,value.var = "RT")
 
-ggsave("ACC_e7_T.pdf", ACC_e7_T, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
+# rename the columns of RT data
+colnames(df.C1.V.RT.subj_noTask_w)[2:5] <- paste("RT", colnames(df.C1.V.RT.subj_noTask_w[,2:5]), sep = "_")
 
+## saving data ####
+# merge the accuracy and RT data and save
+df.C1.V.sum_w <- merge(df.C1.V.acc_w,  df.C1.V.RT.subj_w,by = "Subject")
+df.C1.V.sum_noTask_w <- merge(df.C1.V.acc_noTask_w,  df.C1.V.RT.subj_noTask_w,by = "Subject")
+
+# calculate the effect of self-ref and valence
+df.C1.v.sum_eff_w <- data.frame(df.C1.V.sum_w[,c('Subject')])
+colnames(df.C1.v.sum_eff_w) <- 'Subject'
+df.C1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$RT_Id_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$RT_Id_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+
+df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
+df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
+df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
+df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self
+
+# merge the effect file
+df.v.sum_eff_all_w <- merge(df.M1.v.sum_eff_w,df.C1.v.sum_eff_w,by="Subject")
+
+# merge the RT and ACC data (long-format) ####
+df.C1.V.sum_rt_acc_l <- merge(df.C1.V.acc,df.C1.V.RT.subj,by = c("Subject","Task","Morality",'Identity'))
+df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[order(df.C1.V.sum_rt_acc_l$Subject),]
+
+df.C1.V.sum_rt_acc_l <- df.C1.V.sum_rt_acc_l[,c("Subject","Task","Morality",'Identity',"N.x","countN","ACC","RT")]
+colnames(df.C1.V.sum_rt_acc_l) <- c("Subject","Task","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
+
+# write files to an upper-lelel folder
+setwd(traDir)
+write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
+write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
+setwd(curDir)
 ```
-ANOVA for accuracy with task type (self-other, Good-Bad) * moral character (Good vs. Bad) and self-relatedness (self v. other) as within-subjects factors.
 
-The main effect of `r e7_T.acc_anova[[1]][1,1]`, *F*(`r e7_T.acc_anova[[1]][1,2]`, `r e7_T.acc_anova[[1]][1,3]`) = `r round(e7_T.acc_anova[[1]][1,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][1,7],4)`.
+```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
+#plot the rT data from matching task
+MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
 
-The main effect of `r e7_T.acc_anova[[1]][2,1]`: *F*(`r e7_T.acc_anova[[1]][2,2]`, `r e7_T.acc_anova[[1]][2,3]`) = `r round(e7_T.acc_anova[[1]][2,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][2,7],4)`
-
-The main effect of `r e7_T.acc_anova[[1]][3,1]`: *F*(`r e7_T.acc_anova[[1]][3,2]`, `r e7_T.acc_anova[[1]][3,3]`) = `r round(e7_T.acc_anova[[1]][3,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][3,7],4)`.
-
-The interaction between: `r e7_T.acc_anova[[1]][4,1]`: *F*(`r e7_T.acc_anova[[1]][4,2]`, `r e7_T.acc_anova[[1]][4,3]`) = `r round(e7_T.acc_anova[[1]][4,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][4,7],4)`.
-
-The interaction between: `r e7_T.acc_anova[[1]][5,1]`: *F*(`r e7_T.acc_anova[[1]][5,2]`, `r e7_T.acc_anova[[1]][5,3]`) = `r round(e7_T.acc_anova[[1]][5,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][5,7],4)`.
-
-The interaction between: `r e7_T.acc_anova[[1]][6,1]`: *F*(`r e7_T.acc_anova[[1]][6,2]`, `r e7_T.acc_anova[[1]][6,3]`) = `r round(e7_T.acc_anova[[1]][6,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][6,7],4)`.
-
-The interaction between: `r e7_T.acc_anova[[1]][7,1]`: *F*(`r e7_T.acc_anova[[1]][7,2]`, `r e7_T.acc_anova[[1]][7,3]`) = `r round(e7_T.acc_anova[[1]][7,4],3)`, *p* = `r round(e7_T.acc_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova[[1]][7,7],4)`.
-
-Since there was no signficant interaction between Task type and other two variables, we combined the resuled from identity and valence based categorization.
-Given that the interaction between morality and identity was signficant, we further analyzed the simple effect.
-
-```{r ACC_e7_T_simple_effect, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-# combine data cross task
-# tmp <- aggregate(df.C1.V.acc.subj[,7],list(df.C1.V.acc.subj$Subject,df.C1.V.acc.subj$Morality,df.C1.V.acc.subj$Identity),mean)
-df.C1.V.acc.subj.noTask <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
-df.C1.V.acc.subj.noTask_w <- dcast(df.C1.V.acc.subj.noTask, Subject ~ Identity + Morality ,value.var = "ACC")
-
-df.C1.V.acc.subj.noTask_w$good_bad_slf <- df.C1.V.acc.subj.noTask_w$Self_Good - df.C1.V.acc.subj.noTask_w$Self_Bad
-df.C1.V.acc.subj.noTask_w$good_bad_oth <- df.C1.V.acc.subj.noTask_w$Other_Good - df.C1.V.acc.subj.noTask_w$Other_Bad
-df.C1.V.acc.subj.noTask_w$slf_oth_good <- df.C1.V.acc.subj.noTask_w$Self_Good - df.C1.V.acc.subj.noTask_w$Other_Good
-df.C1.V.acc.subj.noTask_w$slf_oth_bad <- df.C1.V.acc.subj.noTask_w$Self_Bad - df.C1.V.acc.subj.noTask_w$Other_Bad
-
-write.csv(df.C1.V.acc.subj.noTask_w, 'df.C1.V.acc.subj.noTask.csv',row.names = F)
-
-e7_T.acc_anova_noTask1 <- ezANOVA(df.C1.V.acc.subj.noTask,dv = ACC, wid = Subject, within=.(Morality,Identity), type=3)
-# e7_T.acc_anova_noTask1 is exactly the same as in three way rm ANOVA
-
-# simple effect:
-
-# Good self vs Bad self
-e7_T.acc.t.good_bad_slf <- t.test(df.C1.V.acc.subj.noTask_w$Self_Good,df.C1.V.acc.subj.noTask_w$Self_Bad,paired = TRUE)
-e7_T.acc.t.good_bad_slf.CI <- bootES(df.C1.V.acc.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
-
-e7_T.acc.tvalue.good_bad_slf <- round(as.numeric(e7_T.acc.t.good_bad_slf[[1]]),3)
-e7_T.acc.df.good_bad_slf <- as.numeric(e7_T.acc.t.good_bad_slf[[2]])
-e7_T.acc.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_T.acc.t.good_bad_slf[[3]]),"bonferroni",4)
-e7_T.acc.cohens.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[1]],4) 
-e7_T.acc.CI.L.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[12]][1],4)
-e7_T.acc.CI.H.good_bad_slf <- round(e7_T.acc.t.good_bad_slf.CI[[12]][2],4)
-
-# Good other vs Bad other
-e7_T.acc.t.good_bad_oth <- t.test(df.C1.V.acc.subj.noTask_w$Other_Good,df.C1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.acc.t.good_bad_oth.CI <- bootES(df.C1.V.acc.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
-
-e7_T.acc.tvalue.good_bad_oth <- round(as.numeric(e7_T.acc.t.good_bad_oth[[1]]),3)
-e7_T.acc.df.good_bad_oth <- as.numeric(e7_T.acc.t.good_bad_oth[[2]])
-e7_T.acc.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_T.acc.t.good_bad_oth[[3]]),"bonferroni",4)
-e7_T.acc.cohens.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[1]],4) 
-e7_T.acc.CI.L.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[12]][1],4)
-e7_T.acc.CI.H.good_bad_oth <- round(e7_T.acc.t.good_bad_oth.CI[[12]][2],4)
-
-# Good self vs Good other
-e7_T.acc.t.slf_oth_good <- t.test(df.C1.V.acc.subj.noTask_w$Self_Good,df.C1.V.acc.subj.noTask_w$Other_Good,paired = TRUE)
-e7_T.acc.t.slf_oth_good.CI <- bootES(df.C1.V.acc.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
-
-e7_T.acc.tvalue.slf_oth_good <- round(as.numeric(e7_T.acc.t.slf_oth_good[[1]]),3)
-e7_T.acc.df.slf_oth_good <- as.numeric(e7_T.acc.t.slf_oth_good[[2]])
-e7_T.acc.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_T.acc.t.slf_oth_good[[3]]),"bonferroni",4)
-e7_T.acc.cohens.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[1]],4) 
-e7_T.acc.CI.L.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[12]][1],4)
-e7_T.acc.CI.H.slf_oth_good <- round(e7_T.acc.t.slf_oth_good.CI[[12]][2],4)
-
-# Bad self vs Bad other
-e7_T.acc.t.slf_oth_bad <- t.test(df.C1.V.acc.subj.noTask_w$Self_Bad,df.C1.V.acc.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.acc.t.slf_oth_bad.CI <- bootES(df.C1.V.acc.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
-
-e7_T.acc.tvalue.slf_oth_bad <- round(as.numeric(e7_T.acc.t.slf_oth_bad[[1]]),3)
-e7_T.acc.df.slf_oth_bad <- as.numeric(e7_T.acc.t.slf_oth_bad[[2]])
-e7_T.acc.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_T.acc.t.slf_oth_bad[[3]]),"bonferroni",4)
-e7_T.acc.cohens.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[1]],4) 
-e7_T.acc.CI.L.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[12]][1],4)
-e7_T.acc.CI.H.slf_oth_bad <- round(e7_T.acc.t.slf_oth_bad.CI[[12]][2],4)
-
-df.C1.V.acc.sum.noTask <- summarySE(df.C1.V.acc.subj,measurevar = 'ACC',groupvars = c('Morality','Identity'))
-ACC.Mean.Good.Self <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Good']
-ACC.SD.Good.Self <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Good']
-ACC.Mean.Bad.Self <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.SD.Bad.Self <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Self' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.Mean.Good.Other <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Good']
-ACC.SD.Good.Other <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Good']
-ACC.Mean.Bad.Other <- df.C1.V.acc.sum.noTask$ACC[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
-ACC.SD.Bad.Other <- df.C1.V.acc.sum.noTask$sd[df.C1.V.acc.sum.noTask$Identity == 'Other' & df.C1.V.acc.sum.noTask$Morality == 'Bad']
-
-# e7_T.acc_anova_id2 <- ezANOVA(df.C1.V.acc.subj.noTask[df.C1.V.acc.subj.noTask$Identity == 'self',],dv = ACC, wid = Subject, within=.(Morality), type=3)
-
-# e7_T.acc_anova_id3 <- ezANOVA(df.C1.V.acc.subj[df.C1.V.acc.subj$Morality == 'Good',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
-# e7_T.acc_anova_id4 <- ezANOVA(df.C1.V.acc.subj[df.C1.V.acc.subj$Morality == 'Bad',],dv = ACC, wid = Subject, within=.(Task,Identity), type=3)
-
-# plot the data without task variable
-ACC_e7_T_noTask <- ggplot(data =df.C1.V.acc.sum.noTask,aes(y = ACC, x =Morality, group = Identity,shape = Identity, fill = Identity))+
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Accuracy') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("Accuracy for each condition") +
-        coord_cartesian(ylim=c(0.5,1)) +
-        scale_y_continuous(breaks=seq(0.5,1,0.1),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        #facet_grid(.~ Identity) + 
-        apatheme +
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-ggsave("ACC_e7_T_noTask.pdf", ACC_e7_T_noTask, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
+# plot the dprime data from matching task
+MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
 
@@
 
-2 by 2 ANOVA:
-The main effect of `r e7_T.acc_anova_noTask1[[1]][1,1]`, *F*(`r e7_T.acc_anova_noTask1[[1]][1,2]`, `r e7_T.acc_anova_noTask1[[1]][1,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][1,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][1,7],4)`.
+```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
+# plot ACC
+MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
 
-The main effect of `r e7_T.acc_anova_noTask1[[1]][2,1]`: *F*(`r e7_T.acc_anova_noTask1[[1]][2,2]`, `r e7_T.acc_anova_noTask1[[1]][2,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][2,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][2,7],4)`
-
-The interaction `r e7_T.acc_anova_noTask1[[1]][3,1]`: *F*(`r e7_T.acc_anova_noTask1[[1]][3,2]`, `r e7_T.acc_anova_noTask1[[1]][3,3]`) = `r round(e7_T.acc_anova_noTask1[[1]][3,4],3)`, *p* = `r round(e7_T.acc_anova_noTask1[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.acc_anova_noTask1[[1]][3,7],4)`.
-
-As for the self condition, effect of moral valence was significante: t(`r e7_T.acc.df.good_bad_slf`) = `r e7_T.acc.tvalue.good_bad_slf`, p = `r e7_T.acc.pvalue.good_bad_slf.adj`, Cohen's d = `r e7_T.acc.cohens.good_bad_slf`, 95% CI[`r e7_T.acc.CI.L.good_bad_slf` `r e7_T.acc.CI.H.good_bad_slf`].
-For other condition, moral valence was not significante: t(`r e7_T.acc.df.good_bad_oth`) = `r e7_T.acc.tvalue.good_bad_oth`, p = `r e7_T.acc.pvalue.good_bad_oth.adj`, Cohen's d = `r e7_T.acc.cohens.good_bad_oth`, 95% CI[`r e7_T.acc.CI.L.good_bad_oth` `r e7_T.acc.CI.H.good_bad_oth`].
-
-The effect of identity:
-for moral condition, the difference between self and other was significant:t(`r e7_T.acc.df.slf_oth_good`) = `r e7_T.acc.tvalue.slf_oth_good`, p = `r e7_T.acc.pvalue.slf_oth_good.adj`, Cohen's d = `r e7_T.acc.cohens.slf_oth_good`, 95% CI[`r e7_T.acc.CI.L.slf_oth_good` `r e7_T.acc.CI.H.slf_oth_good`].
-for Bad condition, the difference between self and other was not significant:t(`r e7_T.acc.df.slf_oth_bad`) = `r e7_T.acc.tvalue.slf_oth_bad`, p = `r e7_T.acc.pvalue.slf_oth_bad.adj`, Cohen's d = `r e7_T.acc.cohens.slf_oth_bad`, 95% CI[`r e7_T.acc.CI.L.slf_oth_bad` `r e7_T.acc.CI.H.slf_oth_bad`].
-
-Good self: `r ACC.Mean.Good.Self` + `r ACC.SD.Good.Self`
-Bad self:`r ACC.Mean.Bad.Self` + `r ACC.SD.Bad.Self`
-Good other: `r ACC.Mean.Good.Other` + `r ACC.SD.Good.Other`
-Bad other: `r ACC.Mean.Bad.Other` + `r ACC.SD.Bad.Other`
-
-```{r plot2 the ACC_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.C1.V.acc.sum,aes(y = ACC, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = ACC - se, ymax = ACC + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Accuracy') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("Accuracy for each condition") +
-        coord_cartesian(ylim=c(0.5,1))+
-        scale_y_continuous(breaks = seq(0.5,1,0.1),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        facet_grid(.~Task) + 
-        apatheme  +
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-```
-
-The above is the ACC for each condition. left panel is the results of moral-categorization task, the right panel is the self-other categorization task.
-
-###Analaysis of reaction times
-```{r analyzing RT_e7_T,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.C1.V.RT <- df.C1.V[df.C1.V$ACC == 1,]
-# excluded 7035 and subject8
-# df.C1.V.RT <- df.C1.V.RT[!(df.C1.V.RT$Subject %in% c("8","7035")),] 
-df.C1.V.RT.subj <- summarySEwithin(df.C1.V.RT,measurevar = 'RT', withinvar = c('Subject','Task','Morality','Identity'),idvar = 'Subject', na.rm = TRUE)
-
-# define the level of factor
-df.C1.V.RT.subj$Morality <- factor(df.C1.V.RT.subj$Morality, levels=c("Good","Bad")) # make the variables in a specified order
-df.C1.V.RT.subj$Identity <- factor(df.C1.V.RT.subj$Identity, levels=c("Self","Other"))
-
-df.C1.V.RT.subj_w  <- dcast(df.C1.V.RT.subj, Subject ~ Task + Identity + Morality ,value.var = "RT")
-
-# calculate the mean difference for Good effect (Good-Bad)
-df.C1.V.RT.subj_w$Valence_good_bad_slf  <- df.C1.V.RT.subj_w$Valence_task_Self_Good - df.C1.V.RT.subj_w$Valence_task_Self_Bad
-df.C1.V.RT.subj_w$Valence_good_bad_oth  <- df.C1.V.RT.subj_w$Valence_task_Other_Good - df.C1.V.RT.subj_w$Valence_task_Other_Bad
-df.C1.V.RT.subj_w$Id_good_bad_slf       <- df.C1.V.RT.subj_w$Id_task_Self_Good   - df.C1.V.RT.subj_w$Id_task_Self_Bad
-df.C1.V.RT.subj_w$ID_good_bad_oth       <- df.C1.V.RT.subj_w$Id_task_Other_Good - df.C1.V.RT.subj_w$Id_task_Other_Bad
-
-# calculate the mean difference for self effect (self-other)
-df.C1.V.RT.subj_w$Valence_slf_oth_good <- df.C1.V.RT.subj_w$Valence_task_Self_Good   - df.C1.V.RT.subj_w$Valence_task_Other_Good
-df.C1.V.RT.subj_w$valence_slf_oth_bad  <- df.C1.V.RT.subj_w$Valence_task_Self_Bad - df.C1.V.RT.subj_w$Valence_task_Other_Bad
-df.C1.V.RT.subj_w$Id_slf_oth_good      <- df.C1.V.RT.subj_w$Id_task_Self_Good - df.C1.V.RT.subj_w$Id_task_Other_Good
-df.C1.V.RT.subj_w$Id_slf_oth_bad       <- df.C1.V.RT.subj_w$Id_task_Self_Bad - df.C1.V.RT.subj_w$Id_task_Other_Bad
-
-#### save the rt data for later use ####
-colnames(df.C1.V.RT.subj_w) <- paste("T_rt", colnames(df.C1.V.RT.subj_w), sep = "_")
-colnames(df.C1.V.RT.subj_w)[colnames(df.C1.V.RT.subj_w) == 'T_rt_Subject'] <- 'Subject'
-write.csv(df.C1.V.RT.subj_w,"data_catigorization_v_rt.csv",row.names=FALSE)
-###########
-
-df.C1.V.RT.grand <- summarySE(df.C1.V.RT.subj,measurevar = 'RT', groupvar = c('Task','Morality','Identity'),na.rm = TRUE)
-
-df.C1.V.RT_Id_task <- df.C1.V.RT[df.C1.V.RT$Task == "Id_task",]
-df.C1.V.RT_Val_task <- df.C1.V.RT[df.C1.V.RT$Task == "Valence_task",]
-#df.C1.V.RT_match.self <- df.C1.V.RT_match[df.C1.V.RT_match$Identity == 'self',]
-#df.C1.V.RT_match.other <- df.C1.V.RT_match[df.C1.V.RT_match$Identity == 'other',]
-
-e7_T.rt_anova <- ezANOVA(df.C1.V.RT,dv = RT, wid = Subject, within=.(Task,Morality,Identity),
-                         within_full=.(Task,Identity,Morality), type=3)
-
-e7_T.rt_anova.Id_task <- ezANOVA(df.C1.V.RT_Id_task,dv = RT, wid = Subject, 
-                                 within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-
-e7_T.rt_anova.val_task <- ezANOVA(df.C1.V.RT_Val_task,dv = RT, wid = Subject,
-                                  within=.(Morality,Identity),within_full=.(Identity,Morality), type=3)
-
-RT_e7_T <- ggplot(data = df.C1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Reaction times') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("Reaction times for each condition") +
-        coord_cartesian(ylim=c(500,800)) +
-        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        facet_grid(.~ Identity) + 
-        apatheme +
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("id criteria    ","morality criteria")) +
-        theme(strip.text.x = element_text(size = 16, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-ggsave("RT_e7_T.pdf", RT_e7_T, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
+# plot RT
+MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
 
@@
 
-ANOVA for RT with task type (self-other, Good-Bad) * moral character (Good vs. Bad) and self-relatedness (self v. other) as within-subjects factors.
-
-The main effect of `r e7_T.rt_anova[[1]][1,1]`, *F*(`r e7_T.rt_anova[[1]][1,2]`, `r e7_T.rt_anova[[1]][1,3]`) = `r round(e7_T.rt_anova[[1]][1,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][1,7],4)`.
-
-The main effect of `r e7_T.rt_anova[[1]][2,1]`: *F*(`r e7_T.rt_anova[[1]][2,2]`, `r e7_T.rt_anova[[1]][2,3]`) = `r round(e7_T.rt_anova[[1]][2,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][2,7],4)`
-
-The main effect of `r e7_T.rt_anova[[1]][3,1]`: *F*(`r e7_T.rt_anova[[1]][3,2]`, `r e7_T.rt_anova[[1]][3,3]`) = `r round(e7_T.rt_anova[[1]][3,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][3,7],4)`.
-
-The interaction between: `r e7_T.rt_anova[[1]][4,1]`: *F*(`r e7_T.rt_anova[[1]][4,2]`, `r e7_T.rt_anova[[1]][4,3]`) = `r round(e7_T.rt_anova[[1]][4,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][4,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][4,7],4)`.
-
-The interaction between: `r e7_T.rt_anova[[1]][5,1]`: *F*(`r e7_T.rt_anova[[1]][5,2]`, `r e7_T.rt_anova[[1]][5,3]`) = `r round(e7_T.rt_anova[[1]][5,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][5,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][5,7],4)`.
-
-The interaction between: `r e7_T.rt_anova[[1]][6,1]`: *F*(`r e7_T.rt_anova[[1]][6,2]`, `r e7_T.rt_anova[[1]][6,3]`) = `r round(e7_T.rt_anova[[1]][6,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][6,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][6,7],4)`.
-
-The interaction between: `r e7_T.rt_anova[[1]][7,1]`: *F*(`r e7_T.rt_anova[[1]][7,2]`, `r e7_T.rt_anova[[1]][7,3]`) = `r round(e7_T.rt_anova[[1]][7,4],3)`, *p* = `r round(e7_T.rt_anova[[1]][7,5],4)`, $\eta_g^2$ = `r round(e7_T.rt_anova[[1]][7,7],4)`.
-
-Since there was no signficant interaction between identity and other two variables for RT, we combined the results from different shape identity.
-Given that the interaction between Task and moral valence was signficant, we further analyzed the simple effect.
-
-```{r RT_e7_T_simple_effect_noID, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-# combine data cross identity
-df.C1.V.RT.subj.noID <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Task','Morality'))
-df.C1.V.RT.subj.noID_w <- dcast(df.C1.V.RT.subj.noID, Subject ~ Task + Morality ,value.var = "RT")
-
-# valence effect under different task
-df.C1.V.RT.subj.noID_w$good_bad_ID <- df.C1.V.RT.subj.noID_w$Id_task_Good - df.C1.V.RT.subj.noID_w$Id_task_Bad
-df.C1.V.RT.subj.noID_w$good_bad_Val <- df.C1.V.RT.subj.noID_w$Valence_task_Good - df.C1.V.RT.subj.noID_w$Valence_task_Bad
-
-# task effect for differnt valence
-df.C1.V.RT.subj.noID_w$ID_Val_good <- df.C1.V.RT.subj.noID_w$Id_task_Good - df.C1.V.RT.subj.noID_w$Valence_task_Good
-df.C1.V.RT.subj.noID_w$ID_Val_bad <- df.C1.V.RT.subj.noID_w$Id_task_Bad - df.C1.V.RT.subj.noID_w$Valence_task_Bad
-
-write.csv(df.C1.V.RT.subj.noID_w, 'df.C1.V.RT.subj.noID_w.csv',row.names = F)
-
-e7_T.RT_anova_noID <- ezANOVA(df.C1.V.RT.subj.noID,dv = RT, wid = Subject, within=.(Task,Morality), type=3)
-
-# simple effect:
-
-# Id categorization task: Good v. Bad
-e7_T.RT.t.good_bad_ID <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Good,df.C1.V.RT.subj.noID_w$Id_task_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_ID.CI <- bootES(df.C1.V.RT.subj.noID_w$good_bad_ID,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.good_bad_ID <- round(as.numeric(e7_T.RT.t.good_bad_ID[[1]]),3)
-e7_T.RT.df.good_bad_ID <- as.numeric(e7_T.RT.t.good_bad_ID[[2]])
-e7_T.RT.pvalue.good_bad_ID.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_ID[[3]]),"bonferroni",4)
-e7_T.RT.cohens.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[1]],4) 
-e7_T.RT.CI.L.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[12]][1],4)
-e7_T.RT.CI.H.good_bad_ID <- round(e7_T.RT.t.good_bad_ID.CI[[12]][2],4)
-
-# moral task: Good v. Bad
-e7_T.RT.t.good_bad_Val <- t.test(df.C1.V.RT.subj.noID_w$Valence_task_Good,df.C1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_Val.CI <- bootES(df.C1.V.RT.subj.noID_w$good_bad_Val,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.good_bad_Val <- round(as.numeric(e7_T.RT.t.good_bad_Val[[1]]),3)
-e7_T.RT.df.good_bad_Val <- as.numeric(e7_T.RT.t.good_bad_Val[[2]])
-e7_T.RT.pvalue.good_bad_Val.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_Val[[3]]),"bonferroni",4)
-e7_T.RT.cohens.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[1]],4) 
-e7_T.RT.CI.L.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[12]][1],4)
-e7_T.RT.CI.H.good_bad_Val <- round(e7_T.RT.t.good_bad_Val.CI[[12]][2],4)
-
-# Good valence: self task v. moral task
-e7_T.RT.t.ID_Val_good <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Good,df.C1.V.RT.subj.noID_w$Valence_task_Good,paired = TRUE)
-e7_T.RT.t.ID_Val_good.CI <- bootES(df.C1.V.RT.subj.noID_w$ID_Val_good,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.ID_Val_good <- round(as.numeric(e7_T.RT.t.ID_Val_good[[1]]),3)
-e7_T.RT.df.ID_Val_good <- as.numeric(e7_T.RT.t.ID_Val_good[[2]])
-e7_T.RT.pvalue.ID_Val_good.adj <- p.adjust(as.numeric(e7_T.RT.t.ID_Val_good[[3]]),"bonferroni",4)
-e7_T.RT.cohens.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[1]],4) 
-e7_T.RT.CI.L.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[12]][1],4)
-e7_T.RT.CI.H.ID_Val_good <- round(e7_T.RT.t.ID_Val_good.CI[[12]][2],4)
-
-# Bad valence: self task v. moral task
-e7_T.RT.t.ID_Val_bad <- t.test(df.C1.V.RT.subj.noID_w$Id_task_Bad,df.C1.V.RT.subj.noID_w$Valence_task_Bad,paired = TRUE)
-e7_T.RT.t.ID_Val_bad.CI <- bootES(df.C1.V.RT.subj.noID_w$ID_Val_bad,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.ID_Val_bad <- round(as.numeric(e7_T.RT.t.ID_Val_bad[[1]]),3)
-e7_T.RT.df.ID_Val_bad <- as.numeric(e7_T.RT.t.ID_Val_bad[[2]])
-e7_T.RT.pvalue.ID_Val_bad.adj <- p.adjust(as.numeric(e7_T.RT.t.ID_Val_bad[[3]]),"bonferroni",4)
-e7_T.RT.cohens.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[1]],4) 
-e7_T.RT.CI.L.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[12]][1],4)
-e7_T.RT.CI.H.ID_Val_bad <- round(e7_T.RT.t.ID_Val_bad.CI[[12]][2],4)
-
-RT.Mean.ID_task.Good  <- mean(df.C1.V.RT.subj.noID_w$Id_task_Good)
-RT.SD.ID_task.Good  <- sd(df.C1.V.RT.subj.noID_w$Id_task_Good)
-RT.Mean.ID_task.Bad <- mean(df.C1.V.RT.subj.noID_w$Id_task_Bad)
-RT.SD.ID_task.Bad <- sd(df.C1.V.RT.subj.noID_w$Id_task_Bad)
-RT.Mean.Val_task.Good <- mean(df.C1.V.RT.subj.noID_w$Valence_task_Good)
-RT.SD.Val_task.Good <- sd(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
-RT.Mean.Val_task.Bad <- mean(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
-RT.SD.Val_task.Bad <- sd(df.C1.V.RT.subj.noID_w$Valence_task_Bad)
+```{r plot_categ_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
+# plot ACC
+MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
+# plot RT
+MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
 ```
-2 by 2 ANOVA:
-The main effect of `r e7_T.RT_anova_noID[[1]][1,1]`, *F*(`r e7_T.RT_anova_noID[[1]][1,2]`, `r e7_T.RT_anova_noID[[1]][1,3]`) = `r round(e7_T.RT_anova_noID[[1]][1,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][1,7],4)`.
-
-The main effect of `r e7_T.RT_anova_noID[[1]][2,1]`: *F*(`r e7_T.RT_anova_noID[[1]][2,2]`, `r e7_T.RT_anova_noID[[1]][2,3]`) = `r round(e7_T.RT_anova_noID[[1]][2,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][2,7],4)`
-
-The interaction `r e7_T.RT_anova_noID[[1]][3,1]`: *F*(`r e7_T.RT_anova_noID[[1]][3,2]`, `r e7_T.RT_anova_noID[[1]][3,3]`) = `r round(e7_T.RT_anova_noID[[1]][3,4],3)`, *p* = `r round(e7_T.RT_anova_noID[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noID[[1]][3,7],4)`.
-
-As for the Identity task, effect of moral valence was significante: t(`r e7_T.RT.df.good_bad_ID`) = `r e7_T.RT.tvalue.good_bad_ID`, p = `r e7_T.RT.pvalue.good_bad_ID.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_ID`, 95% CI[`r e7_T.RT.CI.L.good_bad_ID` `r e7_T.RT.CI.H.good_bad_ID`].
-For moral task : t(`r e7_T.RT.df.good_bad_Val`) = `r e7_T.RT.tvalue.good_bad_Val`, p = `r e7_T.RT.pvalue.good_bad_Val.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_Val`, 95% CI[`r e7_T.RT.CI.L.good_bad_Val` `r e7_T.RT.CI.H.good_bad_Val`].
-
-The effect of task:
-for moral condition, the difference between self and moral task:t(`r e7_T.RT.df.ID_Val_good`) = `r e7_T.RT.tvalue.ID_Val_good`, p = `r e7_T.RT.pvalue.ID_Val_good.adj`, Cohen's d = `r e7_T.RT.cohens.ID_Val_good`, 95% CI[`r e7_T.RT.CI.L.ID_Val_good` `r e7_T.RT.CI.H.ID_Val_good`].
-for Bad condition, the difference between self and moral task :t(`r e7_T.RT.df.ID_Val_bad`) = `r e7_T.RT.tvalue.ID_Val_bad`, p = `r e7_T.RT.pvalue.ID_Val_bad.adj`, Cohen's d = `r e7_T.RT.cohens.ID_Val_bad`, 95% CI[`r e7_T.RT.CI.L.ID_Val_bad` `r e7_T.RT.CI.H.ID_Val_bad`].
-
-Moral valence for self condition: `r RT.Mean.ID_task.Good ` + `r RT.SD.ID_task.Good `
-Bad for self condition:`r RT.Mean.ID_task.Bad` + `r RT.SD.ID_task.Bad`
-Good for moral condition: `r RT.Mean.Val_task.Good` + `r RT.SD.Val_task.Good`
-Bad for moral condition: `r RT.Mean.Val_task.Bad` + `r RT.SD.Val_task.Bad`
-
-```{r RT_e7_T_simple_effect_noTask, ,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-df.C1.V.RT.subj.noTask <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Subject','Identity','Morality'))
-df.C1.V.RT.subj.noTask_w <- dcast(df.C1.V.RT.subj.noTask, Subject ~ Identity + Morality ,value.var = "RT")
-
-df.C1.V.RT.subj.noTask_w$good_bad_slf <- df.C1.V.RT.subj.noTask_w$Self_Good - df.C1.V.RT.subj.noTask_w$Self_Bad
-df.C1.V.RT.subj.noTask_w$good_bad_oth <- df.C1.V.RT.subj.noTask_w$Other_Good - df.C1.V.RT.subj.noTask_w$Other_Bad
-df.C1.V.RT.subj.noTask_w$slf_oth_good <- df.C1.V.RT.subj.noTask_w$Self_Good - df.C1.V.RT.subj.noTask_w$Other_Good
-df.C1.V.RT.subj.noTask_w$slf_oth_bad <- df.C1.V.RT.subj.noTask_w$Self_Bad - df.C1.V.RT.subj.noTask_w$Other_Bad
-
-write.csv(df.C1.V.RT.subj.noTask_w, 'df.C1.V.RT.subj.noTask_w.csv',row.names = F)
-
-e7_T.RT_anova_noTask <- ezANOVA(df.C1.V.RT.subj.noTask,dv = RT, wid = Subject, within=.(Morality,Identity), type=3)
-# e7_T.RT_anova_noTask1 is exactly the same as in three way rm ANOVA
-
-# simple effect:
-
-# Good self vs Bad self
-e7_T.RT.t.good_bad_slf <- t.test(df.C1.V.RT.subj.noTask_w$Self_Good,df.C1.V.RT.subj.noTask_w$Self_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_slf.CI <- bootES(df.C1.V.RT.subj.noTask_w$good_bad_slf,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.good_bad_slf <- round(as.numeric(e7_T.RT.t.good_bad_slf[[1]]),3)
-e7_T.RT.df.good_bad_slf <- as.numeric(e7_T.RT.t.good_bad_slf[[2]])
-e7_T.RT.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_slf[[3]]),"bonferroni",4)
-e7_T.RT.cohens.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[1]],4) 
-e7_T.RT.CI.L.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[12]][1],4)
-e7_T.RT.CI.H.good_bad_slf <- round(e7_T.RT.t.good_bad_slf.CI[[12]][2],4)
-
-# Good other vs Bad other
-e7_T.RT.t.good_bad_oth <- t.test(df.C1.V.RT.subj.noTask_w$Other_Good,df.C1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.RT.t.good_bad_oth.CI <- bootES(df.C1.V.RT.subj.noTask_w$good_bad_oth,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.good_bad_oth <- round(as.numeric(e7_T.RT.t.good_bad_oth[[1]]),3)
-e7_T.RT.df.good_bad_oth <- as.numeric(e7_T.RT.t.good_bad_oth[[2]])
-e7_T.RT.pvalue.good_bad_oth.adj <- p.adjust(as.numeric(e7_T.RT.t.good_bad_oth[[3]]),"bonferroni",4)
-e7_T.RT.cohens.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[1]],4) 
-e7_T.RT.CI.L.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[12]][1],4)
-e7_T.RT.CI.H.good_bad_oth <- round(e7_T.RT.t.good_bad_oth.CI[[12]][2],4)
-
-# Good self vs Good other
-e7_T.RT.t.slf_oth_good <- t.test(df.C1.V.RT.subj.noTask_w$Self_Good,df.C1.V.RT.subj.noTask_w$Other_Good,paired = TRUE)
-e7_T.RT.t.slf_oth_good.CI <- bootES(df.C1.V.RT.subj.noTask_w$slf_oth_good,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.slf_oth_good <- round(as.numeric(e7_T.RT.t.slf_oth_good[[1]]),3)
-e7_T.RT.df.slf_oth_good <- as.numeric(e7_T.RT.t.slf_oth_good[[2]])
-e7_T.RT.pvalue.slf_oth_good.adj <- p.adjust(as.numeric(e7_T.RT.t.slf_oth_good[[3]]),"bonferroni",4)
-e7_T.RT.cohens.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[1]],4) 
-e7_T.RT.CI.L.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[12]][1],4)
-e7_T.RT.CI.H.slf_oth_good <- round(e7_T.RT.t.slf_oth_good.CI[[12]][2],4)
-
-# Bad self vs Bad other
-e7_T.RT.t.slf_oth_bad <- t.test(df.C1.V.RT.subj.noTask_w$Self_Bad,df.C1.V.RT.subj.noTask_w$Other_Bad,paired = TRUE)
-e7_T.RT.t.slf_oth_bad.CI <- bootES(df.C1.V.RT.subj.noTask_w$slf_oth_bad,R = 20000, effect.type = "cohens.d")
-
-e7_T.RT.tvalue.slf_oth_bad <- round(as.numeric(e7_T.RT.t.slf_oth_bad[[1]]),3)
-e7_T.RT.df.slf_oth_bad <- as.numeric(e7_T.RT.t.slf_oth_bad[[2]])
-e7_T.RT.pvalue.slf_oth_bad.adj <- p.adjust(as.numeric(e7_T.RT.t.slf_oth_bad[[3]]),"bonferroni",4)
-e7_T.RT.cohens.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[1]],4) 
-e7_T.RT.CI.L.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[12]][1],4)
-e7_T.RT.CI.H.slf_oth_bad <- round(e7_T.RT.t.slf_oth_bad.CI[[12]][2],4)
-
-RT.Mean.Good.Self <- mean(df.C1.V.RT.subj.noTask_w$Self_Good)
-RT.SD.Good.Self <- sd(df.C1.V.RT.subj.noTask_w$Self_Good)
-RT.Mean.Bad.Self <- mean(df.C1.V.RT.subj.noTask_w$Self_Bad)
-RT.SD.Bad.Self <- sd(df.C1.V.RT.subj.noTask_w$Self_Bad)
-RT.Mean.Good.Other <- mean(df.C1.V.RT.subj.noTask_w$Other_Good)
-RT.SD.Good.Other <- sd(df.C1.V.RT.subj.noTask_w$Other_Good)
-RT.Mean.Bad.Other <- mean(df.C1.V.RT.subj.noTask_w$Other_Bad)
-RT.SD.Bad.Other <- sd(df.C1.V.RT.subj.noTask_w$Other_Bad)
-
-df.C1.V.RT.sum.noTask <- summarySE(df.C1.V.RT.subj,measurevar = 'RT',groupvars = c('Morality','Identity'))
-RT.Mean.Good.Self <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Good']
-RT.SD.Good.Self <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Good']
-RT.Mean.Bad.Self <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
-RT.SD.Bad.Self <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'self' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
-RT.Mean.Good.Other <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Good']
-RT.SD.Good.Other <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Good']
-RT.Mean.Bad.Other <- df.C1.V.RT.sum.noTask$RT[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
-RT.SD.Bad.Other <- df.C1.V.RT.sum.noTask$sd[df.C1.V.RT.sum.noTask$Identity == 'other' & df.C1.V.RT.sum.noTask$Morality == 'Bad']
-
-# plot the data without task varaible.
-RT_e7_T_noTask <- ggplot(data =df.C1.V.RT.sum.noTask,aes(y = RT, x =Morality, group = Identity,shape = Identity, fill = Identity))+
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Reaction times') +
-        #ylab(" Reaction times") + 
-        #ylim(1, 4) +
-        ggtitle("Reaction times for each condition") +
-        coord_cartesian(ylim=c(500,800)) +
-        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        #theme_classic()
-        apatheme +
-        theme(axis.text = element_text (size = 24)) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Self       ","Other")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-
-ggsave("RT_e7_T_noTask.pdf", RT_e7_T_noTask, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
-
-```
-2 by 2 ANOVA:
-The main effect of `r e7_T.RT_anova_noTask[[1]][1,1]`, *F*(`r e7_T.RT_anova_noTask[[1]][1,2]`, `r e7_T.RT_anova_noTask[[1]][1,3]`) = `r round(e7_T.RT_anova_noTask[[1]][1,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][1,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][1,7],4)`.
-
-The main effect of `r e7_T.RT_anova_noTask[[1]][2,1]`: *F*(`r e7_T.RT_anova_noTask[[1]][2,2]`, `r e7_T.RT_anova_noTask[[1]][2,3]`) = `r round(e7_T.RT_anova_noTask[[1]][2,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][2,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][2,7],4)`
-
-The interaction `r e7_T.RT_anova_noTask[[1]][3,1]`: *F*(`r e7_T.RT_anova_noTask[[1]][3,2]`, `r e7_T.RT_anova_noTask[[1]][3,3]`) = `r round(e7_T.RT_anova_noTask[[1]][3,4],3)`, *p* = `r round(e7_T.RT_anova_noTask[[1]][3,5],4)`, $\eta_g^2$ = `r round(e7_T.RT_anova_noTask[[1]][3,7],4)`.
-
-As for the self condition, effect of moral valence was significant: t(`r e7_T.RT.df.good_bad_slf`) = `r e7_T.RT.tvalue.good_bad_slf`, p = `r e7_T.RT.pvalue.good_bad_slf.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_slf`, 95% CI[`r e7_T.RT.CI.L.good_bad_slf` `r e7_T.RT.CI.H.good_bad_slf`].
-For other condition, moral valence was not significante: t(`r e7_T.RT.df.good_bad_oth`) = `r e7_T.RT.tvalue.good_bad_oth`, p = `r e7_T.RT.pvalue.good_bad_oth.adj`, Cohen's d = `r e7_T.RT.cohens.good_bad_oth`, 95% CI[`r e7_T.RT.CI.L.good_bad_oth` `r e7_T.RT.CI.H.good_bad_oth`].
-
-The effect of identity:
-for moral condition, the difference between self and other was significant:t(`r e7_T.RT.df.slf_oth_good`) = `r e7_T.RT.tvalue.slf_oth_good`, p = `r e7_T.RT.pvalue.slf_oth_good.adj`, Cohen's d = `r e7_T.RT.cohens.slf_oth_good`, 95% CI[`r e7_T.RT.CI.L.slf_oth_good` `r e7_T.RT.CI.H.slf_oth_good`].
-for Bad condition, the difference between self and other was not significant:t(`r e7_T.RT.df.slf_oth_bad`) = `r e7_T.RT.tvalue.slf_oth_bad`, p = `r e7_T.RT.pvalue.slf_oth_bad.adj`, Cohen's d = `r e7_T.RT.cohens.slf_oth_bad`, 95% CI[`r e7_T.RT.CI.L.slf_oth_bad` `r e7_T.RT.CI.H.slf_oth_bad`].
-
-Good self: `r RT.Mean.Good.Self` + `r RT.SD.Good.Self`
-Bad self:`r RT.Mean.Bad.Self` + `r RT.SD.Bad.Self`
-Good other: `r RT.Mean.Good.Other` + `r RT.SD.Good.Other`
-Bad other: `r RT.Mean.Bad.Other` + `r RT.SD.Bad.Other`
-
-```{r plot2 the RT_e7_T, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
-ggplot(data = df.C1.V.RT.grand,aes(y = RT, x = Morality, group = Task,shape = Task, fill = Task)) +
-        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
-        geom_errorbar(aes(ymin = RT - se, ymax = RT + se),
-        #geom_errorbar(aes(ymin = 1, ymax = 4),
-                      size = 1,
-                      width = .2,
-                      position=position_dodge(.6)) +
-        labs(x = 'Moral valence',y = 'Reaction times') +
-        ggtitle("Reaction times for each condition") +
-        coord_cartesian(ylim=c(500,800)) +
-        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
-        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
-        facet_grid(.~ Identity) + 
-        apatheme +
-        theme(axis.text = element_text (size = 24, color = 'black')) + 
-        theme(axis.title = element_text (size = 24)) + 
-        theme(plot.title = element_text(size = 24)) +
-        theme(legend.text = element_text(size =24)) +
-        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
-        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
-        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Id_task  ","Moral_task")) +
-        theme(strip.text.x = element_text(size = 24, colour = "black", angle = 0),panel.margin.x = unit(4, "lines")) +
-        theme(axis.line.x = element_line(color="black", size = 1),
-        axis.line.y = element_line(color="black", size = 1))
-```
-
-The above is the RT for each condition. left panel is the results of moral-categorization task, the right panel is the self-other categorization task.
-
-####Correlation analysis:
-
-The correlation between ACC of match trials in match task and ACC of categorization task
-```{r correlattion between learning and testing_ACC,echo=FALSE,warning=FALSE,message=FALSE }
-# matching task -- d prime
-#ncol(df.M1.V.SDT_ww)
-# matching task -- ACC
-#ncol(df.M1.V.acc_w)
-# matching task -- rt
-#ncol(df.M1.V.RT.subj_w)
-# categorization task -- ACC
-#ncol(df.C1.V.acc.subj_w)
-# categorization task -- rt
-#ncol(df.C1.V.RT.subj_w)
-
-## correlation analysis for ACC
-df.corr.acc <- merge(df.M1.V.acc_w[,1:5],df.C1.V.acc.subj_w[,1:9],by = 'Subject')
-df.corr.acc <- df.corr.acc[,2:13]
-acc.corr <- corr.test(df.corr.acc, use = "pairwise", method = "pearson",adjust = "holm")
-
-postscript("corr_acc_original_p_05.eps", width = 2048, height = 2048)
-# ,main = "acc_original"
-corrplot.mixed(acc.corr[[1]],p.mat = acc.corr[[4]],sig.level = 0.05,insig = "blank")
-dev.off()
-corrplot.mixed(acc.corr[[1]],p.mat = acc.corr[[4]],sig.level = 0.05,insig = "blank")
-```
-
-The correlation between the self-bias and moral bias of ACC of match trials in match task and ACC of categorization task
-```{r correlattion between learning and testing_ACC-bias,echo=FALSE,warning=FALSE,message=FALSE }
-#df.M1.V.acc_w <- read.csv("data_matching_v_acc.csv",header = TRUE, sep = ",")
-#df.C1.V.acc.subj_w <- read.csv("data_catigorization_v_acc.csv",header = TRUE,sep = ",")
-
-df.corr.bias_acc <- merge(df.M1.V.acc_w[,c(1,10:13)],df.C1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
-write.csv(df.corr.bias_acc,"df.corr.bias_acc.csv",row.names = F)
-df.corr.bias_acc <- df.corr.bias_acc[,2:13]
-acc_bias.corr <- corr.test(df.corr.bias_acc,use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE)
-postscript("corr_acc_bias_p_05.eps", width = 2048, height = 1024)
-#:main = "corr coefficient (matching-categorization) - ACC_bias"
-corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
-dev.off()
-corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
-```
-
-The correlation between RT of match trials in match task and ACC of categorization task
-```{r correlattion between learning and testing_RT,echo=FALSE,warning=FALSE,message=FALSE }
-# correlaton analysis for rt
-df.corr.rt <- merge(df.M1.V.RT.subj_w[,1:5],df.C1.V.RT.subj_w[,1:9],by = 'Subject')
-df.corr.rt <- df.corr.rt[,2:13]
-rt.corr <- corr.test(df.corr.rt)
-postscript("corr_rt_original_p_05.eps", width = 2048, height = 2048)
-# ,main = "acc_original"
-corrplot.mixed(rt.corr[[1]],p.mat = rt.corr[[4]],sig.level = 0.05,insig = "blank")
-dev.off()
-corrplot.mixed(rt.corr[[1]],p.mat = rt.corr[[4]],sig.level = 0.05,insig = "blank")
-```
-
-The correlation between the self-bias and moral bias of RT of match trials in match task and ACC of categorization task
-```{r correlattion between learning and testing_RT-bias,echo=FALSE,warning=FALSE,message=FALSE }
-# merge the data by subj ID
-df.corr.bias_rt <- merge(df.M1.V.RT.subj_w[,c(1,10:13)],df.C1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
-write.csv(df.corr.bias_rt,"df.corr.bias_rt.csv",row.names = F)
-df.corr.bias_rt <- df.corr.bias_rt[,2:13]
-rt_bias.corr <- corr.test(df.corr.bias_rt)
-
-postscript("corr_rt_bias_p_05.eps", width = 2048, height = 1024)
-#:main = "corr coefficient (matching-categorization) - ACC_bias"
-corrplot.mixed(rt_bias.corr[[1]],p.mat = rt_bias.corr[[4]],sig.level = 0.05,insig = "blank")
-dev.off()
-corrplot.mixed(rt_bias.corr[[1]],p.mat = rt_bias.corr[[4]],sig.level = 0.05,insig = "blank")
-```
-
-the effect of self on ACC
-The correlation of accuracy between matching task and categrization based on morality criteria
-```{r corr ACC_selfBias_between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
-acc.self_bias_moral <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Valence_slf_oth_good)
-df.acc.self_bias_moral <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Valence_slf_oth_good")]
-colnames(df.acc.self_bias_moral) <- c("ACC_self_bias_match","ACC_self_bias_moral_categorization")
-ggplot(df.acc.self_bias_moral, aes(x=ACC_self_bias_match, y=ACC_self_bias_moral_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm) +   
-    ggtitle("Correlation between ACC of Matching and moral categorization (self-effect)") +
-    apatheme
-#ggsave("p_corr_acc_self1.eps", p_corr_acc_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_acc_self1.pdf",out.type="cairo", width=8, height=6)
-```
-
-The correlation of accuracy between matching task and categrization based on identity criteria
-```{r corr ACC_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
-acc.self_bias_id <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Id_slf_oth_good)
-df.acc.self_bias_id <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Id_slf_oth_good")]
-colnames(df.acc.self_bias_id) <- c("ACC_self_bias_match","ACC_self_bias_id_categorization")
-ggplot(df.acc.self_bias_id, aes(x=ACC_self_bias_match, y=ACC_self_bias_id_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm) +   
-    ggtitle("Correlation between ACC of Matching and id categorization (self-effect)") +
-    apatheme
-#ggsave("p_corr_acc_self2.eps", p_corr_acc_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_acc_self2.pdf",out.type="cairo", width=8, height=6)
-```
-
-The effect of morality 
-The correlation of accuracy between matching task and categrization based on morality criteria
-```{r corr ACC_valBais between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
-acc.moral_bias_moral <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Valence_good_bad_slf)
-df.acc.moral_bias_moral <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Valence_good_bad_slf")]
-colnames(df.acc.moral_bias_moral) <- c("ACC_moral_bias_match","ACC_moral_bias_moral_categorization")
-ggplot(df.acc.moral_bias_moral, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_moral_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm,fill = "gray") +   
-    ggtitle("Correlation between ACC of Matching and moral categorization (moral effect)") +
-    apatheme
-#ggsave("p_corr_acc_moral1.eps", p_corr_acc_moral1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_acc_moral1.pdf",out.type="cairo", width=8, height=6)
-```
-
-The correlation of accuracy between matching task and categrization based on identity criteria
-```{r corr ACC_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
-acc.moral_bias_id <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Id_good_bad_slf)
-df.acc.moral_bias_id <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Id_good_bad_slf")]
-colnames(df.acc.moral_bias_id) <- c("ACC_moral_bias_match","ACC_moral_bias_id_categorization")
-ggplot(df.acc.moral_bias_id, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_id_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm,fill = "gray") +   
-    ggtitle("Correlation between ACC of Matching and id categorization (moral effect)") +
-    apatheme
-# ggsave("p_corr_acc_moral2.eps", p_corr_acc_moral2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_acc_moral2.pdf",out.type="cairo", width=8, height=6)
-```
-
-```{r corr RT_selfBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
-rt.self_bias_moral <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Valence_slf_oth_good)
-df.rt.self_bias_moral <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Valence_slf_oth_good")]
-colnames(df.rt.self_bias_moral) <- c("RT_self_bias_match","RT_self_bias_moral_categorization")
-ggplot(df.rt.self_bias_moral, aes(x=RT_self_bias_match, y=RT_self_bias_moral_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm) +   
-    ggtitle("Correlation between RT of Matching and moral categorization (self-effect)") +
-    apatheme
-#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_RT_self1.pdf",out.type="cairo", width=8, height=6)
-```
-
-```{r corr RT_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
-rt.self_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Id_slf_oth_good)
-df.rt.self_bias_id <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Id_slf_oth_good")]
-colnames(df.rt.self_bias_id) <- c("RT_self_bias_match","RT_self_bias_id_categorization")
-ggplot(df.rt.self_bias_id, aes(x=RT_self_bias_match, y=RT_self_bias_id_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm,fill = "gray") +   
-    ggtitle("Correlation between RT of Matching and id categorization (self-effect)") +
-    apatheme
-#ggsave("p_corr_RT_self2.eps", p_corr_RT_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_RT_self2.pdf",out.type="cairo", width=8, height=6)
-
-```
-
-```{r corr RT_valBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
-rt.moral_bias_val <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Valence_good_bad_slf)
-df.rt.moral_bias_moral <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Valence_good_bad_slf")]
-colnames(df.rt.moral_bias_moral) <- c("RT_moral_bias_match","RT_moral_bias_moral_categorization")
-ggplot(df.rt.moral_bias_moral, aes(x=RT_moral_bias_match, y=RT_moral_bias_moral_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm) +   
-    ggtitle("Correlation between RT of Matching and moral categorization (moral-effect)") +
-    apatheme
-#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_RT_moral1.pdf",out.type="cairo", width=8, height=6)
-```
-
-```{r corr RT_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
-rt.moral_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Id_good_bad_slf)
-df.rt.moral_bias_id <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Id_good_bad_slf")]
-colnames(df.rt.moral_bias_id) <- c("RT_moral_bias_match","RT_moral_bias_id_categorization")
-ggplot(df.rt.moral_bias_id, aes(x=RT_moral_bias_match, y=RT_moral_bias_id_categorization)) +
-    geom_point() +    # Use hollow circles
-    geom_smooth(method=lm) + 
-    ggtitle("Correlation between RT of Matching and id categorization (moral-effect)") +
-    apatheme
-#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
-dev.copy2pdf(file="p_corr_RT_moral2.pdf",out.type="cairo", width=8, height=6)
-```

### 2018-07-10 Replication/Results/data_analysis/preproc/MS_rep_prepro.rmd
revisit the results

--- 2018-07-03 Replication/Results/data_analysis/preproc/Analysis_exp7_rep_prepro.rmd
@@
 setwd(ddmDir)
-write.csv(df.M.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
-write.csv(df.M.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
-write.csv(df.C.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
-write.csv(df.C.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
+write.csv(df.M.hddm_m,'MS_rep_match_hddm.csv',row.names = F)
+write.csv(df.M.hddm_nm,'MS_rep_mismatch_hddm.csv',row.names = F)
+write.csv(df.C.hddm_val,'MS_rep_categ_val_hddm.csv',row.names = F)
+write.csv(df.C.hddm_id,'MS_rep_categ_id_hddm.csv',row.names = F)
 rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
@@
 setwd(traDir)
-write.csv(df.M1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
-write.csv(df.M1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
-write.csv(df.M1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
+write.csv(df.M1.V.sum_w,'MS_rep_match_behav_wide.csv',row.names = F)
+write.csv(df.M1.V.SDT_l,'MS_rep_match__dprime_long.csv',row.names = F)
+write.csv(df.M1.V.sum_rt_acc_l,'MS_rep_match__rt_acc_long.csv',row.names = F)
 setwd(curDir)
@@
 setwd(traDir)
-write.csv(df.C1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
-write.csv(df.C1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
-write.csv(df.C1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
-write.csv(df.v.sum_eff_all_w,'exp7_cross_taskeffect_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
+write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
+write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
 setwd(curDir)
@@
 MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
-#RTdata1 <- df.M1.V.sum_rt_acc_l %>%
-#  select(Subject,Match,Morality,Identity,RT) %>% 
-#  filter(Match == "match" & Morality == "Good")
-#RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-#p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
-#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-#  guides(fill = FALSE) +guides(color = FALSE)+
-#  theme_bw() +
-#  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
-#RTdata2 <- df.M1.V.sum_rt_acc_l %>%
-#  select(Subject,Match,Morality,Identity,RT) %>% 
-#  filter(Match == "match" & Morality == "Bad")
-#RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
-#p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
-#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
-#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
-#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
-#  guides(fill = FALSE) +guides(color = FALSE)+
-#  theme_bw() +
-#  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")
 
-#setwd(traDir)
-#tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
-#p_rt_match <- multiplot(p1,p2,cols = 2)
-#dev.off()
-#setwd(curDir)
-#multiplot(p1,p2,cols = 2)
 ```

### 2018-07-10 Results/preproc/MS_ddm_preproc.rmd
revisit the results

@@
 df.C1.V.acc_w  <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity ,value.var = "ACC")
-
 # rename the column number
@@
 # tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
-df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
-df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")
+#df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
+#df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")
 
-df.C1.V.acc.noTask_w$good_bad_slf <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Self
-df.C1.V.acc.noTask_w$good_bad_oth <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Other
-df.C1.V.acc.noTask_w$slf_oth_good <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Good_Other
-df.C1.V.acc.noTask_w$slf_oth_bad <- df.C1.V.acc.noTask_w$Bad_Self - df.C1.V.acc.noTask_w$Bad_Other
+df.C1.V.acc_noTask_w$good_bad_slf <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Self
+df.C1.V.acc_noTask_w$good_bad_oth <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other
+df.C1.V.acc_noTask_w$slf_oth_good <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Good_Other
+df.C1.V.acc_noTask_w$slf_oth_bad <- df.C1.V.acc_noTask_w$ACC_Bad_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other
 
@@
 
+# merge the RT and ACC data without task (long-format) ####
+df.C1.V.sum_rt_acc_noTask_l <- merge(df.C1.V.acc_noTask,df.C1.V.RT.subj_noTask,by = c("Subject","Morality",'Identity'))
+df.C1.V.sum_rt_acc_noTask_l <- df.C1.V.sum_rt_acc_noTask_l[order(df.C1.V.sum_rt_acc_noTask_l$Subject),]
+
+df.C1.V.sum_rt_acc_noTask_l <- df.C1.V.sum_rt_acc_noTask_l[,c("Subject","Morality",'Identity',"N.x","countN","ACC","RT")]
+colnames(df.C1.V.sum_rt_acc_noTask_l) <- c("Subject","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")
+
 # write files to an upper-lelel folder
@@
 write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
+write.csv(df.C1.V.sum_rt_acc_noTask_l,'MS_categ__rt_acc_noTask_long.csv',row.names = F)
 write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
@@
 ```
+
+```{r plot_noTask_data,echo=FALSE,warning=FALSE, message=FALSE}
+# plot ACC
+MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
+# plot RT
+MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
+```

### 2018-07-10 Replication/Results/data_analysis/preproc/Initial.r

@@ -242,16 +242,23 @@ MSplots <- function(saveDir = traDir, curDir = curDir, task = 'match',type = 'AC
       ACCdata1 <- inData %>%
         select(Subject,Task,Morality,Identity,ACC) %>% 
         filter(Task == "Val"& Morality == 'Good')
-      ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
+      ACCdata2 <- inData %>%
         select(Subject,Task,Morality,Identity,ACC) %>% 
         filter(Task == "Val"& Morality == 'Bad')
-    } else{
+    } else if (task == 'id'){
       ACCdata1 <- inData %>%
         select(Subject,Task,Morality,Identity,ACC) %>% 
         filter(Task == "Id"& Morality == 'Good')
-      ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
+      ACCdata2 <- inData %>%
         select(Subject,Task,Morality,Identity,ACC) %>% 
         filter(Task == "Id"& Morality == 'Bad')
+    }else{
+      ACCdata1 <- inData %>%
+        select(Subject,Morality,Identity,ACC) %>% 
+        filter(Morality == 'Good')
+      ACCdata2 <- inData %>%
+        select(Subject,Morality,Identity,ACC) %>% 
+        filter(Morality == 'Bad')
     }
 
     ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
@@ -304,19 +311,26 @@ MSplots <- function(saveDir = traDir, curDir = curDir, task = 'match',type = 'AC
         select(Subject,Match,Morality,Identity,RT) %>% 
         filter(Match == "match" & Morality == "Bad")
     }else if(task == 'val'){
-      RTdata1 <- df.C1.V.sum_rt_acc_l %>%
+      RTdata1 <- inData %>%
         select(Subject,Task,Morality,Identity,RT) %>% 
         filter(Task == "Val"& Morality == 'Good')
-      RTdata2 <- df.C1.V.sum_rt_acc_l %>%
+      RTdata2 <- inData %>%
         select(Subject,Task,Morality,Identity,RT) %>% 
         filter(Task == "Val"& Morality == 'Bad')
-    }else{
-      RTdata1 <- df.C1.V.sum_rt_acc_l %>%
+    }else if (task == 'id'){
+      RTdata1 <- inData %>%
         select(Subject,Task,Morality,Identity,RT) %>% 
[…]

### 2018-07-10 Replication/Results/data_analysis/tradAnal/cross-task analysis.R
change file names

@@ -1,96 +1,0 @@
-library(tidyverse)
-setwd("C:\\Users\\Lanronics\\Desktop\\moral\\exp7r")
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-  
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-  
-  numPlots = length(plots)
-  
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                     ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-  
-  if (numPlots==1) {
-    print(plots[[1]])
-    
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-    
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-      
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-
-# read data
-M_ACC_data <- read_csv("exp7_rep_match__dprime_long.csv") %>%
-  select(Subject,Morality,Identity,dprime) %>%
-  unite(Type,Morality,Identity) %>%
-  spread(key = Type, value = dprime) %>%
-  mutate("self-referential" = Good_Self - Good_Other, "valence" = Good_Self - Bad_Self)
-M_RT_data<- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
-  filter(Match == "match") %>%
-  select(Subject,Morality,Identity,RT) %>%
-  unite(Type,Morality,Identity) %>%
-  spread(key = Type, value = RT) %>%
-  mutate("self-referential" = Good_Self - Good_Other, "valence" = Good_Self - Bad_Self)
[…]

### 2018-07-10 Replication/Results/data_analysis/tradAnal/match_rt_violin.R

@@ -1,77 +1,0 @@
-# to plot the RT from matched trials
-# by Yuxuan Lan
-# 2018.06.09
-
-library(tidyverse)
-library(ggstatsplot)
-setwd("D:\\HCP_cloud\\Exps\\P1_Pos_Self\\Exp_Behav_Moral_Asso\\Exp_7_model_categ\\Replication\\Results\\data_analysis\\tradAnal")
-multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
-  library(grid)
-  
-  # Make a list from the ... arguments and plotlist
-  plots <- c(list(...), plotlist)
-  
-  numPlots = length(plots)
-  
-  # If layout is NULL, then use 'cols' to determine layout
-  if (is.null(layout)) {
-    # Make the panel
-    # ncol: Number of columns of plots
-    # nrow: Number of rows needed, calculated from # of cols
-    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
-                     ncol = cols, nrow = ceiling(numPlots/cols))
-  }
-  
-  if (numPlots==1) {
-    print(plots[[1]])
-    
-  } else {
-    # Set up the page
-    grid.newpage()
-    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
-    
-    # Make each plot, in the correct location
-    for (i in 1:numPlots) {
-      # Get the i,j matrix positions of the regions that contain this subplot
-      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
-      
-      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
-                                      layout.pos.col = matchidx$col))
-    }
-  }
-}
-RTdata1 <- read_csv("exp7_rep_match__rt_acc_long.csv") %>%
-  select(Subject,Match,Morality,Identity,RT) %>% 
-  filter(Match == "match" & Morality == "Good")
-RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
-p1 <- ggbetweenstats(data = RTdata1, 
-                     x = Identity, 
-                     y = RT,  
-                     xlab = "Good", 
-                     ylab = "Reaction times(ms)",
-                     type = FALSE) + theme_classic() + theme(legend.position = "none",
-                                                             axis.line.x=element_line(size=1.2),
-                                                             axis.line.y=element_line(size=1.2),
-                                                             axis.title.x =element_text(size=14), 
[…]

### 2018-07-10 Results/preproc/MS_ddm_preproc.rmd
revise the cross-task analysis of study 1

@@
 df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
-df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
-df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w$d_Good_selfEffect <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
+df.M1.v.sum_eff_w$d_Self_valEffect   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
 
-df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
-df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_Good_selfEffect <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_Self_valEffect   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
 
@@
 
-# combine data cross task
-# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
-#df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
-#df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")
-
+# calculate the mean differences(?)
 df.C1.V.acc_noTask_w$good_bad_slf <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Self
@@
 
-df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
-df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
-df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
-df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self
+df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Good_Other
+df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Bad_Self
+df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Good_Other
+df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Bad_Self
 

### 2018-07-15 Results/preproc/MS_ddm_preproc.rmd
update ex-Gaussian analysis

@@
 ddmDir <- paste(rootDir,'HDDM',sep = '')
+exgDir <- paste(rootDir,'exGaussian',sep = '')
 ```
@@
 rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
+
+# get the data for exGaussian analysis
+df.C.exG <- df.C.valid
+df.C.exG <- subset(df.C.exG, ACC == 1 & RT > .2)
+setwd(exgDir)
+write.csv(df.C.exG,'MS_categ_exG.csv',row.names = F)
+rm(df.C.exG)
+
 ```

### 2018-07-15 Results/exGaussian/Ex_Gaussian_analysis_formal.R

@@ -6,237 +6,43 @@
 #  hcp     19/07/2016        only the code for final analysis
 #  hcp     20/02/2017        used for the final data
 #  hcp     08/04/2017        save to pdf
+#  hcp     15/07/2018        update to latest format and data
 
 #### This part of the code is preparation ####
-# defube the the system parameters 
-Sys.setenv(LANG = "en")              # set the feedback language to English
-options(scipen = 999)                # force R to output in decimal instead of scientifc notion
-windowsFonts(Times=windowsFont("TT Times New Roman"))  # explicit mapping to "times"
-
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
-# define the d prime function
-dprime <- function(hit,fa) {
-        qnorm(hit) - qnorm(fa)
-}
-# define fuctions: summarySE, summarySEwithin, normDatawithin, and multiplot.
-## code for calculate the summary with sE, adopted from cook book for R
-summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
-                      conf.interval=.95, .drop=TRUE) {
-        library(plyr)
-        
-        # New version of length which can handle NA's : if na.rm == T, don't count the
-        length2 <- function(x, na.rm=FALSE){
-                if(na.rm) sum(!is.na(x))
-                else      length(x)
-        }
-        
-        # this does the summary. For each group's data frame, return a vector with
-        # N, mean, and sd
-        datac <- ddply(data,groupvars, .drop=.drop,
-                       .fun = function(xx,col){
-                               c(N    = length2(xx[[col]],na.rm=na.rm),
-                                 mean = mean(xx[[col]],na.rm=na.rm),
-                                 sd   = sd  (xx[[col]],na.rm=na.rm)
-                               )
-                       },
-                       measurevar
-        )
-        # Rename the "mean" column
-        
-        datac <- rename(datac,c("mean" = measurevar))
-        
-        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean
-        
-        # Confidence interval mltiplier for standard error
-        # calculate t-statistic for confidence interval:
-        # e.g., if conf.interval is .95, use .975 (above/below), and use df.L1 = N-1
-        ciMult <- qt(conf.interval/2 + .5, datac$N-1)
-        datac$ci <- datac$se * ciMult
-        
-        return (datac)
-}
-
[…]

### 2018-07-15 Results/exGaussian/trans_Data.r

@@ -1,0 +1,93 @@
+# this script is used for transfer raw data to usable and sharable data
+
+# initializing
+source('Initial.r')
+
+# set directory
+curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
+rootDir <- gsub('.{7}$', '', curDir)
+rawDir  <- paste(curDir,'/rawData/',sep = '')
+traDir  <- paste(rootDir,'Traditional_Analysis',sep = '')
+ddmDir  <- paste(rootDir,'HDDM',sep = '')
+
+setwd(rawDir)
+file_list.match <- list.files(path = ".", pattern = "*_learn*")
+file_list.categ <- list.files(path = ".", pattern = "*_test*")
+
+# merge the data from each participant
+for (fileL in file_list.match){
+  # if the merged dataset doesn't exist, creat it
+  if (!exists("df.M")){
+    df.M <- read.csv(fileL,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+  }
+  
+  # if the merged dataset does exist, append to it
+  if (exists("df.M")){
+    temp_df.L <- read.csv(fileL,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+    df.M <- rbind(df.M,temp_df.L)
+    rm(temp_df.L)
+  }
+}
+df.M <- subset(df.M,SubjectID != "SubjectID")  # there should be 18672 obs. of 19 variables.
+# write.csv(df.M,"df.Learn.csv", row.names=FALSE)
+
+for (fileT in file_list.categ){
+  # if the merged dataset doesn't exist, creat it
+  if (!exists("df.C")){
+    df.C <- read.csv(fileT,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+  }
+  
+  # if the merged dataset does exist, append to it
+  if (exists("df.C")){
+    temp_df.T <- read.csv(fileT,header = TRUE, sep = ' ', stringsAsFactors=FALSE)
+    df.C <- rbind(df.C,temp_df.T)
+    rm(temp_df.T)
+  }
+}
+df.C <- subset(df.C,SubjectID != "SubjectID")   # there should be 29808 obs. of 19 variables
+# write.csv(df.C,"df.Test.csv", row.names=FALSE)  # save the data
+
+setwd(curDir)
+# render the data in numeric format for future analysis
[…]

### 2018-07-17 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
change folder name

--- 2018-07-10 Replication/Results/data_analysis/preproc/MS_rep_prepro.rmd
@@
 write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
-write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
+write.csv(df.v.sum_eff_all_w,'MS_rep_cross_taskeffect_wide.csv',row.names = F)
 setwd(curDir)

### 2018-09-24 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
add more cross-task correlation

@@
 df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
-df.M1.v.sum_eff_w$d_Good_Self_Other <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
-df.M1.v.sum_eff_w$d_Self_Good_Bad   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w$d_goodslf_goodoth <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
+df.M1.v.sum_eff_w$d_goodslf_badslf   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w$d_goodoth_badoth   <- df.M1.V.sum_w$d_Good_Other - df.M1.V.sum_w$d_Bad_Other
+df.M1.v.sum_eff_w$d_badslf_badoth   <- df.M1.V.sum_w$d_Bad_Self - df.M1.V.sum_w$d_Bad_Other
 
-df.M1.v.sum_eff_w$RT_Good_Self_Other <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
-df.M1.v.sum_eff_w$RT_Self_Good_Bad   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodslf_goodoth <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodslf_badslf  <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodoth_badoth <- df.M1.V.sum_w$RT_match_Bad_Other -  df.M1.V.sum_w$RT_match_Good_Other
+df.M1.v.sum_eff_w$RT_badslf_badoth  <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Bad_Other
 
@@
 colnames(df.C1.v.sum_eff_w) <- 'Subject'
-df.C1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
-df.C1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
-df.C1.v.sum_eff_w$RT_Id_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
-df.C1.v.sum_eff_w$RT_Id_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodslf_goodoth <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodslf_badslf  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Val_Bad_Other - df.C1.V.sum_w$RT_Val_Good_Other
+df.C1.v.sum_eff_w$Val_RT_badslf_badoth <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Bad_Other
 
-df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Good_Self
-df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Good_Self
-df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Good_Self
-df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other
+df.C1.v.sum_eff_w$Id_RT_badslf_badoth <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Bad_Other
+
+df.C1.v.sum_eff_w$Val_ACC_goodslf_goodoth <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Good_Other
+df.C1.v.sum_eff_w$Val_ACC_goodslf_badslf <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Bad_Self
+df.C1.v.sum_eff_w$Val_ACC_goodoth_badoth <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Bad_Other
+df.C1.v.sum_eff_w$Val_ACC_badslf_badoth <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Bad_Other
+
+df.C1.v.sum_eff_w$Id_ACC_goodslf_goodoth  <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Good_Other
+df.C1.v.sum_eff_w$Id_ACC_goodslf_badslf   <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Bad_Self
+df.C1.v.sum_eff_w$Id_ACC_goodoth_badoth <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Bad_Other
+df.C1.v.sum_eff_w$Id_ACC_badslf_badoth <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Bad_Other
 

### 2018-09-24 Results/preproc/MS_ddm_preproc.rmd
add more cross-task correlation

@@
 df.M1.v.sum_eff_w <- df.M1.V.sum_w[,1:3]
-df.M1.v.sum_eff_w$d_Good_selfEffect <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
-df.M1.v.sum_eff_w$d_Self_valEffect   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w$d_goodslf_goodoth <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Good_Other
+df.M1.v.sum_eff_w$d_goodslf_badslf   <- df.M1.V.sum_w$d_Good_Self - df.M1.V.sum_w$d_Bad_Self
+df.M1.v.sum_eff_w$d_goodoth_badoth   <- df.M1.V.sum_w$d_Good_Other - df.M1.V.sum_w$d_Bad_Other
+df.M1.v.sum_eff_w$d_badslf_badoth   <- df.M1.V.sum_w$d_Bad_Self - df.M1.V.sum_w$d_Bad_Other
 
-df.M1.v.sum_eff_w$RT_Good_selfEffect <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
-df.M1.v.sum_eff_w$RT_Self_valEffect   <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodslf_goodoth <- df.M1.V.sum_w$RT_match_Good_Other -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodslf_badslf  <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Good_Self
+df.M1.v.sum_eff_w$RT_goodoth_badoth <- df.M1.V.sum_w$RT_match_Bad_Other -  df.M1.V.sum_w$RT_match_Good_Other
+df.M1.v.sum_eff_w$RT_badslf_badoth  <- df.M1.V.sum_w$RT_match_Bad_Self -  df.M1.V.sum_w$RT_match_Bad_Other
 
@@
 colnames(df.C1.v.sum_eff_w) <- 'Subject'
-df.C1.v.sum_eff_w$RT_Val_Good_selfEffect <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
-df.C1.v.sum_eff_w$RT_Val_Self_valEffect  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
-df.C1.v.sum_eff_w$RT_Id_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
-df.C1.v.sum_eff_w$RT_Id_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodslf_goodoth <- df.C1.V.sum_w$RT_Val_Good_Other - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodslf_badslf  <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Good_Self
+df.C1.v.sum_eff_w$Val_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Val_Bad_Other - df.C1.V.sum_w$RT_Val_Good_Other
+df.C1.v.sum_eff_w$Val_RT_badslf_badoth <- df.C1.V.sum_w$RT_Val_Bad_Self - df.C1.V.sum_w$RT_Val_Bad_Other
 
-df.C1.v.sum_eff_w$ACC_Val_Good_selfEffect <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Good_Other
-df.C1.v.sum_eff_w$ACC_Val_Self_valEffect  <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Bad_Self
-df.C1.v.sum_eff_w$ACC_Id_Good_selfEffect  <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Good_Other
-df.C1.v.sum_eff_w$ACC_Id_Self_valEffect   <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Bad_Self
+df.C1.v.sum_eff_w$Id_RT_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other
+df.C1.v.sum_eff_w$Id_RT_badslf_badoth <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Bad_Other
+
+df.C1.v.sum_eff_w$Val_ACC_goodslf_goodoth <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Good_Other
+df.C1.v.sum_eff_w$Val_ACC_goodslf_badslf <- df.C1.V.sum_w$ACC_Val_Good_Self - df.C1.V.sum_w$ACC_Val_Bad_Self
+df.C1.v.sum_eff_w$Val_ACC_goodoth_badoth <- df.C1.V.sum_w$ACC_Val_Good_Other - df.C1.V.sum_w$ACC_Val_Bad_Other
+df.C1.v.sum_eff_w$Val_ACC_badslf_badoth <- df.C1.V.sum_w$ACC_Val_Bad_Self - df.C1.V.sum_w$ACC_Val_Bad_Other
+
+df.C1.v.sum_eff_w$Id_ACC_goodslf_goodoth  <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Good_Other
+df.C1.v.sum_eff_w$Id_ACC_goodslf_badslf   <- df.C1.V.sum_w$ACC_Id_Good_Self - df.C1.V.sum_w$ACC_Id_Bad_Self
+df.C1.v.sum_eff_w$Id_ACC_goodoth_badoth <- df.C1.V.sum_w$ACC_Id_Good_Other - df.C1.V.sum_w$ACC_Id_Bad_Other
+df.C1.v.sum_eff_w$Id_ACC_badslf_badoth <- df.C1.V.sum_w$ACC_Id_Bad_Self - df.C1.V.sum_w$ACC_Id_Bad_Other
 

### 2018-09-25 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
correct two variable names

@@
 
-df.C1.v.sum_eff_w$Id_RT_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
-df.C1.v.sum_eff_w$Id_RT_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_goodslf_goodoth  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
+df.C1.v.sum_eff_w$Id_RT_goodslf_badslf   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
 df.C1.v.sum_eff_w$Id_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other

### 2018-10-01 Results/preproc/MS_ddm_preproc.rmd
add questionnaire data

@@
 
-# write files to an upper-lelel folder
+# write files to an upper-level folder
 setwd(traDir)
@@
 write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
+setwd(curDir)
+```
+
+```{r preproc questionnair,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+# load the data
+df.quest <- read.csv("exp7_survey_monkey_raw_c.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
+
+# calculate the reliability of each questionnair
+# get the name and key for each scale
+slfEsteemNames <- c( "slfEsteem_1", "slfEsteem_2", "slfEsteem_3", "slfEsteem_4", "slfEsteem_5",
+                     "slfEsteem_6", "slfEsteem_7", "slfEsteem_8", "slfEsteem_9", "slfEsteem_10")
+slfEsteemKeys  <- c(1,2,-3,4,-5,6,7,-8,-9,-10)        # for current dataset
+slfEsteemKeys2 <- c( "slfEsteem_1", "slfEsteem_2", "-slfEsteem_3", "slfEsteem_4", "-slfEsteem_5",
+                     "slfEsteem_6", "slfEsteem_7", "-slfEsteem_8", "-slfEsteem_9", "-slfEsteem_10")
+slfEsteemAlpha <- psych::alpha(df.quest[,slfEsteemNames],keys = slfEsteemKeys) # alpha
+print(slfEsteemAlpha$total[2])
+slfEsteemOmega <- psych::omega(df.quest[,slfEsteemNames]) # omega
+print(c(slfEsteemOmega$omega_h,slfEsteemOmega$omega.tot))
+
+# calculate the score for the trait self-esteem
+slfEsteemScore <- psych::scoreItems(slfEsteemKeys2,df.quest[,slfEsteemNames], totals = F, min = 1, max = 4)
+df.quest$slfEsteem <- slfEsteemScore$scores
+
+# calculate for moral identity
+moralIdNames <- c("MoralId_1","MoralId_2","MoralId_3","MoralId_4","MoralId_5","MoralId_6",
+                  "MoralId_7","MoralId_8","MoralId_9","MoralId_10","MoralId_11","MoralId_12",
+                  "MoralId_13","MoralId_14","MoralId_15")
+moralIdKeys <- c(1,2,3,4,-5,6,7,8,9,10,11,12,13,14,15)
+
+moralIdAlpha <- psych::alpha(df.quest[,moralIdNames],keys = moralIdKeys) # alpha
+print(moralIdAlpha$total[2])
+moralIdOmega <- psych::omega(df.quest[,moralIdNames]) # omega
+print(c(moralIdOmega$omega_h,moralIdOmega$omega.tot))
+
+moralIdinNames <- c("MoralId_1","MoralId_2","MoralId_5","MoralId_8","MoralId_10",
+                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
+moralIdinKeys <- c(1,2,-3,4,5,6,7,8,9)
+moralIdinKeys2 <- c("MoralId_1","MoralId_2","-MoralId_5","MoralId_8","MoralId_10",
+                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
+moralIdinAlpha <- psych::alpha(df.quest[,moralIdinNames],keys = moralIdinKeys) # alpha
+print(moralIdinAlpha$total[2])
+moralIdinOmega <- psych::omega(df.quest[,moralIdinNames]) # omega
+print(c(moralIdinOmega$omega_h,moralIdinOmega$omega.tot))
+
+# caculate the score for internal moral identity
+moralIdinScore <- psych::scoreItems(moralIdinKeys2,df.quest[,moralIdinNames], totals = F, min = -2, max = 2)
+df.quest$moralIdinScore <- moralIdinScore$scores
+
+moralIdexNames <- c("MoralId_3","MoralId_4","MoralId_6",
+                  "MoralId_7","MoralId_9","MoralId_15")
+moralIdexKeys <- c(1,2,3,4,5,6)
+moralIdexAlpha <- psych::alpha(df.quest[,moralIdexNames],keys = moralIdexKeys) # alpha
+print(moralIdexAlpha$total[2])
+moralIdexOmega <- psych::omega(df.quest[,moralIdexNames]) # omega
+print(c(moralIdexOmega$omega_h,moralIdexOmega$omega.tot))
+
+# calculate the score for external moral identity
+moralIdexScore <- psych::scoreItems(moralIdexNames,df.quest[,moralIdexNames], totals = F, min = -2, max = 2)
+df.quest$moralIdexScore <- moralIdexScore$scores
+
+# find the intersection between behavioral data and questionnarie data.
+tmp <- merge(df.v.sum_eff_all_w,df.quest[,c("subjID","slfEsteem","moralIdinScore","moralIdexScore")],by.x = "Subject",by.y = "subjID",all = TRUE)
+tmp <- tmp[complete.cases(tmp),]
+
+# write files to an upper-level folder
+setwd(traDir)
+write.csv(tmp,'MS_cross_taskeffect_wide_w_scale.csv',row.names = F)
 setwd(curDir)

### 2018-10-02 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
update scale-behavioral correlation analysis for rep-exp

@@
 ```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
-
 # clean data for trad. analysis
@@
 
+```{r preproc questionnair,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
+# load the data
+df.quest1 <- read.csv("exp7_rep_Q4.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) %>%
+      filter(session == 1)
+df.quest2 <- read.csv("exp7_rep_Q5.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) %>%
+      filter(session == 1)
+df.quest <- merge(df.quest1,df.quest2,by = "subjID")
+# calculate the reliability of each questionnair
+# get the name and key for each scale
+slfEsteemNames <- c( "slfEsteem_1", "slfEsteem_2", "slfEsteem_3", "slfEsteem_4", "slfEsteem_5",
+                     "slfEsteem_6", "slfEsteem_7", "slfEsteem_8", "slfEsteem_9", "slfEsteem_10")
+slfEsteemKeys  <- c(1,2,-3,4,-5,6,7,-8,-9,-10)        # for current dataset
+slfEsteemKeys2 <- c( "slfEsteem_1", "slfEsteem_2", "-slfEsteem_3", "slfEsteem_4", "-slfEsteem_5",
+                     "slfEsteem_6", "slfEsteem_7", "-slfEsteem_8", "-slfEsteem_9", "-slfEsteem_10")
+slfEsteemAlpha <- psych::alpha(df.quest[,slfEsteemNames],keys = slfEsteemKeys) # alpha
+print(slfEsteemAlpha$total[2]) # 0.8593
+slfEsteemOmega <- psych::omega(df.quest[,slfEsteemNames]) # omega 0.7455 0.9341
+print(c(slfEsteemOmega$omega_h,slfEsteemOmega$omega.tot))
+
+# calculate the score for the trait self-esteem
+slfEsteemScore <- psych::scoreItems(slfEsteemKeys2,df.quest[,slfEsteemNames], totals = F, min = 1, max = 4)
+df.quest$slfEsteem <- slfEsteemScore$scores
+
+# calculate for moral identity
+moralIdNames <- c("MoralId_1","MoralId_2","MoralId_3","MoralId_4","MoralId_5","MoralId_6",
+                  "MoralId_7","MoralId_8","MoralId_9","MoralId_10","MoralId_11","MoralId_12",
+                  "MoralId_13","MoralId_14","MoralId_15")
+moralIdKeys <- c(1,2,3,4,-5,6,7,8,9,10,11,12,13,14,15)
+
+moralIdAlpha <- psych::alpha(df.quest[,moralIdNames],keys = moralIdKeys) # alpha
+print(moralIdAlpha$total[2]) # 0.9178
+moralIdOmega <- psych::omega(df.quest[,moralIdNames]) # omega 0.7583 0.9454
+print(c(moralIdOmega$omega_h,moralIdOmega$omega.tot))
+
+moralIdinNames <- c("MoralId_1","MoralId_2","MoralId_5","MoralId_8","MoralId_10",
+                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
+moralIdinKeys <- c(1,2,-3,4,5,6,7,8,9)
+moralIdinKeys2 <- c("MoralId_1","MoralId_2","-MoralId_5","MoralId_8","MoralId_10",
+                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
+moralIdinAlpha <- psych::alpha(df.quest[,moralIdinNames],keys = moralIdinKeys) # alpha
+print(moralIdinAlpha$total[2]) # 0.8884
+moralIdinOmega <- psych::omega(df.quest[,moralIdinNames]) # omega 0.7115 0.939
+print(c(moralIdinOmega$omega_h,moralIdinOmega$omega.tot))
+
+# caculate the score for internal moral identity
+moralIdinScore <- psych::scoreItems(moralIdinKeys2,df.quest[,moralIdinNames], totals = F, min = -2, max = 2)
+df.quest$moralIdinScore <- moralIdinScore$scores
+
+moralIdexNames <- c("MoralId_3","MoralId_4","MoralId_6",
+                  "MoralId_7","MoralId_9","MoralId_15")
+moralIdexKeys <- c(1,2,3,4,5,6)
+moralIdexAlpha <- psych::alpha(df.quest[,moralIdexNames],keys = moralIdexKeys) # alpha
+print(moralIdexAlpha$total[2]) # 0.844
+moralIdexOmega <- psych::omega(df.quest[,moralIdexNames]) # omega 0.684 0.91
+print(c(moralIdexOmega$omega_h,moralIdexOmega$omega.tot))
+
+# calculate the score for external moral identity
+moralIdexScore <- psych::scoreItems(moralIdexNames,df.quest[,moralIdexNames], totals = F, min = -2, max = 2)
+df.quest$moralIdexScore <- moralIdexScore$scores
+
+# find the intersection between behavioral data and questionnarie data.
+tmp <- merge(df.v.sum_eff_all_w,df.quest[,c("subjID","slfEsteem","moralIdinScore","moralIdexScore")],by.x = "Subject",by.y = "subjID",all = TRUE)
+tmp <- tmp[complete.cases(tmp),]
+
+# write files to an upper-level folder
+setwd(traDir)
+write.csv(tmp,'MS_cross_taskeffect_wide_w_scale.csv',row.names = F)
+setwd(curDir)
+
+# load data from exp1
+crossf_effect_scale_1 <- read.csv("D:\\HCP_cloud\\Exps\\P1_Pos_Self\\Exp_Behav_Moral_Asso\\Exp_7_share\\Results\\Traditional_Analysis\\MS_cross_taskeffect_wide_w_scale.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
+colnames(tmp) == colnames(crossf_effect_scale_1)
+colnames(tmp)[colnames(tmp) == 'Sex'] <- 'Gender'
+tmp <- tmp[,colnames(crossf_effect_scale_1)]
+new_tmp <- rbind(crossf_effect_scale_1,tmp)
+# write files to an upper-level folder
+setwd(traDir)
+write.csv(new_tmp,'MS_effect_w_scales_all.csv',row.names = F)
+setwd(curDir)
+```
+
 ```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}

### 2018-10-02 Replication/Results/dataAnalysis/tradAnal/match_accuracy_violin.R

@@ -1,0 +1,102 @@
+library(readr)
+library(cowplot)
+library(tidyverse)
+library(ggstatsplot)
+source("R_rainclouds.R")
+#setwd("C:\\Users\\Lanronics\\Desktop\\?½??ļ???\\moral\\exp7r")
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+#y_scale <- scale_y_continuous(limits = range(ACCdata1$ACC))
+ACCdata2 <- read_csv("MS_rep_match__rt_acc_long.csv") %>%
+  select(Subject,Match,Morality,Identity,ACC) %>% 
+  filter(Match == "match" & Morality == "Bad")
+ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
+p2 <- ggbetweenstats(data = ACCdata2, 
+                     x = Identity, 
+                     y = ACC,  
+                     xlab = "Bad", 
+                     ylab = "",
+                     type = FALSE) + theme_classic() + theme(legend.position = "none",
+                                                             axis.line.x=element_line(size=1.2),
+                                                             axis.title.x =element_text(size=14),
+                                                             axis.text.x=element_text(size=12,color = "black"),
[…]

### 2018-10-03 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
updae plots

@@
 
-```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
+```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
+#MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
+Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)
 
@@
 
-```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
+```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)
 ```
-
-```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
-
-```
-
-```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
-```
-
-```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
-
-```
-
-```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
-MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
-```

### 2018-10-03 Results/preproc/MS_ddm_preproc.rmd
updae plots

@@
 ```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
-#plot the rT data from matching task
-MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
-
-# plot the dprime data from matching task
-MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
-
+Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.C1.V.sum_rt_acc_l)
 ```
 
-```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-# plot ACC
-MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
+```{r plot_categ_data,echo=FALSE,warning=FALSE, message=FALSE}
+# plot id-based data
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)
 
-# plot RT
-MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
+# plot val-based data
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)
 
-```
-
-```{r plot_categ_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
-# plot ACC
-MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
-# plot RT
-MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
 ```
@@
 # plot ACC
-MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'categ', df.C1.V.sum_rt_acc_noTask_l)
+#MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
 # plot RT
-MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
+#MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
 ```

### 2018-10-03 Replication/Results/dataAnalysis/preproc/Initial.r

@@ -38,14 +38,32 @@ apatheme = theme_bw()+
               text=element_text(family='Times'),
               legend.title=element_blank(),
               legend.text = element_text(size =16),
-              legend.position='top',
-              plot.title = element_text(size = 16),
+              #legend.position='top',
+              plot.title = element_text(lineheight=.8, face="bold", size = 16),
               axis.text = element_text (size = 16, color = 'black'),
+#              axis.text.x = element_text(angle = 45, vjust = 0.5),   # x-axis's label font
               axis.title = element_text (size = 16),
-              axis.title.y = element_text(margin=margin(0,16,0,0)),  # increase the space between title and y axis
-              axis.title.x = element_text(margin=margin(16,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.title.x = element_text(margin=margin(10,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.title.y = element_text(margin=margin(0,12,0,0)),  # increase the space between title and y axis
               axis.line.x = element_line(color='black', size = 1),   # increase the size of font
               axis.line.y = element_line(color='black', size = 1))   # increase the size of font
+
+#raincloud_theme <-  theme_bw() + 
+#      theme(panel.grid.major = element_blank(),
+#            panel.grid.minor = element_blank(),
+#            panel.background = element_blank(),
+#            panel.border = element_blank(),
+#            text=element_text(family='Times'), # text = element_text(size = 10),
+#      axis.title.x = element_text(size = 16),
+#      axis.title.y = element_text(size = 16),
+#      axis.text = element_text(size = 14),
+#      axis.text.x = element_text(angle = 45, vjust = 0.5),
+#      legend.title=element_text(size=16,colour = 'black'),
+#      legend.text=element_text(size=16,colour = 'black'),
+#      legend.position = "right",
+#      plot.title = element_text(lineheight=.8, face="bold", size = 16,colour = 'black'),
+#      axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
[…]

### 2018-10-03 Results/preproc/Initial.r

@@ -5,8 +5,8 @@ Sys.setlocale("LC_ALL", "English")  # set local encoding to English
 Sys.setenv(LANG = "en") # set the feedback language to English
 options(scipen = 999)   # force R to output in decimal instead of scientifc notion
 options(digits=5)       # limit the number of reporting
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
+#rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+rm(list = ls())
 pkgTest <- function(x)
 {
         if (!require(x,character.only = TRUE))
@@ -38,14 +38,32 @@ apatheme = theme_bw()+
               text=element_text(family='Times'),
               legend.title=element_blank(),
               legend.text = element_text(size =16),
-              legend.position='top',
-              plot.title = element_text(size = 16),
+              #legend.position='top',
+              plot.title = element_text(lineheight=.8, face="bold", size = 16),
               axis.text = element_text (size = 16, color = 'black'),
+#              axis.text.x = element_text(angle = 45, vjust = 0.5),   # x-axis's label font
               axis.title = element_text (size = 16),
-              axis.title.y = element_text(margin=margin(0,16,0,0)),  # increase the space between title and y axis
-              axis.title.x = element_text(margin=margin(16,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.title.x = element_text(margin=margin(10,0,0,0)),  # increase the sapce betwen title and x axis
+              axis.title.y = element_text(margin=margin(0,12,0,0)),  # increase the space between title and y axis
               axis.line.x = element_line(color='black', size = 1),   # increase the size of font
               axis.line.y = element_line(color='black', size = 1))   # increase the size of font
+
+#raincloud_theme <-  theme_bw() + 
+#      theme(panel.grid.major = element_blank(),
+#            panel.grid.minor = element_blank(),
+#            panel.background = element_blank(),
+#            panel.border = element_blank(),
+#            text=element_text(family='Times'), # text = element_text(size = 10),
[…]

### 2018-10-04 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
update plots of replciation study

@@
 write.csv(df.C.hddm_id,'MS_rep_categ_id_hddm.csv',row.names = F)
-rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
+rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id','df.M.ddm.v','df.C.ddm.v')
 setwd(curDir)
@@
 #MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
-Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)
+Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7_rep', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)
 
@@
 ```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
-CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)
-CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7_rep', task = 'id', df.C1.V.sum_rt_acc_l)
+CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7_rep', task = 'val', df.C1.V.sum_rt_acc_l)
 ```

### 2018-10-04 Replication/Results/dataAnalysis/preproc/Initial.r

@@ -5,8 +5,8 @@ Sys.setlocale("LC_ALL", "English")  # set local encoding to English
 Sys.setenv(LANG = "en") # set the feedback language to English
 options(scipen = 999)   # force R to output in decimal instead of scientifc notion
 options(digits=5)       # limit the number of reporting
-rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
-
+#rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions
+rm(list = ls())
 pkgTest <- function(x)
 {
         if (!require(x,character.only = TRUE))
@@ -257,19 +257,19 @@ CAplots <- function(saveDir = traDir, curDir = curDir,expName = 'exp7', task = '
           } else if (task == 'id'){   # id-based categorization
             ACCdata <- inData %>%
                   select(Subject,Task,Morality,Identity,ACC) %>% 
-                  filter(Task == "id")
+                  filter(Task == "Id")
             rtData <- inData %>%
                   select(Subject,Task,Morality,Identity,RT) %>% 
-                  filter(Task == "id")
+                  filter(Task == "Id")
           }else{                         #  combined for experiment 1
-            ACCData <- inData %>%
+            ACCdata <- inData %>%
                   select(Subject,Morality,Identity,ACC)
             rtData <- inData %>%
                   select(Subject,Morality,Identity,RT)
             
       }
 
-    P.acc <- ggplot(ACCData,aes(x = Morality, 
+    P.acc <- ggplot(ACCdata,aes(x = Morality, 
                                 y = ACC, fill = Identity))+
           geom_flat_violin(aes(fill = Identity),position = position_nudge(x = 0.1, y = 0),
                            adjust = 1.5, trim = FALSE, alpha = 0.5,color = NA) +
@@ -303,7 +303,7 @@ CAplots <- function(saveDir = traDir, curDir = curDir,expName = 'exp7', task = '
           scale_fill_brewer(palette = "Dark2")+
           ylab("Reaction Times")+
           #scale_x_discrete(breaks = c(1,2),labels = c("Good","Bad")) +
-          scale_y_continuous(expand = c(0, 0),limits = c(400,1000))+
+          scale_y_continuous(expand = c(0, 0),limits = c(200,1000))+
           apatheme
     
     fileName = paste0('p_',expName,'_',task,'_RT','.pdf')
[…]

### 2018-10-05 Replication/Results/dataAnalysis/hddmMod/HDDM_MS_rep_id_linux_final.py
update HDDM results: plotting v and t

@@ -52,7 +52,7 @@ C_Id_vtz.find_starting_values()
 C_Id_vtz.sample(10000,burn = 1000, dbname='traces_id_vtz.db', db='pickle')
 # save the model
 C_Id_vtz.save('C_Id_vtz')
-# C_Id_vtz = hddm.load('C_Id_vtz')
+#C_Id_vtz = hddm.load('C_Id_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()
@@ -131,37 +131,37 @@ stats_C_id = C_Id_vtz.gen_stats()
 stats_C_id.to_csv('C_Id_vtz_20170125.csv', sep = ',')
 
 #  look at the posterior of each parameters for different conditions
-v_GoodSelf,v_BadSelf, v_GoodOther, v_BadOther = C_Id_vtz.nodes_db.node[['v(Self.Good)','v(Self.Bad)','v(Other.Good)','v(Other.Bad)']]
-hddm.analyze.plot_posterior_nodes([v_GoodSelf,v_BadSelf, v_GoodOther, v_BadOther])
+v_GoodSelf_id,v_BadSelf_id, v_GoodOther_id, v_BadOther_id = C_Id_vtz.nodes_db.node[['v(Self.Good)','v(Self.Bad)','v(Other.Good)','v(Other.Bad)']]
+hddm.analyze.plot_posterior_nodes([v_GoodSelf_id,v_BadSelf_id, v_GoodOther_id, v_BadOther_id])
 plt.savefig('exp7_rep_C_Id_vtz_fig_v.pdf')
 
-z_GoodSelf,z_BadSelf, z_GoodOther, z_BadOther = C_Id_vtz.nodes_db.node[['z(Self.Good)','z(Self.Bad)','z(Other.Good)','z(Other.Bad)']]
-hddm.analyze.plot_posterior_nodes([z_GoodSelf,z_BadSelf, z_GoodOther, z_BadOther])
+z_GoodSelf_id,z_BadSelf_id, z_GoodOther_id, z_BadOther_id = C_Id_vtz.nodes_db.node[['z(Self.Good)','z(Self.Bad)','z(Other.Good)','z(Other.Bad)']]
+hddm.analyze.plot_posterior_nodes([z_GoodSelf_id,z_BadSelf_id, z_GoodOther_id, z_BadOther_id])
 plt.savefig('exp7_rep_C_Id_vtz_fig_z.pdf')
 
[…]

### 2018-10-05 Replication/Results/dataAnalysis/hddmMod/HDDM_MS_rep_match_linux_final.py

@@ -56,7 +56,7 @@ M_match_vtz.find_starting_values()
 M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
 # save the model
 M_match_vtz.save('exp7_rep_match_vtz')
-M_match_vtz = hddm.load('exp7_rep_match_vtz')
+#M_match_vtz = hddm.load('exp7_rep_match_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()

### 2018-10-05 Replication/Results/dataAnalysis/hddmMod/HDDM_MS_rep_val_linux_final.py

@@ -56,7 +56,7 @@ C_val_vtz.sample(10000,burn = 1000, dbname='traces_val_vtz.db', db='pickle')
    
 # save the model
 C_val_vtz.save('C_val_vtz')
-# C_val_vtz = hddm.load('C_val_vtz')
+#C_val_vtz = hddm.load('C_val_vtz')
 
 # doing Gelman-Rubin statistic
 models_categ_val = []

### 2018-10-05 Results/HDDM/Exp_MS_HDDM_categ_linux.py

@@ -15,7 +15,15 @@ This experiment included two tasks: matching judgment and categorization.
 This script used for HDDM analysis of categorization task.
 """
 
-import os
+import os, hddm, time, csv
+
+# get the tool box
+import pandas as pd
+import matplotlib.pyplot as plt
+# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
+
+from cycler import cycler
+plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
 
 # get the current directory and change the cd
 os.getcwd()
@@ -23,22 +31,12 @@ os.getcwd()
 # change the current directory to the working directory
 os.chdir("/home/brain/host/hddm_exp7/")
 
-# get the tool box
-import pandas as pd
-import matplotlib.pyplot as plt
-# plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
-
-from cycler import cycler
-plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
-
 # load data from cateogriztion based on moral valence
-dat_M_Categ_val = hddm.load_csv('data_Categ_hddm_val_task.csv')
+dat_M_Categ_val = hddm.load_csv('MS_categ_val_hddm.csv')
 dat_M_Categ_val.head(10)
 
 # load data from cateogriztion based on identity
-dat_M_Categ_id = hddm.load_csv('data_Categ_hddm_ID_task.csv')
+dat_M_Categ_id = hddm.load_csv('MS_categ_id_hddm.csv')
 dat_M_Categ_id.head(10)
 
 # flip the error RTs to be negative
@@ -50,30 +48,29 @@ fig = plt.figure()
 ax = fig.add_subplot(111, xlabel='RT', ylabel='count', title='RT distributions')
 for i, subj_data in dat_M_Categ_val.groupby('subj_idx'):
     subj_data.rt.hist(bins=20, histtype='step', ax=ax)
-plt.savefig('plot_exp7_Categ_val_flipped.pdf')
+plt.savefig('plot_MS_Categ_val_flipped.pdf')
     
 fig = plt.figure()
[…]

### 2018-10-05 Results/HDDM/Exp_MS_HDDM_match_linux.py

@@ -25,14 +25,13 @@ os.chdir("/home/brain/host/hddm_exp7/")
 import pandas as pd
 import matplotlib.pyplot as plt
 # plt.rcParams['image.cmap'] = 'viridis'  # change default colormap
-import hddm
-import time
+import hddm, time, csv
 
 from cycler import cycler
 plt.rcParams['axes.prop_cycle'] = cycler(color='bgrcmyk')
 
 # Load match data from csv file into a NumPy structured array
-dat_M_match = hddm.load_csv('data_M_match_hddm.csv')
+dat_M_match = hddm.load_csv('MS_match_hddm.csv')
 dat_M_match.head(10)
 
 # flip the error RTs to be negative
@@ -45,18 +44,19 @@ for i, subj_data in dat_M_match.groupby('subj_idx'):
     subj_data.rt.hist(bins=20, histtype='step', ax=ax)
 plt.savefig('hddm_exp7_L_match2_fig_1.pdf')
 
+start_time = time.time() # the start time of the processing
 #### model 1, free v, t,z
-M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'t':['moral','id']}, include=['v', 'z', 't'],p_outlier=.05)
+M_match_vtz = hddm.HDDM(dat_M_match,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
 M_match_vtz.find_starting_values()
 M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
 # save the model
 M_match_vtz.save('M_match_vtz')
-#M_match_vtz = hddm.load('M_match_vtz')
+M_match_vtz = hddm.load('M_match_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()
 for i in range(5):
-    m = hddm.HDDM(dat_M_match,depends_on = {'v':['moral','id'],'z':['moral','id'],'t':['moral','id']}, include=['v', 'z', 't'],p_outlier=.05)
+    m = hddm.HDDM(dat_M_match,depends_on = {'v':['val','id'],'z':['val','id'],'t':['val','id']}, include=['v', 'z', 't'],p_outlier=.05)
[…]

### 2018-10-06 Replication/Results/dataAnalysis/hddmMod/HDDM_MS_rep_id_linux_final.py
update plot of DDM

@@ -52,7 +52,7 @@ C_Id_vtz.find_starting_values()
 C_Id_vtz.sample(10000,burn = 1000, dbname='traces_id_vtz.db', db='pickle')
 # save the model
 C_Id_vtz.save('C_Id_vtz')
-#C_Id_vtz = hddm.load('C_Id_vtz')
+C_Id_vtz = hddm.load('C_Id_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()
@@ -151,9 +151,9 @@ print("P(v_GoodOther_id > v_BadOther_id) = ", (v_GoodOther_id.trace() > v_BadOth
 print("P(v_GoodOther_id > v_BadSelf_id) = ", (v_GoodOther_id.trace() > v_BadSelf_id.trace()).mean())        # .488
 print("P(v_BadOther_id > v_BadSelf_id) = ", (v_BadOther_id.trace() > v_BadSelf_id.trace()).mean())       # .819
 
-print("P(z_GoodSelf > v_BadSelf) = ", (z_GoodSelf_id.trace() > z_BadSelf_id.trace()).mean())        # 
-print("P(z_GoodSelf > z_GoodOther) = ", (z_GoodSelf_id.trace() > z_GoodOther_id.trace()).mean())    # 
-print("P(z_GoodSelf > z_BadOther) = ", (z_GoodSelf_id.trace() > z_BadOther_id.trace()).mean())      # 
+print("P(z_BadSelf > z_GoodSelf) = ", ( z_BadSelf_id.trace() > z_GoodSelf_id.trace() ).mean())          # 0.984
+print("P(z_BadSelf > z_GoodOther) = ", (z_BadSelf_id.trace() > z_GoodOther_id.trace()).mean())          # 0.998 
+print("P(z_BadSelf > z_BadOther) = ", (z_BadSelf_id.trace() > z_BadOther_id.trace()).mean())            # 0.987
 print("P(z_GoodOther > z_BadOther) = ", (z_GoodOther_id.trace() > z_BadOther_id.trace()).mean())    # 
 print("P(v_BadSelf > z_GoodOther) = ", (z_BadSelf_id.trace() > z_GoodOther_id.trace()).mean())      # 
 print("P(v_BadSelf > z_BadOther) = ", (z_BadSelf_id.trace() > z_BadOther_id.trace()).mean())        # 

### 2018-10-06 Replication/Results/dataAnalysis/hddmMod/HDDM_MS_rep_val_linux_final.py

@@ -144,15 +144,15 @@ print("--- %s seconds ---" % (end_time - start_time)) #56149.486803770065 second
 #  look at the posterior of each parameters for different conditions
 v_GoodSelf_val,v_BadSelf_val, v_GoodOther_val, v_BadOther_val = C_val_vtz.nodes_db.node[['v(Self.Good)','v(Self.Bad)','v(Other.Good)','v(Other.Bad)']]
 hddm.analyze.plot_posterior_nodes([v_GoodSelf_val,v_BadSelf_val, v_GoodOther_val, v_BadOther_val])
-plt.savefig('exp7_rep_C_vzt_val_v.pdf')
+plt.savefig('exp7_rep_C_vzt_val_fig_v.pdf')
 
 z_GoodSelf_val,z_BadSelf_val, z_GoodOther_val, z_BadOther_val = C_val_vtz.nodes_db.node[['z(Self.Good)','z(Self.Bad)','z(Other.Good)','z(Other.Bad)']] 
 hddm.analyze.plot_posterior_nodes([z_GoodSelf_val,z_BadSelf_val, z_GoodOther_val, z_BadOther_val]) 
-plt.savefig('exp7_rep_C_val_z.pdf') 
+plt.savefig('exp7_rep_C_val_fig_z.pdf') 
 
 t_GoodSelf_val,t_BadSelf_val, t_GoodOther_val, t_BadOther_val= C_val_vtz.nodes_db.node[['t(Self.Good)','t(Self.Bad)','t(Other.Good)','t(Other.Bad)']] 
 hddm.analyze.plot_posterior_nodes([t_GoodSelf_val,t_BadSelf_val, t_GoodOther_val, t_BadOther_val]) 
-plt.savefig('exp7_rep_C_val_t.pdf') 
+plt.savefig('exp7_rep_C_val_fig_t.pdf') 
 
 # print the comparision
 print("P(v_M_GoodSelf > v_M_BadSelf ) = ", (v_GoodSelf_val.trace() > v_BadSelf_val.trace()).mean())       # 0.997

### 2018-10-06 Results/HDDM/Exp_MS_HDDM_match_linux.py

@@ -51,7 +51,7 @@ M_match_vtz.find_starting_values()
 M_match_vtz.sample(10000,burn = 1000, dbname='traces_m_vtz.db', db='pickle')
 # save the model
 M_match_vtz.save('M_match_vtz')
-M_match_vtz = hddm.load('M_match_vtz')
+#M_match_vtz = hddm.load('M_match_vtz')
 
 # check convergence of MCMC  #### out put of gelman_rubin ######
 models_vtz = list()
@@ -129,15 +129,15 @@ stats_match_vtz.to_csv('stats_match_vtz.csv', sep = ',')
 #  look at the posterior of each parameters for different conditions
 v_GoodSelf,v_BadSelf, v_GoodOther, v_BadOther = M_match_vtz.nodes_db.node[['v(Self.Good)','v(Self.Bad)','v(Other.Good)','v(Other.Bad)']]
 hddm.analyze.plot_posterior_nodes([v_GoodSelf,v_BadSelf, v_GoodOther, v_BadOther])
-plt.savefig('MS_match_vtz_fig_v.pdf')
+plt.savefig('exp7_M_match_vtz_v.pdf')
 
 z_GoodSelf,z_BadSelf, z_GoodOther, z_BadOther = M_match_vtz.nodes_db.node[['z(Self.Good)','z(Self.Bad)','z(Other.Good)','z(Other.Bad)']]
 hddm.analyze.plot_posterior_nodes([z_GoodSelf,z_BadSelf, z_GoodOther, z_BadOther])
-plt.savefig('MS_match_vtz_fig_z.pdf')
+plt.savefig('exp7_M_match_vtz_z.pdf')
 
 t_GoodSelf,t_BadSelf, t_GoodOther, t_BadOther = M_match_vtz.nodes_db.node[['t(Self.Good)','t(Self.Bad)','t(Other.Good)','t(Other.Bad)']]
 hddm.analyze.plot_posterior_nodes([t_GoodSelf,t_BadSelf, t_GoodOther, t_BadOther])
-plt.savefig('MS_match_vtz_fig_t.pdf')
+plt.savefig('exp7_M_match_vtz_t.pdf')
 
 # compare the posterior differences for each condition
 print("P(v_GoodSelf > v_BadSelf) = ", (v_GoodSelf.trace() > v_BadSelf.trace()).mean())         # 0.9998
[…]

### 2018-12-02 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
plot cross-task correlation

@@
 setwd(curDir)
+
+# plot four scatter point.
+# p1: goodself-goodother (d in matching and acc in id-based)
+cor_p1 <- ggplot(df.v.sum_eff_all_w, aes(d_goodslf_goodoth, Id_ACC_goodslf_goodoth))+ 
+          geom_point() + 
+          labs(x = "Matching task (d prime)", y = "Identity-base Categorization task (accuracy)") +
+          geom_smooth(method="lm")
+
+# p2: goodself-goodother (RT in matching and RT in id-based)
+# p3: badself-badother (d in matching and acc in id-based)
+# p4: badself-badother (RT in matching and RT in id-based)
+
 ```

### 2018-12-02 Results/plot_cross_task_effect.r

@@ -1,0 +1,120 @@
+rm(list = ls())
+Sys.setlocale("LC_ALL", "English")  # set local encoding to English
+Sys.setenv(LANG = "en") # set the feedback language to English
+options(scipen = 999)   # force R to output in decimal instead of scientifc notion
+options(digits=5)       # limit the number of reporting
+
+# get the working directory of the script
+curDir <- dirname(rstudioapi::getSourceEditorContext()$path) #Get the directory ofcurrent script
+setwd(curDir)
+
+library(ggplot2)
+library(bootES)
+
+# APA format-related code for plots
+windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
+apatheme = theme_bw()+
+      theme(panel.grid.major = element_blank(),
+            panel.grid.minor = element_blank(),
+            panel.background = element_blank(),
+            panel.border = element_blank(),
+            text=element_text(family='Times'),
+            legend.title=element_blank(),
+            legend.text = element_text(size =16),
+            #legend.position='top',
+            plot.title = element_text(lineheight=.8, face="bold", size = 16,hjust = 0.5),
+            axis.text = element_text (size = 16, color = 'black'),
+            #              axis.text.x = element_text(angle = 45, vjust = 0.5),   # x-axis's label font
+            axis.title = element_text (size = 18),
+            axis.title.x = element_text(margin=margin(10,0,0,0)),  # increase the sapce betwen title and x axis
+            axis.title.y = element_text(margin=margin(0,10,0,0)),  # increase the space between title and y axis
+            axis.line.x = element_line(color='black', size = 1),   # increase the size of font
+            axis.line.y = element_line(color='black', size = 1))   # increase the size of font
+
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+      library(grid)
+      
+      # Make a list from the ... arguments and plotlist
+      plots <- c(list(...), plotlist)
+      
+      numPlots = length(plots)
+      
+      # If layout is NULL, then use 'cols' to determine layout
+      if (is.null(layout)) {
+            # Make the panel
+            # ncol: Number of columns of plots
[…]

### 2019-01-03 Results/preproc/MS_ddm_preproc.rmd
Check the results, and start using tidyverse for preprocessing

@@
 
-This script is aimed at making the analysis of the moral self experiment (DDM) reproducible. We analyzezd the data using the traditional ways (d prime/Accuracy and mean of RT)
+This script is used to preprocessing the data of the moral self experiment (DDM), experiment 1.
+
+Input: 
+  MS_matchTask_raw.csv -- raw data of matching task;
+  MS_categTask_raw.csv -- raw data of categorization task;
+
+Output:
+  df.M.hddm_m.csv  -- clean data of matching trials from matchign task, for HDDM analysis;
+  df.M.hddm_nm.csv -- clean data of nonmatching trials from matchign task, for HDDM analysis;
+  df.C.hddm_val    -- clean data of valence-based categorization trials, for HDDM analysis;
+  df.C.hddm_id     -- clean data of identity-based categorization trials, for HDDM analysis;
+
+  MS_categ_behav_wide.csv -- cleaned summary results (wide-format) of categorization task for statistical analysis in JASP
+  MS_categ_behav_noTask_wide.csv -- cleaned summary results (wide-format) of categorization task (collapsed data from different task) for statistical analysis in JASP
+  MS_categ__rt_acc_long.csv -- cleaned summary results of RT and accuracy (long-format) of categorization task, for JASP analysis
+  MS_categ__rt_acc_noTask_long.csv -- cleaned summary reuslt of RT and accuracy (long-format) of categorization task (collapsed data from different task) for JASP analysis
+  MS_cross_taskeffect_wide.csv-- cleaned summary results for cross task analysis
 
@@
 source('Initial.r')
-curDir  <- getwd()
+curDir  <- getwd() # get the current working directory
 #curDir  <- dirname(rstudioapi::getSourceEditorContext()$path)   # directory for preprocessing
-rootDir <- gsub('.{7}$', '', curDir)
+
+rootDir <- gsub('.{7}$', '', curDir)                      # get the parental folder
 #rawDir <- paste(curDir,'/data/',sep = '')
-traDir <- paste(rootDir,'Traditional_Analysis',sep = '')
-ddmDir <- paste(rootDir,'HDDM',sep = '')
-exgDir <- paste(rootDir,'exGaussian',sep = '')
+traDir <- paste(rootDir,'Traditional_Analysis',sep = '')  # folder for traditional analsysi
+ddmDir <- paste(rootDir,'HDDM',sep = '')                  # folder for DDM analysis
+exgDir <- paste(rootDir,'exGaussian',sep = '')            # folder for ExGaussian analysis
 ```
@@
 
-# make the variables in a specified order
 df.C$Morality <- factor(df.C$Morality, levels=c("Good","Bad"))    
@@
 df.M <- df.M.fm  # all the experimental trials
-rm(subNo,df.M.fm,df.tmp)
+rm(subNo,df.M.fm,df.tmp) # remove the intermedia variables
 
 # exlude subject criterion 2: less than 50% overall accuracy
-# change no response to error
+# re-code trials without response as incorrect
 df.M.tmp <- df.M
@@
 df.C.valid <- df.C[!(df.C$Subject %in% excldSub2.M),]
-df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),]
+df.C.valid <- df.C.valid[!(df.C.valid$Subject %in% excldSub2.C),] # one participants were excluded for categorization task
 rm(df.M,df.C,df.M.tmp,df.C.tmp)
@@
 
-# excld.trials, criterion 2: correct response within 200 ms
+# excld.trials, criterion 3: correct response within 200 ms
 excld.trials.M <- df.M1[df.M1$RT <= 200,]
@@
 ## Basic information of the data ####
-df.M1.T.basic <- df.M1[!duplicated(df.M1$Subject), 1:4]
-numT.subj <- nrow(df.M1.T.basic)
-numT.female <- sum(df.M1.T.basic$Gender == 'female');
-numT.male <- sum(df.M1.T.basic$Gender == 'male');
-ageT.mean <- round(mean(df.M1.T.basic$Age),2);
-ageT.std <- round(sd(df.M1.T.basic$Age),2);
+df.M1.T.basic.info <- df.M1 %>%
+  dplyr::select(Subject, Age, Gender) %>%
+  dplyr::distinct(Subject, Age, Gender) %>%
+  dplyr::summarise(N = length(Subject),
+                   N.f = sum(Gender == 'female'),
+                   N.m = sum(Gender == 'male'),
+                   MeanAge = round(mean(Age),2),
+                   SDAge   = round(sd(Age),2))
+#numT.subj <- nrow(df.M1.T.basic)
+#numT.female <- sum(df.M1.T.basic$Gender == 'female');
+#numT.male <- sum(df.M1.T.basic$Gender == 'male');
+#ageT.mean <- round(mean(df.M1.T.basic$Age),2);
+#ageT.std <- round(sd(df.M1.T.basic$Age),2);
 num.excldSub2.M <- length(unique(excldSub2.M))
@@
 
-# valide data for matching task
-df.M1.V.basic <- df.M1.V[!duplicated(df.M1.V$Subject), 1:4]
-numV.female <- sum(df.M1.V.basic$Gender == 'female');
-numV.male <- sum(df.M1.V.basic$Gender == 'male');
-ageV.mean <- round(mean(df.M1.V.basic$Age),2);
-ageV.std <- round(sd(df.M1.V.basic$Age),2);
+# valid data for matching task
+df.M1.V.basic.info <- df.M1.V %>%
+  dplyr::select(Subject, Age, Gender) %>%
+  dplyr::distinct(Subject, Age, Gender) %>%
+  dplyr::summarise(N = length(Subject),
+                   N.f = sum(Gender == 'female'),
+                   N.m = sum(Gender == 'male'),
+                   MeanAge = round(mean(Age),2),
+                   SDAge   = round(sd(Age),2))
+
 ratio.excld.trials.M <- nrow(excld.trials.M)/nrow(df.M1)
@@
 # valid data for categorization task
-df.C1.V.basic <- df.C1.V[!duplicated(df.C1.V$Subject), 1:4]
-numV.female.C <- sum(df.C1.V.basic$Gender == 'female');
-numV.male.C <- sum(df.C1.V.basic$Gender == 'male');
-ageV.mean.C <- round(mean(df.C1.V.basic$Age),2);
-ageV.std.C <- round(sd(df.C1.V.basic$Age),2);
+df.C1.V.basic.info <- df.C1.V %>%
+  dplyr::select(Subject, Age, Gender) %>%
+  dplyr::distinct(Subject, Age, Gender) %>%
+  dplyr::summarise(N = length(Subject),
+                   N.f = sum(Gender == 'female'),
+                   N.m = sum(Gender == 'male'),
+                   MeanAge = round(mean(Age),2),
+                   SDAge   = round(sd(Age),2))
+
 ratio.excld.trials.C <- nrow(excld.trials.C)/nrow(df.C1)
 
-rm(df.M1,df.C1) # remove the no longer used varibles.
-
-# get the data file for hddm analysis ####
-df.M.ddm.v <- df.M.valid   # exclude the invalid subjects
-df.C.ddm.v <- df.C.valid
-
+###########################################################
+########   get the data file for hddm analysis      #######
+###########################################################
 # exclusion trials, criterion: trials without response or wrong key
 # Note: we didn't remove the correct response less than 200 ms
-df.M.hddm <- subset(df.M.ddm.v, ACC ==1 | ACC == 0)  
-df.C.hddm <- subset(df.C.ddm.v, ACC ==1 | ACC == 0)
 
-df.M.hddm_m <- subset(df.M.hddm, Match == 'match') # select data
-df.M.hddm_m <- df.M.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
-colnames(df.M.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name
+df.M.hddm_m <- df.M.valid %>%                          # start from the valid data, RT in seconds.
+  dplyr::filter(ACC == 1 | ACC == 0) %>%               # exclude trials without response or with wrong keys
+  dplyr::filter(Match == 'match') %>%
+  dplyr::select(Subject,Morality,Identity,RT,ACC) %>%  # select column
+  dplyr::rename(subj_idx = Subject, val = Morality, id = Identity, rt = RT, response = ACC) # rename column
 
-df.M.hddm_nm <- subset(df.M.hddm, Match == 'nonmatch')
-df.M.hddm_nm <- df.M.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.M.hddm_nm) <- c("subj_idx","val",'id','rt','response')
+df.M.hddm_nm <- df.M.valid %>%
+  dplyr::filter(ACC == 1 | ACC == 0) %>%               # exclude trials without response or with wrong keys
+  dplyr::filter(Match == 'nonmatch') %>%
+  dplyr::select(Subject,Morality,Identity,RT,ACC) %>%  # select column
+  dplyr::rename(subj_idx = Subject, val = Morality, id = Identity, rt = RT, response = ACC) # rename column
 
-df.C.hddm_val <- subset(df.C.hddm, Task == 'Val')
-df.C.hddm_val <- df.C.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.C.hddm_val) <- c("subj_idx","val",'id','rt','response')
+df.C.hddm_val <- df.C.valid %>%
+  dplyr::filter(ACC == 1 | ACC == 0) %>%               # exclude trials without response or with wrong keys
+  dplyr::filter(Task == 'Val') %>%                     # select the valence-based task
+  dplyr::select(Subject,Morality,Identity,RT,ACC) %>%  # select column
+  dplyr::rename(subj_idx = Subject, val = Morality, id = Identity, rt = RT, response = ACC) # rename column
 
-df.C.hddm_id <- subset(df.C.hddm, Task == 'Id')
-df.C.hddm_id <- df.C.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
-colnames(df.C.hddm_id) <- c("subj_idx","val",'id','rt','response')
+df.C.hddm_id <- df.C.valid %>%
+  dplyr::filter(ACC == 1 | ACC == 0) %>%               # exclude trials without response or with wrong keys
+  dplyr::filter(Task == 'Id') %>%                      # select the valence-based task
+  dplyr::select(Subject,Morality,Identity,RT,ACC) %>%  # select column
+  dplyr::rename(subj_idx = Subject, val = Morality, id = Identity, rt = RT, response = ACC) # rename column
 
@@
 setwd(curDir)
-rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
+rm('df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
 
-# get the data for exGaussian analysis
-df.C.exG <- df.C.valid
-df.C.exG <- subset(df.C.exG, ACC == 1 & RT > .2)
+###########################################################
+######## get the data file for exGaussian analysis  #######
+###########################################################
+df.C.exG <- df.C.valid %>%
+  dplyr::filter(ACC == 1 & RT > .2)    # only for correct and valid trials
+
 setwd(exgDir)

### 2019-01-04 Results/preproc/MS_DD_preproc_exp1.r
from Rmarkdonw to r

@@ -1,90 +1,69 @@
----
-title: "Data_Analysis_MS_ddm_exp1"
-author: "hcp"
-date: "2017-12"
-output: word_document
----
-<style type="text/css">
+### This script is used to preprocessing the data of the moral self experiment (DDM), experiment 1. 
+#
+### Hu, C-P., Lan, Y., Macrae, N., & Sui. J. (2019) 
+### Script author: Chuan-Peng Hu
+### Email = hcp4715@gmail.com       twitter= @hcp4715
+#
+### Input: 
+###      MS_matchTask_raw.csv -- raw data of matching task;
+###      MS_categTask_raw.csv -- raw data of categorization task;
+#
+### Output:
+###     df.M.hddm_m.csv  -- clean data of matching trials from matchign task, for HDDM analysis;
+###     df.M.hddm_nm.csv -- clean data of nonmatching trials from matchign task, for HDDM analysis;
+###     df.C.hddm_val    -- clean data of valence-based categorization trials, for HDDM analysis;
+###     df.C.hddm_id     -- clean data of identity-based categorization trials, for HDDM analysis;
+# 
+###     MS_categ_behav_wide.csv        -- cleaned summary results (wide-format) of categorization task for 
+###                                             statistical analysis in JASP
+###     MS_categ_behav_noTask_wide.csv -- cleaned summary results (wide-format) of categorization task (collapsed
+###                                             data from different task) for statistical analysis in JASP
+###     MS_categ__rt_acc_long.csv      -- cleaned summary results of RT and accuracy (long-format) of 
+###                                             categorization task, for JASP analysis
+###     MS_categ__rt_acc_noTask_long.csv -- cleaned summary reuslt of RT and accuracy (long-format) of categorization 
+###                                             task (collapsed data from different task) for JASP analysis
+###     MS_cross_taskeffect_wide.csv    -- cleaned summary results for cross task analysis
 
-body{ /* Normal  */
-   font-family: Times     
-   font-size: 12px;
-}
-td {  /* Table  */
-   font-size: 8px;
-}
-h1 { /* Header 1 */
- font-size: 28px;
-}
-h2 { /* Header 2 */
- font-size: 22px;
-}
-h3 { /* Header 3 */
- font-size: 18px;
[…]
